### 2022-05-24 Writing/manuscript_gwr.rmd
corrected directory names and made the knitting work

---
title: "Economic Evaluation of Geographically Weighted Regression Analysis for Site-specific Nitrogen Management"
author:
  - Taro Mieno^[University of Nebraska Lincoln, tmieno2@unl.edu], Xiaofei Li^[Mississippi State University, xiaofei.li@msstate.edu], David S. Bullock^[University of Illinois, dsbulloc@illinois.edu]
output:
  officedown::rdocx_document:
    toc: false
    toc_depth: 1
    number_sections: true
    reference_docx: "word_template.docx"
    plots:
      style: Normal
      align: center
      caption:
       style: Image Caption
       pre: "Figure "
       sep: ": "
    tables:
      style: Table
      layout: autofit
      width: 1.0
      caption:
       style: Table Caption
       pre: "Table "
       sep: ": "
bibliography: PA.bib
csl: field-crops-research.csl
abstract: ""
---

```{r echo = F, cache = F}
suppressMessages(library(knitr))
suppressMessages(library(here))
suppressMessages(library(officedown))
suppressMessages(library(officer))

opts_chunk$set(
  fig.align = "center",
  fig.retina = 5,
  warning = F,
  message = F,
  cache = F,
  echo = F,
  fig.cap = TRUE
)
```

```{r cache = F}
#--- packages ---#
library(data.table)
library(tidyverse)
library(flextable)
library(stringr)
library(sf)
library(lfe)
library(modelsummary)
library(patchwork)
```

```{r figure_setup, cache = F}
theme_update(
  axis.title.x =
    element_text(
      size = 12, angle = 0, hjust = .5, vjust = -0.3, face = "plain"
    ),
  axis.title.y =
    element_text(
      size = 12, angle = 90, hjust = .5, vjust = .9, face = "plain"
    ),
  axis.text.x =
    element_text(
      size = 10, angle = 0, hjust = .5, vjust = 1.5, face = "plain"
    ),
  axis.text.y =
    element_text(
      size = 10, angle = 0, hjust = 1, vjust = 0, face = "plain"
    ),
  axis.ticks =
    element_line(
      size = 0.3, linetype = "solid"
    ),
  axis.ticks.length = unit(.15, "cm"),
  #--- legend ---#
  legend.text =
    element_text(
      size = 10, angle = 0, hjust = 0, vjust = 0, face = "plain"
    ),
  legend.title =
    element_text(
      size = 10, angle = 0, hjust = 0, vjust = 0, face = "plain"
    ),
  legend.key.size = unit(0.5, "cm"),
  #--- strip (for faceting) ---#
  strip.text = element_text(size = 10),
  #--- plot title ---#
  plot.title = element_text(family = "Times", face = "bold", size = 12),
  #--- margin ---#
  # plot.margin = margin(0, 0, 0, 0, "cm"),
  #--- panel ---#
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background = element_blank(),
  panel.border = element_rect(fill = NA)
)
```

```{r include = FALSE}
# /*===========================================================
#' # Prepare data and results for writing
# /*===========================================================
#* source all the functions in the Functions folder
fs::dir_ls(here("GitControlled", "Codes", "Functions"), full.names = TRUE) %>%
  lapply(., function(x) source(x))

#* read the results rds file
results <-
  here("Shared", "Results", "pi_data.rds") %>%
  readRDS() %>%
  .[, type := ifelse(transfer == 0, "GWR-R", "GWR-T")] %>%
  .[, bias := pi_diff_est - pi_diff]

pi_dif_gwr <-
  results[, .(pi_dif = mean(pi_diff)), by = type] %>%
  .[, diff(pi_dif)]

#* create figures
source(here("GitControlled", "Codes", "3_make_figures_publication.R"))
```

**Abstract**: Geographically-weighted regression (GWR) has been presented as a prominent tool to estimate site-specific yield response functions to generate site-specific input rate recommendations using data generated by on-farm precision experimentation (OFPE). The key objectives of this paper are two-fold. First, it evaluates two sets of functional-form specifications made by two recent published studies of site-specific input management that apply GWR to data from OFPE. We show that one set of functional-form specification performs significantly better than the other. Second, we investigate the possibility of bias when GWR is used to estimate the value of site-specific vs. uniform-rate input management. We show that GWR suffers significant positive bias, which can lead to great over-estimation of the value of applying GWR methods. Our study is the first to systematically examine the statistical and economic properties of the use of GWR in OPFE settings. We reveal that in many circumstances using GWR is far less profitable than claimed by previous studies, which provides a necessary cautionary message to researchers who might otherwise “over-sell” to other researchers the value of using GWR methods in empirical work involving the estimation of site-specific input management.

**Keywords**: on-farm precision experimentation, site-specific input management, geographically-weighted regression, economically optimal nitrogen rate

**Acknowledgement**: This research was supported by a USDA-NIFA-AFRI Food Security Program Coordinated Agricultural Project, titled “Using Precision Technology in On-farm Field Trials to Enable Data-Intensive Fertilizer Management,” (Accession Number 2016-68004-24769), and also by the a USDA-NRCS Conservation Innovation Grant from the On-farm Trials Program, titled “Improving the Economic and Ecological Sustainability of US Crop Production through On-Farm Precision Experimentation” (Award Number NR213A7500013G021).

`r run_pagebreak()`

# Introduction

In recent years, On-farm Precision Experimentation (OFPE) has gained traction with both researchers and practitioners as a means of generating high-resolution spatial data to inform site-specific crop input management decisions [@bullock2019data; @lacoste2021farm]. Accompanying interest is surging among researchers in identifying efficient statistical methods to estimate site-specific yield response functions, which have examined various methods, ranging from Geographically Weighted Regression (GWR) [@rakshit2020; @evans2020assessment; @trevisan2021spatial] to machine learning methods including random forest [@krause2020random] and convolutional neural network [@barbosa2020modeling] approaches. Among these methods applied to OFPE data, GWR is distinct in that it does not require potentially costly collection of site-specific field and soil information in estimating site-specific yield response functions.

On any given field, it is typical for U.S. Midwestern row crop farmers to pay for 1-ha grid soil sampling and chemical analysis every three or four years [@morris2018strengths]. The data is often used to derive fertilizer application recommendations, for example by applying comparatively simple formulas provided by university extension services (e.g., Culman, et al. 2020). But the expense of soil sampling and analysis is driving development of sensor technologies that gather data on site-specific field and crop characteristics or proxies of those characteristics. For example, Trimble Agriculture's GreenSeeker and AgLeader's OptRx® systems use optical sensors mounted on fertilizer application booms to digitally record vegetative index imagery as farm machinery is driven through fields during early crop growth stages. GreenSeeker then basically uses Oklahoma State University's Sensor-based N Rate Calculator to convert those data into recommended nitrogen fertilizer (N) application rate maps ($R_xs$). Veris Technologies manufactures sensor equipment that can be towed through fields to gather apparent electroconductivity (EC) data, which can be used to infer properties of soil content. The "decision tool" software FieldRevealTM allows users to upload EC data, elevation data, and vegetative index data, which FieldRevealTM's professional agronomists analyze to provide $R_x$s to farmers. FieldApex creates N $R_x$s using foliar vegetative index data from satellite imagery, and SlantRange uses drone imagery for similar purposes.

However, deploying sophisticated sensors to gather field characteristics data is also costly, and the effects of their generation and use on farm profitability remains in question [@gardner2021economic]. Recognizing the significant costs of obtaining useful, high-resolution soil and field properties data, @trevisan2021spatial demonstrated a method of providing site specific management recommendations without such data. The study estimated site-specific yield response functions by applying GWR techniques on data from OFPEs [@bullock2019data]. @trevisan2021spatial reported dramatic results, estimating an average potential gain of \$65 ha$^{-1}$ from applying seed and N at optimal uniform rates (instead of at the rates the farmers would have chosen if not participating in the research), and an additional potential gain of \$58 ha$^{-1}$ when changing from optimal uniform application rates to optimal site-specific application rates. @rakshit2020 also applied GWR to on-farm experiment data. However, while they did estimate site-specific yield response functions, they did not derive site-specific economically optimal nitrogen rates based on them, and thus did not conduct economic analysis unlike @trevisan2021spatial. @evans2020assessment explored using GWR with a linear model specification to detect low- and high-response areas, but like @rakshit2020 also did not estimate site-specific economically optimal nitrogen rates.

This study has two key objectives. The first is to determine which of the model specifications used by @rakshit2020 and @trevisan2021spatial result in more profitable $R_xs$. While both @rakshit2020 and @trevisan2021spatial proposed using GWR to estimate site-specific yield response functions, they use different model specifications. Both assume a quadratic response of yield to nitrogen rate ($N$). However, while @trevisan2021spatial estimate the coefficient on $N^2$ as a global parameter, @rakshit2020 estimate it locally for each point. At first, it appears that the specification used by @rakshit2020 is superior since it is more flexible than the specification used by @trevisan2021spatial. However, the flexibility can be a disadvantage rather than an advantage because the estimation of EONR is highly sensitive to the coefficient estimates on $N^2$, and GWR often provides inaccurate local estimation of that coefficient.

Second, we will examine the degree and direction of bias in the estimation of the value of GWR-based variable rate application (VRA) and question the extremely high estimates of that value reported by @trevisan2021spatial. In general, researchers take the following steps to estimate the value of VRA based using OFPE data [e.g., @swinton1998evaluating; @bullock2002adding; @anselin2004spatial; @liu2006site]: (1) estimate site-specific yield response functions based on a method chosen by the researcher; (2) use the estimated yield response functions to estimate the economically optimal site-specific input rates (EOIR) and economically optimal uniform input rates; (3) plug the estimated site-specific EOIRs and uniform EOIR into the estimated yield response functions to calculate estimated profits under both strategies; and (4) find the difference in the two strategies' estimated profits. However, this approach can result in significant bias in the estimation of the value of VRA because of the assumption made on step (3), which is that the estimated yield response functions are the true yield response functions. @trevisan2021spatial provide an example. At step (3), they used their estimated GWR as the true yield response functions. This assumption is generally unavoidable for researchers since they cannot observe any real field's true yield response function of any real field. Use of these procedures assumes accurate estimation of yield response functions, which when untrue can result in significant bias in the estimation of the value of VRA. This bias problem can be particularly severe when the method used tends to exaggerate the true heterogeneity in yield response functions. We suspect that the high value of VRA estimated by @trevisan2021spatial displays this bias.

In the following, we pursue the two objectives just described above by conducting Monte Carlo simulations in which we first generate and then analyze stylized OFPE data. We cannot test which model specification results in more profitable site-specific nitrogen rate recommendations using real data because it is impossible to observe the true yield response functions. For the same reason, we cannot test whether @trevisan2021spatial over-estimates the actual value of VRA, either. But in the Monte Carlo simulations we specify yield response functions and generate stylized data from those functions, which enables us to quantify in the context of the simulations the value of GWR and the bias in GWR-based estimation of the value of VRA. Monte Carlo simulations are commonly used in this way to gain insights into the statistical properties of trial designs and estimations methods [@mckinion2001analysis; @gebbers2010application; @bullock2020value; @alesso2021design].

One of the principal findings of this article is that the model specification used by @trevisan2021spatial creates more valuable information than does the model specification used by @rakshit2020. This is primarily due to GWR's poor local estimation of the coefficients on $N^2$. Since the coefficients on $N^2$ is highly influential in determining site-specific EONR, inaccuracy in its estimation can result in significant economic loss. We also show that even under the method used by @trevisan2021spatial, the benefit of VRA over URA is rather small, averaging only about \$5 ha$^{-1}$; we conclude that both @rakshit2020 and @trevisan2021spatial significantly over-estimated that value. Our results suggest that the prospects of using GWR to generate site-specific input recommendations are bleaker than stated in @trevisan2021spatial.

# Materials and Methods

## Experimental Field Layout

Figure \@ref(fig:field-layout) shows the field layout and defines the spatial units of the simulated on-farm precision experiments in this study. The basic spatial unit of the field is the 6m $\times$ 6m "cell", which is the resolution at which the field characteristics data (i.e., parameters of the "true" yield response function) were allowed to vary. It was assumed, however, that yields could not be monitored at such a high resolution. Rather, the mechanical harvester was assumed to be 18m wide, and, in cases in which the N rate was unchanged, in need of harvesting on a run of no less than 12m to provide accurate yield data. Therefore, the yield data's resolution was 18m $\times$ 12m (3 cells $\times$ 2 cells, called a "subplot"). The N rate unit consisted of five "subplots", that is, 18m $\times$ 72m (3 cells $\times$ 12 cells, called a "plot") to accommodate the variable-rate applicator's application resolution. A 12m "transition zone" was placed between two plots (that is, a 6m "transition zone" on each end of a plot), so that when the experimental N rate changed, the harvester had 12 m to "clear" and begin to record accurately on a plot with an N rate different from its predecessor's.

The field was 432m (72 cells) wide and 864m (144 cells) long, making its area 37.3 ha. Data from the 6-m-wide headlands, side-lands (there are no transition zones on the north and south ends of the field), and 12-m-wide "transition zones" were not included in the data analyzed. In total there were 1440 subplots available for experimental data analysis. The index $j \in {1, 2, \dots, 1440}$ identifies the field's subplots, and the index $k \in {1, \dots , 6}$ identifies the cells within a subplot. The couplet (j, k) is used to identify individual cells.

## True Cell-specific Yield Response Function

An extensive literature examines the choice of functional form in yield response estimation [@cerrato1990comparison, @frank1990comparison, @bullock1994quadratic, @tembo2008crop]. The quadratic, linear-plateau, quadratic-plateau, and Mitscherlich‐Baule are commonly used functional forms. In this study, each cell (j, k)'s "true" yield response function is assumed to follow the quadratic-plateau functional form:

$$
\begin{equation}
y_{j,k} = f_{j, k} (N) = f(N, c_{j,k}) = 
  \begin{cases}
  \alpha_{j,k} + \beta_{j,k} N + \gamma_{j,k} N^2 + \varepsilon_{j,k} \, ,& N < \tau_{j,k} \\
  \alpha_{j,k} + \beta_{j,k} \tau_{j,k} + \gamma_{j,k} \tau_{j,k}^2 + \varepsilon_{j,k} \, ,& N \ge \tau_{j,k}
  \end{cases}
\end{equation}
$$

where $c_{j,k} = (\alpha_{j,k},\beta_{j,k},\gamma_{j,k},\tau_{j,k})$ is the vector of yield response function parameters. $\tau_{j,k}$ can be interpreted as the critical value of N rate at which cell $(j, k)$'s yield reaches the plateau level (i.e., where yield no longer increases with additional N fertilizer). $\varepsilon_{j, k}$ is a stochastic error term. The quadratic-plateau functional form implies a diminishing marginal product of N and a yield plateau, which are desirable properties for a yield response function [@frank1990comparison]. It is a widely observed corn nitrogen response pattern by existing agronomic studies. Note that the cell-specific yield response function $f_{j, k} (N)$ is the reduced form of the meta response function $f$ when the characteristics vector takes on the value $c_{j, k}$. In other words, all the soil or field properties that could affect yield response to N are embedded in the simulated parameters.

The spatial distributions of cell-level parameters $\alpha_{j, k}$, $\beta_{j, k}$, $\gamma_{j,k}$, $\tau_{j, k}$, and the error term $\varepsilon_{j, k}$ were simulated by generating spatially correlated random fields using unconditional Gaussian geostatistical simulation based on the specified variograms [@dietrich1996fast, @wood1994simulation], and the simulation processes were conducted using the R package gstat [@graler16]. Specifically, the model is spherical, the nugget variance is zero, and the range is 600 meters. The nugget value of zero means that infinitesimally close observations have a zero covariance (i.e., they are identical). The range of 600m means that observations separated by more than 600m are not spatially correlated. A higher range value indicates increased spatial dependence, meaning less abrupt differences are observed between the production function parameters of neighboring cells. The mean and sill variance of each parameter were specified to result in a realistic mean yield of $11,416$ kg ha$^{-1}$, and such that the cells' true economically optimal N rate ranged from $113$ kg ha$^{-1}$ to $273$ kg ha$^{-1}$ among all the simulations, which most real-world N rate recommendations fall into (e.g., @sawyer2018). Note that the range of the optimal N rates of individual rounds of simulations are narrower. In defining the magnitude of the error term, we utilized the experimental data generated through eight on-farm randomized N field trials conducted by the DIFM project in 2018 by the Data-Intensive Farm Management Project (DIFM), [@bullock2019data]. Using the data from each of the eight actual trials, separate regressions of yield on N were run, and standard deviations of the residuals were calculated. The mean value of the eight standard deviations was $1370$ kg ha$^{-1}$, which was the value of sill variances assigned to the simulations' error terms.

## Trial Design

Figures \@ref(fig:field-layout) and \@ref(fig:field-N-design) illustrate the Latin square trial design schema assumed in each simulation. The field was partitioned into a 4-block $\times$ 2-block grid, in which each block was partitioned into a 6-plot $\times$ 6-plot grid with each of six N rates assigned to exactly one plot in each row and each column of the block. The design ensured that no adjacent N plots were assigned the same N rate. Furthermore, the order of N rates in each row of every block was specified to avoid relatively large changes in N rates (due the technological limitations of N application equipment commonly witnessed in real-world OFPE).

Letting $p$ represent the crop price and $w$ represent the price of nitrogen fertilizer, in each simulation the "true" economically optimal N rate for each cell $(j, k)$ was calculated as

$$
N^*_{j,k} \equiv argmax_N \Big[p\cdot f_{j,k}(N)-w\cdot N\Big].
$$

In each simulation, six trial N rates were assigned by calculating the 0%, 20%, 40%, 60%, 80%, and 100% quantiles of the simulation's true cell-specific optimal N rates. The means of these trial N rates across simulations were approximately, {80, 130, 154, 184, 219, and 270} kg ha$^{-1}$.

## Yield Data Generation

In each simulation, for each cell $(j, k)$, the simulation's true yield $y_{j, k}$ was generated based on the cell's assigned application rate $N_{j,k}$, true response parameters $c_{j,k} = (\alpha_{j,k}, \beta_{j,k}, \gamma_{j,k}, \tau_{j,k})$, and error term $\varepsilon\_{j,k}$. This procedure generated a field-level, cell-specific data set, $\{(y_{j, k},N_{j, k} ):j=1,\dots,1440;k=1,\dots, 6 \}$. To maintain consistency with real-world OFPEs, it was assumed that harvesting equipment could only record yields accurately at an 18m $\times$ 12m (subplot) resolution. Since every cell in a plot received the same N application rate, then so did every cell within a subplot, so $N_{j,1} = N_{j,2}= \dots = N_{j,6} = N_j$ for each subplot $j$. Letting $\mu_j$ denote the mean of the yields of the cells in subplot $j$, the analysis of each round's data was based on 1440 $(\mu_j,N_j )$ observations.

## Estimation of Yield Response Function and EONR

Three approaches to estimate yield response functions and their associated EONRs were used. The first approach used the shape-constrained additive model (SCAM) to estimate a single yield response function for the entire field, and to estimate and economically optimal uniform nitrogen application rate for the field. The other two approaches both used GWR, but assumed different specifications in modeling the impact of nitrogen on yield. The first GWR approach (GWR-R) followed the specification used by @rakshit2020, and the second GWR approach (GWR-T) followed the specification used by @trevisan2021spatial. Further details of each approach are presented below. SCAM and GWR estimations were performed using $R$'s scam [@scam-R] and GWmodel [@gwmodel-R] packages.

### Spatially Uniform Management after Non-Spatial Regression Analysis of OFPE Data

In the lower benchmark situation, a researcher was assumed to run OFPEs to gather data, then to estimate a single "full-field" yield response function using the SCAM non-parametric regression framework, which is a spline-based series estimation that can impose a shape-constraints on the estimated function [@pya2015shape]. In using SCAM, the yield response function was restricted to be monotonically increasing and concave with respect to the N application rate, which are traits well substantiated by agronomic research. When the chosen shape constraints are correct, SCAM is more statistically efficient than a fully non-parametric regression [@pya2015shape]. The estimated model is represented mathematically as follows,

$$y_j = \alpha + \sum_{l=1}^l \beta_l g_l(N_j)+ \varepsilon_j$$

where $g_l(\cdot)$ is the $l$th spline basis and $\beta_l$ is its coefficient to be estimated. The $\beta_l$s were constrained such that the resulting relationship between $y_j$ and $N_j$ is such that $y_j$ monotonically increases as $N_j$ increases, but at a diminishing rate.

Let $\hat{f}_{scam}(\cdot)$ represent the estimated whole-yield yield response function ($\sum_{k=1}^K \hat{\beta}_k g_k(\cdot)$). Given the information derived from the SCAM approach, the estimate of the economically optimal uniform N rate is,

$$\hat{N}_{scam}^* \equiv argmax_N⁡ \big[p\cdot \hat{f}_{scam} (N)-w\cdot N\big]$$

### GWR-Rakshit (GWR-R)

In the GWR-R approach, yield response was modeled as subplot-specific quadratic functions of the nitrogen rate, which for each subplot $j \in {1, 2, \dots, 1440}$ was specified as,

$$y_j= \alpha_j+ \beta_j N_j + \eta_j N_j^2+ \epsilon_j$$

The GWR-R estimation produced subplot-specific estimates of coefficients $\hat{\alpha}_j$, $\hat{\beta}_j$, and $\hat{\eta}_j$, and so of the yield response function $\hat{f}_{gwr-r,j}(N)$ for $j = 1, 2, \dots, 1440$. The estimated economically optimal N application rate for subplot $j$ was calculated by solving the subplot's profit maximization problem:

$$\hat{N}_{gwr-r,j}^{*} \equiv argmax_N⁡[p\hat{f}_{gwr-r, j} (N) -wN]$$.

### GWR-Trevisan (GWR-T)

In the GWR-T approach, unlike GWR-Rakshit, the coefficient on $N^2$ was estimated as a global parameter while the coefficient on $N$ was estimated subplot-specifically. For each subplot $j \in {1, 2, \dots, 1440}$, the assumed yield response was,

$$y_j= \alpha_j+ \beta N_j + \eta N_j^2+ \epsilon_j$$.

where $\eta$ was assumed invariant among subplots. Because the coefficients on some variables were estimated as global parameters, the model used can be classified as a Mixed GWR model.

Let $\hat{f}_{gwr-t,j}(N)$ for $j = 1, 2, \dots, 1440$ denote the estimated yield response function for subplot $j$. The estimated economically optimal N application rate for subplot $j$ was then,

$$\hat{N}^*_{gwr-t,j} \equiv argmax_N⁡[p\hat{f}_{gwr-t,j} (N) -wN]$$.

## The value of GWR-based VRA over scam-based URA

To estimate the bias in the estimation of the value of GWR-based VRA, the true per-ha net revenues ("profits") of the SCAM-based URA and GWR-based VRA were calculated by plugging in the estimated optimal nitrogen rates into the "true" yield response functions. Profits from the SCAM approach were

$$\Pi_{scam}^* = 1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 \big[pf_{j, k} (\hat{N}_{scam}^* )-w\hat{N}_{scam}^*\big]$$

where $f_{j, k}(\cdot)$ denotes the true yield response function at cell $(j, k)$.

For $m = R, T$, the true per-ha net revenues ("profits") resulting from applying the profit-maximizing cell-specific N rate plan estimated by GWR-m were,

$$\Pi_{gwr-m}=1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 [pf_{j, k} (\hat{N}_{gwr-m, j}^*)-w\hat{N}_{gwr-m,j}^*]$$

where $f_{j, k} (\hat{N}_{gwr-j}^*)$ denote the true yield generated at cell $(j, k)$ with subplot $l$'s N rate.

The true value of the GWR-based VRA compared to the SCAM-based URA is defined by the difference of their partial profits:

$\Delta_{gwr-m} = \Pi_{gwr-m} - \Pi_{scam}$

To find the bias in estimating the value of VRA, the "estimated" profits of the SCAM-based URA and GWR-based VRA were calculated by plugging in the estimated optimal nitrogen rates into the cell-specific yield response functions estimated by GWR. Estimated per-ha net revenues for SCAM-based URA and GWR-based VRA are found as follows:

$$\hat{\Pi}_{scam}^* = 1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 \big[p\hat{f}^{gwr}_{j, k} (\hat{N}_{scam}^* )-w\hat{N}_{scam}^*\big]$$

$$\hat{\Pi}_{gwr-m}^*=1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 [p\hat{f}^{gwr-m}_{j, k} (\hat{N}_{gwr-m}^{j*} )-w\hat{N}_{gwr-m}^{j*}]$$

The estimated value of the GWR-based VRA compared to the SCAM-based URA is defined as

$$\hat{\Delta}_{gwr-m} = \hat{\Pi}_{gwr-m}^* - \hat{\Pi}_{scam}^*$$

Finally, the bias in the estimation of the value of GWR-based VRA was calculated as follows:

$$bias = \hat{\Delta}_{gwr-m} - \Delta_{gwr-m}$$

# Results

## Comparing the values of GWR-based VRA and SCAM-based URA

Figure \@ref(fig:pi-dif-dist) shows the distribution of $\hat{\Delta}_{gwr-m}$, profit difference between the GWR-based VRA and the SCAM-based URA. The distribution of the value of VRA from GWR-R is centered around 0, indicating that VRA based on GWR-R is on average no more profitable than SCAM-based URA. This result comes from GWR-R's highly inaccurate estimation of the subplot-level $N$ and $N^2$ coefficients, which led to unreliable subplot-specific nitrogen rate recommendations. Figure \@ref(fig:true-vs-estimated-coef-gwr-r) illustrates the accuracy of GWR-R in estimating the $N$ and $N^2$ coefficients in one simulation round. Estimates of the $N^2$ coefficients are positive for some subplots, indicating an increasing marginal product of the nitrogen rate, which contradicts a well-established agronomic property. The result is consistent with the bottom panel of Figure 12 in @rakshit2020. Figure \@ref(fig:true-vs-estimated-optn-gwr-r) plots the estimated cell-specific optimal N against the true optimal N for the same simulation round, and again shows that GWR-R can be highly unreliable, and consequently that basing variable rate management on GWR-R may be no better than taking a simple URA approach. Basically, not enough information is available locally to estimate reliably the coefficients on both $N$ and $N^2$ by subplot.

The GWR-T approach, however, performed better than SCAM-URA in majority of cases, with some cases showing values-added exceeding \$10 ha$^{-1}$. This may seem surprising as the model estimated in the GWR-T approach is more restrictive than that in the GWR-R approach because the coefficient on $N^2$ is assumed to be global. However, unlike GWR-R, this restriction helps avoid estimating positive subplot-level coefficients on $N^2$. This result implies that the value of avoiding highly unreliable estimates of coefficients on $N^2$ subplot-specifically was greater than loss of local flexibility in the coefficients on $N^2$.

## Bias in the estimation of the value of GWR-based VRA

Next we examine the bias in the "estimated" value of GWR-based VRA that researchers would encounter using real data. Figure \@ref(fig:bias-est-pi) shows the distribution of the bias in "estimated" profit between the GWR-based VRA and SCAM-based URA. Unlike the true difference in profit, VRA based on GWR-R appears to perform overwhelmingly better, with its average profit about \$`r round(pi_dif_gwr, digits = 2)` ha$^{-1}$ greater than that of the SCAM-based URA. That is, researchers would tend to significantly over-estimate the value of VRA based on GWR-R. When the GWR estimates are considered to define true yield response, the inaccuracy of GWR-R generates over-estimation of the heterogeneity of yield response within the field, which can lead to significant over-estimation of the value of GWR-R itself. Under GWR-T, the bias is more than \$10 ha$^{-1}$ for `r results[type == "GWR-T", mean(abs(bias) > 10)] * 100` % of the simulation cases: under GWR-R, that bias is greater than \$10 ha$^{-1}$ in `r results[type == "GWR-R", mean(abs(bias) > 10)] * 100` % of the simulated cases. However, as can be seen in the bottom panel of Figure \@ref(fig:bias-est-pi), the distribution of bias from GWR-T has a fatter tail than GWR-R with more mass on higher bias values. Bias is more than \$50 ha$^{-1}$ for `r results[type == "GWR-T", mean(abs(bias) > 50)] * 100` % of the simulation cases for GWR-T as opposed to `r results[type == "GWR-R", mean(abs(bias) > 50)] * 100` % for GWR-R.

Figure \@ref(fig:why-bias-many) illustrates how over-estimations can occur. It shows yield response functions estimated by GWR-T and estimated yields associated with the GWR-based EONR rates and SCAM-based EONR rates for 50 randomly chosen cells in a single simulation. Since GWR-based EONRs were obtained assuming the yield response functions estimated by GWR, by construction they out-perform better the SCAM-based estimates in every cell. For many cells, the SCAM-based estimated EONR is significantly higher than the actual yield-maximizing N rate, resulting in a yield far lower because of the quadratic functional form assumption. Figure \@ref(fig:why-bias-single) focuses on a single cell and compares estimated and true yields between GWR and SCAM (panel (a)) and estimated and true profits between GWR and SCAM (panel (b)). The cell's true yield response functions plateaus at a nitrogen rate of about $140$ kg ha$^{-1}$, but the GWR-estimated yield response function suggests that yield should peak at a nitrogen rate of about $190$ kg ha$^{-1}$ and then yield declines afterward. In reality, the yield differential between GWR and SCAM is 0, while the estimated yield differential is about $0.25$ ton ha$^{-1}$, leading to the over-estimation of the value of GWR in panel (b). Based on the true profit response curve, applying the GWR-based recommendation is about \$`r round(- true_yield_data[type != "True", diff(profit)], digits = 0)` ha$^{-1}$ more profitable than applying the SCAM-based recommendation. This profit differential comes soley from the difference in nitrogen cost since GWR and SCAM yields are equal. However, if calculations are based on the cell's GWR-based estimation of the response function, profits from the GWR-based recommendation are measured to be about \$`r round(- point_data_gwr[, diff(profit)], digits = 0)` ha$^{-1}$ greater than from the SCAM-based recommendation. Beyond the difference in nitrogen cost, the falsely estimated yield boost by GWR contributes to the profit differential, thus significantly over-estimating the actual value of GWR.

# Discussions

Our results on the relative performance of GWR-T and GWR-R show clearly that GWR-T performs better than GWR-R, and GWR-T should be used when researchers employ a GWR-based approach to find site-specific input recommendations. These findings, however, have important implications beyond just GWR-R and GWR-T. An obvious extension of the parametric GWR approaches would be a semi-parametric or non-parametric GWR where the yield response functions are estimated without assuming particular functional forms (like SCAM). However, such a method is likely to encounter a very similar problem to that faced by GWR-R: insufficient information available locally to estimate reliably the shape of yield response curve locally.

It is important to be aware that researchers need to be extremely cautious about their estimated value of VRA based on GWR whether they follow GWR-R or GWR-T. Our results show that it is likely that they will over-estimate their true values and the bias can be misleadingly high at the non-negligible probability. Extremely high values of VRA reported in @trevisan2021spatial are likely to have reflected this bias. Indeed, the bias problem we raised here is likely to be observed for other statistical methods because the bias comes from the assumption that the _estimated_ yield response functions are true. Whatever the underlying statistical method for yield response functions may be, researchers are likely to overestimate the true value of their methods. It would be an interesting future research to investigate the bias in other major statistical methods that are commonly used in the literature.

# Conclusions

This articles examined the value of GWR-based VRA and the bias in its estimation in the context of OFPE. We showed that restricting the coefficient on $N^2$ to a global parameter as done in @trevisan2021spatial leads to site-specific nitrogen rate recommendations with higher profits compared to the specification used by @rakshit2020, which allows the coefficients on $N^2$ to vary locally. However, we also found that both specifications can result in significant over-estimation of the true value of GWR-based site-specific nitrogen rate recommendations. It can be concluded that researchers need to be cautious about promoting the GWR-based approach.

A fruitful extension of GWR-based approach would be to employ more flexible yield reponse model specifications. This study has shown the assumed quadratic functional form to be the main culprit of the significant over-estimation of the value of GWR-based VRA. Applying GWR with a quadratic-plateau or linear-plateau specifications might substantially alleviate the reported bias problem.

`r run_pagebreak()`

# Figures

```{r fig.id = "field-layout", fig.cap = "Simulated field layout with spatial unit definitions", fig.dim = c(6, 6)}
g_layout
```

```{r fig.id = "field-N-design", fig.cap = "Experiment design of nitrogen (N) rates"}
g_exp
```

```{r, fig.id = "pi-dif-dist", fig.cap = "The value of GWR-based VRA over SCAM-based URA for GWR-R and GWR-T"}
g_value
```

```{r fig.id = "true-vs-estimated-coef-gwr-r", fig.cap = "Comparison of Estimated and True Coefficients"}
g_comp_coef
```

```{r fig.id = "true-vs-estimated-optn-gwr-r", fig.cap = "Comparison of Estimated and True EONR"}
g_comp_eonr
```

```{r fig.id = "bias-est-pi", fig.cap = "Bias in the estimation of the value of GWR-based VRA over SCAM-based URA for GWR-R and GWR-T"}
g_bias
```

```{r fig.id = "why-bias-many", fig.cap = "The cause of significant over-estimation of the value of GWR-based VRA"}
g_why_bias_many
```

```{r fig.id = "why-bias-single", fig.cap = "An illustration of over-estimation of the value of GWR-based VRA over SCAM-based URA",fig.dim = c(6, 7)}
g_why_bias_single
```

`r run_pagebreak()`

# References

<br />

<div id="refs"></div>

### 2022-05-24 Codes/3_make_figures_publication.R

@@ -5,7 +5,7 @@
 # fig.cap = "Simulated field layout with spatial unit definitions",
 # fig.dim = c(6, 6)
 
-field_with_design <- readRDS(here("Data/field_with_design.rds"))
+field_with_design <- readRDS(here("Shared/Data/field_with_design.rds"))
 field_sf <- field_with_design[1, ]$field_sf[[1]]
 
 plot_sf <-
@@ -95,7 +95,7 @@ g_layout <- g_field / g_inside_plot
 # fig.cap = "Experiment design of nitrogen (N) rates"
 
 reg_data <-
-  readRDS(here("Data/LatinSquareFixed_144.rds")) %>%
+  readRDS(here("Shared/Data/LatinSquareFixed_144.rds")) %>%
   pull(reg_data) %>%
   .[[1]] %>%
   .[1]
@@ -135,7 +135,7 @@ g_exp <-
 # fig.id = "pi-dif-dist",
 # fig.cap = "The value of GWR-based VRA over SCAM-based URA for GWR-R and GWR-T"
 
-# results <- readRDS(here("Results/pi_data.rds"))%>%
+# results <- readRDS(here("Shared/Results/pi_data.rds"))%>%
 #   .[, type := ifelse(transfer == 0, "GWR-R", "GWR-T")]
 
 mean_data <- 
@@ -168,7 +168,7 @@ g_value <-
 
 #* read the simulation data for a sigle simulationused for illustration
 single_sim <-
-  here("Results", "aunit_sim_single.rds") %>%
+  here("Shared", "Results", "aunit_sim_single.rds") %>%
   readRDS() %>%
   .[, type := ifelse(transfer == 0, "GWR-R", "GWR-T")]
 
@@ -256,7 +256,7 @@ g_bias <-
 # /*+++++++++++++++++++++++++++++++++++
 #' # Prepare parameters
 # /*+++++++++++++++++++++++++++++++++++
-field_parameters <- readRDS(here("Data/field_parameters.rds"))
+field_parameters <- readRDS(here("Shared/Data/field_parameters.rds"))
 
 pCorn <- field_parameters$pCorn
 pN <- pCorn * field_parameters$pRatio_ls[[1]][2]     # medium price scenario
@@ -265,7 +265,7 @@ pN <- pCorn * field_parameters$pRatio_ls[[1]][2]     # medium price scenario
 #' # Prepare yield response curves
[…]

### 2022-05-25 Writing/manuscript_gwr.rmd
incorporated Xiaofei's editing to the manuscript rmd file (except for the citations)

@@
 
-**Abstract**: Geographically-weighted regression (GWR) has been presented as a prominent tool to estimate site-specific yield response functions to generate site-specific input rate recommendations using data generated by on-farm precision experimentation (OFPE).
+**Abstract**: Geographically weighted regression (GWR) has been presented as a prominent tool to estimate site-specific yield response functions to generate site-specific input rate recommendations using data generated by on-farm precision experimentation (OFPE).
 The key objectives of this paper are two-fold.
 First, it evaluates two sets of functional-form specifications made by two recent published studies of site-specific input management that apply GWR to data from OFPE.
-We show that one set of functional-form specification performs significantly better than the other.
+We show that one set of functional-form specification performs significantly better than the other under usual historical price scenarios.
 Second, we investigate the possibility of bias when GWR is used to estimate the value of site-specific vs.
@@
 
-**Keywords**: on-farm precision experimentation, site-specific input management, geographically-weighted regression, economically optimal nitrogen rate
+**Keywords**: on-farm precision experimentation, site-specific input management, geographically weighted regression, economically optimal nitrogen rate
 
@@
 
-However, deploying sophisticated sensors to gather field characteristics data is also costly, and the effects of their generation and use on farm profitability remains in question [@gardner2021economic].
+However, deploying sophisticated sensors to gather field characteristics data is also costly, and the effects of their generation and use on farming profitability remains in question [@gardner2021economic].
 Recognizing the significant costs of obtaining useful, high-resolution soil and field properties data, @trevisan2021spatial demonstrated a method of providing site specific management recommendations without such data.
@@
 However, while they did estimate site-specific yield response functions, they did not derive site-specific economically optimal nitrogen rates based on them, and thus did not conduct economic analysis unlike @trevisan2021spatial.
-@evans2020assessment explored using GWR with a linear model specification to detect low- and high-response areas, but like @rakshit2020 also did not estimate site-specific economically optimal nitrogen rates.
+@evans2020assessment explored using GWR with a linear model specification to detect low- and high-response areas, but like @rakshit2020, they also did not estimate site-specific economically optimal nitrogen rates.
 
@@
 
-One of the principal findings of this article is that the model specification used by @trevisan2021spatial creates more valuable information than does the model specification used by @rakshit2020.
+One of the principal findings of this article is that the model specification used by @trevisan2021spatial creates more valuable information than does the model specification used by @rakshit2020 under usual corn and N fertilizer prices.
 This is primarily due to GWR's poor local estimation of the coefficients on $N^2$.
@@
 $$
-\begin{equation}
+\begin{equation} \tag{1}
 y_{j,k} = f_{j, k} (N) = f(N, c_{j,k}) = 
@@
 In each simulation, six trial N rates were assigned by calculating the 0%, 20%, 40%, 60%, 80%, and 100% quantiles of the simulation's true cell-specific optimal N rates.
-The means of these trial N rates across simulations were approximately, {80, 130, 154, 184, 219, and 270} kg ha$^{-1}$.
+When using the historical average corn and N prices (past 20 years, 2002-2021), the means of these trial N rates across simulations were approximately, {80, 130, 154, 184, 219, and 270} kg ha$^{-1}$.
 
@@
 
-In the GWR-R approach, yield response was modeled as subplot-specific quadratic functions of the nitrogen rate, which for each subplot $j \in {1, 2, \dots, 1440}$ was specified as,
+The GWR-R model is simply the basic GWR model (Fotheringham et al., 1996; Brunsdon et al., 1999; Fotheringham et al., 2002), where yield response was modeled as subplot-specific quadratic functions of the nitrogen rate, which for each subplot $j \in {1, 2, \dots, 1440}$ was specified as,
 
-$$y_j= \alpha_j+ \beta_j N_j + \eta_j N_j^2+ \epsilon_j$$
+$$y_j= \alpha_j+ \beta_j N_j + \eta_j N_j^2+ \epsilon_j .$$
 
+The coefficients $\alpha_j$, $\beta_j$, and $\eta_j$ were continuous functions of subplot $j$’s coordinates ($lon_j$, $lat_j$).
 The GWR-R estimation produced subplot-specific estimates of coefficients $\hat{\alpha}_j$, $\hat{\beta}_j$, and $\hat{\eta}_j$, and so of the yield response function $\hat{f}_{gwr-r,j}(N)$ for $j = 1, 2, \dots, 1440$.
@@
 
-$$\hat{N}_{gwr-r,j}^{*} \equiv argmax_N⁡[p\hat{f}_{gwr-r, j} (N) -wN]$$.
+$$\hat{N}_{gwr-r,j}^{*} \equiv argmax_N⁡[p\hat{f}_{gwr-r, j} (N) -wN] .$$
 
@@
 
-In the GWR-T approach, unlike GWR-Rakshit, the coefficient on $N^2$ was estimated as a global parameter while the coefficient on $N$ was estimated subplot-specifically.
+The GWR-T model is also named as “mixed” GWR in the literature (Brunsdon et al., 1999) where some parameters are fixed globally while others vary geographically.
+In our model, the coefficient on $N^2$ was estimated as a global parameter while the coefficient on $N$ was estimated subplot-specifically.
 For each subplot $j \in {1, 2, \dots, 1440}$, the assumed yield response was,
 
-$$y_j= \alpha_j+ \beta N_j + \eta N_j^2+ \epsilon_j$$.
+$$y_j= \alpha_j+ \beta N_j + \eta N_j^2+ \epsilon_j ,$$
 
-where $\eta$ was assumed invariant among subplots. Because the coefficients on some variables were estimated as global parameters, the model used can be classified as a Mixed GWR model.
+where $\eta$ was assumed invariant among subplots.
 
@@
 
-$$\hat{N}^*_{gwr-t,j} \equiv argmax_N⁡[p\hat{f}_{gwr-t,j} (N) -wN]$$.
+$$\hat{N}^*_{gwr-t,j} \equiv argmax_N⁡[p\hat{f}_{gwr-t,j} (N) -wN] .$$
+
+The Gaussian kernel function was used when estimating both GWR models, and the optimal bandwidth was selected through the corrected AIC approach (Fotheringham et al., 2002).
+The optimal bandwidth differed slightly across each simulated experiment, and the average bandwidth was around 18 meters.
 
@@
 
-$\Delta_{gwr-m} = \Pi_{gwr-m} - \Pi_{scam}$
+$$\Delta_{gwr-m} = \Pi_{gwr-m} - \Pi_{scam} .$$
 
@@
 Estimates of the $N^2$ coefficients are positive for some subplots, indicating an increasing marginal product of the nitrogen rate, which contradicts a well-established agronomic property.
-The result is consistent with the bottom panel of Figure 12 in @rakshit2020.
+The result is consistent with the bottom panel of Figure 12 in @rakshit2020 as well as the widely criticized poor coefficient estimation accuracy of GWR model in the literature (Griffith, 2008; Páez et al., 2011; Silva and Fotheringham, 2016; Harris, 2019).
 Figure \@ref(fig:true-vs-estimated-optn-gwr-r) plots the estimated cell-specific optimal N against the true optimal N for the same simulation round, and again shows that GWR-R can be highly unreliable, and consequently that basing variable rate management on GWR-R may be no better than taking a simple URA approach.
@@
 
-Our results on the relative performance of GWR-T and GWR-R show clearly that GWR-T performs better than GWR-R, and GWR-T should be used when researchers employ a GWR-based approach to find site-specific input recommendations.
-These findings, however, have important implications beyond just GWR-R and GWR-T.
-An obvious extension of the parametric GWR approaches would be a semi-parametric or non-parametric GWR where the yield response functions are estimated without assuming particular functional forms (like SCAM).
+Our simulation results show the basic GWR model (GWR-R) has little economic value for site-specific $R_xs$.
+The GWR-R based VRA is on average no more profitable than SCAM-based URA under historically common price scenarios.
+This finding reveals the economic consequences of the widely recognized statistical inaccuracy issue of GWR estimation (Griffith, 2008; Páez et al., 2011; Silva and Fotheringham, 2016; Harris, 2019), and in agreement with the previous critique that GWR should be used as an exploratory tool rather than an inferential tool (Wheeler and Tiefelsdorf, 2005; Páez et al., 2011).
+Precision agriculture practitioners should be cautious when using GWR for site-specific $R_xs$.
+If GWR-based approach must be employed to find site-specific input recommendations (e.g., due to lack of field and soil information), our simulation results show that GWR-T performs relatively better than GWR-R, though its profitability improvement against URA is only moderate.
+
+_(Our results on the relative performance of GWR-T and GWR-R show clearly that GWR-T performs better than GWR-R, and GWR-T should be used when researchers employ a GWR-based approach to find site-specific input recommendations.
+-> This major conclusion only applies to one price scenario.) (These findings, however, have important implications beyond just GWR-R and GWR-T.
+-> I am not sure what this sentence means here.)_
+
+An obvious cause of the GWR models’ poor economic performances in this work is the quadratic functional form used in GWR that differs from the true quadratic-plateau yield response functions.
+One solution could be to upgrade to nonlinear GWR models.
+Lambert and Cho (2022) have recently developed a linear-plateau GWR model, which could be worthy of future examinations of its economic value.
+Another solution is to extend the parametric GWR approaches to a semi-parametric or non-parametric GWR where the yield response functions are estimated without assuming particular functional forms (like SCAM).
 However, such a method is likely to encounter a very similar problem to that faced by GWR-R: insufficient information available locally to estimate reliably the shape of yield response curve locally.
+It is also noted that the recently developed multiscale GWR model (Fotheringham et al., 2017; Oshan et al., 2019; Lu et al., 2019;)
+
+[@yu2020inference; @comber2022route] allows the bandwidth to be derived separately for each covariate in the model, which would potentially improve the performances of GWR estimates and be incorporated into future research.
 
@@
 
-This articles examined the value of GWR-based VRA and the bias in its estimation in the context of OFPE.
+This article examined the economic value of GWR-based VRA and the bias in its estimation in the context of OFPE.
 We showed that restricting the coefficient on $N^2$ to a global parameter as done in @trevisan2021spatial leads to site-specific nitrogen rate recommendations with higher profits compared to the specification used by @rakshit2020, which allows the coefficients on $N^2$ to vary locally.
 However, we also found that both specifications can result in significant over-estimation of the true value of GWR-based site-specific nitrogen rate recommendations.
-It can be concluded that researchers need to be cautious about promoting the GWR-based approach.
+It can be concluded that researchers need to be cautious about promoting the GWR-based approach in VRA recommendation.
 
@@
 
-```{r fig.id = "field-N-design", fig.cap = "Experiment design of nitrogen (N) rates"}
+```{r fig.id = "field-N-design", fig.cap = "Experiment design of nitrogen (N) rates", fig.dim = c(6, 3.5)}
 g_exp

### 2022-05-25 Writing/manuscript_gwr.rmd
bibliography updates

@@
 First, it evaluates two sets of functional-form specifications made by two recent published studies of site-specific input management that apply GWR to data from OFPE.
-We show that one set of functional-form specification performs significantly better than the other under usual historical price scenarios.
-Second, we investigate the possibility of bias when GWR is used to estimate the value of site-specific vs.
+We show that one set of functional-form specification performs significantly better than the other under usual historical price scenarios _(Our trial design simulations show the two GWR models beat each other under different price scenarios.)_.
+Second, we investigate the possibility of bias _(Can we think of another term rather than “bias”?
+The term “bias” will tempt some reviewers (the not-so-smart ones) to think it is about the GWR coefficient estimation accuracy issue.)_ when GWR is used to estimate the value of site-specific vs.
 uniform-rate input management.
 We show that GWR suffers significant positive bias, which can lead to great over-estimation of the value of applying GWR methods.
-Our study is the first to systematically examine the statistical and economic properties of the use of GWR in OPFE settings.
+Our study is the first to systematically examine the statistical _(Maybe remove “statistical” to avoid any further attacks from statistician reviewers?)_ and economic properties of the use of GWR in OPFE settings.
 We reveal that in many circumstances using GWR is far less profitable than claimed by previous studies, which provides a necessary cautionary message to researchers who might otherwise “over-sell” to other researchers the value of using GWR methods in empirical work involving the estimation of site-specific input management.
@@
 Second, we will examine the degree and direction of bias in the estimation of the value of GWR-based variable rate application (VRA) and question the extremely high estimates of that value reported by @trevisan2021spatial.
-In general, researchers take the following steps to estimate the value of VRA based using OFPE data [e.g., @swinton1998evaluating; @bullock2002adding; @anselin2004spatial; @liu2006site]: (1) estimate site-specific yield response functions based on a method chosen by the researcher; (2) use the estimated yield response functions to estimate the economically optimal site-specific input rates (EOIR) and economically optimal uniform input rates; (3) plug the estimated site-specific EOIRs and uniform EOIR into the estimated yield response functions to calculate estimated profits under both strategies; and (4) find the difference in the two strategies' estimated profits.
+In general, researchers take the following steps to estimate the value of VRA based using OFPE data [e.g., @anselin2004spatial; @swinton1998evaluating; @bullock2002adding;  @liu2006site]: (1) estimate site-specific yield response functions based on a method chosen by the researcher; (2) use the estimated yield response functions to estimate the economically optimal site-specific input rates (EOIR) and economically optimal uniform input rates; (3) plug the estimated site-specific EOIRs and uniform EOIR into the estimated yield response functions to calculate estimated profits under both strategies; and (4) find the difference in the two strategies' estimated profits.
 However, this approach can result in significant bias in the estimation of the value of VRA because of the assumption made on step (3), which is that the estimated yield response functions are the true yield response functions.
@@
 The index $j \in {1, 2, \dots, 1440}$ identifies the field's subplots, and the index $k \in {1, \dots , 6}$ identifies the cells within a subplot.
-The couplet (j, k) is used to identify individual cells.
+The couplet $(j, k)$ is used to identify individual cells.
 
@@
 The quadratic, linear-plateau, quadratic-plateau, and Mitscherlich‐Baule are commonly used functional forms.
-In this study, each cell (j, k)'s "true" yield response function is assumed to follow the quadratic-plateau functional form:
+_(How about we just focus on quadratic-plateau, which is well documented in the agronomy literature.
+So no reviewers will keep asking to do "robustness checks" of other functional forms.)_ In this study, each cell $(j, k)$'s "true" yield response function is assumed to follow the quadratic-plateau functional form: _(I tried adding equation number by using the "\tag{}".
+It works in .rmd, but won't be knitted into .docx file.)_
 
@@
 A higher range value indicates increased spatial dependence, meaning less abrupt differences are observed between the production function parameters of neighboring cells.
-The mean and sill variance of each parameter were specified to result in a realistic mean yield of $11,416$ kg ha$^{-1}$, and such that the cells' true economically optimal N rate ranged from $113$ kg ha$^{-1}$ to $273$ kg ha$^{-1}$ among all the simulations, which most real-world N rate recommendations fall into (e.g., @sawyer2018).
+The mean and sill variance of each parameter were specified to result in a realistic mean yield of $11,416$ kg ha$^{-1}$, and such that the cells' true economically optimal N rate ranged from $113$ kg ha$^{-1}$ to $273$ kg ha$^{-1}$ among all the simulations, which most real-world N rate recommendations fall into [e.g., @sawyer2018].
 Note that the range of the optimal N rates of individual rounds of simulations are narrower.
@@
 
-The GWR-R model is simply the basic GWR model (Fotheringham et al., 1996; Brunsdon et al., 1999; Fotheringham et al., 2002), where yield response was modeled as subplot-specific quadratic functions of the nitrogen rate, which for each subplot $j \in {1, 2, \dots, 1440}$ was specified as,
+The GWR-R model is simply the basic GWR model [@fotheringham1996geography; @brunsdon1999some; @fotheringham2003geographically], where yield response was modeled as subplot-specific quadratic functions of the nitrogen rate, which for each subplot $j \in {1, 2, \dots, 1440}$ was specified as,
 
@@
 
-The GWR-T model is also named as “mixed” GWR in the literature (Brunsdon et al., 1999) where some parameters are fixed globally while others vary geographically.
+The GWR-T model is also named as “mixed” GWR in the literature [@brunsdon1999some] where some parameters are fixed globally while others vary geographically.
 In our model, the coefficient on $N^2$ was estimated as a global parameter while the coefficient on $N$ was estimated subplot-specifically.
@@
 
-The Gaussian kernel function was used when estimating both GWR models, and the optimal bandwidth was selected through the corrected AIC approach (Fotheringham et al., 2002).
+The Gaussian kernel function was used when estimating both GWR models, and the optimal bandwidth was selected through the corrected AIC approach [@fotheringham2003geographically].
 The optimal bandwidth differed slightly across each simulated experiment, and the average bandwidth was around 18 meters.
@@
 Estimates of the $N^2$ coefficients are positive for some subplots, indicating an increasing marginal product of the nitrogen rate, which contradicts a well-established agronomic property.
-The result is consistent with the bottom panel of Figure 12 in @rakshit2020 as well as the widely criticized poor coefficient estimation accuracy of GWR model in the literature (Griffith, 2008; Páez et al., 2011; Silva and Fotheringham, 2016; Harris, 2019).
+The result is consistent with the bottom panel of Figure 12 in @rakshit2020 as well as the widely criticized poor coefficient estimation accuracy of GWR model in the literature [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation].
 Figure \@ref(fig:true-vs-estimated-optn-gwr-r) plots the estimated cell-specific optimal N against the true optimal N for the same simulation round, and again shows that GWR-R can be highly unreliable, and consequently that basing variable rate management on GWR-R may be no better than taking a simple URA approach.
@@
 The GWR-R based VRA is on average no more profitable than SCAM-based URA under historically common price scenarios.
-This finding reveals the economic consequences of the widely recognized statistical inaccuracy issue of GWR estimation (Griffith, 2008; Páez et al., 2011; Silva and Fotheringham, 2016; Harris, 2019), and in agreement with the previous critique that GWR should be used as an exploratory tool rather than an inferential tool (Wheeler and Tiefelsdorf, 2005; Páez et al., 2011).
+This finding reveals the economic consequences of the widely recognized statistical inaccuracy issue of GWR estimation [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation], and in agreement with the previous critique that GWR should be used as an exploratory tool rather than an inferential tool [@wheeler2005multicollinearity; @paez2011simulation].
 Precision agriculture practitioners should be cautious when using GWR for site-specific $R_xs$.
@@
 One solution could be to upgrade to nonlinear GWR models.
-Lambert and Cho (2022) have recently developed a linear-plateau GWR model, which could be worthy of future examinations of its economic value.
+@lambert2022geographically have recently developed a linear-plateau GWR model, which could be worthy of future examinations of its economic value.
 Another solution is to extend the parametric GWR approaches to a semi-parametric or non-parametric GWR where the yield response functions are estimated without assuming particular functional forms (like SCAM).
 However, such a method is likely to encounter a very similar problem to that faced by GWR-R: insufficient information available locally to estimate reliably the shape of yield response curve locally.
-It is also noted that the recently developed multiscale GWR model (Fotheringham et al., 2017; Oshan et al., 2019; Lu et al., 2019;)
-
-[@yu2020inference; @comber2022route] allows the bandwidth to be derived separately for each covariate in the model, which would potentially improve the performances of GWR estimates and be incorporated into future research.
+It is also noted that the recently developed multiscale GWR model [@fotheringham2017multiscale; @yu2020inference; @comber2022route] allows the bandwidth to be derived separately for each covariate in the model, which would potentially improve the performances of GWR estimates and be incorporated into future research.
 
@@
 This study has shown the assumed quadratic functional form to be the main culprit of the significant over-estimation of the value of GWR-based VRA.
-Applying GWR with a quadratic-plateau or linear-plateau specifications might substantially alleviate the reported bias problem.
+Applying GWR with a quadratic-plateau or linear-plateau _(Since Lambert has already developed the linear-plateau model, how about we delete it here?)_ specifications might substantially alleviate the reported bias problem.
 

### 2022-05-27 Writing/manuscript_gwr.rmd
several modifications on the manuscript

@@
 The key objectives of this paper are two-fold.
-First, it evaluates two sets of functional-form specifications made by two recent published studies of site-specific input management that apply GWR to data from OFPE.
-We show that one set of functional-form specification performs significantly better than the other under usual historical price scenarios _(Our trial design simulations show the two GWR models beat each other under different price scenarios.)_.
-Second, we investigate the possibility of bias _(Can we think of another term rather than “bias”?
-The term “bias” will tempt some reviewers (the not-so-smart ones) to think it is about the GWR coefficient estimation accuracy issue.)_ when GWR is used to estimate the value of site-specific vs.
-uniform-rate input management.
-We show that GWR suffers significant positive bias, which can lead to great over-estimation of the value of applying GWR methods.
-Our study is the first to systematically examine the statistical _(Maybe remove “statistical” to avoid any further attacks from statistician reviewers?)_ and economic properties of the use of GWR in OPFE settings.
+First, it evaluates two sets of functional-form specifications used by two recent published studies of site-specific input management that apply GWR to data from OFPE.
+We show that one set of functional-form specification performs significantly better than the other under three price scenarios observed historically.
+Second, we investigate the possibility of bias in estimating the "economic" value of site-specific recommendation maps based on GWR.
+We show that GWR suffers significant positive bias, which can lead to great over-estimation of the "economic" value of applying GWR methods.
+Our study is the first to systematically examine the "economic" properties of the use of GWR in OPFE settings.
 We reveal that in many circumstances using GWR is far less profitable than claimed by previous studies, which provides a necessary cautionary message to researchers who might otherwise “over-sell” to other researchers the value of using GWR methods in empirical work involving the estimation of site-specific input management.
@@
 @trevisan2021spatial reported dramatic results, estimating an average potential gain of \$65 ha$^{-1}$ from applying seed and N at optimal uniform rates (instead of at the rates the farmers would have chosen if not participating in the research), and an additional potential gain of \$58 ha$^{-1}$ when changing from optimal uniform application rates to optimal site-specific application rates.
+This is rather surprising give the poor accuracy of GWR estimates [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation].
 @rakshit2020 also applied GWR to on-farm experiment data.
@@
 
-Second, we will examine the degree and direction of bias in the estimation of the value of GWR-based variable rate application (VRA) and question the extremely high estimates of that value reported by @trevisan2021spatial.
+Second, we will examine the degree and direction of bias in the estimation of the "economic" value of GWR-based variable rate application (VRA) and question the extremely high estimates of that value reported by @trevisan2021spatial (It is critical to keep in mind that it is not our objective at all to see the bias in the coefficient estimation by GWR, unlike [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation].
+Rather, we are interested in its economic implication in this study.).
 In general, researchers take the following steps to estimate the value of VRA based using OFPE data [e.g., @anselin2004spatial; @swinton1998evaluating; @bullock2002adding;  @liu2006site]: (1) estimate site-specific yield response functions based on a method chosen by the researcher; (2) use the estimated yield response functions to estimate the economically optimal site-specific input rates (EOIR) and economically optimal uniform input rates; (3) plug the estimated site-specific EOIRs and uniform EOIR into the estimated yield response functions to calculate estimated profits under both strategies; and (4) find the difference in the two strategies' estimated profits.
@@
 An extensive literature examines the choice of functional form in yield response estimation [@cerrato1990comparison, @frank1990comparison, @bullock1994quadratic, @tembo2008crop].
-The quadratic, linear-plateau, quadratic-plateau, and Mitscherlich‐Baule are commonly used functional forms.
-_(How about we just focus on quadratic-plateau, which is well documented in the agronomy literature.
-So no reviewers will keep asking to do "robustness checks" of other functional forms.)_ In this study, each cell $(j, k)$'s "true" yield response function is assumed to follow the quadratic-plateau functional form: _(I tried adding equation number by using the "\tag{}".
-It works in .rmd, but won't be knitted into .docx file.)_
+In this study, each cell $(j, k)$'s "true" yield response function is assumed to follow the quadratic-plateau functional form, which is one of the most commonly used functional forms:
 
@@
 
-To estimate the bias in the estimation of the value of GWR-based VRA, the true per-ha net revenues ("profits") of the SCAM-based URA and GWR-based VRA were calculated by plugging in the estimated optimal nitrogen rates into the "true" yield response functions.
+To estimate the bias in the estimation of the economic value of GWR-based VRA, the true per-ha net revenues ("profits") of the SCAM-based URA and GWR-based VRA were calculated by plugging in the estimated optimal nitrogen rates into the "true" yield response functions.
 Profits from the SCAM approach were
@@
 
-_(Our results on the relative performance of GWR-T and GWR-R show clearly that GWR-T performs better than GWR-R, and GWR-T should be used when researchers employ a GWR-based approach to find site-specific input recommendations.
--> This major conclusion only applies to one price scenario.) (These findings, however, have important implications beyond just GWR-R and GWR-T.
--> I am not sure what this sentence means here.)_
-
-An obvious cause of the GWR models’ poor economic performances in this work is the quadratic functional form used in GWR that differs from the true quadratic-plateau yield response functions.
+An obvious cause of the GWR models' poor economic performances in this work is the quadratic functional form used in GWR that differs from the true quadratic-plateau yield response functions.
 One solution could be to upgrade to nonlinear GWR models.
@@
 It is also noted that the recently developed multiscale GWR model [@fotheringham2017multiscale; @yu2020inference; @comber2022route] allows the bandwidth to be derived separately for each covariate in the model, which would potentially improve the performances of GWR estimates and be incorporated into future research.
+Please note, however, that multiscale GWR models are not necessary in out simulations as we have only one covaraite ($N$) in our simulations.
 
@@
 It can be concluded that researchers need to be cautious about promoting the GWR-based approach in VRA recommendation.
-
-A fruitful extension of GWR-based approach would be to employ more flexible yield reponse model specifications.
-This study has shown the assumed quadratic functional form to be the main culprit of the significant over-estimation of the value of GWR-based VRA.
-Applying GWR with a quadratic-plateau or linear-plateau _(Since Lambert has already developed the linear-plateau model, how about we delete it here?)_ specifications might substantially alleviate the reported bias problem.
 

### 2022-05-27 Writing/knit.R

@@ -1,0 +1,1 @@
+rmarkdown::render(here::here("GitControlled/Writing/manuscript_gwr.rmd"))

### 2022-06-06 Writing/manuscript_gwr.rmd
updated results with five price ratio scenarios: 5%, 25%, 50%, 75%, 95%

@@
 library(patchwork)
+library(ggplot2)
+library(ggh4x)
 ```
@@
   .[, type := ifelse(transfer == 0, "GWR-R", "GWR-T")] %>%
-  .[, bias := pi_diff_est - pi_diff]
+  .[, bias := pi_diff_est - pi_diff] %>% 
+  #=== label price ratio
+  .[, pLabelName := "Price Ratio (N/corn)"]
+  # .[, pLabel := "Middle"] %>% 
+  # .[pRatio==min(pRatio), pLabel := "Low"] %>% 
+  # .[pRatio==max(pRatio), pLabel := "High"] %>% 
+  # .[, pLabel := factor(pLabel, levels = c("Low", "Middle", "High"))]
 
@@
 Figure \@ref(fig:pi-dif-dist) shows the distribution of $\hat{\Delta}_{gwr-m}$, profit difference between the GWR-based VRA and the SCAM-based URA.
+
+, for the two GWR models and three N/corn price ratios. The
+
+Three price ratios (nitrogen fertilizer price divided by corn price, both in $/kg) were used in the simulations: 4.16 (low), 6.56 (medium), and 10.35 (high).
+They were obtained by taking the 5%, 50%, and 95% of historical monthly price ratios from 1990 to 2022.
+The recent period (April 2022) corn price of about $0.28/kg was used in the simulation results.
+Our main scenario to discuss was the medium price ratio, where the nitrogen fertilizer price was $1.8/kg (that was close to the recent market price).
+Note that this setting may generate some extreme prices.
+For example, the high price ratio scenario was corresponding to nitrogen price of $2.85/kg, which was unrealistic in history.
+But that did not affect the EONR estimations since they were only affected by the relative nitrogen-corn price ratio rather than absolute the prices.
+The final profit values 〖∆Π〗_^* could be over- or under-estimated by extreme prices, but those over- or under-estimations were linear scale-up or scale-down of the actual profit values and would not affect the economic performance rankings of trial designs.
+
 The distribution of the value of VRA from GWR-R is centered around 0, indicating that VRA based on GWR-R is on average no more profitable than SCAM-based URA.

### 2022-06-06 Codes/2_post_sim_analysis.R

@@ -28,7 +28,7 @@ library(here)
 setwd(here())
 
 #* Load functions
-fs::dir_ls(here("Codes", "Functions"), full.names = TRUE) %>%
+fs::dir_ls(here("GitControlled", "Codes", "Functions"), full.names = TRUE) %>%
   lapply(., function(x) source(x))
 
 # /*===========================================================
@@ -36,9 +36,9 @@ fs::dir_ls(here("Codes", "Functions"), full.names = TRUE) %>%
 # /*===========================================================
 
 #* load generated parameters
-field_data <- readRDS(here("Data/field_data.rds"))
-field_with_design <- readRDS(here("Data/field_with_design.rds"))
-field_parameters <- readRDS(here("Data/field_parameters.rds"))
+field_data <- readRDS(here("Shared/Data/field_data.rds"))
+field_with_design <- readRDS(here("Shared/Data/field_with_design.rds"))
+field_parameters <- readRDS(here("Shared/Data/field_parameters.rds"))
 
 #* cell-level true data (sprange=600 scenario)
 cell_data <- field_parameters %>%
@@ -61,7 +61,7 @@ rowwise() %>%
 # cell_data <- cell_data[field_dt[, .(cell_id, aunit_id)], on = "cell_id"]
 
 #* load simulation results data
-mc_sim_results <- readRDS(file = here("Results/mc_sim_results.rds"))
+mc_sim_results <- readRDS(file = here("Shared/Results/mc_sim_results.rds"))
 
 #* aunit-level estimated data
 ## -------------------------------------
@@ -174,7 +174,7 @@ pi_data <- rbindlist(pi_data_ls) %>%
   .[, pRatio := (pN / pCorn) %>% round(2) ] %>% 
   .[, pLabel := factor(pRatio, 
                        levels = str_sort(unique(pRatio), numeric = TRUE))] 
-saveRDS(pi_data, here("Results/pi_data.rds"))
+saveRDS(pi_data, here("Shared/Results/pi_data.rds"))
 
 
 
@@ -204,7 +204,7 @@ il_data_oe <-
   .[sim == sim_id, ] %>%
   .[transfer == 1, ] 
 
-saveRDS(il_data_oe, here("Results/il_data_oe.rds"))
+saveRDS(il_data_oe, here("Shared/Results/il_data_oe.rds"))
 
 # /*===========================================================
 #' # Find extreme cases of simulation results
[…]

### 2022-06-06 Codes/3_make_figures_publication.R

@@ -141,7 +141,7 @@ g_exp <-
 mean_data <- 
   results %>%
   .[, .(pi_diff = mean(pi_diff)),
-    by=c("field_col", "pLabel", "type")] %>%
+    by=c("field_col", "pLabelName", "pLabel", "type")] %>%
   print()
 
 g_value <-
@@ -151,10 +151,11 @@ g_value <-
   geom_vline(data = mean_data, aes(xintercept = pi_diff), 
              color = "red", linetype = 8, size = 1) +
   geom_text(data = mean_data, color = "red",
-            aes(x = pi_diff, y = 200,
-                label = paste0("mean = ", round(pi_diff, 2))),
+            aes(x = pi_diff + 10, y = 200,
+                label = paste0(round(pi_diff, 2))),
             angle = 0, hjust = -0.1, vjust = 0, size = 3 ) +
-  facet_grid(pLabel ~ type) +
+  facet_nested(pLabelName + pLabel ~ type,
+               nest_line = element_line(linetype = 1)) +
   scale_y_continuous(expand = c(0, 0)) +
   xlab("The value of VRA over URA ($ per ha)") +
   ylab("Number of Simulation Cases")
@@ -225,7 +226,7 @@ mean_data <-
   results %>%
   .[, bias := pi_diff_est - pi_diff] %>%
   .[, .(bias = mean(bias)),
-    by=c("field_col", "pLabel", "type")] %>%
+    by=c("field_col", "pLabelName", "pLabel", "type")] %>%
   print()
 
 g_bias <-
@@ -238,9 +239,9 @@ g_bias <-
              color = "red", linetype = 8, size = 1) +
   geom_text(data = mean_data, color = "red",
             aes(x = bias, y = 200,
-                label = paste0("mean = ", round(bias, 2))),
+                label = paste0(round(bias, 2))),
             angle = 0, hjust = -0.1, vjust = 0, size = 3 ) +
-  facet_grid(pLabel ~ type) +
+  facet_nested(pLabelName + pLabel ~ type) +
   scale_y_continuous(expand = c(0, 0)) +
   xlab("Bias in the Estimation of the Value of VRA over URA ($ per ha)") +
   ylab("Number of Simulation Cases")

### 2022-06-09 Writing/manuscript_gwr.rmd
update results with 3 price ratios: 25% (5.44), 50% (6.56), 75% (7.67)

--- 2022-05-27 Writing/manuscript_gwr.rmd
@@
   .[, type := ifelse(transfer == 0, "GWR-R", "GWR-T")] %>%
-  .[, bias := pi_diff_est - pi_diff]
+  .[, bias := pi_diff_est - pi_diff] %>% 
+  #only display the 25% (5.44), 50% (6.56), 75% (7.67) price ratio
+  .[pRatio %in% c(5.44, 6.56, 7.67), ] %>% 
+  #=== label price ratio
+  .[, pLabelName := "Price Ratio (N/corn)"] %>% 
+  .[pRatio==5.44, pLabel := "Low"] %>%
+  .[pRatio==6.56, pLabel := "Middle"] %>%
+  .[pRatio==7.67, pLabel := "High"] %>%
+  .[, pLabel := factor(pLabel, levels = c("Low", "Middle", "High"))]
 
@@
 
-Figure \@ref(fig:pi-dif-dist) shows the distribution of $\hat{\Delta}_{gwr-m}$, profit difference between the GWR-based VRA and the SCAM-based URA.
+Figure \@ref(fig:pi-dif-dist) shows the distribution of $\hat{\Delta}_{gwr-m}$, the profit difference between the GWR-based VRA and the SCAM-based URA.
+Three price ratios (nitrogen fertilizer price $\$$ kg$^{-1}$ divided by corn price $\$$ kg$^{-1}$) were used in the simulations: 5.44 (low), 6.56 (medium), and 7.67 (high).
+The three price ratios were selected by taking the 25%, 50%, and 75% quantile of the historical monthly price ratios from the years 1990 to 2022, where the historical corn prices were collected from the USDA-NASS, and nitrogen fertilizer prices were collected from the DTN website.
+The price ratio represents the relative nitrogen fertilizer price to corn price.
+For Figure \@ref(fig:pi-dif-dist) results, the recent period (June 2022) corn price of about $\$$ 0.28kg$^{-1}$ was used, which are corresponding to absolute nitrogen fertilizer prices of $\$$ 0.69kg$^{-1}$ (low), $\$$ 0.83kg$^{-1}$ (medium), and $\$$ 1.31kg$^{-1}$ (high).
+Using other corn prices will change the absolute sizes of profit difference.
+But since the optimal nitrogen rate ($\hat{N}^*$) calculation is only affected by the relative nitrogen-to-corn price ratio, the changes in the absolute sizes of profit difference will be proportional to the values in Figure \@ref(fig:pi-dif-dist), and the distribution shapes will not be affected.
+For example, if corn price used is 10% lower, the profit differences will also be 10% lower.
+
+*(The results part needs to be rewritten)*
+
 The distribution of the value of VRA from GWR-R is centered around 0, indicating that VRA based on GWR-R is on average no more profitable than SCAM-based URA.

### 2022-06-09 Codes/3_make_figures_publication.R

@@ -151,7 +151,7 @@ g_value <-
   geom_vline(data = mean_data, aes(xintercept = pi_diff), 
              color = "red", linetype = 8, size = 1) +
   geom_text(data = mean_data, color = "red",
-            aes(x = pi_diff + 10, y = 200,
+            aes(x = pi_diff + 5, y = 200,
                 label = paste0(round(pi_diff, 2))),
             angle = 0, hjust = -0.1, vjust = 0, size = 3 ) +
   facet_nested(pLabelName + pLabel ~ type,
@@ -238,7 +238,7 @@ g_bias <-
   geom_vline(data = mean_data, aes(xintercept = bias), 
              color = "red", linetype = 8, size = 1) +
   geom_text(data = mean_data, color = "red",
-            aes(x = bias, y = 200,
+            aes(x = bias + 10, y = 150,
                 label = paste0(round(bias, 2))),
             angle = 0, hjust = -0.1, vjust = 0, size = 3 ) +
   facet_nested(pLabelName + pLabel ~ type) +

### 2022-09-07 Writing/manuscript_gwr.rmd
manuscript updates according to the comments

--- 2022-05-27 Writing/manuscript_gwr.rmd
@@
     element_text(
-      size = 12, angle = 0, hjust = .5, vjust = -0.3, face = "plain"
+      size = 12, angle = 0, hjust = .5, vjust = -0.3, family = "Times"
     ),
@@
     element_text(
-      size = 12, angle = 90, hjust = .5, vjust = .9, face = "plain"
+      size = 12, angle = 90, hjust = .5, vjust = .9, family = "Times"
     ),
@@
     element_text(
-      size = 10, angle = 0, hjust = .5, vjust = 1.5, face = "plain"
+      size = 10, angle = 0, hjust = .5, vjust = 1.5, family = "Times"
     ),
@@
     element_text(
-      size = 10, angle = 0, hjust = 1, vjust = 0, face = "plain"
+      size = 10, angle = 0, hjust = 1, vjust = 0, family = "Times"
     ),
@@
     element_text(
-      size = 10, angle = 0, hjust = 0, vjust = 0, face = "plain"
+      size = 10, angle = 0, hjust = 0, vjust = 0, family = "Times"
     ),
@@
 The key objectives of this paper are two-fold.
-First, it evaluates two sets of functional-form specifications used by two recent published studies of site-specific input management that apply GWR to data from OFPE.
-We show that one set of functional-form specification performs significantly better than the other under three price scenarios observed historically.
-Second, we investigate the possibility of bias in estimating the "economic" value of site-specific recommendation maps based on GWR.
-We show that GWR suffers significant positive bias, which can lead to great over-estimation of the "economic" value of applying GWR methods.
-Our study is the first to systematically examine the "economic" properties of the use of GWR in OPFE settings.
+First, it evaluates economically the two sets of functional-form specifications used by two recent published studies of site-specific input management that apply GWR to data from OFPE.
+We show that the relative performance of the two approaches vary depending on the crop-fertilizer price ratios due to their tendency to over-/under-estimate EONR.
+Second and more important, we investigate the possibility of bias in estimating the economic value of site-specific recommendation maps based on GWR.
+We show that both GWR approaches suffer significant positive bias, which can lead to large over-estimation of the economic value of applying GWR methods.
+Our study is the first to systematically examine the economic (not statistical) properties of the use of GWR in OPFE settings.
 We reveal that in many circumstances using GWR is far less profitable than claimed by previous studies, which provides a necessary cautionary message to researchers who might otherwise “over-sell” to other researchers the value of using GWR methods in empirical work involving the estimation of site-specific input management.
@@
 In recent years, On-farm Precision Experimentation (OFPE) has gained traction with both researchers and practitioners as a means of generating high-resolution spatial data to inform site-specific crop input management decisions [@bullock2019data; @lacoste2021farm].
-Accompanying interest is surging among researchers in identifying efficient statistical methods to estimate site-specific yield response functions, which have examined various methods, ranging from Geographically Weighted Regression (GWR) [@rakshit2020; @evans2020assessment; @trevisan2021spatial] to machine learning methods including random forest [@krause2020random] and convolutional neural network [@barbosa2020modeling] approaches.
+Accompanying interest is surging among researchers in identifying efficient statistical methods to estimate site-specific yield response functions, which have examined various methods, ranging from Geographically Weighted Regression (GWR) [@rakshit2020; @evans2020assessment; @trevisan2021spatial] to machine learning methods including random forest [@krause2020random], convolutional neural network [@barbosa2020modeling], and causal forest [@kakimoto2022causal] approaches.
 Among these methods applied to OFPE data, GWR is distinct in that it does not require potentially costly collection of site-specific field and soil information in estimating site-specific yield response functions.
@@
 @trevisan2021spatial reported dramatic results, estimating an average potential gain of \$65 ha$^{-1}$ from applying seed and N at optimal uniform rates (instead of at the rates the farmers would have chosen if not participating in the research), and an additional potential gain of \$58 ha$^{-1}$ when changing from optimal uniform application rates to optimal site-specific application rates.
-This is rather surprising give the poor accuracy of GWR estimates [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation].
+This is rather surprising give the poor statistical accuracy of GWR estimates [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation].
 @rakshit2020 also applied GWR to on-farm experiment data.
@@
 
-Second, we will examine the degree and direction of bias in the estimation of the "economic" value of GWR-based variable rate application (VRA) and question the extremely high estimates of that value reported by @trevisan2021spatial (It is critical to keep in mind that it is not our objective at all to see the bias in the coefficient estimation by GWR, unlike [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation].
-Rather, we are interested in its economic implication in this study.).
-In general, researchers take the following steps to estimate the value of VRA based using OFPE data [e.g., @anselin2004spatial; @swinton1998evaluating; @bullock2002adding;  @liu2006site]: (1) estimate site-specific yield response functions based on a method chosen by the researcher; (2) use the estimated yield response functions to estimate the economically optimal site-specific input rates (EOIR) and economically optimal uniform input rates; (3) plug the estimated site-specific EOIRs and uniform EOIR into the estimated yield response functions to calculate estimated profits under both strategies; and (4) find the difference in the two strategies' estimated profits.
+Second, we will examine the degree and direction of bias in the estimation of the economic value of GWR-based variable rate application (VRA) and question the extremely high estimates of that value reported by @trevisan2021spatial.
+It is critical to keep in mind that it is not our objective at all to see the bias in the coefficient estimation by GWR, unlike [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation].
+Rather, we are interested in the economic implication of the statistical inaccuracy in estimating the coefficients of the model in this study.
+In general, researchers take the following steps to estimate the value of VRA using OFPE data [e.g., @anselin2004spatial; @swinton1998evaluating; @bullock2002adding; @liu2006site]: (1) estimate site-specific yield response functions based on a method chosen by the researcher; (2) use the estimated yield response functions to estimate the economically optimal site-specific input rates (EOIR) and economically optimal uniform input rates; (3) plug the estimated site-specific EOIRs and uniform EOIR into the estimated yield response functions to calculate estimated profits under both strategies; and (4) find the difference in the two strategies' estimated profits.
 However, this approach can result in significant bias in the estimation of the value of VRA because of the assumption made on step (3), which is that the estimated yield response functions are the true yield response functions.
@@
 
-In the following, we pursue the two objectives just described above by conducting Monte Carlo simulations in which we first generate and then analyze stylized OFPE data.
-We cannot test which model specification results in more profitable site-specific nitrogen rate recommendations using real data because it is impossible to observe the true yield response functions.
+In the following, we pursue the two objectives by conducting Monte Carlo simulations in which we first generate and then analyze stylized OFPE data.
+We cannot test which model specification results in more profitable site-specific nitrogen rate recommendations using real data because it is impossible to observe the true yield response functions using real-world data.
 For the same reason, we cannot test whether @trevisan2021spatial over-estimates the actual value of VRA, either.
 But in the Monte Carlo simulations we specify yield response functions and generate stylized data from those functions, which enables us to quantify in the context of the simulations the value of GWR and the bias in GWR-based estimation of the value of VRA.
-Monte Carlo simulations are commonly used in this way to gain insights into the statistical properties of trial designs and estimations methods [@mckinion2001analysis; @gebbers2010application; @bullock2020value; @alesso2021design].
+Monte Carlo simulations are commonly used in this way to gain insights into the statistical and economic properties of trial designs and estimations methods [@mckinion2001analysis; @gebbers2010application; @bullock2020value; @alesso2021design].
 
-One of the principal findings of this article is that the model specification used by @trevisan2021spatial creates more valuable information than does the model specification used by @rakshit2020 under usual corn and N fertilizer prices.
-This is primarily due to GWR's poor local estimation of the coefficients on $N^2$.
-Since the coefficients on $N^2$ is highly influential in determining site-specific EONR, inaccuracy in its estimation can result in significant economic loss.
-We also show that even under the method used by @trevisan2021spatial, the benefit of VRA over URA is rather small, averaging only about \$5 ha$^{-1}$; we conclude that both @rakshit2020 and @trevisan2021spatial significantly over-estimated that value.
+One of the principal findings of this article is that the model specification used by @trevisan2021spatial tends to outperforms that by @rakshit2020 when the ratio of nitrogen price to corn price is low (nitrogen is relatively cheap), but the relationship reverses when the price ratio is high.
+This is due the tendency of the specification by @trevisan2021spatial and @rakshit2020 to over- and under-estimate EONR, respectively.
+We also show that the benefit of VRA over URA is rather small irrespective of which specification to use, averaging only about \$5 ha$^{-1}$; we conclude that both @rakshit2020 and @trevisan2021spatial would significantly over-estimate that value.
 Our results suggest that the prospects of using GWR to generate site-specific input recommendations are bleaker than stated in @trevisan2021spatial.
+
+<span style = "color: blue;"> this needs to be rewritten </span>
 
@@
 
-To find the bias in estimating the value of VRA, the "estimated" profits of the SCAM-based URA and GWR-based VRA were calculated by plugging in the estimated optimal nitrogen rates into the cell-specific yield response functions estimated by GWR.
+To find the bias in estimating the value of VRA, the l rofitsof the SCAM-based URA and GWR-based VRA were calculated by plugging in the estimated optimal nitrogen rates into the cell-specific yield response functions estimated by GWR.
 Estimated per-ha net revenues for SCAM-based URA and GWR-based VRA are found as follows:
@@
 
-Figure \@ref(fig:pi-dif-dist) shows the distribution of $\hat{\Delta}_{gwr-m}$, profit difference between the GWR-based VRA and the SCAM-based URA.
-The distribution of the value of VRA from GWR-R is centered around 0, indicating that VRA based on GWR-R is on average no more profitable than SCAM-based URA.
-This result comes from GWR-R's highly inaccurate estimation of the subplot-level $N$ and $N^2$ coefficients, which led to unreliable subplot-specific nitrogen rate recommendations.
-Figure \@ref(fig:true-vs-estimated-coef-gwr-r) illustrates the accuracy of GWR-R in estimating the $N$ and $N^2$ coefficients in one simulation round.
-Estimates of the $N^2$ coefficients are positive for some subplots, indicating an increasing marginal product of the nitrogen rate, which contradicts a well-established agronomic property.
-The result is consistent with the bottom panel of Figure 12 in @rakshit2020 as well as the widely criticized poor coefficient estimation accuracy of GWR model in the literature [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation].
-Figure \@ref(fig:true-vs-estimated-optn-gwr-r) plots the estimated cell-specific optimal N against the true optimal N for the same simulation round, and again shows that GWR-R can be highly unreliable, and consequently that basing variable rate management on GWR-R may be no better than taking a simple URA approach.
-Basically, not enough information is available locally to estimate reliably the coefficients on both $N$ and $N^2$ by subplot.
+Figure \@ref(fig:pi-dif-dist) shows the distribution of $\Delta_{gwr-m}$, true profit difference between the GWR-based VRA and the SCAM-based URA, at various price scenarios.
+The comparative advantage of GWR-R and GWR-T varies significantly depending on nitrogen-corn price ratio.
+Specifically, GWR-R performs better as the price ratio increases (as nitrogen becomes more expensive relative to corn), while the opposite is the case for GWR-T.
+At the low price ratio of 4.16 and 5.44, VRA based on GWR-R is no better than SCAM-based URA.
+However, when the price ratio is $10.35$, the median benefit of GWR-R is `r round(mean_data_value[type == "GWR-R" & pLabel == "10.35", pi_diff], digits = 2)`.
+On the other hand, the median benefit of VRA based on GWR-T when the price ratio is 4.16 is `r round(mean_data_value[type == "GWR-T" & pLabel == "4.16", pi_diff], digits = 2)`, but the its benefit is even negative at `r round(mean_data_value[type == "GWR-T" & pLabel == "10.35", pi_diff], digits = 2)` when the price ratio is 10.35.
 
-The GWR-T approach, however, performed better than SCAM-URA in majority of cases, with some cases showing values-added exceeding \$10 ha$^{-1}$.
-This may seem surprising as the model estimated in the GWR-T approach is more restrictive than that in the GWR-R approach because the coefficient on $N^2$ is assumed to be global.
-However, unlike GWR-R, this restriction helps avoid estimating positive subplot-level coefficients on $N^2$.
-This result implies that the value of avoiding highly unreliable estimates of coefficients on $N^2$ subplot-specifically was greater than loss of local flexibility in the coefficients on $N^2$.
+Figure \@ref(fig:bias-est-eonr) provides insights into this phenomenon, which shows the distribution of average ratio of estimated EONR to true EONR.
+A value lower than 1 means EONR is underestimated on average.
+GWR-R tends to over-estimate EONR at lower price ratios, but the magnitude of over-estimation goes down as the price reatio goes up.
+The opposite trend is true for GWR-T.
+At the price ratio of 10.35, the degree of EONR over-estimation is quite significant.
+Since high-price ratio means nitrogen is relatively expensive, over-estimation of EONR hurts more economically compared to the cases with lower price ratios.
+
+Figure \@ref(fig:true-vs-estimated-optn-gwr-r) presents the estimated site-specific EONR plotted against true site-specific EONR by GWR approach for a single simulation round.
+Even though it is just for a single simulation round, it is illustrative in understanding the difference in GWR-R and GWR-T.
+Neither Site-specific EONR estimated by GWR-R is not very accurate, but inaccurate in a different manner.
+The range of EONR estimates by GWR-R is very wide due to the fact that the coefficient on $N^2$ is allowed to vary site specifically in GWR-R.
+Since the estimation of the coefficient on $N^2$ is highly inaccurate, the range of estimated EONR is much wider than the range of true site-specific EONR.
+On the contrary, GWR-T has a very narrow range of EONR estimates.
+This is due to the fact that the coefficient on $N^2$ is constrained to be the same for all the sites.
+Consequently, GWR-T fails to capture the true heterogeneity in EONR.
+Therefore, they fail to estimate site-specific EONR well for different reasons.
 
@@
 
-Next we examine the bias in the "estimated" value of GWR-based VRA that researchers would encounter using real data.
-Figure \@ref(fig:bias-est-pi) shows the distribution of the bias in "estimated" profit between the GWR-based VRA and SCAM-based URA.
-Unlike the true difference in profit, VRA based on GWR-R appears to perform overwhelmingly better, with its average profit about \$`r round(pi_dif_gwr, digits = 2)` ha$^{-1}$ greater than that of the SCAM-based URA.
+Next, we examine the bias in the estimated value of GWR-based VRA.
+Figure \@ref(fig:bias-est-pi) shows the distribution of the bias in the estimation of the value of GWR-based VRA over SCAM-based URA (profit difference between the GWR-based VRA and SCAM-based URA).
+For example, the value of 10 would mean that the estimated value of GWR-based VRA over-estimates its true value by $10 per ha.
+As the figure suggests, VRA based on GWR-R appears to perform overwhelmingly better than it truly is, presenting significant positive bias across the price range.
 That is, researchers would tend to significantly over-estimate the value of VRA based on GWR-R.
 When the GWR estimates are considered to define true yield response, the inaccuracy of GWR-R generates over-estimation of the heterogeneity of yield response within the field, which can lead to significant over-estimation of the value of GWR-R itself.
-Under GWR-T, the bias is more than \$10 ha$^{-1}$ for `r results[type == "GWR-T", mean(abs(bias) > 10)] * 100` % of the simulation cases: under GWR-R, that bias is greater than \$10 ha$^{-1}$ in `r results[type == "GWR-R", mean(abs(bias) > 10)] * 100` % of the simulated cases.
-However, as can be seen in the bottom panel of Figure \@ref(fig:bias-est-pi), the distribution of bias from GWR-T has a fatter tail than GWR-R with more mass on higher bias values.
-Bias is more than \$50 ha$^{-1}$ for `r results[type == "GWR-T", mean(abs(bias) > 50)] * 100` % of the simulation cases for GWR-T as opposed to `r results[type == "GWR-R", mean(abs(bias) > 50)] * 100` % for GWR-R.
 
-Figure \@ref(fig:why-bias-many) illustrates how over-estimations can occur.
+GWR-T exhibits a different pattern of bias.
+At low price ratios, GWR-T approach has smaller bias compared to GWR-R.
+This is partially because GWR-T tends to understate the heterogeneity of site-specific yield response function as we saw in figure \@ref(true-vs-estimated-optn-gwr-r).
+As the price ratio goes up, bias becomes greater.
+This is due to significant over-estimation of EONR by GWR-T as we saw in figure \@ref(fig:bias-est-eonr).
+Unlike the GWR-R approach, the distribution of the bias by the GWR-T approach has a fat tail, indicating that there is a greater chance of encountering large positive bias in the value of VRA over URA.
+
+Figure \@ref(fig:why-bias-many) illustrates how over-estimation of the value of VRA can occur.
 It shows yield response functions estimated by GWR-T and estimated yields associated with the GWR-based EONR rates and SCAM-based EONR rates for 50 randomly chosen cells in a single simulation.
-Since GWR-based EONRs were obtained assuming the yield response functions estimated by GWR, by construction they out-perform better the SCAM-based estimates in every cell.
+Since GWR-based EONRs were obtained assuming the yield response functions estimated by GWR, they out-perform the SCAM-based estimates in every cell by construction.
 For many cells, the SCAM-based estimated EONR is significantly higher than the actual yield-maximizing N rate, resulting in a yield far lower because of the quadratic functional form assumption.
@@
 Based on the true profit response curve, applying the GWR-based recommendation is about \$`r round(- true_yield_data[type != "True", diff(profit)], digits = 0)` ha$^{-1}$ more profitable than applying the SCAM-based recommendation.
-This profit differential comes soley from the difference in nitrogen cost since GWR and SCAM yields are equal.
+This profit differential comes solely from the difference in nitrogen cost since GWR and SCAM yields are equal.
 However, if calculations are based on the cell's GWR-based estimation of the response function, profits from the GWR-based recommendation are measured to be about \$`r round(- point_data_gwr[, diff(profit)], digits = 0)` ha$^{-1}$ greater than from the SCAM-based recommendation.
@@
 
-Our simulation results show the basic GWR model (GWR-R) has little economic value for site-specific $R_xs$.
-The GWR-R based VRA is on average no more profitable than SCAM-based URA under historically common price scenarios.
+Our simulation results show the basic GWR model (GWR-R) tends to have little economic value for site-specific $R_xs$.
+The GWR-R based VRA is on average no more profitable than SCAM-based URA under many price scenarios particularly when nitrogen price is relatively low compared to corn price.
 This finding reveals the economic consequences of the widely recognized statistical inaccuracy issue of GWR estimation [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation], and in agreement with the previous critique that GWR should be used as an exploratory tool rather than an inferential tool [@wheeler2005multicollinearity; @paez2011simulation].
@@
 Another solution is to extend the parametric GWR approaches to a semi-parametric or non-parametric GWR where the yield response functions are estimated without assuming particular functional forms (like SCAM).
-However, such a method is likely to encounter a very similar problem to that faced by GWR-R: insufficient information available locally to estimate reliably the shape of yield response curve locally.
-It is also noted that the recently developed multiscale GWR model [@fotheringham2017multiscale; @yu2020inference; @comber2022route] allows the bandwidth to be derived separately for each covariate in the model, which would potentially improve the performances of GWR estimates and be incorporated into future research.
-Please note, however, that multiscale GWR models are not necessary in out simulations as we have only one covaraite ($N$) in our simulations.
+However, such a method may well encounter a very similar problem to that faced by GWR-R: insufficient information available locally to estimate reliably the shape of yield response curve locally.
+It is also noted that the recently developed multi-scale GWR model [@fotheringham2017multiscale; @yu2020inference; @comber2022route] allows the bandwidth to be derived separately for each covariate in the model, which would potentially improve the performances of GWR estimates and be incorporated into future research.
+Please note, however, that multi-scale GWR models are not necessary in our simulations as we have only one covariate ($N$) in our simulations.
 
-It is important to be aware that researchers need to be extremely cautious about their estimated value of VRA based on GWR whether they follow GWR-R or GWR-T.
+Most important, it is crucial to be aware that researchers need to be extremely cautious about their estimated value of VRA based on GWR whether they follow GWR-R or GWR-T.
 Our results show that it is likely that they will over-estimate their true values and the bias can be misleadingly high at the non-negligible probability.
@@
 This article examined the economic value of GWR-based VRA and the bias in its estimation in the context of OFPE.
-We showed that restricting the coefficient on $N^2$ to a global parameter as done in @trevisan2021spatial leads to site-specific nitrogen rate recommendations with higher profits compared to the specification used by @rakshit2020, which allows the coefficients on $N^2$ to vary locally.
-However, we also found that both specifications can result in significant over-estimation of the true value of GWR-based site-specific nitrogen rate recommendations.
+We showed that VRA based on GWR provides small economic benefits over URA based on SCAM.
+The relative performance of the model specifications used by @trevisan2021spatial and @rakshit2020 differs based on nitrogen-corn price ratio.
+Finally and most important, we found that both specifications can result in significant over-estimation of the true value of GWR-based site-specific nitrogen rate recommendations.
 It can be concluded that researchers need to be cautious about promoting the GWR-based approach in VRA recommendation.
@@
 
-```{r, fig.id = "pi-dif-dist", fig.cap = "The value of GWR-based VRA over SCAM-based URA for GWR-R and GWR-T"}
+```{r, fig.id = "pi-dif-dist", fig.cap = "The value of GWR-based VRA over SCAM-based URA for GWR-R and GWR-T", fig.height = 5, fig.width = 6}
 g_value
@@
 
-```{r fig.id = "true-vs-estimated-coef-gwr-r", fig.cap = "Comparison of Estimated and True Coefficients"}
+```{r fig.id = "true-vs-estimated-coef-gwr-r", fig.cap = "Comparison of Estimated and True Coefficients", eval = F}
 g_comp_coef
@@
 
-```{r fig.id = "bias-est-pi", fig.cap = "Bias in the estimation of the value of GWR-based VRA over SCAM-based URA for GWR-R and GWR-T"}
+```{r fig.id = "bias-est-eonr", fig.cap = "Average bias in the estimation of EONR by GWR-R and GWR-T", fig.height = 5, fig.width = 6}
+g_eonr_bias
+```
+
+```{r fig.id = "bias-est-pi", fig.cap = "Bias in the estimation of the value of GWR-based VRA over SCAM-based URA for GWR-R and GWR-T", fig.height = 5, fig.width = 6}
 g_bias

### 2022-09-07 Codes/2_post_sim_analysis.R

@@ -28,7 +28,7 @@ library(here)
 setwd(here())
 
 #* Load functions
-fs::dir_ls(here("Codes", "Functions"), full.names = TRUE) %>%
+fs::dir_ls(here("GitControlled/Codes/Functions"), full.names = TRUE) %>%
   lapply(., function(x) source(x))
 
 # /*===========================================================
@@ -36,13 +36,13 @@ fs::dir_ls(here("Codes", "Functions"), full.names = TRUE) %>%
 # /*===========================================================
 
 #* load generated parameters
-field_data <- readRDS(here("Data/field_data.rds"))
-field_with_design <- readRDS(here("Data/field_with_design.rds"))
-field_parameters <- readRDS(here("Data/field_parameters.rds"))
+field_data <- readRDS(here("Shared/Data/field_data.rds"))
+field_with_design <- readRDS(here("Shared/Data/field_with_design.rds"))
+field_parameters <- readRDS(here("Shared/Data/field_parameters.rds"))
 
 #* cell-level true data (sprange=600 scenario)
 cell_data <- field_parameters %>%
-rowwise() %>%
+  rowwise() %>%
   # === match cell_id and aunit_id ===#
   mutate(
     field_pars = list(
@@ -61,7 +61,7 @@ rowwise() %>%
 # cell_data <- cell_data[field_dt[, .(cell_id, aunit_id)], on = "cell_id"]
 
 #* load simulation results data
-mc_sim_results <- readRDS(file = here("Results/mc_sim_results.rds"))
+mc_sim_results <- readRDS(file = here("Shared/Results/mc_sim_results.rds"))
 
 #* aunit-level estimated data
 ## -------------------------------------
@@ -80,7 +80,7 @@ est_data <-
   unnest(sim_results) %>%
   rowwise()
 
-
+saveRDS(est_data, here("Shared/Results/est_data.rds"))
 
 # /*===========================================================
 #' # Profitability Calculation
@@ -95,11 +95,12 @@ for (i in 1:nrow(est_data)) {
   cell_data_i <-
     cell_data %>%
     filter(field_col == est_data[i, ]$field_col) %>%
-    pull(field_pars) %>% .[[1]]
-  
-  econ_data_ls[[i]] <- 
+    pull(field_pars) %>%
+    .[[1]]
+
+  econ_data_ls[[i]] <-
[…]

### 2022-09-07 Codes/3_make_figures_publication.R

@@ -138,27 +138,76 @@ g_exp <-
 # results <- readRDS(here("Shared/Results/pi_data.rds"))%>%
 #   .[, type := ifelse(transfer == 0, "GWR-R", "GWR-T")]
 
-mean_data <- 
+mean_data_value <-
   results %>%
-  .[, .(pi_diff = mean(pi_diff)),
-    by=c("field_col", "pLabel", "type")] %>%
+  .[, .(pi_diff = median(pi_diff)),
+    by = c("field_col", "pLabel", "type")
+  ] %>%
   print()
 
 g_value <-
   results %>%
   ggplot(data = .) +
-  geom_histogram(aes(x = pi_diff), fill = NA, color = "black") +
-  geom_vline(data = mean_data, aes(xintercept = pi_diff), 
-             color = "red", linetype = 8, size = 1) +
-  geom_text(data = mean_data, color = "red",
-            aes(x = pi_diff, y = 200,
-                label = paste0("mean = ", round(pi_diff, 2))),
-            angle = 0, hjust = -0.1, vjust = 0, size = 3 ) +
+  geom_histogram(
+    aes(x = pi_diff),
+    fill = NA,
+    color = "blue",
+    bins = 50,
+    size = 0.2
+  ) +
+  geom_vline(
+    data = mean_data_value,
+    aes(xintercept = pi_diff),
+    color = "red",
+    size = 0.5
+  ) +
+  geom_text(
+    data = mean_data_value, color = "red",
+    aes(
+      x = ifelse(pi_diff < 65, pi_diff + 5, pi_diff - 20), y = 150,
+      label = paste0("Median = ", round(pi_diff, 2))
+    ),
+    angle = 0, hjust = -0.1, vjust = 0, size = 3
+  ) +
   facet_grid(pLabel ~ type) +
   scale_y_continuous(expand = c(0, 0)) +
+  scale_x_continuous(breaks = 20 * (-2:3), limits = c(-45, 60)) +
   xlab("The value of VRA over URA ($ per ha)") +
   ylab("Number of Simulation Cases")
 
+
+# /*===========================================================
+#' # EONR estimation tendency
+# /*===========================================================
+
+# ggplot(est_data) +
+# geom_histogram(aes(x = opt_N_scam)) +
+# facet_grid(round(pN, digits = 2) ~ .)
+
+est_data <-
[…]

### 2022-09-07 Writing/manuscript_gwr.rmd

@@
 Estimated per-ha net revenues for SCAM-based URA and GWR-based VRA are found as follows:
+To find the bias in estimating the value of VRA, the "estimated" profits of the SCAM-based URA and GWR-based VRA were calculated by plugging in the estimated optimal nitrogen rates into the cell-specific yield response functions estimated by GWR.
+Estimated per-ha net revenues for SCAM-based URA and GWR-based VRA are found as follows:
 

### 2022-09-07 Writing/manuscript_gwr.rmd
finalized manuscript for PA

--- 2022-09-07 Writing/manuscript_gwr.rmd
@@
 library(patchwork)
+library(ggplot2)
 ```
@@
 ```{r include = FALSE}
+#| include: false
+
 # /*===========================================================
@@
   .[, type := ifelse(transfer == 0, "GWR-R", "GWR-T")] %>%
-  .[, bias := pi_diff_est - pi_diff]
-
-pi_dif_gwr <-
-  results[, .(pi_dif = mean(pi_diff)), by = type] %>%
-  .[, diff(pi_dif)]
+  .[, bias := pi_diff_est - pi_diff] %>%
+  # only display the 25% (5.44), 50% (6.56), 75% (7.67) price ratio
+  .[pRatio %in% c(5.44, 6.56, 7.67), ] %>%
+  # === label price ratio
+  .[, pLabelName := "Price Ratio (N/corn)"] %>%
+  .[pRatio == 5.44, pLabel := "Low"] %>%
+  .[pRatio == 6.56, pLabel := "Middle"] %>%
+  .[pRatio == 7.67, pLabel := "High"] %>%
+  .[, pLabel := factor(pLabel, levels = c("Low", "Middle", "High"))]
 
 #* create figures
-source(here("GitControlled", "Codes", "3_make_figures_publication.R"))
+source(here("GitControlled/Codes/3_make_figures_publication.R"))
 ```
@@
 
-To find the bias in estimating the value of VRA, the l rofitsof the SCAM-based URA and GWR-based VRA were calculated by plugging in the estimated optimal nitrogen rates into the cell-specific yield response functions estimated by GWR.
+To find the bias in estimating the value of VRA, the estimated profits of the SCAM-based URA and GWR-based VRA were calculated by plugging in the estimated optimal nitrogen rates into the cell-specific yield response functions estimated by GWR.
 Estimated per-ha net revenues for SCAM-based URA and GWR-based VRA are found as follows:
@@
 A value lower than 1 means EONR is underestimated on average.
-GWR-R tends to over-estimate EONR at lower price ratios, but the magnitude of over-estimation goes down as the price reatio goes up.
+GWR-R tends to over-estimate EONR at lower price ratios, but the magnitude of over-estimation goes down as the price ratio goes up.
 The opposite trend is true for GWR-T.
@@
 As the price ratio goes up, bias becomes greater.
-This is due to significant over-estimation of EONR by GWR-T as we saw in figure \@ref(fig:bias-est-eonr).
+This is due to the significant over-estimation of EONR by GWR-T as we saw in figure \@ref(fig:bias-est-eonr).
 Unlike the GWR-R approach, the distribution of the bias by the GWR-T approach has a fat tail, indicating that there is a greater chance of encountering large positive bias in the value of VRA over URA.

### 2022-09-07 Codes/2_post_sim_analysis.R

@@ -34,13 +34,14 @@ fs::dir_ls(here("GitControlled", "Codes", "Functions"), full.names = TRUE) %>%
 # /*===========================================================
 #' # Load simulated data
 # /*===========================================================
-
 #* load generated parameters
+field_data <- readRDS(here("Shared/Data/field_data.rds"))
+field_with_design <- readRDS(here("Shared/Data/field_with_design.rds"))
+field_parameters <- readRDS(here("Shared/Data/field_parameters.rds"))
 
 #* cell-level true data (sprange=600 scenario)
 cell_data <- field_parameters %>%
   rowwise() %>%
-rowwise() %>%
   # === match cell_id and aunit_id ===#
   mutate(
     field_pars = list(
@@ -59,6 +60,7 @@ rowwise() %>%
 # cell_data <- cell_data[field_dt[, .(cell_id, aunit_id)], on = "cell_id"]
 
 #* load simulation results data
+mc_sim_results <- readRDS(file = here("Shared/Results/mc_sim_results.rds"))
 
 #* aunit-level estimated data
 ## -------------------------------------
@@ -97,12 +99,8 @@ for (i in 1:nrow(est_data)) {
     .[[1]]
 
   econ_data_ls[[i]] <-
-    pull(field_pars) %>% .[[1]]
-  
-  econ_data_ls[[i]] <- 
     est_data[i, ] %>%
     rowwise() %>%
-    rowwise() %>% 
     # === merge est data (aunit) with true pars (cell) ===#
     mutate(
       data = list(
@@ -125,7 +123,7 @@ for (i in 1:nrow(est_data)) {
           .[, yield_opt := gen_yield_QP(b0, b1, b2, Nk, opt_N)] %>%
           .[, pi_opt := pCorn * yield_opt - pN * opt_N] %>%
           ## ======based on true response parameters======##
-          ##======based on true response parameters======##
+          ## ======based on true response parameters======##
           #--- SCAM ---#
           .[, yield_scam := gen_yield_QP(b0, b1, b2, Nk, opt_N_scam)] %>%
           .[, pi_scam := pCorn * yield_scam - pN * opt_N_scam] %>%
@@ -137,7 +135,7 @@ for (i in 1:nrow(est_data)) {
           #--- GWR gain over SCAM ---#
[…]

### 2022-10-05 Writing/manuscript_gwr.rmd
manuscript finalized for PA submission

@@
 
-**Abstract**: Geographically weighted regression (GWR) has been presented as a prominent tool to estimate site-specific yield response functions to generate site-specific input rate recommendations using data generated by on-farm precision experimentation (OFPE).
+**Abstract**: Geographically weighted regression (GWR) has been presented as a prominent tool to estimate site-specific yield response functions to derive site-specific input rate recommendations from data generated by on-farm precision experimentation (OFPE).
 The key objectives of this paper are two-fold.
-First, it evaluates economically the two sets of functional-form specifications used by two recent published studies of site-specific input management that apply GWR to data from OFPE.
+The first objective is to evaluate economically the two sets of functional-form specifications used by two recent published studies of site-specific input management that apply GWR to data from OFPE.
 We show that the relative performance of the two approaches vary depending on the crop-fertilizer price ratios due to their tendency to over-/under-estimate EONR.
-Second and more important, we investigate the possibility of bias in estimating the economic value of site-specific recommendation maps based on GWR.
+The second and more important, we investigate the possibility of bias in estimating the economic value of site-specific recommendation maps based on GWR.
 We show that both GWR approaches suffer significant positive bias, which can lead to large over-estimation of the economic value of applying GWR methods.
@@
 
-**Acknowledgement**: This research was supported by a USDA-NIFA-AFRI Food Security Program Coordinated Agricultural Project, titled “Using Precision Technology in On-farm Field Trials to Enable Data-Intensive Fertilizer Management,” (Accession Number 2016-68004-24769), and also by the a USDA-NRCS Conservation Innovation Grant from the On-farm Trials Program, titled “Improving the Economic and Ecological Sustainability of US Crop Production through On-Farm Precision Experimentation” (Award Number NR213A7500013G021).
+**Acknowledgements**: This research was supported by a USDA-NIFA-AFRI Food Security Program Coordinated Agricultural Project, titled “Using Precision Technology in On-farm Field Trials to Enable Data-Intensive Fertilizer Management,” (Accession Number 2016-68004-24769), and also by the a USDA-NRCS Conservation Innovation Grant from the On-farm Trials Program, titled “Improving the Economic and Ecological Sustainability of US Crop Production through On-Farm Precision Experimentation” (Award Number NR213A7500013G021), and by USDA NIFA's Hatch Project 470-362.
 
@@
 
-In recent years, On-farm Precision Experimentation (OFPE) has gained traction with both researchers and practitioners as a means of generating high-resolution spatial data to inform site-specific crop input management decisions [@bullock2019data; @lacoste2021farm].
-Accompanying interest is surging among researchers in identifying efficient statistical methods to estimate site-specific yield response functions, which have examined various methods, ranging from Geographically Weighted Regression (GWR) [@rakshit2020; @evans2020assessment; @trevisan2021spatial] to machine learning methods including random forest [@krause2020random], convolutional neural network [@barbosa2020modeling], and causal forest [@kakimoto2022causal] approaches.
+In recent years, on-farm precision experimentation (OFPE) has gained traction with both researchers and practitioners as a means of generating high-resolution spatial data to inform site-specific crop input management decisions [@bullock2019data; @lacoste2021farm].
+Accompanying interest is surging among researchers in identifying efficient statistical methods to estimate site-specific yield response functions, which have examined various methods, ranging from Geographically Weighted Regression (GWR) [@rakshit2020; @evans2020assessment; @trevisan2021spatial] to machine learning methods, including the random forest [@krause2020random], convolutional neural network [@barbosa2020modeling], and causal forest [@kakimoto2022causal] approaches.
 Among these methods applied to OFPE data, GWR is distinct in that it does not require potentially costly collection of site-specific field and soil information in estimating site-specific yield response functions.
@@
 However, deploying sophisticated sensors to gather field characteristics data is also costly, and the effects of their generation and use on farming profitability remains in question [@gardner2021economic].
-Recognizing the significant costs of obtaining useful, high-resolution soil and field properties data, @trevisan2021spatial demonstrated a method of providing site specific management recommendations without such data.
-The study estimated site-specific yield response functions by applying GWR techniques on data from OFPEs [@bullock2019data].
-@trevisan2021spatial reported dramatic results, estimating an average potential gain of \$65 ha$^{-1}$ from applying seed and N at optimal uniform rates (instead of at the rates the farmers would have chosen if not participating in the research), and an additional potential gain of \$58 ha$^{-1}$ when changing from optimal uniform application rates to optimal site-specific application rates.
-This is rather surprising give the poor statistical accuracy of GWR estimates [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation].
+Recognizing the significant costs of obtaining useful, high-resolution soil and field properties data, @trevisan2021spatial demonstrated a method of providing site-specific management recommendations without such data.
+They estimated site-specific yield response functions by applying GWR techniques on data from OFPEs [@bullock2019data], and reported dramatic results, estimating an average potential gain of \$65 ha$^{-1}$ from applying seed and N at optimal uniform rates (instead of at the rates the farmers would have chosen if not participating in the research), and an additional potential gain of \$58 ha$^{-1}$ when changing from optimal uniform application rates to optimal site-specific application rates.
+This is rather surprising given the often-reported poor statistical accuracy of GWR estimates [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation].
 @rakshit2020 also applied GWR to on-farm experiment data.
-However, while they did estimate site-specific yield response functions, they did not derive site-specific economically optimal nitrogen rates based on them, and thus did not conduct economic analysis unlike @trevisan2021spatial.
+However, while they did estimate site-specific yield response functions, they did not derive site-specific economically optimal nitrogen rates based on them, and thus did not conduct economic analysis, unlike @trevisan2021spatial.
 @evans2020assessment explored using GWR with a linear model specification to detect low- and high-response areas, but like @rakshit2020, they also did not estimate site-specific economically optimal nitrogen rates.
@@
 The first is to determine which of the model specifications used by @rakshit2020 and @trevisan2021spatial result in more profitable $R_xs$.
-While both @rakshit2020 and @trevisan2021spatial proposed using GWR to estimate site-specific yield response functions, they use different model specifications.
-Both assume a quadratic response of yield to nitrogen rate ($N$).
-However, while @trevisan2021spatial estimate the coefficient on $N^2$ as a global parameter, @rakshit2020 estimate it locally for each point.
+While both @rakshit2020 and @trevisan2021spatial proposed using GWR to estimate site-specific yield response functions, they used different model specifications.
+Both assumed a quadratic response of yield to nitrogen rate ($N$).
+However, while @trevisan2021spatial estimated the coefficient on $N^2$ as a global parameter, @rakshit2020 estimated it locally for each point.
 At first, it appears that the specification used by @rakshit2020 is superior since it is more flexible than the specification used by @trevisan2021spatial.
@@
 Second, we will examine the degree and direction of bias in the estimation of the economic value of GWR-based variable rate application (VRA) and question the extremely high estimates of that value reported by @trevisan2021spatial.
-It is critical to keep in mind that it is not our objective at all to see the bias in the coefficient estimation by GWR, unlike [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation].
-Rather, we are interested in the economic implication of the statistical inaccuracy in estimating the coefficients of the model in this study.
-In general, researchers take the following steps to estimate the value of VRA using OFPE data [e.g., @anselin2004spatial; @swinton1998evaluating; @bullock2002adding; @liu2006site]: (1) estimate site-specific yield response functions based on a method chosen by the researcher; (2) use the estimated yield response functions to estimate the economically optimal site-specific input rates (EOIR) and economically optimal uniform input rates; (3) plug the estimated site-specific EOIRs and uniform EOIR into the estimated yield response functions to calculate estimated profits under both strategies; and (4) find the difference in the two strategies' estimated profits.
-However, this approach can result in significant bias in the estimation of the value of VRA because of the assumption made on step (3), which is that the estimated yield response functions are the true yield response functions.
-@trevisan2021spatial provide an example.
-At step (3), they used their estimated GWR as the true yield response functions.
-This assumption is generally unavoidable for researchers since they cannot observe any real field's true yield response function of any real field.
-Use of these procedures assumes accurate estimation of yield response functions, which when untrue can result in significant bias in the estimation of the value of VRA.
+It is critical to keep in mind that it is not our objective to measure the bias in the coefficient estimation by GWR, unlike [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation].
+Rather, we are interested in the economic implications of the statistical inaccuracy in estimating the coefficients of the model in this study.
+In general, researchers take the following steps to estimate the value of VRA using OFPE data [e.g., @anselin2004spatial; @swinton1998evaluating; @bullock2002adding; @liu2006site]: (1) estimate site-specific yield response functions based on a method chosen by the researcher; (2) use the estimated yield response functions to estimate the economically optimal site-specific input rates (EOIRs) and economically optimal uniform input rates; (3) plug the estimated site-specific EOIRs and uniform EOIR into the estimated yield response functions to calculate estimated profits under both strategies; and (4) find the difference in the two strategies' estimated profits.
+However, this approach can result in significant bias in the estimation of the value of VRA because of the step 3's assumption that the estimated yield response functions are the true yield response functions.
+@trevisan2021spatial provided an example at step (3) by assuming that their GWR estimates provided "true" site-specific yield response functions.
+This assumption is generally unavoidable for researchers since they cannot observe any real field's true site-specific yield response functions.
+But, inaccurate estimation in this methodology can result in significant bias in the estimation of the value of VRA.
 This bias problem can be particularly severe when the method used tends to exaggerate the true heterogeneity in yield response functions.
@@
 This is due the tendency of the specification by @trevisan2021spatial and @rakshit2020 to over- and under-estimate EONR, respectively.
-We also show that the benefit of VRA over URA is rather small irrespective of which specification to use, averaging only about \$5 ha$^{-1}$; we conclude that both @rakshit2020 and @trevisan2021spatial would significantly over-estimate that value.
+We also show that the benefit of VRA over URA is rather small irrespective of the specification used, averaging only about \$5 ha$^{-1}$; we conclude that both @rakshit2020 and @trevisan2021spatial may have significantly over-estimated that value.
 Our results suggest that the prospects of using GWR to generate site-specific input recommendations are bleaker than stated in @trevisan2021spatial.
@@
 
-Figure \@ref(fig:field-layout) shows the field layout and defines the spatial units of the simulated on-farm precision experiments in this study.
-The basic spatial unit of the field is the 6m $\times$ 6m "cell", which is the resolution at which the field characteristics data (i.e., parameters of the "true" yield response function) were allowed to vary.
+Figure \@ref(fig:field-layout) shows the simulated field's layout and defines the spatial units of the simulated on-farm precision experiments in this study.
+The basic spatial unit of the field is a 6m $\times$ 6m "cell", which is the resolution at which the field characteristics data (i.e., parameters of the "true" yield response function) were allowed to vary.
 It was assumed, however, that yields could not be monitored at such a high resolution.
@@
 An extensive literature examines the choice of functional form in yield response estimation [@cerrato1990comparison, @frank1990comparison, @bullock1994quadratic, @tembo2008crop].
-In this study, each cell $(j, k)$'s "true" yield response function is assumed to follow the quadratic-plateau functional form, which is one of the most commonly used functional forms:
+Out simulation assume that each cell $(j, k)$'s "true" yield response function is assumed to follows the commonly-used quadratic-plateau functional form:
 
@@
 where $c_{j,k} = (\alpha_{j,k},\beta_{j,k},\gamma_{j,k},\tau_{j,k})$ is the vector of yield response function parameters.
-$\tau_{j,k}$ can be interpreted as the critical value of N rate at which cell $(j, k)$'s yield reaches the plateau level (i.e., where yield no longer increases with additional N fertilizer).
+$\tau_{j,k}$ can be interpreted as the critical value of N rate at which cell $(j, k)$'s yield reaches its plateau, where yield no longer increases with N rate.
 $\varepsilon_{j, k}$ is a stochastic error term.
-The quadratic-plateau functional form implies a diminishing marginal product of N and a yield plateau, which are desirable properties for a yield response function [@frank1990comparison].
-It is a widely observed corn nitrogen response pattern by existing agronomic studies.
+The quadratic-plateau functional form implies a diminishing marginal product of N until a yield plateau, which are desirable properties for a yield response function [@frank1990comparison] and a pattern commonly observed in agronomic studies.
 Note that the cell-specific yield response function $f_{j, k} (N)$ is the reduced form of the meta response function $f$ when the characteristics vector takes on the value $c_{j, k}$.
@@
 The nugget value of zero means that infinitesimally close observations have a zero covariance (i.e., they are identical).
-The range of 600m means that observations separated by more than 600m are not spatially correlated.
+The range of 600m means that observations separated by more than 600m are spatially uncorrelated.
 A higher range value indicates increased spatial dependence, meaning less abrupt differences are observed between the production function parameters of neighboring cells.
-The mean and sill variance of each parameter were specified to result in a realistic mean yield of $11,416$ kg ha$^{-1}$, and such that the cells' true economically optimal N rate ranged from $113$ kg ha$^{-1}$ to $273$ kg ha$^{-1}$ among all the simulations, which most real-world N rate recommendations fall into [e.g., @sawyer2018].
+The mean and sill variance of each parameter were specified to result in a realistic mean yield of $11,416$ kg ha$^{-1}$, and such that the cells' true economically optimal N rate ranged from $113$ kg ha$^{-1}$ to $273$ kg ha$^{-1}$ among all the simulations, a range into which most real-world N rate recommendations fall [e.g., @sawyer2018].
 Note that the range of the optimal N rates of individual rounds of simulations are narrower.
@@
 
-The GWR-R model is simply the basic GWR model [@fotheringham1996geography; @brunsdon1999some; @fotheringham2003geographically], where yield response was modeled as subplot-specific quadratic functions of the nitrogen rate, which for each subplot $j \in {1, 2, \dots, 1440}$ was specified as,
+The GWR-R model is simply the basic GWR model [@fotheringham1996geography; @brunsdon1999some; @fotheringham2003geographically], where subplot-specific yield responses were modeled as quadratic functions of the nitrogen rate, which for each subplot $j \in {1, 2, \dots, 1440}$ was specified as,
 
-$$y_j= \alpha_j+ \beta_j N_j + \eta_j N_j^2+ \epsilon_j .$$
+$$y_j= \alpha_j+ \beta_j N_j + \eta_j N_j^2+ \epsilon_j, \;\; j \in 1, 2, \dots, 1440.$$
 
@@
 
-$$\hat{N}_{gwr-r,j}^{*} \equiv argmax_N⁡[p\hat{f}_{gwr-r, j} (N) -wN] .$$
+$$\hat{N}_{gwr-r,j}^{*} \equiv argmax_N⁡[p\hat{f}_{gwr-r, j} (N) -wN], \;\; j \in 1, 2, \dots, 1440.$$
 
@@
 
-The GWR-T model is also named as “mixed” GWR in the literature [@brunsdon1999some] where some parameters are fixed globally while others vary geographically.
+The GWR-T model is also called as “mixed” GWR in the literature [@brunsdon1999some], where some parameters are fixed globally while others vary geographically.
 In our model, the coefficient on $N^2$ was estimated as a global parameter while the coefficient on $N$ was estimated subplot-specifically.
@@
 
-To estimate the bias in the estimation of the economic value of GWR-based VRA, the true per-ha net revenues ("profits") of the SCAM-based URA and GWR-based VRA were calculated by plugging in the estimated optimal nitrogen rates into the "true" yield response functions.
+To estimate the bias in the estimation of the economic value of GWR-based VRA, the true per-ha net revenues ("profits") of the SCAM-based URA and GWR-based VRA were calculated by substituting the estimated optimal nitrogen rates into the "true" yield response functions.
 Profits from the SCAM approach were
@@
 
-To find the bias in estimating the value of VRA, the estimated profits of the SCAM-based URA and GWR-based VRA were calculated by plugging in the estimated optimal nitrogen rates into the cell-specific yield response functions estimated by GWR.
+To find the bias in estimating the value of VRA, the profits of the SCAM-based URA and GWR-based VRA were calculated by substituting the estimated optimal nitrogen rates into the cell-specific yield response functions estimated by GWR.
 Estimated per-ha net revenues for SCAM-based URA and GWR-based VRA are found as follows:
@@
 
-Figure \@ref(fig:pi-dif-dist) shows the distribution of $\Delta_{gwr-m}$, true profit difference between the GWR-based VRA and the SCAM-based URA, at various price scenarios.
+Figure \@ref(fig:pi-dif-dist) shows the distribution of $\Delta_{gwr-m}$, the true profit difference between the GWR-based VRA and the SCAM-based URA, at various price scenarios.
 The comparative advantage of GWR-R and GWR-T varies significantly depending on nitrogen-corn price ratio.
@@
 
-Figure \@ref(fig:bias-est-eonr) provides insights into this phenomenon, which shows the distribution of average ratio of estimated EONR to true EONR.
+Figure \@ref(fig:bias-est-eonr) provides insights into this phenomenon, showing the distribution of the average ratio of estimated EONR to true EONR.
 A value lower than 1 means EONR is underestimated on average.
@@
 At the price ratio of 10.35, the degree of EONR over-estimation is quite significant.
-Since high-price ratio means nitrogen is relatively expensive, over-estimation of EONR hurts more economically compared to the cases with lower price ratios.
+Since a high-price ratio means nitrogen is relatively expensive, the economic cost of over-estimation of EONR increases with the price ratio.
 
-Figure \@ref(fig:true-vs-estimated-optn-gwr-r) presents the estimated site-specific EONR plotted against true site-specific EONR by GWR approach for a single simulation round.
-Even though it is just for a single simulation round, it is illustrative in understanding the difference in GWR-R and GWR-T.
-Neither Site-specific EONR estimated by GWR-R is not very accurate, but inaccurate in a different manner.
-The range of EONR estimates by GWR-R is very wide due to the fact that the coefficient on $N^2$ is allowed to vary site specifically in GWR-R.
-Since the estimation of the coefficient on $N^2$ is highly inaccurate, the range of estimated EONR is much wider than the range of true site-specific EONR.
-On the contrary, GWR-T has a very narrow range of EONR estimates.
-This is due to the fact that the coefficient on $N^2$ is constrained to be the same for all the sites.
-Consequently, GWR-T fails to capture the true heterogeneity in EONR.
-Therefore, they fail to estimate site-specific EONR well for different reasons.
+To illustrate the difference in the GWR-R and GWR-T outcomes, Figure \@ref(fig:true-vs-estimated-optn-gwr-r) presents for a single simulation round the estimated site-specific EONR plotted against the true site-specific EONR.
+The site-specific EONR estimates are both inaccurate, but differently inaccurate.
+The range of EONR estimates by GWR-R is very wide because the coefficient on $N^2$ is allowed to vary site specifically in GWR-R.
+Since the estimation of the coefficient on $N^2$ is highly inaccurate, the range of estimated EONRs is much wider than the range of true site-specific EONR.
+But, GWR-T's range of EONR estimates is very narrow because the coefficient on $N^2$ is constrained to be equal across sites, making GWR-T fail to capture the EONR's true heterogeneity.
 
@@
 Next, we examine the bias in the estimated value of GWR-based VRA.
-Figure \@ref(fig:bias-est-pi) shows the distribution of the bias in the estimation of the value of GWR-based VRA over SCAM-based URA (profit difference between the GWR-based VRA and SCAM-based URA).
+Figure \@ref(fig:bias-est-pi) shows the distribution of the bias in the estimation of the profit difference from GWR-based VRA and SCAM-based URA (profit difference between the GWR-based VRA and SCAM-based URA).
 For example, the value of 10 would mean that the estimated value of GWR-based VRA over-estimates its true value by $10 per ha.
@@
 GWR-T exhibits a different pattern of bias.
-At low price ratios, GWR-T approach has smaller bias compared to GWR-R.
-This is partially because GWR-T tends to understate the heterogeneity of site-specific yield response function as we saw in figure \@ref(true-vs-estimated-optn-gwr-r).
-As the price ratio goes up, bias becomes greater.
-This is due to the significant over-estimation of EONR by GWR-T as we saw in figure \@ref(fig:bias-est-eonr).
-Unlike the GWR-R approach, the distribution of the bias by the GWR-T approach has a fat tail, indicating that there is a greater chance of encountering large positive bias in the value of VRA over URA.
+At low price ratios, the GWR-T approach has smaller bias compared to GWR-R.
+This is partially because GWR-T tends to understate the heterogeneity of site-specific yield response function as was seen in figure \@ref(true-vs-estimated-optn-gwr-r).
+As the price ratio rises, bias increases.
+This is due to the significant over-estimation of EONR by GWR-T, as illustrated by figure \@ref(fig:bias-est-eonr).
+Unlike the GWR-R approach, the distribution of the bias by the GWR-T approach has a fat tail, indicating that there is a greater chance of encountering large positive bias in the estimated value of VRA over URA.
 
@@
 It shows yield response functions estimated by GWR-T and estimated yields associated with the GWR-based EONR rates and SCAM-based EONR rates for 50 randomly chosen cells in a single simulation.
-Since GWR-based EONRs were obtained assuming the yield response functions estimated by GWR, they out-perform the SCAM-based estimates in every cell by construction.
-For many cells, the SCAM-based estimated EONR is significantly higher than the actual yield-maximizing N rate, resulting in a yield far lower because of the quadratic functional form assumption.
+Since GWR-based EONRs were obtained assuming the yield response functions estimated by GWR, by construction they out-perform the SCAM-based estimates in every cell.
+For many cells, the SCAM-based estimated EONR is significantly higher than the actual yield-maximizing N rate, resulting in an estimated yield far lower because of the quadratic functional form assumption.
 Figure \@ref(fig:why-bias-single) focuses on a single cell and compares estimated and true yields between GWR and SCAM (panel (a)) and estimated and true profits between GWR and SCAM (panel (b)).
-The cell's true yield response functions plateaus at a nitrogen rate of about $140$ kg ha$^{-1}$, but the GWR-estimated yield response function suggests that yield should peak at a nitrogen rate of about $190$ kg ha$^{-1}$ and then yield declines afterward.
+The cell's true yield response functions plateaus at a nitrogen rate of about $140$ kg ha$^{-1}$, but the GWR-estimated yield response function suggests that yield should peak at a nitrogen rate of about $190$ kg ha$^{-1}$ and thereafter decline.
 In reality, the yield differential between GWR and SCAM is 0, while the estimated yield differential is about $0.25$ ton ha$^{-1}$, leading to the over-estimation of the value of GWR in panel (b).
@@
 This profit differential comes solely from the difference in nitrogen cost since GWR and SCAM yields are equal.
-However, if calculations are based on the cell's GWR-based estimation of the response function, profits from the GWR-based recommendation are measured to be about \$`r round(- point_data_gwr[, diff(profit)], digits = 0)` ha$^{-1}$ greater than from the SCAM-based recommendation.
+However, if calculations are based on the cell's GWR-based estimation of the response function, profits from the GWR-based recommendation are measured to exceed those from the SCAM-based recommendation by about \$`r round(- point_data_gwr[, diff(profit)], digits = 0)` ha$^{-1}$.
 Beyond the difference in nitrogen cost, the falsely estimated yield boost by GWR contributes to the profit differential, thus significantly over-estimating the actual value of GWR.
@@
 
-Our simulation results show the basic GWR model (GWR-R) tends to have little economic value for site-specific $R_xs$.
-The GWR-R based VRA is on average no more profitable than SCAM-based URA under many price scenarios particularly when nitrogen price is relatively low compared to corn price.
-This finding reveals the economic consequences of the widely recognized statistical inaccuracy issue of GWR estimation [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation], and in agreement with the previous critique that GWR should be used as an exploratory tool rather than an inferential tool [@wheeler2005multicollinearity; @paez2011simulation].
+Our simulation results show that generating site-specific $R_x$s by applying the basic GWR model (GWR-R) to OFPE data tends to have little economic value for site-specific $R_x$s.
+The GWR-R based VRA is on average no more profitable than SCAM-based URA under many price scenarios, particularly when nitrogen price is relatively low compared to the corn price.
+This finding reveals the economic consequences of the widely recognized statistical inaccuracy issue of GWR estimation [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation], and is in agreement with previous critiques concluding that GWR should be used as an exploratory tool rather than an inferential tool [@wheeler2005multicollinearity; @paez2011simulation].
 Precision agriculture practitioners should be cautious when using GWR for site-specific $R_xs$.
@@
 
-An obvious cause of the GWR models' poor economic performances in this work is the quadratic functional form used in GWR that differs from the true quadratic-plateau yield response functions.
+An obvious cause of the GWR models' poor economic performances in this work is that their assumed quadratic functional form of yield response differs from the true quadratic-plateau yield response functions.
 One solution could be to upgrade to nonlinear GWR models.
@@
 Another solution is to extend the parametric GWR approaches to a semi-parametric or non-parametric GWR where the yield response functions are estimated without assuming particular functional forms (like SCAM).
-However, such a method may well encounter a very similar problem to that faced by GWR-R: insufficient information available locally to estimate reliably the shape of yield response curve locally.
+However, such a method may well encounter a very similar problem to that faced by GWR-R: insufficient information available locally to estimate reliably the shape of local yield response curves.
 It is also noted that the recently developed multi-scale GWR model [@fotheringham2017multiscale; @yu2020inference; @comber2022route] allows the bandwidth to be derived separately for each covariate in the model, which would potentially improve the performances of GWR estimates and be incorporated into future research.
@@
 
-Most important, it is crucial to be aware that researchers need to be extremely cautious about their estimated value of VRA based on GWR whether they follow GWR-R or GWR-T.
-Our results show that it is likely that they will over-estimate their true values and the bias can be misleadingly high at the non-negligible probability.
-Extremely high values of VRA reported in @trevisan2021spatial are likely to have reflected this bias.
-Indeed, the bias problem we raised here is likely to be observed for other statistical methods because the bias comes from the assumption that the _estimated_ yield response functions are true.
+Most important, whether using GWR-R or GWR-R, researchers must be cautious about their estimated value of VRA.
+Our results show that it is likely that they will over-estimate their true values and the bias can be misleadingly high with non-negligible probability.
+The extremely high values of VRA reported in @trevisan2021spatial are likely to have reflected this bias.
+Indeed, the bias problem we have raised here is likely to be observed for other statistical methods because the bias comes from the assumption that the _estimated_ yield response functions are true.
 Whatever the underlying statistical method for yield response functions may be, researchers are likely to overestimate the true value of their methods.
@@
 This article examined the economic value of GWR-based VRA and the bias in its estimation in the context of OFPE.
-We showed that VRA based on GWR provides small economic benefits over URA based on SCAM.
-The relative performance of the model specifications used by @trevisan2021spatial and @rakshit2020 differs based on nitrogen-corn price ratio.
+We showed that VRA based on GWR provides only small economic benefits over URA based on SCAM.
+The relative performances of the model specifications used by @trevisan2021spatial and @rakshit2020 differs based on nitrogen-corn price ratio.
 Finally and most important, we found that both specifications can result in significant over-estimation of the true value of GWR-based site-specific nitrogen rate recommendations.
-It can be concluded that researchers need to be cautious about promoting the GWR-based approach in VRA recommendation.
+It can be concluded that researchers need to be cautious about promoting the GWR-based approach to VRA recommendation.
 

### 2023-02-13 Writing/manuscript_gwr.rmd
manuscript ready to send
add citations

@@
 The first objective is to evaluate economically the two sets of functional-form specifications used by two recent published studies of site-specific input management that apply GWR to data from OFPE.
-We show that the relative performance of the two approaches vary depending on the crop-fertilizer price ratios due to their tendency to over-/under-estimate EONR.
+We show that the relative performance of the two approaches vary depending on the crop-fertilizer price ratios due to their tendency to over-/under-estimate EONR (**perhaps use the full name of EONR here**).
 The second and more important, we investigate the possibility of bias in estimating the economic value of site-specific recommendation maps based on GWR.
@@
 
+Precision agriculture (also known as site-specific farming, or variable-rate technology) is a management strategy that adjusts farm management decisions according to the spatial and temporal variability of soil and crop conditions within a field.
+Over the past few decades, numerous technological innovations have been made in collecting detailed field information (e.g., yield mapping, soil sampling, remote sensing, etc.) and developing site-specific management recommendations based on the information.
+However, the long-standing question of whether the economic benefit of precision agriculture can offset the technology and information costs [@lowenberg1996revolution; @weiss1996precision] remains difficult to answer, particularly in the context of large-scale production systems [@mcfadden2022information].
+
 In recent years, on-farm precision experimentation (OFPE) has gained traction with both researchers and practitioners as a means of generating high-resolution spatial data to inform site-specific crop input management decisions [@bullock2019data; @lacoste2021farm].
@@
 
-On any given field, it is typical for U.S.
+(**I feel we are talking too much about the soil sampling data; maybe we can make this paragraph more concise**) On any given field, it is typical for U.S.
 Midwestern row crop farmers to pay for 1-ha grid soil sampling and chemical analysis every three or four years [@morris2018strengths].
@@
 Therefore, the yield data's resolution was 18m $\times$ 12m (3 cells $\times$ 2 cells, called a "subplot").
-The N rate unit consisted of five "subplots", that is, 18m $\times$ 72m (3 cells $\times$ 12 cells, called a "plot") to accommodate the variable-rate applicator's application resolution.
-A 12m "transition zone" was placed between two plots (that is, a 6m "transition zone" on each end of a plot), so that when the experimental N rate changed, the harvester had 12 m to "clear" and begin to record accurately on a plot with an N rate different from its predecessor's.
+The N rate unit consisted of five (**it should be six**) "subplots", that is, 18m $\times$ 72m (3 cells $\times$ 12 cells, called a "plot") to accommodate the variable-rate applicator's application resolution.
+A 12m "transition zone" was placed between two plots (that is, a 6m "transition zone" on each end of a plot), so that when the experimental N rate changed, the harvester had 12m to "clear" and begin to record accurately on a plot with an N rate different from its predecessor's.
 
 The field was 432m (72 cells) wide and 864m (144 cells) long, making its area 37.3 ha.
-Data from the 6-m-wide headlands, side-lands (there are no transition zones on the north and south ends of the field), and 12-m-wide "transition zones" were not included in the data analyzed.
+Data from the 6-m-wide (**is it wide or long?**) headlands, side-lands (there are no transition zones on the north and south ends of the field), and 12-m-wide "transition zones" were not included in the data analyzed.
 In total there were 1440 subplots available for experimental data analysis.
@@
 An extensive literature examines the choice of functional form in yield response estimation [@cerrato1990comparison, @frank1990comparison, @bullock1994quadratic, @tembo2008crop].
-Out simulation assume that each cell $(j, k)$'s "true" yield response function is assumed to follows the commonly-used quadratic-plateau functional form:
+Our simulation assume that each cell $(j, k)$'s "true" yield response function is assumed to follow the commonly-used quadratic-plateau functional form:
 
@@
 
-```{r fig.id = "true-vs-estimated-coef-gwr-r", fig.cap = "Comparison of Estimated and True Coefficients", eval = F}
+```{r fig.id = "true-vs-estimated-coef-gwr-r", fig.cap = "Comparison of Estimated and True Coefficients"}
 g_comp_coef

### 2023-02-13 Writing/manuscript_gwr.rmd
manuscript for JAAEA

@@
 The key objectives of this paper are two-fold.
-The first objective is to evaluate economically the two sets of functional-form specifications used by two recent published studies of site-specific input management that apply GWR to data from OFPE.
-We show that the relative performance of the two approaches vary depending on the crop-fertilizer price ratios due to their tendency to over-/under-estimate EONR (**perhaps use the full name of EONR here**).
+The first is to economically evaluate the two sets of functional-form specifications used by two recent published studies of site-specific input management that apply GWR to data from OFPE.
+We show that the relative performance of the two approaches vary depending on the crop-fertilizer price ratios due to their tendency to over-/under-estimate the economically optimal nitrogen rate.
 The second and more important, we investigate the possibility of bias in estimating the economic value of site-specific recommendation maps based on GWR.
@@
 
-(**I feel we are talking too much about the soil sampling data; maybe we can make this paragraph more concise**) On any given field, it is typical for U.S.
+On any given field, it is typical for U.S.
 Midwestern row crop farmers to pay for 1-ha grid soil sampling and chemical analysis every three or four years [@morris2018strengths].
@@
 At first, it appears that the specification used by @rakshit2020 is superior since it is more flexible than the specification used by @trevisan2021spatial.
-However, the flexibility can be a disadvantage rather than an advantage because the estimation of EONR is highly sensitive to the coefficient estimates on $N^2$, and GWR often provides inaccurate local estimation of that coefficient.
+However, the flexibility can be a disadvantage rather than an advantage because the estimation of economically optimal nitrogen rate (EONR) is highly sensitive to the coefficient estimates on $N^2$, and GWR often provides inaccurate local estimation of that coefficient.
 
@@
 Therefore, the yield data's resolution was 18m $\times$ 12m (3 cells $\times$ 2 cells, called a "subplot").
-The N rate unit consisted of five (**it should be six**) "subplots", that is, 18m $\times$ 72m (3 cells $\times$ 12 cells, called a "plot") to accommodate the variable-rate applicator's application resolution.
+The N rate unit consisted of five "subplots", that is, 18m $\times$ 72m (3 cells $\times$ 12 cells, called a "plot") to accommodate the variable-rate applicator's application resolution.
 A 12m "transition zone" was placed between two plots (that is, a 6m "transition zone" on each end of a plot), so that when the experimental N rate changed, the harvester had 12m to "clear" and begin to record accurately on a plot with an N rate different from its predecessor's.
@@
 The field was 432m (72 cells) wide and 864m (144 cells) long, making its area 37.3 ha.
-Data from the 6-m-wide (**is it wide or long?**) headlands, side-lands (there are no transition zones on the north and south ends of the field), and 12-m-wide "transition zones" were not included in the data analyzed.
+Data from the 6-m-long headlands, side-lands (there are no transition zones on the north and south ends of the field), and 12-m-wide "transition zones" were not included in the data analyzed.
 In total there were 1440 subplots available for experimental data analysis.

### 2023-04-22 Writing/manuscript_gwr.rmd
minor edit

--- 2023-02-13 Writing/manuscript_gwr.rmd
@@
 
-Precision agriculture (also known as site-specific farming, or variable-rate technology) is a management strategy that adjusts farm management decisions according to the spatial and temporal variability of soil and crop conditions within a field.
+Precision agriculture is a management strategy that adjusts farm management decisions according to the spatial and temporal variability of soil and crop conditions within a field.
 Over the past few decades, numerous technological innovations have been made in collecting detailed field information (e.g., yield mapping, soil sampling, remote sensing, etc.) and developing site-specific management recommendations based on the information.

### 2023-05-06 Writing/manuscript_gwr.rmd
change in introduction

@@
 **Abstract**: Geographically weighted regression (GWR) has been presented as a prominent tool to estimate site-specific yield response functions to derive site-specific input rate recommendations from data generated by on-farm precision experimentation (OFPE).
-The key objectives of this paper are two-fold.
-The first is to economically evaluate the two sets of functional-form specifications used by two recent published studies of site-specific input management that apply GWR to data from OFPE.
-We show that the relative performance of the two approaches vary depending on the crop-fertilizer price ratios due to their tendency to over-/under-estimate the economically optimal nitrogen rate.
-The second and more important, we investigate the possibility of bias in estimating the economic value of site-specific recommendation maps based on GWR.
+However, the current application of GWR in this context assumes quadratic yield response function even though many of the yield-input relationships has been shown to be better represeted by the quadratic-plateau functional form.
+This is due to lack of readily available methods and satistical packages that allow researchers to estimate non-linear model undet the GWR framework, including quadratic-plateau.
+The key objective of this paper is to investigate the possibility of bias in estimating the economic value of site-specific recommendation maps based on GWR with quadratic functional form assumption when in reality the true underlying yield-input relationship is quadratic-plateau.
+We consider two sets of functional-form specifications used by two recent published studies of site-specific input management that apply GWR to data from OFPE.
 We show that both GWR approaches suffer significant positive bias, which can lead to large over-estimation of the economic value of applying GWR methods.
-Our study is the first to systematically examine the economic (not statistical) properties of the use of GWR in OPFE settings.
 We reveal that in many circumstances using GWR is far less profitable than claimed by previous studies, which provides a necessary cautionary message to researchers who might otherwise “over-sell” to other researchers the value of using GWR methods in empirical work involving the estimation of site-specific input management.
@@
 They estimated site-specific yield response functions by applying GWR techniques on data from OFPEs [@bullock2019data], and reported dramatic results, estimating an average potential gain of \$65 ha$^{-1}$ from applying seed and N at optimal uniform rates (instead of at the rates the farmers would have chosen if not participating in the research), and an additional potential gain of \$58 ha$^{-1}$ when changing from optimal uniform application rates to optimal site-specific application rates.
-This is rather surprising  given the often-reported poor statistical accuracy of GWR estimates [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation].
+This is rather surprising given the often-reported poor statistical accuracy of GWR estimates [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation] and also much lower value of VRA over URA reported in previous studies (cite).
 @rakshit2020 also applied GWR to on-farm experiment data.
@@
 
-This study has two key objectives.
-The first is to determine which of the model specifications used by @rakshit2020 and @trevisan2021spatial result in more profitable $R_xs$.
+While the results reported by @trevisan2021spatial look rosy and GWR looks like a promising method, there are two potentially dangerous factors that may have
+
 While both @rakshit2020 and @trevisan2021spatial proposed using GWR to estimate site-specific yield response functions, they used different model specifications.
@@
 We suspect that the high value of VRA estimated by @trevisan2021spatial displays this bias.
+Another layer of potential bias in using GWR is
 

### 2023-05-08 Codes/2_post_sim_analysis.R
update: GWR simulations with kernel choices

@@ -59,8 +59,14 @@ cell_data <- field_parameters %>%
 # field_dt <- field_parameters$field_sf[[1]] %>% data.table()
 # cell_data <- cell_data[field_dt[, .(cell_id, aunit_id)], on = "cell_id"]
 
+
 #* load simulation results data
-mc_sim_results <- readRDS(file = here("Shared/Results/mc_sim_results.rds"))
+#*************************************
+# choose the kernel used for GWR from:
+#   "gaussian", "bisquare", "exponential", "tricube", "boxcar"
+#*************************************
+kernel_choice = "boxcar"
+mc_sim_results <- readRDS(here("Shared", "Results", kernel_choice, "mc_sim_results.rds"))
 
 #* aunit-level estimated data
 ## -------------------------------------
@@ -79,7 +85,7 @@ est_data <-
   unnest(sim_results) %>%
   rowwise()
 
-saveRDS(est_data, here("Shared/Results/est_data.rds"))
+saveRDS(est_data, here("Shared", "Results", kernel_choice, "est_data.rds"))
 
 
 # /*===========================================================
@@ -180,7 +186,8 @@ pi_data <-
     levels = str_sort(unique(pRatio), numeric = TRUE)
   )]
 
-saveRDS(pi_data, here("Shared/Results/pi_data.rds"))
+saveRDS(pi_data, here("Shared", "Results", kernel_choice, "pi_data.rds"))
+
 
 # /*===========================================================
 #' # Find an illustrative sim case for overestimation
@@ -208,7 +215,7 @@ il_data_oe <-
   .[sim == sim_id, ] %>%
   .[transfer == 1, ]
 
-saveRDS(il_data_oe, here("Shared/Results/il_data_oe.rds"))
+saveRDS(il_data_oe, here("Shared", "Results", kernel_choice, "il_data_oe.rds"))
 
 # /*===========================================================
 #' # Find extreme cases of simulation results
@@ -241,7 +248,7 @@ sim_id <-
 # === sim=644 seems to have the worst predicted N results ===#
 aunit_sim_single <- aunit_results[sim == sim_id, ]
 
-saveRDS(aunit_sim_single, here("Shared/Results/aunit_sim_single.rds"))
+saveRDS(aunit_sim_single, here("Shared", "Results", kernel_choice, "aunit_sim_single.rds"))
 
 # === single simulation results graphing ===#
 {

### 2023-05-08 Codes/3_figures.R

@@ -1,349 +1,0 @@
-# /*===========================================================
-#' # Visualization the field and spatial units
-# /*===========================================================
-# fig.id = "field-layout", 
-# fig.cap = "Simulated field layout with spatial unit definitions", 
-# fig.dim = c(6, 6)
-
-field_with_design <- readRDS(here("Data/field_with_design.rds"))
-field_sf <- field_with_design[1, ]$field_sf[[1]]
-
-plot_sf <-
-  field_sf %>%
-  nest_by(plot_id) %>%
-  mutate(data = list(
-    st_union(data)
-  )) %>%
-  unnest() %>%
-  st_as_sf()
-
-block_sf <-
-  field_sf %>%
-  nest_by(block_id) %>%
-  mutate(data = list(
-    st_union(data)
-  )) %>%
-  unnest() %>%
-  st_as_sf()
-
-block_text_sf <- st_centroid(block_sf)
-
-#* Field: plots and blocks
-g_field <-
-  ggplot() +
-  geom_sf(data = plot_sf, size = 0.2, fill = NA) +
-  geom_sf(data = filter(plot_sf, plot_id == 264), fill = "red", alpha = 0.5) +
-  geom_sf(data = block_sf, fill = NA, size = 1.5) +
-  annotate("text", x = 830, y = 74, label = "plot", color = "red", size = 5) +
-  geom_segment(
-    aes(x = 830, xend = 830, y = 30, yend = -80),
-    arrow = arrow(length = unit(0.5, "cm")),
-    size = 1,
-    color = "red"
-  ) +
-  geom_sf_text(
-    data = block_text_sf,
-    aes(label = paste0("block ", block_id)),
-    size = 5
-  ) +
-  theme_void() +
-  ggtitle("Panel (a): Plots and blocks in an experimental field")
-
-## inside a plot
-plot_sf_focus <- filter(field_sf, plot_id == 1)
-
-subplot_sf <-
-  plot_sf_focus %>%
-  nest_by(aunit_id, buffer) %>%
-  mutate(data = list(
-    st_union(data)
-  )) %>%
-  unnest() %>%
-  st_as_sf() %>%
-  mutate(label = ifelse(
-    buffer == 1,
-    "buffer",
[…]

### 2023-05-08 Codes/3_make_figures_publication.R

@@ -135,9 +135,6 @@ g_exp <-
 # fig.id = "pi-dif-dist",
 # fig.cap = "The value of GWR-based VRA over SCAM-based URA for GWR-R and GWR-T"
 
-# results <- readRDS(here("Shared/Results/pi_data.rds"))%>%
-#   .[, type := ifelse(transfer == 0, "GWR-R", "GWR-T")]
-
 mean_data_value <-
   results %>%
   .[, .(pi_diff = median(pi_diff)),

### 2023-05-08 Codes/0_data_preparation.R
update (cont'd): new files or files with new names

@@ -1,0 +1,170 @@
+
+
+#'  This file creates simulated on-farm experiments, and estimates site-specific
+#'  yield response coefficients by GWR model.
+
+
+
+## ==============================================================
+##                          Preparation                        =
+## ==============================================================
+
+rm(list = ls())
+
+
+# === Packages ===#
+library(sp)
+library(spdep)
+library(spatialreg)
+library(sf)
+library(raster)
+library(data.table)
+library(tidyverse)
+library(dplyr)
+library(magrittr)
+library(gstat)
+library(GWmodel)
+library(scam)
+library(mgcv)
+library(magic)
+library(stringr)
+library(ggplot2)
+library(tictoc)
+library(here)
+options(stringsAsFactors = FALSE)
+
+
+
+# === Set working directory ===#
+setwd(here())
+
+# === load functions ===#
+#* source all the functions in the Functions folder
+fs::dir_ls(here("GitControlled", "Codes", "Functions"), full.names = TRUE) %>%
+    lapply(., function(x) source(x))
+
+
+# /*===========================================================
+#' # Create a field
+# /*===========================================================
+# ! Define field and plot characteristics here
+
+field_data <-
+    # ! This is where you set the experiment parameters
+    CJ(
+        plot_length = 12, # the length of a plot (in number of cells)
+        plot_width = 3, # the width of a plot (in number of cells)
+        cell_buffer = 1,
+        aunit_length = 2, # the length of an analysis unit (in number of cells)
+        aunit_width = 3, # the width of an analysis unit (in number of cells)
+        cell = 6, # the length of a cell in meter
+        #* how wide the field is
+        field_col = c(144), # the number of cell columns
+        #* how tall the field is
+        field_row = 72, # the number of row columns
+        sp_range = c(600),
+        gstat_model = "Sph"
+    ) %>%
+    rowwise() %>%
+    mutate(
+        field_sf = list(
+            make_field(
+                field_col = field_col,
+                field_row = field_row,
+                aunit_length = aunit_length,
+                aunit_width = aunit_width,
+                cell = cell,
+                cell_buffer = cell_buffer
+            )
+        ),
+        #* price ratio scenarios
+        pCorn = 7 / 25.4, # $/kg
+        pRatio_ls = list(c(4.16, 5.44, 6.56, 7.67, 10.35))
+    )
+
+#* save the fields
+saveRDS(field_data, here("Shared/Data/field_data.rds"))
[…]

### 2023-05-08 Codes/3_figures_illustrate.R

@@ -1,0 +1,431 @@
+
+
+#'  Illustrate and play around with the graphs of simulation results.
+#'  The final figures are knitted by the 3_make_figures_publication
+
+## ==============================================================
+##                          Preparation                        =
+## ==============================================================
+
+rm(list = ls())
+
+# === Packages ===#
+library(sp)
+library(spdep)
+library(spatialreg)
+library(sf)
+library(raster)
+library(data.table)
+library(tidyverse)
+library(dplyr)
+library(magrittr)
+library(gstat)
+library(GWmodel)
+library(scam)
+library(mgcv)
+library(magic)
+library(stringr)
+library(ggplot2)
+library(tictoc)
+library(here)
+options(stringsAsFactors = FALSE)
+
+# === Set working directory ===#
+setwd(here())
+
+
+
+# choose the kernel used for GWR
+# choice: "gaussian", "bisquare", "exponential", "tricube", "boxcar"
+kernel_choice = "gaussian"
+
+# load estimation results
+results <-
+    here("Shared", "Results", kernel_choice, "pi_data.rds") %>%
+    readRDS() %>%
+    .[, type := ifelse(transfer == 0, "GWR-R", "GWR-T")] %>%
+    .[, bias := pi_diff_est - pi_diff] %>%
+    # only display the 25% (5.44), 50% (6.56), 75% (7.67) price ratio
+    .[pRatio %in% c(5.44, 6.56, 7.67), ] %>%
+    # === label price ratio
+    .[, pLabelName := "Price Ratio (N/corn)"] %>%
+    .[pRatio == 5.44, pLabel := "Low"] %>%
+    .[pRatio == 6.56, pLabel := "Middle"] %>%
+    .[pRatio == 7.67, pLabel := "High"] %>%
+    .[, pLabel := factor(pLabel, levels = c("Low", "Middle", "High"))]
+
+# /*===========================================================
+#' # The value of GWR-based VRA over SCAM-based URA for GWR-R and GWR-T
+# /*===========================================================
+# fig.id = "pi-dif-dist",
+# fig.cap = "The value of GWR-based VRA over SCAM-based URA for GWR-R and GWR-T"
+
+mean_data_value <-
+    results %>%
[…]

### 2023-05-10 Writing/manuscript_gwr.rmd

@@
 We reveal that in many circumstances using GWR is far less profitable than claimed by previous studies, which provides a necessary cautionary message to researchers who might otherwise “over-sell” to other researchers the value of using GWR methods in empirical work involving the estimation of site-specific input management.
+We encourage the statistical community to extend the current GWR capability by allowing researchers to model yield-inpute response more flexibly than currently possible.
 
@@
 In recent years, on-farm precision experimentation (OFPE) has gained traction with both researchers and practitioners as a means of generating high-resolution spatial data to inform site-specific crop input management decisions [@bullock2019data; @lacoste2021farm].
-Accompanying interest is surging among researchers in identifying efficient statistical methods to estimate site-specific yield response functions, which have examined various methods, ranging from Geographically Weighted Regression (GWR) [@rakshit2020; @evans2020assessment; @trevisan2021spatial] to machine learning methods, including the random forest [@krause2020random], convolutional neural network [@barbosa2020modeling], and causal forest [@kakimoto2022causal] approaches.
+Accompanying interest is surging among researchers in identifying efficient statistical methods to estimate site-specific yield response functions, which have examined various methods, ranging from Geographically Weighted Regression (GWR) [@rakshit2020; @evans2020assessment; @trevisan2021spatial] to machine learning methods, including the random forest [@krause2020random, @de2023predicting], convolutional neural network [@barbosa2020modeling], and causal forest [@kakimoto2022causal] approaches.
 Among these methods applied to OFPE data, GWR is distinct in that it does not require potentially costly collection of site-specific field and soil information in estimating site-specific yield response functions.
@@
 
-While the results reported by @trevisan2021spatial look rosy and GWR looks like a promising method, there are two potentially dangerous factors that may have
+While the results reported by @trevisan2021spatial look rosy and GWR looks like a promising method, there are two potentially dangerous factors that may have caused them to snigificantly over-estimate the value of GWR as a tool to estimate site-specific EONR.
+First, they used quadratic functionl form in their GWR estimation even though it is widely accepted by scientific community that corn yield reseponse to nitrogen is better approximated by quadratic-plateau functional form.
+It is likely that their choice of quadratic functional form is merely a compromise because there did (does) not exist any statistical software of package that implements GWR with quadratic-plateau functional form.
+Second source of over-estimation bias is endemic to any study that evaluates the value of variable rate application, not just @trevisan2021spatial.
+In general, researchers take the following steps to estimate the value of VRA using OFPE data [e.g., @anselin2004spatial; @swinton1998evaluating; @bullock2002adding; @liu2006site]: (1) estimate site-specific yield response functions based on a method chosen by the researcher; (2) use the estimated yield response functions to estimate the economically optimal site-specific input rates (EOIRs) and economically optimal uniform input rates; (3) plug the estimated site-specific EOIRs and uniform EOIR into the estimated yield response functions to calculate estimated profits under both strategies; and (4) find the difference in the two strategies' estimated profits.
+However, this approach can result in significant bias in the estimation of the value of VRA because of the step 3's assumption that the estimated yield response functions are the true yield response functions.
+@trevisan2021spatial provided an example at step (3) by assuming that their GWR estimates provided "true" site-specific yield response functions.
+This assumption is generally unavoidable for researchers since they cannot observe any real field's true site-specific yield response functions.
+But, inaccurate estimation of yield response function in this methodology can result in significant bias in the estimation of the value of VRA.
+This bias problem can be particularly severe when the method used tends to exaggerate the true heterogeneity in yield response functions, such as GWR.
 
-While both @rakshit2020 and @trevisan2021spatial proposed using GWR to estimate site-specific yield response functions, they used different model specifications.
+The primary obejctive of this study is examine the degree and direction of bias in the estimation of the economic value of GWR-based variable rate application (VRA) when GWR model is specified as quadratic when the true yield response function follows the quadratic-plateau functional form.
+We evaluate two sets of GWR quadratic specifications used in @rakshit2020 and @trevisan2021spatial.
 Both assumed a quadratic response of yield to nitrogen rate ($N$).
@@
 However, the flexibility can be a disadvantage rather than an advantage because the estimation of economically optimal nitrogen rate (EONR) is highly sensitive to the coefficient estimates on $N^2$, and GWR often provides inaccurate local estimation of that coefficient.
-
-Second, we will examine the degree and direction of bias in the estimation of the economic value of GWR-based variable rate application (VRA) and question the extremely high estimates of that value reported by @trevisan2021spatial.
 It is critical to keep in mind that it is not our objective to measure the bias in the coefficient estimation by GWR, unlike [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation].
 Rather, we are interested in the economic implications of the statistical inaccuracy in estimating the coefficients of the model in this study.
-In general, researchers take the following steps to estimate the value of VRA using OFPE data [e.g., @anselin2004spatial; @swinton1998evaluating; @bullock2002adding; @liu2006site]: (1) estimate site-specific yield response functions based on a method chosen by the researcher; (2) use the estimated yield response functions to estimate the economically optimal site-specific input rates (EOIRs) and economically optimal uniform input rates; (3) plug the estimated site-specific EOIRs and uniform EOIR into the estimated yield response functions to calculate estimated profits under both strategies; and (4) find the difference in the two strategies' estimated profits.
-However, this approach can result in significant bias in the estimation of the value of VRA because of the step 3's assumption that the estimated yield response functions are the true yield response functions.
-@trevisan2021spatial provided an example at step (3) by assuming that their GWR estimates provided "true" site-specific yield response functions.
-This assumption is generally unavoidable for researchers since they cannot observe any real field's true site-specific yield response functions.
-But, inaccurate estimation in this methodology can result in significant bias in the estimation of the value of VRA.
-This bias problem can be particularly severe when the method used tends to exaggerate the true heterogeneity in yield response functions.
-We suspect that the high value of VRA estimated by @trevisan2021spatial displays this bias.
-Another layer of potential bias in using GWR is
+As part of identifying bias in the estimation of the economic value of VRA based on the GWR approaches, we evaluate their actual values.
+Finally, we also evaluate their relative performances compared to URA based on shape-constrained additive model approach.
 
-In the following, we pursue the two objectives by conducting Monte Carlo simulations in which we first generate and then analyze stylized OFPE data.
+We pursue the objective by conducting Monte Carlo simulations in which we first generate and then analyze stylized OFPE data.
 We cannot test which model specification results in more profitable site-specific nitrogen rate recommendations using real data because it is impossible to observe the true yield response functions using real-world data.
@@
 
-One of the principal findings of this article is that the model specification used by @trevisan2021spatial tends to outperforms that by @rakshit2020 when the ratio of nitrogen price to corn price is low (nitrogen is relatively cheap), but the relationship reverses when the price ratio is high.
-This is due the tendency of the specification by @trevisan2021spatial and @rakshit2020 to over- and under-estimate EONR, respectively.
-We also show that the benefit of VRA over URA is rather small irrespective of the specification used, averaging only about \$5 ha$^{-1}$; we conclude that both @rakshit2020 and @trevisan2021spatial may have significantly over-estimated that value.
+We found that the benefit of VRA over URA is rather small irrespective of the specification used, averaging only about \$5 ha$^{-1}$.
+More important, both specifications by trevisan2021spatial and rakshit2020 tend to significantly over-estimate the economic value of VRA based on GWR.
+Their assumption of quadratic funcitonal form is one of the main culplits.
+When quadratic functional form is assumed, over-application of nitrogen is modeled to result in large economic loss due to yield loss when in reality over-application of nitrogen is not associated with any yield loss when the true yield-response function is quadratic-plateau.
 Our results suggest that the prospects of using GWR to generate site-specific input recommendations are bleaker than stated in @trevisan2021spatial.
+It is important to develop GWR with more flexible functional forms than currently possible if precision agriculture practitioner is interested in using GWR as one of the tools to estimate site-specific input use recommendation.
 
@@
 
-# Discussions
+# Discussions and conclusions
 
-Our simulation results show that generating site-specific $R_x$s by applying the basic GWR model (GWR-R) to OFPE data tends to have little economic value for site-specific $R_x$s.
+Our simulation results show that generating site-specific $R_x$s by applying the basic GWR model (GWR-R) with quadratic functional form to OFPE data tends to have little economic value for site-specific $R_x$s when the true yield response function is quadratic-plateau.
 The GWR-R based VRA is on average no more profitable than SCAM-based URA under many price scenarios, particularly when nitrogen price is relatively low compared to the corn price.
-This finding reveals the economic consequences of the widely recognized statistical inaccuracy issue of GWR estimation [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation], and is in agreement with previous critiques concluding that GWR should be used as an exploratory tool rather than an inferential tool [@wheeler2005multicollinearity; @paez2011simulation].
+This finding reveals the economic consequences of the widely recognized statistical inaccuracy issue of GWR estimation [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation] and also the problem of assuming quadratic functional form when the true yield response function follows the quadratic-plateau functional form like corn-nitrogen relationship.
 Precision agriculture practitioners should be cautious when using GWR for site-specific $R_xs$.
@@
 
-An obvious cause of the GWR models' poor economic performances in this work is that their assumed quadratic functional form of yield response differs from the true quadratic-plateau yield response functions.
-One solution could be to upgrade to nonlinear GWR models.
-@lambert2022geographically have recently developed a linear-plateau GWR model, which could be worthy of future examinations of its economic value.
-Another solution is to extend the parametric GWR approaches to a semi-parametric or non-parametric GWR where the yield response functions are estimated without assuming particular functional forms (like SCAM).
-However, such a method may well encounter a very similar problem to that faced by GWR-R: insufficient information available locally to estimate reliably the shape of local yield response curves.
+Our results clealy show it can be dangerous to use GWR with quadratic functional form when yield-input relationship is quadratic plateau as done in @trevisan2021spatial.
+Their choice of quadratic functional form is likely due to the fact there is no readily usable statistical software or package that implements non-linear GWR.
+The only non-linear model available at the moment is the linear-plateau GWR by @lambert2022geographically.
+Unfortunately, economically optimal input rate cannot be adjusted according to price using linear-plateau model as the economically optimal input rate occurs always at the kink.
+Given that many yield-input relationships follow quadratic-plateau functional form for many crops, it would be fruitful to develop a GWR method with quadratic-plateau functional form.
+It should be also possible and interesting to build semi-parametric GWR where the yield response functions are estimated without assuming particular functional forms (like SCAM).
 It is also noted that the recently developed multi-scale GWR model [@fotheringham2017multiscale; @yu2020inference; @comber2022route] allows the bandwidth to be derived separately for each covariate in the model, which would potentially improve the performances of GWR estimates and be incorporated into future research.
@@
 
-Most important, whether using GWR-R or GWR-R, researchers must be cautious about their estimated value of VRA.
+Most important, whether using GWR-T or GWR-R, researchers must be cautious about their estimated value of VRA when model is assumed to be quadratic when the true underlying yield-input response is quadratic-plateau in relity.
 Our results show that it is likely that they will over-estimate their true values and the bias can be misleadingly high with non-negligible probability.
@@
 
-# Conclusions
+Finally, it would be interesting to examine the pure performance of GWR.
+The objecive of this article was to evaluate GWR with quadratic functional form when the true yield-input relationship is quadratic-plateau.
+Therefore, we evaluated GWR when model is misspecified in a particular manner.
+Once, GWR with quadratic-plateau model is developed, it would be interesting to see how it performs when the true yield reponse to input is quadratic-plateau.
+In this case, there is no functional form misspecification and the pure ability of GWR can be isolated.
+
+<!-- # Conclusions
 
@@
 It can be concluded that researchers need to be cautious about promoting the GWR-based approach to VRA recommendation.
+-->
 
@@
 <div id="refs"></div>
+
+`r run_pagebreak()`
+
+# Appendix

### 2023-05-10 Codes/3_make_figures_publication.R
updated figure making module, with kernel_choice in the file path

@@ -182,15 +182,23 @@ g_value <-
 # facet_grid(round(pN, digits = 2) ~ .)
 
 est_data <-
-  readRDS(here("Shared/Results/est_data.rds")) %>%
+  readRDS(here("Shared", "Results", kernel_choice, "est_data.rds")) %>%
   unnest() %>%
   data.table() %>%
   .[, type := ifelse(transfer == 0, "GWR-R", "GWR-T")]
 
 eorn_ratio_data <-
-  est_data %>%
-  .[, pn_pc := pN / pCorn] %>%
-  .[, .(eonr_ratio = mean(opt_N_gwr / opt_N_scam)), by = .(type, sim, pn_pc)]
+    est_data %>%
+    .[, pRatio := pN / pCorn] %>%
+    # only display the 25% (5.44), 50% (6.56), 75% (7.67) price ratio
+    .[pRatio %in% c(5.44, 6.56, 7.67), ] %>%
+    # === label price ratio
+    .[, pLabelName := "Price Ratio (N/corn)"] %>%
+    .[pRatio == 5.44, pLabel := "Low"] %>%
+    .[pRatio == 6.56, pLabel := "Middle"] %>%
+    .[pRatio == 7.67, pLabel := "High"] %>%
+    .[, pLabel := factor(pLabel, levels = c("Low", "Middle", "High"))] %>% 
+    .[, .(eonr_ratio = mean(opt_N_gwr / opt_N_scam)), by = .(type, sim, pLabel)]
 
 g_eonr_bias <-
   ggplot(data = eorn_ratio_data) +
@@ -202,9 +210,10 @@ g_eonr_bias <-
     size = 0.2
   ) +
   geom_vline(xintercept = 1, color = "red") +
-  facet_grid(pn_pc ~ type) +
+  facet_grid(pLabel ~ type) +
   xlab("Number of Simulation Cases") +
   xlab("Average Ratio of Estimated EONR to true EONR")
+
 
 # /*===========================================================
 #' # Comparison of Estimated and True Coefficients
@@ -214,7 +223,7 @@ g_eonr_bias <-
 
 #* read the simulation data for a sigle simulationused for illustration
 single_sim <-
-  here("Shared", "Results", "aunit_sim_single.rds") %>%
+  here("Shared", "Results", kernel_choice, "aunit_sim_single.rds") %>%
   readRDS() %>%
   .[, type := ifelse(transfer == 0, "GWR-R", "GWR-T")]
 

### 2023-05-25 Writing/JAAEA/1stRoundRevision/reply_to_editor.rmd
reply to editor completed

---
output:
  word_document: default
  html_document: default
---
# Reply to the editor

Blur blur, . Your comments are in blue, and our responses are in black.

<span style = "color: blue;"> Based on the reviews and your email response, I have decided to give you the opportunity to revise the manuscript and respond to reviewer comments. One major point is that your true DGP assumed a quadratic plateau, but the estimated models use quadratic. This will lead the estimated models to give biased results. In your email response you indicate that you used quadratic plateau as the “true” functional form based on agronomy studies. If the dominant approach in recent literature is to use quadratic functions, then it does seem valuable to quantify the bias from using quadratic rather than quadratic plateau. Please document clearly in the manuscript that quadratic is the common practice (__point 1__). However, the title of your paper is about an economic evaluation of GWR analysis, and the choice of quadratic or quadratic-plateau is not an issue with GWR and this needs to be clear (__point 2__). Also reading through your discussion section, the implications are primarily framed about how GWR performed, but it might completely be an issue with functional form, but the current simulations don't inform us about the source of bias. Ideally, you would compare a GWR model that is quadratic with a GWR model that is quadratic-plateau functional form (__point 3__). </span>

Reply to <span style = "color: blue;"> __point 1__ </span>:

Actually, the dominant functional form used in the literature is quadratic-plateau for non-GWR (regualr parametric) regression because agronomists have long known that it better represents corn-nitrogen relationship. Application of GWR is very new to the field and GWR is not currently flexible in funcional form. There is no readily available statistical software or packages that lets researchers to use quadratic-plateau functionl form under the GWR framework. That is the primary reason that both Trevisan et al () and Rakshit et al () are using quadratic functional form. So, their choice of functional form is not coming from agronomic facts, rather from technical limitations. We are trying to point out this can be a problem with GWR just like it is a problem for regular regression framework. So, our paper is imporatnt because many use quadratic-plateau in regular regression framework, but the GWR promoted by the two studies use quadratic just because it is hard to do so. We believe it is imporatnt that this technical limitation is not trivial and would like to avoid practitioners or researcher to believe GWR is better than it truly is. We further suggest that it is important to develope a statistical package that allows to model yield-input relationship more flexibly.

Reply to <span style = "color: blue;"> __point 2__ </span>:

We fully agree with this point. We are assuming that readers know yield-nitrogen relationship is better represented by quadaratic-plateau and that point was kept implicit tghroughout the article. We made significant modifications to the manuscript so that we are not trying to blame GWR itself.

Reply to <span style = "color: blue;"> __point 3__ </span>:

This is a problem of our writing and we apologize for that. Our objective is not to evaluate the problem of GWR itself, rather the current practice of using GWR with quadratic form when the true underlying true relationship is quadratic-plateau as in Trevisan et al (). But, we agree fully that it is interesting to see how GWR performs when the assumed funtional form in regression and true functional form in the data generating process are the same. However, please note that quadratic-plateu is a non-linear model and GWR with quadratic-plate cannot be estimated readily as of now.

<span style = "color: blue;"> The other major critique of reviewer #1 is that the “true” DGP of the parameters does not correspond with a GWR. For example, reviewer #1 argues that the spatial distribution of parameters described in lines 173-193 does not correspond with a GWR DGP. Is there evidence from the agronomy literature that the DGP (aside from the functional form assumption) follows the process that you specify? Or alternatively, is there evidence from the agronomy literature that the DGP does not follow the GWR DGP described by reviewer #1 in comment #5? My guess is that the agronomy literature has little or nothing to say about this (compared to the functional form assumption), but maybe I'm wrong about that. If there is no evidence to support your proposed DGP or the GWR DGP as “true,” then it is difficult to critique GWR for not correctly estimating your proposed DGP (__specific point 1__). In your email response you state “Our choice of true yield response function is deliberate and just as valid as the data generating process Reviewer #1 recommends.” But if the DGP that you used and the DGP recommended by reviewer #1 are equally valid, then why critique GWR for not correctly estimating your DGP? To critique GWR, you need to argue that your DGP is more valid than the GWR DGP (__specific point 2__). Or you can estimate if GWR is robust to alternative, but equally valid, DGPs.

</span>

Fiest, it is important to reiterate that we are not interested in evaluating GWR itself even though our writing did give that impression, rather we are interested in evaluating GWR with quadratic functional form when the true underlying relationship is quadratic-plateau. This point alone addresses lots of your and reviwer 1's comments (as we discussed above, this is an important problem to address). We are critiqing the use of GWR with quadratic functional form when the true underlying relationship is quadratic-plateau.

Second, the data generating process suggested by reviewer is not even very different from our DGP in principle even though you seem to have an impression that they are vastly different.

While it may look complicated, the DGP suggested by the reviewer is basically the same as ours at the core (except functional form). Here is what the reviewer suggested.

$$
\begin{aligned}
y^* = X(X'W(s)X)^{-1}X'W(s)y + e^*
\end{aligned}
$$

Another way of writing this is simply

$$
\begin{aligned}
y_i = X_i\beta_i + e_i
\end{aligned}
$$

as shown in Leung, Y., Mei, C. L., & Zhang, W. X. (2000), where $\beta_i$ is the coefficient specific to observation $i$. $W(s)$ ensures that $\beta$ are spatially correlated. The choice of $W(s)$ is arbitrary and if you use the same $W(s)$ used in DGP for GWR regression as well, then you would be cheating, giving an unfair advantage to GWR because we (researchers) never know $W(s)$ in reality just like we do not know the weight matrix in spatial econometric approaches like spatial error model. This is the "correct" GWR DGP only if you know what $W(s)$ is priori.

In our DGP, we generate parameters (alpha, ... in equation )for individual $i$ in a spatially correlated manner (as opposed to what the reviewer thought). So, aside from the functional form, the only difference is in the spatial pattern of parameters. It is kind of like, we are using a different $W(s)$ in the above equation, which is an arbitrary parameter chosen by the researcher running MC simulations in the first place. In this sense, our DGP is just as "valid" as the GWR DGP.

Indeed, I would say our DGP is superior because ours is much more flexible. The DGP suggested by the reviewer cannot even accommodate non-linear model, while our DGP can use any functional relationship between $Y$ and $X$ as evident in our paper. Indeed, this is critical to our study because the data generating process <span style = "color: red;"> needs </span> to be quadratic-plateau to better represent the actual functional relationship exhibited by corn-nitogen response.

You are right that no agronomic studies suggest eigher our or the reviewer's DGP as a better DGP. However, our DGP has been used in an article in a prominent agronomy and precision agriculture journal (cite), meaning that our DGP was accepted by agronomists who reviewed them. On the other hand, the data generating process suggested by the reviewer has never been applied in the cotext of precision agriculture. Of course, we are not saying that our DGP is correct. And, this is not the main reason why we do not use the DGP suggested by the reviewer.

The reviewer clearly did not spend time trying to understand our DGP as the reviewer suggested him/herself. Also, the reviewer's criticism is based on his understanding that we are trying to test GWR itself and also test the its accuracy in parameter estimation, not EONR and profit estimation. Our impression of this reviewer from his/her comments is that he/she lacks domain knowledge and also economics.

Reply to <span style = "color: blue;"> __specific point 1__ </span>:

It seems that you have an impression that the GWR DGP is the "correct" DGP if we are estimating with GWR. But, as I argued above, there is no such thing as the "correct" DGP. In GWR DGP, the choice of $W(s)$ is arbitrary and no researchers should know it. In that sense, you are destined to misspecify the underlying DGP in a realistic situation. The most important part of the DGP is by far the functinal form of yield and nitrogen.

We will not use the GWR DGP process for two reasons. First, as we mentioned, we are not interested in criticizing GWR itself, but GWR with quadratic form when the true yield response function is better represented by quadratic-plateau (we aruged why this is important in our replies above). Also, the GWR DGP process suggested by the reviewer is limited to linear-in-parmeter model (like quadratic model). It simply cannot be used for quadratic-plateau. If we were to use quadratic functional form for our true yield-nitrogen response, then this study is completely useless and loses its significance in the literature of precision agriculture.

Reply to <span style = "color: blue;"> __specific point 2__ </span>:

First, as we have communicated in our message to you ealier, we are not interested in evaluating GWR itself. So, I do not think your comments really apply to our manuscript.

But, suppose we are interested in evaluating GWR itself. And, also suppose our DGP and the GWR DGP are very different even though they are in reality very similar as argued above. Even then, we can definitely criticize GWR by using our DGP. Nobody knows the true data generating process of OFPE in the real world. If we use the GWR DGP and find out that GWR performs well, then does that mean GWR performs well in the real world? No. It says that GWR performs well if the data generated in OFEP indeed follow GWR DGP, which of course may not be the true DGP in real world. If GWR does not perform well for a single DGP that is just as valid as GWR DGP, then that would mean we need to be careful applying GWR in the real world. This is not to say, GWR is always bad. But, it is enough to warrant researchers and practitioners that GWR <span style = "color: red;"> may </span> fail. If we show that GWR does not work well with "a" valid DGP, then it is enought to warn people about its potential danger.

<span style = "color: blue;"> In general, it is important in your paper to clarify how much of the bias you estimate is due to the functional form assumption versus the assumption about the DGP. Also, you need to more clearly defend the DGP you choose as the “true” DGP or compare results with alternative DGPs. It seems to me that you will need to rethink your simulations so that you can more clearly sort out the sources of bias. </span>

Reply:

It is not important in this paper to distinguish and isolate the sources of bias. Our interest is in showing the bias of using GWR with quadratic form (because of technical limitation) even though the underlying relatinship is quadratic-plateau (like corn-nitrogen) as done by Trevisan et al (). It is actually impossible in our paper to isolate them and we are not interested in doing so either. Also, please note that functional form is part of DGP and indeed the most important part of a DGP. There is no such thing as isolating the source of bias of funcitonal form assumption and DGP assumption.

If our interest is understanding the problem of estiamtion inaccurcy by GWR alone, then we should have used quadratic-plateau in our GWR estimation so that the functional forms match. But, this is not our interest at least in this paper and it is also technically too cumbersome at the moment because there is no readily available statistical software to implement it. We are criticizing the practice that has been used by a researcher that can have false impression about how valuable GWR is for variable rate nitrogen application in the OFEP setting.

### 2023-06-08 Writing/JAAEA/1stRoundRevision/reply_to_reviewer_2.rmd
Appendix (docx file done; rmd not working), response to reviewer 2 (mostly done)

---
output:
  word_document: default
  html_document: default
---
# Reply to the Reviewer #2

Your comments are in blue, and our responses are in black.

<span style = "color: blue;">This study examines the economic value associated with three statistical methods used to generate site-specific nitrogen application rates: 1) geographically weighted regressions using the method of Rakshit et al. (2020) denoted as GWR-R, 2) geographically weighted regressions using the method of Trevisan et al. (2021) denoted as GWR-T, and 3) shape-constrained additive models (SCAM). Using straightforward Monte Carlo simulations, the two GWR methods are used to determine the economically optimal nitrogen rate (EONR) and profits from variable rate applications (VRA), while the SCAM methodology is used to determine the EONRs and profits for uniform rate applications (URA). These rates are based on estimations of site-specific corn yield functions for six cells across 1,440 subplots. The authors find the GWR-T outperforms GWR-R when the nitrogen price (relative to corn) is low, but GWR-R outperforms GWR-T when the nitrogen price is relatively high. This is because of the relative over- and underestimation of the EONRs. The study also finds that both GWR-T and GWR-R may have substantially overestimated the economic value of VRA; the net benefit of VRA over URA is much smaller, roughly $2 per acre (just over $5 per hectare, on average).
For convenience, my review below is organized into a set of general comments, specific comments, and comments related to the exposition and writing, with each being arranged in order of page number. All comments are designed to strengthen the research.</span>  
General reply: We are very grateful

<br>

<span style = "color: blue;">General Comments</span>

<span style = "color: blue;">To some extent, this research is related to studies that examine the “value” of forecasting models by assessing their measure of inaccuracy. Given that determining the value of general regression methodologies is not overly common in the relevant literature here, why not add 1-2 paragraphs that ties your study to other studies that measure the “value” of certain econometric techniques?
</span>  
Reply: Very good point. What makes this study differ from previous studies is the model “value” is not measured by the accuracy of parameter estimates, but the ultimate economic return. We agree it is a good idea to add more review of previous studies and highlight our difference. 
More discussion, literature review, is added on page xx, lines xxx.

One of the most important questions in the literature relates to how variable rate technologies (VRT) can reduce negative externalities like fertilizer and chemical runoff and leaching. Clearly, this is not the research objective, and addressing a much more burning question in the literature would involve additional terms in the equation on p. 10, line 294 that represent the negative environmental externalities. The authors should clarify early on that “economically optimal” means “privately optimal” rather than “socially optimal.”
Reply: That is correct. Thank you for the reminder. We modified the writing and made it more explicit that the economically optimal VRT is privately optimal which only considers farmer’s private profit. Environmental externalities were not considered in this study.

It strikes me as odd that, even with a minor clause on line 207 of p. 10, there is no real discussion of the corn price or nitrogen price in the methods section. What are the summary statistics and/or assumptions about p and w? What is the underlying intuition regarding the dependence of the relative performance of GWRR/GWRT to the corn-to-nitrogen price ratio (though this is partially explained in the paragraph on pages 15-16)? Any intuition about the ratios of 4.2, 5.4, and 10.4?
Response: That is our ignorance. Thank you for pointing it out. We added the historical summary of p and w. We choose the historically high (10 or 7), middle, and low price ratio.
Reply: Figure of historical price trend in the appendix; argue that our partial explanation is sufficient.

<span style = "color: blue;">Where is there no in-text reference to, or explanation of, Figure 4? I do not know what to make of this lone figure.</span>  
Reply: We apologize for this mistake. That figure was to compare the estimated and true GWR coefficients $\beta_1$ and $\beta_2$. But since we have already compared the estimated and true EONR's in the next figure, the coefficient comparisons do not seem necessary anymore, and we forgot to remove it from the final manuscript. It is now removed. (__Taro: I removed that figure. Is it OK, or you want to say something about it?__)

<br>

<span style = "color: blue;">Specific Comments</span>

<span style = "color: blue;">P. 1, line 23: Site-specific farming, these days, does not have to be very precise, although the early literature conflated precision ag and site-specific farming. More importantly, VRT is just one component of precision ag; they are not synonymous.</span>  
Reply: We agree with the reviewer's comment that precision agriculture, site-specific farming, and variable-rate technology are not the same thing. Although in the literature those terms are often used interchangeably, they are not strictly speaking equivalent. We removed the statement in the parentheses "also known as site-specific farming, or variable-rate technology" to avoid misleading the audiences.

<span style = "color: blue;">P. 5, lines 89-90: By this point, it would have been useful to add 1-2 sentences or a footnote about parallels with nonparametric estimators. Using multiple data points to derive local estimates, as in kernel density estimation, is nothing new. It would be helpful to provide more background on this. More broadly, at this point, besides the economics, why should we care about GWR relative to other spatial statistics methods?</span>  
Reply: We agree with the reviewer's comment that there are many nonparametric estimators that can estimate local yield responses, among which GWR is only one of them. However, the goal of this study is not to compare GWR with other estimators or to advocate the use of GWR. As stated  in the introduction section (page 1, lines 41-42xx; page 2, lines 61-65xx), the background of this study is that GWR model has gained attention in developing site-specific input recommendations due to its minimum requirement of costly field data collection. Our interest is to further test whether GWR is truly economically viable in this application and provide guidance for precision farming practice. The current study does not intend to involve other spatial statistics methods. But we do have plans to conduct similar simulation-based economic evaluations of other local response estimation methods (such as the spatial kriging smoothing) in future research.

<span style = "color: blue;">P. 9, line 192: Here, do you mean that you set the 1370 kg ha-1 to be the square root of the sill variances?</span>  
Reply: We apologize for the typo. Yes, it should be the square root of the sill variances since 1379 kg ha$^{-1}$ was the mean of standard deviations. Thank you for pointing out this typo. We have corrected that statement (see page x, line xx in the revised manuscript).

<span style = "color: blue;">P. 11, line 220: At the first mention of shape-constrained additive models (SCAM), there should be a few sentences of explanation, either in the body or as a footnote. Even after the partial explanation on lines 232-233, it is still somewhat unclear and warrants more detail. The general readers of JAAEA are likely to not know, either.</span>  
Reply: Thank you for the suggestion. We added a few more explanations of the SCAM to make it more clear to the general JAAEA readers that it is a regression model that can fit a more flexible and non-linear response relationship, and also allows for shape constraints that can incorporate prior knowledge or theories. (see page xx, lines xxx of the revised manuscript.)

<span style = "color: blue;">Pp. 11-12, lines 238-245: To check, l=K, i.e., the total number of splines from the equation on line 238 equals the total number of splines used for f ̂_SCAM (∙)? If so, use the same notation.</span>  
Reply: Thank you for pointing out this typo of notations. Yes, the $l$ and $k$ should be the same. We corrected the notations to use $k$ in the revised manuscript.

<span style = "color: blue;">P. 13, lines 268-270: How robust are the N ̂_(GWR-T,j )^*rates to variations in the AIC-chosen bandwidth parameters? More information about this needs to be provided.</span>  
Reply: If we understand the question correctly, we believe it is asking about the robustness of GWR estimates to bandwidth selection. Choosing bandwidth is indeed a crucial step in GWR estimation, and there are many different bandwidth selection methods in the literature. In this study we used the corrected version of AIC approach [@fotheringham2017multiscale; @lu2017geographically] to determine the optimal bandwidth. It is a commonly used approach in practice, and also the same approach used by @rakshit2020 and @trevisan2021spatial which can make our simulation evaluations consistent. Since the corrected AIC method generates a unique bandwidth, we did not conduct any robustness check to bandwidths. We agree the GWR results could vary when choosing different bandwidths, but the choices of other bandwidth values other than the AIC-chosen one may be arbitrary. We added more discussions about bandwidth selection in page x, lines xxx of the revised manuscript.

<span style = "color: blue;">P. 15, lines 303-305: Why are the numbers from these sentences blank? In particular, the median benefit of VRA under GWRR is ? and the median benefit of VRA under GWRT is…?</span>  
Reply: Our apologies for the typos. We have corrected them and filled out the numbers. (See page x, line xx in the revised manuscript.)

<span style = "color: blue;">P. 15: You first discuss figure 6 and then move to figure 5. Put all figures in order.</span>  
Reply: Thank you for pointing out the wrong order of the figures. We have corrected the order of Figures 5 and 6.

<br>

<span style = "color: blue;">
Writing
</span>

<span style = "color: blue;">P. 2, line 45: This should be “data are”, not “data is”. </span>  
Reply: This grammar error was corrected. The new sentence is now on page xx, line xx of the revised manuscript.

<span style = "color: blue;">P. 2, line 52: Basically or actually? Vagueness here makes it difficult to assess the degree to which OSU’s calculators are being used directly. </span>  
Reply: The term "basically" used here does sounds a little oral and vague. We removed it in the revised manuscript (see page x, line xxx) to avoid any confusion.

<span style = "color: blue;">P. 2, line 54: To avoid confusing a general agricultural economics audience, I would use an abbreviation other than Rx for site-specific recommendations. </span>  
Reply: In precision agriculture, the site-specific recommendation map  is commonly called "prescription" or "$R_x$" by researchers and the industry. There may be other abbreviations but they are not as popular as the "$R_x$". We added a brief note to explain that "$R_x$" means "prescription" in where "$R_x$" first shows up (page x, line xxx in revised manuscript) to make sure the abbreviation's meaning is clear to the general agricultural economics audience who are not familiar with precision agriculture.

<span style = "color: blue;">P. 2, lines 49-60: All of these current commercial examples would work better as a footnote as they may become inaccurate in the next 3-10 years (or fewer). </span>  
Reply: Thank you for the suggestion. We also agree putting those commercial examples in a footnote is a better idea. Those part of contents is now all in footnote 1 on page xx.

<span style = "color: blue;">P. 5, lines 91-114: This page-long paragraph should be split up into at least two paragraphs. The length is taxing. I would consider starting a new paragraph with the sentence beginning on line 97.</span>  
Reply: We followed the reviewer's suggestion and broke those discussion into two paragraphs. The second paragraph starts on page x, line xx. We also made some slight wording changes to the beginning of this paragraph.

<span style = "color: blue;">P. 7, line 137: This comment should have been removed by the authors prior to manuscript submission.</span>  
Reply: This typo has been removed. Thank you for pointing it out.

<span style = "color: blue;">P. 9, line 189: The acronym DIFM is used before it’s spelled out in the sentence, but you should spell it out first and then use the acronym. </span>  
Reply: Thank you for identifying this writing issue. The acronym DIFM is now put after the full name. See page x, line xx.

<span style = "color: blue;">P. 10, line 212: The (j,k) index should be subscripted here.</span>  
Reply: We very appreciate the reviewer's careful reading of the manuscript and pointing out this typo. It is not corrected to $\varepsilon_{j,k}$. (See page x, line xx.)

<span style = "color: blue;">P. 11, line 221: The second “and” should be “an”. </span>  
Reply: The typo is corrected. Thank you so much for finding this typo.

<span style = "color: blue;">P. 11, line 232: Are you using one shape constraint or more than one shape constraint? The language here really matters so as to avoid confusion on the part of the readers.</span>  
Reply: The model described here is a single yield response function for the full field, in other words, not variable rate responses. We agree that the language used may cause confusion on whether it is a "single" response function or "single" shape constraint. To avoid the confusion, we removed the term "single". (See page x, line xx in the revised manuscript.)

<span style = "color: blue;">P. 11, line 235: It seems that 1-2 citations could be added (or are missing) after “well substantiated by agronomic research.”</span>  
Reply: We followed the reviewer's comment and added two citations of agronomic studies to support this statement. (See page x, line xx in the revised manuscript.)

<span style = "color: blue;">P. 12, line 253: I know what you mean by the notation f ̂_(GWR-R,j) (N), but the hyphen in the notation almost seems like a subtraction sign. I would recommend changing GWR-R and GWR-T to GWRR and GWRT and then having superscripts here. That is, f ̂_j^GWRR (∙) and f ̂_j^GWRT (∙).</span>  
Reply: Thank you for the recommendation. We think the GWRR and GWRT look more concise than GWR-R and GWR-T, and have made the changes as suggested throughout the text. We also put all model names (GWR and SCAM) in superscripts of equations. We thank the reviewer's comment to make our notations more consistent throughout the manuscript.

<span style = "color: blue;">P. 13, line 271: In keeping with your past usage, you should make sure the acronym SCAM is in uppercase throughout the text.</span>  
Reply: Thank you for pointing out this formatting error. We have corrected all the acronym SCAM to uppercase throughout the text. In addition, we also changed all the acronyms in equations to uppercase as well.

<span style = "color: blue;">P. 15, line 304: “but the its benefit is even negative at when the” should have the typos/redundant wording removed.</span>  
Reply: Thank you for pointing out those typos. They have been corrected. (See page x, line xx in the revised manuscript.)

<span style = "color: blue;">P. 17, line 335: Figure 0?</span>  
Reply: Our apologies for the typo. It should be Figure x. (__Taro: Which figure are you referring to here? I don't think it should be Figure 5.__)

<span style = "color: blue;">P. 18, line 362: Section title should just be “Discussion”. </span>  
Reply: The title has been changed to “Discussion”. Furthermore, we combined this section with the conclusions section.

<span style = "color: blue;">P. 34, Figure 8 horizontal axis label: “Estiamated” should be “Estimated”. </span>
Reply: We are very thankful for the reviewer to find out this typo. It was corrected by the revised manuscript.

<span style = "color: blue;">Pp. 19-20, lines 398-400: Can this sentence be sharpened? Right now, it is a bit too vague to be completely useful as a guide to researchers in this area. Specifically, what other statistical estimators should be reconsidered and how (specifically) should they be reassessed?</span>  
Reply: Thank you for pointing out the vagueness of this sentence. We added more details to explain that the other statistical methods that are commonly used in the site-specific yield response estimation literature include the regression with interaction terms of field characteristics, machine learning, etc. The approach of assessment is the similar simulation-based evaluation used by this study.

### 2023-06-08 Writing/Online-Appendix_supp.rmd
Appendix (docx file done; rmd not working), response to reviewer 2 (mostly done)

---
title: "Appendix for Paper"
output:
  officedown::rdocx_document:
    toc: false
    toc_depth: 1
    number_sections: true
    reference_docx: "word_template.docx"
    plots:
      style: Normal
      align: center
      caption:
       style: Image Caption
       pre: "Figure "
       sep: ": "
    tables:
      style: Table
      layout: autofit
      width: 1.0
      caption:
       style: Table Caption
       pre: "Table "
       sep: ": "
bibliography: PA.bib
csl: field-crops-research.csl
abstract: ""
header-includes:
   - \usepackage{subfig}
---

```{r echo = F, cache = F}
suppressMessages(library(knitr))
suppressMessages(library(here))
suppressMessages(library(officedown))
suppressMessages(library(officer))

opts_chunk$set(
  fig.align = "center",
  fig.retina = 5,
  warning = F,
  message = F,
  cache = F,
  echo = F,
  fig.cap = TRUE
)
```

```{r cache = F}
#--- packages ---#
library(data.table)
library(tidyverse)
library(flextable)
library(stringr)
library(sf)
library(lfe)
library(modelsummary)
library(patchwork)
library(ggplot2)
```

```{r figure_setup, cache = F}
theme_update(
  axis.title.x =
    element_text(
      size = 12, angle = 0, hjust = .5, vjust = -0.3, family = "Times"
    ),
  axis.title.y =
    element_text(
      size = 12, angle = 90, hjust = .5, vjust = .9, family = "Times"
    ),
  axis.text.x =
    element_text(
      size = 10, angle = 0, hjust = .5, vjust = 1.5, family = "Times"
    ),
  axis.text.y =
    element_text(
      size = 10, angle = 0, hjust = 1, vjust = 0, family = "Times"
    ),
  axis.ticks =
    element_line(
      size = 0.3, linetype = "solid"
    ),
  axis.ticks.length = unit(.15, "cm"),
  #--- legend ---#
  legend.text =
    element_text(
      size = 10, angle = 0, hjust = 0, vjust = 0, family = "Times"
    ),
  legend.title =
    element_text(
      size = 10, angle = 0, hjust = 0, vjust = 0, family = "Times"
    ),
  legend.key.size = unit(0.5, "cm"),
  #--- strip (for faceting) ---#
  strip.text = element_text(size = 10),
  #--- plot title ---#
  plot.title = element_text(family = "Times", face = "bold", size = 12),
  #--- margin ---#
  # plot.margin = margin(0, 0, 0, 0, "cm"),
  #--- panel ---#
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background = element_blank(),
  panel.border = element_rect(fill = NA)
)
```

```{r include = FALSE}
#| include: false

# /*===========================================================
#' # Prepare data and results for writing
# /*===========================================================

# "gaussian", "bisquare", "exponential", "tricube", "boxcar"

# kernel_choice <- "gaussian"
# 
# #* read the results rds file
# results <-
#   here("Shared", "Results", kernel_choice, "pi_data.rds") %>%
#   readRDS() %>%
#   .[, type := ifelse(transfer == 0, "GWRR", "GWRT")] %>%
#   .[, bias := pi_diff_est - pi_diff] %>%
#   # only display the 25% (5.44), 50% (6.56), 75% (7.67) price ratio
#   .[pRatio %in% c(5.44, 6.56, 7.67), ] %>%
#   # === label price ratio
#   .[, pLabelName := "Price Ratio (N/corn)"] %>%
#   .[pRatio == 5.44, pLabel := "Low"] %>%
#   .[pRatio == 6.56, pLabel := "Middle"] %>%
#   .[pRatio == 7.67, pLabel := "High"] %>%
#   .[, pLabel := factor(pLabel, levels = c("Low", "Middle", "High"))]
# 
# #* create figures
# source(here("GitControlled/Codes/3_make_figures_publication.R"))
# assign("g_value_gaussian", g_value)
# assign("g_bias_gaussian", g_bias)
# 
# 
# 
# kernel_choice <- "exponential"
# 
# #* read the results rds file
# results <-
#   here("Shared", "Results", kernel_choice, "pi_data.rds") %>%
#   readRDS() %>%
#   .[, type := ifelse(transfer == 0, "GWRR", "GWRT")] %>%
#   .[, bias := pi_diff_est - pi_diff] %>%
#   # only display the 25% (5.44), 50% (6.56), 75% (7.67) price ratio
#   .[pRatio %in% c(5.44, 6.56, 7.67), ] %>%
#   # === label price ratio
#   .[, pLabelName := "Price Ratio (N/corn)"] %>%
#   .[pRatio == 5.44, pLabel := "Low"] %>%
#   .[pRatio == 6.56, pLabel := "Middle"] %>%
#   .[pRatio == 7.67, pLabel := "High"] %>%
#   .[, pLabel := factor(pLabel, levels = c("Low", "Middle", "High"))]
# 
# #* create figures
# source(here("GitControlled/Codes/3_make_figures_publication.R"))
# assign("g_value_exponential", g_value)
# assign("g_bias_exponential", g_bias)
```

`r run_pagebreak()`

Economic Evaluation of Geographically Weighted Regression Analysis for Site-specific Nitrogen Management

# Results of Alternative Kernel Functions

There are many different kernel functions to define the distance-decay weightings for GWR model. In the main text, the Gaussian kernel function was employed, which can be mathematically represented as follows:

$$w_{ab}=exp⁡(-0.5[\frac{d_{ab}}{h}]^2 ),$$
where $d_{ab}$ denotes the Euclidean distance between observation $b$ and regression location $a$, $w_{ab}$ denotes the kernel weight assigned to observation $b$, and $h$ denotes the bandwidth.

This appendix compares several other alternative kernel functions, including the Exponential, Boxcar, Bi-square, and Tri-cube, in additional to the Gaussian. The functional forms and graphical representations of these kernels can be found in Figure A1.

The estimation results obtained using alternative kernel functions, apart from the Gaussian, are presented in Figures A2 and A3. For the case of Exponential kernel, which is a continuous kernel like the Gaussian, the optimal bandwidth selection follows a similar corrected AIC approach and results in a similar bandwidth of 18 meters. For the discontinuous kernels of Boxcar, Bi-square, and Tri-cube, however, the 18-meter bandwidth does not encompass a sufficient number of neighboring observations for reliable local regressions, resulting in unrealistic estimation outcomes. To address this issue, an empirical bandwidth of 100 meters is chosen for these discontinuous kernels to enable the inclusion of an adequate number of local observations. Other bandwidth values (such as 80 meters, 150 meters) are also conducted and the resulting estimation outcomes are found to be comparable.

## Comparing the values of GWR-based VRA and SCAM-based URA

Figure A2 shows the distribution of the true economic value of GWR, denoted as the profit difference between the GWR-based VRA (Variable Rate Application) and SCAM-based URA (Uniform Rate Application),
$$\Delta^{GWR}=\Pi^{GWR}-\Pi^{SCAM},$$
which aligns with Figure 3 in the main text but uses alternative kernel functions. The findings observed in Figure 3 under Gaussian kernel, where GWRR performs better as the price ratio increases, and GWRT performs better as the price ratio decreases, hold true across all other kernel function choices. Although there are slight variations in the magnitudes of computed $\Delta^{GWR}$ among different kernel function choices, these differences do not significantly affect the conclusions drawn in the main text.

## Bias in the estimation of the value of GWR-based VRA

Figure A3 shows the distribution of the bias (over-estimation) in the estimated economic value of GWR, measured as the difference between the estimated and true values of GWR-based VRA,
$$bias=\hat{\Delta}^{GWR}-\Delta^{GWR},$$
which aligns with Figure 6 in the main text but uses alternative kernel functions. Similar to the findings of Figure 6 under the Gaussian kernel, the GWRR consistently exhibits significant over-estimation of the value of GWR-based VRA across all other kernel function choices. Also, the GWRT demonstrates smaller over-estimation at low price ratios compared to GWRR, while the over-estimation increases as price ratio rises. The presence of a similar fat tail in the GWRT bias distribution is also evident. The magnitudes of the estimation bias vary across kernel function choices, but the differences are not substantial and do not significantly affect the conclusions drawn in the main text.

Overall, the economic evaluation results of GWR models presented in this study are not significantly influenced by the selection of the kernel function in GWR estimation. Despite slight variations in calculated profit and bias among the different kernels, the qualitative consistency of the final conclusions remains intact regardless of the chosen kernel.

`r run_pagebreak()`

# Figures

```{r, fig.id = "kernel_des", fig.cap = "Figure A1. Different kernel functions for GWR modeling. In the curve diagrams of the right panel, the y-axis is the kernel weight, and the x-axis is the ratio of (d_ab/h)."}
#
```

```{r, fig.id = "pi-dif-dist", fig.cap = "The value of GWR-based VRA over SCAM-based URA for GWRR and GWRT", fig.subcap = c("Gaussian", "Exponential"), fig.height = 5, out.width="50%", fig.asp=1, fig.ncol = 2}
#g_value_gaussian
#g_value_exponential
```

`r run_pagebreak()`

# References

<br />

<div id="refs"></div>

`r run_pagebreak()`

# Appendix

### 2023-06-08 Codes/3_figures_illustrate.R

@@ -33,17 +33,17 @@ options(stringsAsFactors = FALSE)
 # === Set working directory ===#
 setwd(here())
 
-
-
+# =================================#
 # choose the kernel used for GWR
-# choice: "gaussian", "bisquare", "exponential", "tricube", "boxcar"
-kernel_choice = "gaussian"
+# choices: "gaussian", "exponential", "boxcar", "bisquare", "tricube"
+kernel_choice = "tricube"
+# =================================#
 
 # load estimation results
 results <-
     here("Shared", "Results", kernel_choice, "pi_data.rds") %>%
     readRDS() %>%
-    .[, type := ifelse(transfer == 0, "GWR-R", "GWR-T")] %>%
+    .[, type := ifelse(transfer == 0, "GWRR", "GWRT")] %>%
     .[, bias := pi_diff_est - pi_diff] %>%
     # only display the 25% (5.44), 50% (6.56), 75% (7.67) price ratio
     .[pRatio %in% c(5.44, 6.56, 7.67), ] %>%
@@ -66,7 +66,6 @@ mean_data_value <-
       by = c("field_col", "pLabel", "type")
     ] %>%
     print()
-
 ggplot(data = results) +
     geom_histogram(
         aes(x = pi_diff),
@@ -84,7 +83,7 @@ ggplot(data = results) +
     geom_text(
         data = mean_data_value, color = "red",
         aes(
-            x = ifelse(pi_diff < 65, pi_diff + 5, pi_diff - 20), y = 100,
+            x = ifelse(pi_diff < 65, pi_diff + 4, pi_diff - 20), y = 100,
             label = paste0("Median = ", round(pi_diff, 2))
         ),
         angle = 0, hjust = -0.1, vjust = 0, size = 3
@@ -93,10 +92,106 @@ ggplot(data = results) +
     scale_y_continuous(expand = c(0, 0)) +
     scale_x_continuous(breaks = 20 * (-2:3), limits = c(-45, 60)) +
     xlab("The value of VRA over URA ($ per ha)") +
-    ylab("Number of Simulation Cases")
+    ylab("Number of Simulation Cases") +
+    theme(
+        panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        panel.background = element_blank(),
+        panel.border = element_rect(fill = NA)
+    )
 ggsave(here("Shared", "Figures", paste0("g_value_", kernel_choice, ".png")),
-       height=6, width=6)
+       height = 4, width = 5)
 
+# /*===========================================================
[…]

### 2023-06-08 Codes/3_make_figures_publication.R

@@ -341,7 +341,7 @@ pN <- pCorn * field_parameters$pRatio_ls[[1]][2] # medium price scenario
 #' # Prepare yield response curves
 # /*+++++++++++++++++++++++++++++++++++
 il_data_oe <-
-  readRDS(here("Shared/Results/il_data_oe.rds")) %>%
+  readRDS(here("Shared", "Results", kernel_choice, "il_data_oe.rds")) %>%
   .[,
     lapply(.SD, mean),
     by = aunit_id,
@@ -408,7 +408,7 @@ g_why_bias_many <-
   theme(
     legend.position = "bottom"
   ) +
-  scale_color_discrete(name = "Estiamted EONR")
+  scale_color_discrete(name = "Estimated EONR")
 
 # /*===========================================================
 #' # An illustration of over-estimation of the value of GWR-based VRA over SCAM-based URA

### 2023-06-12 Writing/manuscript_gwr.rmd

@@
   readRDS() %>%
-  .[, type := ifelse(transfer == 0, "GWR-R", "GWR-T")] %>%
+  .[, type := ifelse(transfer == 0, "GWRR", "GWRT")] %>%
   .[, bias := pi_diff_est - pi_diff] %>%
@@
 Midwestern row crop farmers to pay for 1-ha grid soil sampling and chemical analysis every three or four years [@morris2018strengths].
-The data is often used to derive fertilizer application recommendations, for example by applying comparatively simple formulas provided by university extension services (e.g., Culman, et al.
+The data are often used to derive fertilizer application recommendations, for example by applying comparatively simple formulas provided by university extension services (e.g., Culman, et al.
 2020).
-But the expense of soil sampling and analysis is driving development of sensor technologies that gather data on site-specific field and crop characteristics or proxies of those characteristics.
-For example, Trimble Agriculture's GreenSeeker and AgLeader's OptRx® systems use optical sensors mounted on fertilizer application booms to digitally record vegetative index imagery as farm machinery is driven through fields during early crop growth stages.
-GreenSeeker then basically uses Oklahoma State University's Sensor-based N Rate Calculator to convert those data into recommended nitrogen fertilizer (N) application rate maps ($R_xs$).
+But the expense of soil sampling and analysis is driving development of sensor technologies that gather data on site-specific field and crop characteristics or proxies of those characteristics, and the conversion of those data into recommended nitrogen fertilizer (N) application rate maps (usually called "prescriptions" or $R_x$s).^[For example, Trimble Agriculture's GreenSeeker and AgLeader's OptRx® systems use optical sensors mounted on fertilizer application booms to digitally record vegetative index imagery as farm machinery is driven through fields during early crop growth stages.
+GreenSeeker then uses Oklahoma State University's Sensor-based N Rate Calculator to convert those data into recommended nitrogen fertilizer (N) $R_x$s.
 Veris Technologies manufactures sensor equipment that can be towed through fields to gather apparent electroconductivity (EC) data, which can be used to infer properties of soil content.
 The "decision tool" software FieldRevealTM allows users to upload EC data, elevation data, and vegetative index data, which FieldRevealTM's professional agronomists analyze to provide $R_x$s to farmers.
-FieldApex creates N $R_x$s using foliar vegetative index data from satellite imagery, and SlantRange uses drone imagery for similar purposes.
+FieldApex creates N $R_x$s using foliar vegetative index data from satellite imagery, and SlantRange uses drone imagery for similar purposes.]
 
@@
 
-While the results reported by @trevisan2021spatial look rosy and GWR looks like a promising method, there are two potentially dangerous factors that may have caused them to snigificantly over-estimate the value of GWR as a tool to estimate site-specific EONR.
-First, they used quadratic functionl form in their GWR estimation even though it is widely accepted by scientific community that corn yield reseponse to nitrogen is better approximated by quadratic-plateau functional form.
+While the results reported by @trevisan2021spatial look rosy and GWR looks like a promising method, there are two potentially dangerous factors that may have caused them to significantly over-estimate the value of GWR as a tool to estimate site-specific EONR.
+First, they used quadratic functional form in their GWR estimation even though it is widely accepted by scientific community that corn yield response to nitrogen is better approximated by quadratic-plateau functional form.
 It is likely that their choice of quadratic functional form is merely a compromise because there did (does) not exist any statistical software of package that implements GWR with quadratic-plateau functional form.
-Second source of over-estimation bias is endemic to any study that evaluates the value of variable rate application, not just @trevisan2021spatial.
+
+The second source of over-estimation bias is endemic to any study that evaluates the value of variable rate application, not just @trevisan2021spatial.
 In general, researchers take the following steps to estimate the value of VRA using OFPE data [e.g., @anselin2004spatial; @swinton1998evaluating; @bullock2002adding; @liu2006site]: (1) estimate site-specific yield response functions based on a method chosen by the researcher; (2) use the estimated yield response functions to estimate the economically optimal site-specific input rates (EOIRs) and economically optimal uniform input rates; (3) plug the estimated site-specific EOIRs and uniform EOIR into the estimated yield response functions to calculate estimated profits under both strategies; and (4) find the difference in the two strategies' estimated profits.
@@
 
-The primary obejctive of this study is examine the degree and direction of bias in the estimation of the economic value of GWR-based variable rate application (VRA) when GWR model is specified as quadratic when the true yield response function follows the quadratic-plateau functional form.
+The primary objective of this study is examine the degree and direction of bias in the estimation of the economic value of GWR-based variable rate application (VRA) when GWR model is specified as quadratic when the true yield response function follows the quadratic-plateau functional form.
 We evaluate two sets of GWR quadratic specifications used in @rakshit2020 and @trevisan2021spatial.
-Both assumed a quadratic response of yield to nitrogen rate ($N$).
+Both of them assumed a quadratic response of yield to nitrogen rate ($N$).
 However, while @trevisan2021spatial estimated the coefficient on $N^2$ as a global parameter, @rakshit2020 estimated it locally for each point.
@@
 It is important to develop GWR with more flexible functional forms than currently possible if precision agriculture practitioner is interested in using GWR as one of the tools to estimate site-specific input use recommendation.
-
-<span style = "color: blue;"> this needs to be rewritten </span>
 
@@
 Note that the range of the optimal N rates of individual rounds of simulations are narrower.
-In defining the magnitude of the error term, we utilized the experimental data generated through eight on-farm randomized N field trials conducted by the DIFM project in 2018 by the Data-Intensive Farm Management Project (DIFM), [@bullock2019data].
+In defining the magnitude of the error term, we utilized the experimental data generated through eight on-farm randomized N field trials conducted by the Data-Intensive Farm Management Project (DIFM) project in 2018 [@bullock2019data].
 Using the data from each of the eight actual trials, separate regressions of yield on N were run, and standard deviations of the residuals were calculated.
-The mean value of the eight standard deviations was $1370$ kg ha$^{-1}$, which was the value of sill variances assigned to the simulations' error terms.
+The mean value of the eight standard deviations was $1370$ kg ha$^{-1}$, which was the square root value of the sill variances assigned to the simulations' error terms.
 
@@
 
-In each simulation, for each cell $(j, k)$, the simulation's true yield $y_{j, k}$ was generated based on the cell's assigned application rate $N_{j,k}$, true response parameters $c_{j,k} = (\alpha_{j,k}, \beta_{j,k}, \gamma_{j,k}, \tau_{j,k})$, and error term $\varepsilon\_{j,k}$.
+In each simulation, for each cell $(j, k)$, the simulation's true yield $y_{j, k}$ was generated based on the cell's assigned application rate $N_{j,k}$, true response parameters $c_{j,k} = (\alpha_{j,k}, \beta_{j,k}, \gamma_{j,k}, \tau_{j,k})$, and error term $\varepsilon_{j,k}$.
 This procedure generated a field-level, cell-specific data set, $\{(y_{j, k},N_{j, k} ):j=1,\dots,1440;k=1,\dots, 6 \}$.
@@
 Three approaches to estimate yield response functions and their associated EONRs were used.
-The first approach used the shape-constrained additive model (SCAM) to estimate a single yield response function for the entire field, and to estimate and economically optimal uniform nitrogen application rate for the field.
+The first approach used the shape-constrained additive model (SCAM) to estimate a single yield response function for the entire field, and to estimate an economically optimal uniform nitrogen application rate for the field.
 The other two approaches both used GWR, but assumed different specifications in modeling the impact of nitrogen on yield.
-The first GWR approach (GWR-R) followed the specification used by @rakshit2020, and the second GWR approach (GWR-T) followed the specification used by @trevisan2021spatial.
+The first GWR approach (GWRR) followed the specification used by @rakshit2020, and the second GWR approach (GWRT) followed the specification used by @trevisan2021spatial.
 Further details of each approach are presented below.
@@
 
-In the lower benchmark situation, a researcher was assumed to run OFPEs to gather data, then to estimate a single "full-field" yield response function using the SCAM non-parametric regression framework, which is a spline-based series estimation that can impose a shape-constraints on the estimated function [@pya2015shape].
-In using SCAM, the yield response function was restricted to be monotonically increasing and concave with respect to the N application rate, which are traits well substantiated by agronomic research.
+In the lower benchmark situation, a researcher was assumed to run OFPEs to gather data and then to estimate a "full-field" uniform yield response function using the SCAM non-parametric regression framework [@pya2015shape].
+SCAM is a type of generalized additive model (GAM) [@hastie1986gam] which allows for more flexible and non-linear  relationships between the response variable and the predictors through a combination of smooth functions (also known as "splines").
+In comparison with the conventional GAM technique, SCAM allows for the imposing of shape constraints on the estimated relationship, which is particularly useful when prior knowledge or theoretical considerations suggest certain shape restrictions of the relationship.
+In the SCAM of this study, the yield response function was restricted to be monotonically increasing and concave with respect to the N application rate, which are traits well substantiated by agronomic research [@cerrato1990comparison; @bullock1994quadratic].
 When the chosen shape constraints are correct, SCAM is more statistically efficient than a fully non-parametric regression [@pya2015shape].
@@
 
-$$y_j = \alpha + \sum_{l=1}^l \beta_l g_l(N_j)+ \varepsilon_j$$
+$$y_j = \alpha + \sum_{k=1}^K \beta_k g_k(N_j)+ \varepsilon_j$$
 
-where $g_l(\cdot)$ is the $l$th spline basis and $\beta_l$ is its coefficient to be estimated.
-The $\beta_l$s were constrained such that the resulting relationship between $y_j$ and $N_j$ is such that $y_j$ monotonically increases as $N_j$ increases, but at a diminishing rate.
+where $g_k(\cdot)$ is the $k$th spline basis and $\beta_k$ is its coefficient to be estimated.
+The $\beta_k$s were constrained such that the resulting relationship between $y_j$ and $N_j$ is such that $y_j$ monotonically increases as $N_j$ increases, but at a diminishing rate.
 
-Let $\hat{f}_{scam}(\cdot)$ represent the estimated whole-yield yield response function ($\sum_{k=1}^K \hat{\beta}_k g_k(\cdot)$).
+Let $\hat{f}^{SCAM}(\cdot)$ represent the estimated whole-yield yield response function ($\sum_{k=1}^K \hat{\beta}_k g_k(\cdot)$).
 Given the information derived from the SCAM approach, the estimate of the economically optimal uniform N rate is,
 
-$$\hat{N}_{scam}^* \equiv argmax_N⁡ \big[p\cdot \hat{f}_{scam} (N)-w\cdot N\big]$$
+$$\hat{N}^{*SCAM} \equiv argmax_N⁡ \big[p\cdot \hat{f}^{SCAM} (N)-w\cdot N\big]$$
 
-### GWR-Rakshit (GWR-R)
+### GWR-Rakshit (GWRR)
 
-The GWR-R model is simply the basic GWR model [@fotheringham1996geography; @brunsdon1999some; @fotheringham2003geographically], where subplot-specific yield responses were modeled as quadratic functions of the nitrogen rate, which for each subplot $j \in {1, 2, \dots, 1440}$ was specified as,
+The GWRR model is simply the basic GWR model [@fotheringham1996geography; @brunsdon1999some; @fotheringham2003geographically], where subplot-specific yield responses were modeled as quadratic functions of the nitrogen rate, which for each subplot $j \in {1, 2, \dots, 1440}$ was specified as,
 
@@
 The coefficients $\alpha_j$, $\beta_j$, and $\eta_j$ were continuous functions of subplot $j$’s coordinates ($lon_j$, $lat_j$).
-The GWR-R estimation produced subplot-specific estimates of coefficients $\hat{\alpha}_j$, $\hat{\beta}_j$, and $\hat{\eta}_j$, and so of the yield response function $\hat{f}_{gwr-r,j}(N)$ for $j = 1, 2, \dots, 1440$.
+The GWRR estimation produced subplot-specific estimates of coefficients $\hat{\alpha}_j$, $\hat{\beta}_j$, and $\hat{\eta}_j$, and so of the yield response function $\hat{f}^{GWRR}_j(N)$ for $j = 1, 2, \dots, 1440$.
 The estimated economically optimal N application rate for subplot $j$ was calculated by solving the subplot's profit maximization problem:
 
-$$\hat{N}_{gwr-r,j}^{*} \equiv argmax_N⁡[p\hat{f}_{gwr-r, j} (N) -wN], \;\; j \in 1, 2, \dots, 1440.$$
+$$\hat{N}^{*GWRR}_j \equiv argmax_N⁡[p\hat{f}^{GWRR}_j (N) -wN], \;\; j \in 1, 2, \dots, 1440.$$
 
-### GWR-Trevisan (GWR-T)
+### GWR-Trevisan (GWRT)
 
-The GWR-T model is also called as “mixed” GWR in the literature [@brunsdon1999some], where some parameters are fixed globally while others vary geographically.
+The GWRT model is also called as “mixed” GWR in the literature [@brunsdon1999some], where some parameters are fixed globally while others vary geographically.
 In our model, the coefficient on $N^2$ was estimated as a global parameter while the coefficient on $N$ was estimated subplot-specifically.
@@
 
-Let $\hat{f}_{gwr-t,j}(N)$ for $j = 1, 2, \dots, 1440$ denote the estimated yield response function for subplot $j$. The estimated economically optimal N application rate for subplot $j$ was then,
+Let $\hat{f}^{GWRT}_j(N)$ for $j = 1, 2, \dots, 1440$ denote the estimated yield response function for subplot $j$. The estimated economically optimal N application rate for subplot $j$ was then,
 
-$$\hat{N}^*_{gwr-t,j} \equiv argmax_N⁡[p\hat{f}_{gwr-t,j} (N) -wN] .$$
+$$\hat{N}^{*GWRT}_j \equiv argmax_N⁡[p\hat{f}^{GWRT}_j (N) -wN] .$$
 
-The Gaussian kernel function was used when estimating both GWR models, and the optimal bandwidth was selected through the corrected AIC approach [@fotheringham2003geographically].
+The Gaussian kernel function was used when estimating both GWR models (other kernel functions were also tried and the final conclusions are quantitatively similar; see appendix).
+For the optimal kernel bandwidth selection, while there are several frequently used approaches in the literature such as cross-validation [@cleveland1979robust; @bowman1984alternative] and Akaike Information Criterion (AIC) [@akaike1973], this study used the corrected version of the AIC approach following the most recent GWR literature [@fotheringham2003geographically; @fotheringham2017multiscale; @lu2017geographically], which is also the same approach used by @rakshit2020 and @trevisan2021spatial.
 The optimal bandwidth differed slightly across each simulated experiment, and the average bandwidth was around 18 meters.
 
-## The value of GWR-based VRA over scam-based URA
+## The value of GWR-based VRA over SCAM-based URA
 
@@
 
-$$\Pi_{scam}^* = 1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 \big[pf_{j, k} (\hat{N}_{scam}^* )-w\hat{N}_{scam}^*\big]$$
+$$\Pi^{*SCAM} = 1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 \big[pf_{j, k} (\hat{N}^{*SCAM})-w\hat{N}^{*SCAM}\big]$$
 
@@
 
-For $m = R, T$, the true per-ha net revenues ("profits") resulting from applying the profit-maximizing cell-specific N rate plan estimated by GWR-m were,
+The true per-ha net revenues ("profits") resulting from applying the profit-maximizing cell-specific N rate plan estimated by GWR (either GWRR or GWRT) model were,
 
-$$\Pi_{gwr-m}=1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 [pf_{j, k} (\hat{N}_{gwr-m, j}^*)-w\hat{N}_{gwr-m,j}^*]$$
+$$\Pi^{GWR}=1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 [pf_{j, k} (\hat{N}^{*GWR}_j)-w\hat{N}^{*GWR}_j]$$
 
-where $f_{j, k} (\hat{N}_{gwr-j}^*)$ denote the true yield generated at cell $(j, k)$ with subplot $l$'s N rate.
+where $f_{j, k} (\hat{N}^{*GWR}_j)$ denote the true yield generated at cell $(j, k)$ with subplot $j$'s GWR estimated N rate.
 
@@
 
-$$\Delta_{gwr-m} = \Pi_{gwr-m} - \Pi_{scam} .$$
+$$\Delta^{GWR} = \Pi^{GWR} - \Pi^{SCAM} .$$
 
@@
 
-$$\hat{\Pi}_{scam}^* = 1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 \big[p\hat{f}^{gwr}_{j, k} (\hat{N}_{scam}^* )-w\hat{N}_{scam}^*\big]$$
+$$\hat{\Pi}^{*SCAM} = 1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 \big[p\hat{f}^{GWR}_{j, k} (\hat{N}^{*SCAM} )-w\hat{N}^{*SCAM}\big]$$
 
-$$\hat{\Pi}_{gwr-m}^*=1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 [p\hat{f}^{gwr-m}_{j, k} (\hat{N}_{gwr-m}^{j*} )-w\hat{N}_{gwr-m}^{j*}]$$
+$$\hat{\Pi}^{*GWR}=1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 [p\hat{f}^{GWR}_{j, k} (\hat{N}^{*GWR}_{j} )-w\hat{N}^{*GWR}_{j}]$$
 
@@
 
-$$\hat{\Delta}_{gwr-m} = \hat{\Pi}_{gwr-m}^* - \hat{\Pi}_{scam}^*$$
+$$\hat{\Delta}^{GWR} = \hat{\Pi}^{*GWR} - \hat{\Pi}^{*SCAM}$$
 
@@
 
-$$bias = \hat{\Delta}_{gwr-m} - \Delta_{gwr-m}$$
+$$bias = \hat{\Delta}^{GWR} - \Delta^{GWR}$$
 
@@
 
-Figure \@ref(fig:pi-dif-dist) shows the distribution of $\Delta_{gwr-m}$, the true profit difference between the GWR-based VRA and the SCAM-based URA, at various price scenarios.
-The comparative advantage of GWR-R and GWR-T varies significantly depending on nitrogen-corn price ratio.
-Specifically, GWR-R performs better as the price ratio increases (as nitrogen becomes more expensive relative to corn), while the opposite is the case for GWR-T.
-At the low price ratio of 4.16 and 5.44, VRA based on GWR-R is no better than SCAM-based URA.
-However, when the price ratio is $10.35$, the median benefit of GWR-R is `r round(mean_data_value[type == "GWR-R" & pLabel == "10.35", pi_diff], digits = 2)`.
-On the other hand, the median benefit of VRA based on GWR-T when the price ratio is 4.16 is `r round(mean_data_value[type == "GWR-T" & pLabel == "4.16", pi_diff], digits = 2)`, but the its benefit is even negative at `r round(mean_data_value[type == "GWR-T" & pLabel == "10.35", pi_diff], digits = 2)` when the price ratio is 10.35.
+Figure \@ref(fig:pi-dif-dist) shows the distribution of $\Delta^{GWR}$, the true profit difference between the GWR-based VRA and the SCAM-based URA, at various price scenarios.
+The comparative advantage of GWRR and GWRT varies significantly depending on nitrogen-corn price ratio.
+Specifically, GWRR performs better as the price ratio increases (as nitrogen becomes more expensive relative to corn), while the opposite is the case for GWRT.
+At the low price ratio of 5.44, VRA based on GWRR is no better than SCAM-based URA.
+However, when the price ratio increases to $6.56$, the median benefit of GWRR is `r round(mean_data_value[type == "GWRR" & pLabel == "6.56", pi_diff], digits = 2)`.
+At high price ratio of 7.67, the median benefit increases to `r round(mean_data_value[type == "GWRR" & pLabel == "7.67", pi_diff], digits = 2)`.
+On the other hand, the median benefit of VRA based on GWRT when the price ratio is low of 5.44 is `r round(mean_data_value[type == "GWRT" & pLabel == "5.44", pi_diff], digits = 2)`, but the benefit reduces to `r round(mean_data_value[type == "GWRT" & pLabel == "6.56", pi_diff], digits = 2)` when the price ratio is 6.56, and `r round(mean_data_value[type == "GWRT" & pLabel == "7.67", pi_diff], digits = 2)` when 7.67.
 
@@
 A value lower than 1 means EONR is underestimated on average.
-GWR-R tends to over-estimate EONR at lower price ratios, but the magnitude of over-estimation goes down as the price ratio goes up.
-The opposite trend is true for GWR-T.
-At the price ratio of 10.35, the degree of EONR over-estimation is quite significant.
+GWRR tends to over-estimate EONR at lower price ratios, but the magnitude of over-estimation goes down as the price ratio goes up.
+The opposite trend is true for GWRT.
+At the high price ratio, the degree of EONR over-estimation is quite significant.
 Since a high-price ratio means nitrogen is relatively expensive, the economic cost of over-estimation of EONR increases with the price ratio.
 
-To illustrate the difference in the GWR-R and GWR-T outcomes, Figure \@ref(fig:true-vs-estimated-optn-gwr-r) presents for a single simulation round the estimated site-specific EONR plotted against the true site-specific EONR.
+To illustrate the difference in the GWRR and GWRT outcomes, Figure \@ref(fig:true-vs-estimated-optn-gwr-r) presents for a single simulation round the estimated site-specific EONR plotted against the true site-specific EONR.
 The site-specific EONR estimates are both inaccurate, but differently inaccurate.
-The range of EONR estimates by GWR-R is very wide because the coefficient on $N^2$ is allowed to vary site specifically in GWR-R.
+The range of EONR estimates by GWRR is very wide because the coefficient on $N^2$ is allowed to vary site specifically in GWRR.
 Since the estimation of the coefficient on $N^2$ is highly inaccurate, the range of estimated EONRs is much wider than the range of true site-specific EONR.
-But, GWR-T's range of EONR estimates is very narrow because the coefficient on $N^2$ is constrained to be equal across sites, making GWR-T fail to capture the EONR's true heterogeneity.
+But, GWRT's range of EONR estimates is very narrow because the coefficient on $N^2$ is constrained to be equal across sites, making GWRT fail to capture the EONR's true heterogeneity.
 
@@
 For example, the value of 10 would mean that the estimated value of GWR-based VRA over-estimates its true value by $10 per ha.
-As the figure suggests, VRA based on GWR-R appears to perform overwhelmingly better than it truly is, presenting significant positive bias across the price range.
-That is, researchers would tend to significantly over-estimate the value of VRA based on GWR-R.
-When the GWR estimates are considered to define true yield response, the inaccuracy of GWR-R generates over-estimation of the heterogeneity of yield response within the field, which can lead to significant over-estimation of the value of GWR-R itself.
+As the figure suggests, VRA based on GWRR appears to perform overwhelmingly better than it truly is, presenting significant positive bias across the price range.
+That is, researchers would tend to significantly over-estimate the value of VRA based on GWRR.
+When the GWR estimates are considered to define true yield response, the inaccuracy of GWRR generates over-estimation of the heterogeneity of yield response within the field, which can lead to significant over-estimation of the value of GWRR itself.
 
-GWR-T exhibits a different pattern of bias.
-At low price ratios, the GWR-T approach has smaller bias compared to GWR-R.
-This is partially because GWR-T tends to understate the heterogeneity of site-specific yield response function as was seen in figure \@ref(true-vs-estimated-optn-gwr-r).
+GWRT exhibits a different pattern of bias.
+At low price ratios, the GWRT approach has smaller bias compared to GWRR.
+This is partially because GWRT tends to understate the heterogeneity of site-specific yield response function as was seen in figure \@ref(fig:true-vs-estimated-optn-gwr-r).
 As the price ratio rises, bias increases.
-This is due to the significant over-estimation of EONR by GWR-T, as illustrated by figure \@ref(fig:bias-est-eonr).
-Unlike the GWR-R approach, the distribution of the bias by the GWR-T approach has a fat tail, indicating that there is a greater chance of encountering large positive bias in the estimated value of VRA over URA.
+This is due to the significant over-estimation of EONR by GWRT, as illustrated by figure \@ref(fig:bias-est-eonr).
+Unlike the GWRR approach, the distribution of the bias by the GWRT approach has a fat tail, indicating that there is a greater chance of encountering large positive bias in the estimated value of VRA over URA.
 
 Figure \@ref(fig:why-bias-many) illustrates how over-estimation of the value of VRA can occur.
-It shows yield response functions estimated by GWR-T and estimated yields associated with the GWR-based EONR rates and SCAM-based EONR rates for 50 randomly chosen cells in a single simulation.
+It shows yield response functions estimated by GWRT and estimated yields associated with the GWR-based EONR rates and SCAM-based EONR rates for 50 randomly chosen cells in a single simulation.
 Since GWR-based EONRs were obtained assuming the yield response functions estimated by GWR, by construction they out-perform the SCAM-based estimates in every cell.
@@
 
-# Discussions and conclusions
+# Discussion and conclusions
 
-Our simulation results show that generating site-specific $R_x$s by applying the basic GWR model (GWR-R) with quadratic functional form to OFPE data tends to have little economic value for site-specific $R_x$s when the true yield response function is quadratic-plateau.
-The GWR-R based VRA is on average no more profitable than SCAM-based URA under many price scenarios, particularly when nitrogen price is relatively low compared to the corn price.
+Our simulation results show that generating site-specific $R_x$s by applying the basic GWR model (GWRR) with quadratic functional form to OFPE data tends to have little economic value for site-specific $R_x$s when the true yield response function is quadratic-plateau.
+The GWRR based VRA is on average no more profitable than SCAM-based URA under many price scenarios, particularly when nitrogen price is relatively low compared to the corn price.
 This finding reveals the economic consequences of the widely recognized statistical inaccuracy issue of GWR estimation [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation] and also the problem of assuming quadratic functional form when the true yield response function follows the quadratic-plateau functional form like corn-nitrogen relationship.
 Precision agriculture practitioners should be cautious when using GWR for site-specific $R_xs$.
-If GWR-based approach must be employed to find site-specific input recommendations (e.g., due to lack of field and soil information), our simulation results show that GWR-T performs relatively better than GWR-R, though its profitability improvement against URA is only moderate.
+If GWR-based approach must be employed to find site-specific input recommendations (e.g., due to lack of field and soil information), our simulation results show that GWRT performs relatively better than GWRR, though its profitability improvement against URA is only moderate.
 
@@
 
-Most important, whether using GWR-T or GWR-R, researchers must be cautious about their estimated value of VRA when model is assumed to be quadratic when the true underlying yield-input response is quadratic-plateau in relity.
+Most important, whether using GWRT or GWRR, researchers must be cautious about their estimated value of VRA when model is assumed to be quadratic when the true underlying yield-input response is quadratic-plateau in relity.
 Our results show that it is likely that they will over-estimate their true values and the bias can be misleadingly high with non-negligible probability.
 The extremely high values of VRA reported in @trevisan2021spatial are likely to have reflected this bias.
-Indeed, the bias problem we have raised here is likely to be observed for other statistical methods because the bias comes from the assumption that the _estimated_ yield response functions are true.
-Whatever the underlying statistical method for yield response functions may be, researchers are likely to overestimate the true value of their methods.
-It would be an interesting future research to investigate the bias in other major statistical methods that are commonly used in the literature.
+Indeed, the bias problem we have raised here is likely to be observed for other statistical methods as well because the bias comes from the assumption that the _estimated_ yield response functions are true.
+Whatever the underlying statistical methods for yield response functions may be, researchers are likely to overestimate the true value of their methods.
+It would be an interesting future research to investigate the bias in other commonly used statistical methods in the literature on site-specific yield response estimation (such as regression with interaction terms of field characteristics, machine learning, and more) by using a similar simulation-based evaluation approach as done in this study.
 
@@
 
-```{r, fig.id = "pi-dif-dist", fig.cap = "The value of GWR-based VRA over SCAM-based URA for GWR-R and GWR-T", fig.height = 5, fig.width = 6}
+```{r, fig.id = "pi-dif-dist", fig.cap = "The value of GWR-based VRA over SCAM-based URA for GWRR and GWRT", fig.height = 5, fig.width = 6}
 g_value
@@
 
-```{r fig.id = "true-vs-estimated-coef-gwr-r", fig.cap = "Comparison of Estimated and True Coefficients"}
-g_comp_coef
+```{r fig.id = "bias-est-eonr", fig.cap = "Average bias in the estimation of EONR by GWRR and GWRT", fig.height = 5, fig.width = 6}
+g_eonr_bias
 ```
@@
 
-```{r fig.id = "bias-est-eonr", fig.cap = "Average bias in the estimation of EONR by GWR-R and GWR-T", fig.height = 5, fig.width = 6}
-g_eonr_bias
-```
-
-```{r fig.id = "bias-est-pi", fig.cap = "Bias in the estimation of the value of GWR-based VRA over SCAM-based URA for GWR-R and GWR-T", fig.height = 5, fig.width = 6}
+```{r fig.id = "bias-est-pi", fig.cap = "Bias in the estimation of the value of GWR-based VRA over SCAM-based URA for GWRR and GWRT", fig.height = 5, fig.width = 6}
 g_bias

### 2023-06-13 Writing/manuscript_gwr.rmd
supplementary appendix modified

@@
     reference_docx: "word_template.docx"
+    base_format: "bookdown::word_document2"
     plots:
@@
 results <-
-  here("Shared", "Results", "pi_data.rds") %>%
+  here("Shared/Results/gaussian/pi_data.rds") %>%
   readRDS() %>%

### 2023-06-13 Codes/1_gwr_estimation.R

@@ -33,8 +33,6 @@ library(tictoc)
 library(here)
 options(stringsAsFactors = FALSE)
 
-
-
 # === Set working directory ===#
 setwd(here())
 
@@ -43,14 +41,10 @@ setwd(here())
 fs::dir_ls(here("GitControlled", "Codes", "Functions"), full.names = TRUE) %>%
   lapply(., function(x) source(x))
 
-
-
 # /*===========================================================
 #' # Load simulated regression data
 # /*===========================================================
 field_with_design <- readRDS(here("Shared/Data/field_with_design.rds"))
-
-
 
 # /*===========================================================
 #' # GWR estimation of MC simulation data
@@ -60,22 +54,23 @@ field_with_design <- readRDS(here("Shared/Data/field_with_design.rds"))
 # choose the kernel used for GWR from:
 #   "gaussian", "bisquare", "exponential", "tricube", "boxcar"
 #*************************************
-kernel_choice = "bisquare"
-obw_choice = ifelse(kernel_choice %in% c("gaussian", "exponential"), 
-                    # continuous kernel
-                    18, 
-                    # discontinuous kernel
-                    100)
 
-tic()
+kernel_choice <- "gaussian"
+obw_choice <-
+  ifelse(
+    kernel_choice %in% c("gaussian", "exponential"),
+    # continuous kernel
+    18,
+    # discontinuous kernel
+    100
+  )
+
 mc_sim_results <-
-    lapply(
-        1:nrow(field_with_design),
-        function(x) run_mc_sim(x, field_with_design)
-    ) %>%
-    rbindlist()
-toc()
+  lapply(
+    1:nrow(field_with_design),
+    function(x) run_mc_sim(x, field_with_design)
+  ) %>%
+  rbindlist()
 
 #* save the field parameters
 saveRDS(mc_sim_results, here("Shared", "Results", kernel_choice, "mc_sim_results.rds"))
-

### 2023-06-15 Writing/JAAEA/1stRoundRevision/reply_to_reviewer_2.rmd
price history; a few other edits

@@
 # Reply to the Reviewer #2
+
+__Other changes__
+1. Subscript (j,k) changed to (j,i). k is already used in spline notation.
 
@@
 All comments are designed to strengthen the research.</span>
-General reply: We are very grateful
+General reply: We would like to express our sincere gratitude for the reviewer's careful and thorough review of our research paper.
+The insightful comments and suggestions have significantly contributed to improving the clarity, detail, and overall strength of our manuscript.
+We truly appreciate the time and effort the reviewer has dedicated to this review process.
+We have carefully addressed each of the comments and incorporated the necessary revisions into the manuscript.
 
@@
 
-It strikes me as odd that, even with a minor clause on line 207 of p.
+<span style = "color: blue;">It strikes me as odd that, even with a minor clause on line 207 of p.
 10, there is no real discussion of the corn price or nitrogen price in the methods section.
@@
 What is the underlying intuition regarding the dependence of the relative performance of GWRR/GWRT to the corn-to-nitrogen price ratio (though this is partially explained in the paragraph on pages 15-16)?
-Any intuition about the ratios of 4.2, 5.4, and 10.4?
+Any intuition about the ratios of 4.2, 5.4, and 10.4?</span>
 Response: That is our ignorance. Thank you for pointing it out. We added the historical summary of p and w. We choose the historically high (10 or 7), middle, and low price ratio.

### 2023-06-15 Writing/Online-Appendix.rmd
price history; a few other edits

--- 2023-06-08 Writing/Online-Appendix_supp.rmd
@@
 In the curve diagrams of the right panel, the y-axis is the kernel weight, and the x-axis is the ratio of (d_ab/h)."}
-#
+knitr::include_graphics(here("Shared/Figures/kernel_functions.png"))
 ```

### 2023-06-15 Codes/3_figures_illustrate.R

@@ -179,13 +179,14 @@ ggplot(data = kernel_data) +
     scale_y_continuous(breaks = c(0, 0.5, 1), limits = c(0, 1.1)) +
     theme(
         panel.grid = element_blank(),
+        panel.spacing = unit(1, "lines"),
         strip.background = element_blank(),
         strip.text.x = element_blank(),
         axis.title = element_blank(),
         axis.text = element_text(colour="black")
     )
 ggsave(here("Shared", "Figures", "kernel_functions.png"),
-       height = 5, width = 2, units = "in", dpi = 300)
+       height = 6, width = 2, units = "in", dpi = 300)
 
 
 

### 2023-06-15 Writing/supplemenraty_appendix.rmd

---
title: "Supplementary Appendix"
output:
  officedown::rdocx_document:
    toc: false
    toc_depth: 1
    number_sections: false
    reference_docx: "word_template_no_section_numbers.docx"
    base_format: "bookdown::word_document2"
    plots:
      style: Normal
      align: center
      caption:
       style: Image Caption
       pre: "Figure A"
       sep: ": "
    tables:
      style: Table
      layout: autofit
      width: 1.0
      caption:
       style: Table Caption
       pre: "Table A"
       sep: ": "
bibliography: PA.bib
csl: field-crops-research.csl
---

```{r echo = F, cache = F}
suppressMessages(library(knitr))
suppressMessages(library(here))
suppressMessages(library(officedown))
suppressMessages(library(officer))

opts_chunk$set(
  fig.align = "center",
  fig.retina = 5,
  warning = F,
  message = F,
  cache = F,
  echo = F,
  fig.cap = TRUE
)
```

```{r}
#--- packages ---#
library(data.table)
library(tidyverse)
library(flextable)
library(stringr)
library(sf)
library(lfe)
library(modelsummary)
library(patchwork)
library(ggplot2)
```

```{r figure_setup}
theme_update(
  axis.title.x =
    element_text(
      size = 12, angle = 0, hjust = .5, vjust = -0.3, family = "Times"
    ),
  axis.title.y =
    element_text(
      size = 12, angle = 90, hjust = .5, vjust = .9, family = "Times"
    ),
  axis.text.x =
    element_text(
      size = 10, angle = 0, hjust = .5, vjust = 1.5, family = "Times"
    ),
  axis.text.y =
    element_text(
      size = 10, angle = 0, hjust = 1, vjust = 0, family = "Times"
    ),
  axis.ticks =
    element_line(
      size = 0.3, linetype = "solid"
    ),
  axis.ticks.length = unit(.15, "cm"),
  #--- legend ---#
  legend.text =
    element_text(
      size = 10, angle = 0, hjust = 0, vjust = 0, family = "Times"
    ),
  legend.title =
    element_text(
      size = 10, angle = 0, hjust = 0, vjust = 0, family = "Times"
    ),
  legend.key.size = unit(0.5, "cm"),
  #--- strip (for faceting) ---#
  strip.text = element_text(size = 10),
  #--- plot title ---#
  plot.title = element_text(family = "Times", face = "bold", size = 12),
  #--- margin ---#
  # plot.margin = margin(0, 0, 0, 0, "cm"),
  #--- panel ---#
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background = element_blank(),
  panel.border = element_rect(fill = NA)
)
```

```{r include = FALSE}
kernel_ls <- c("gaussian", "bisquare", "exponential", "tricube", "boxcar")

gg_appendix <-
  data.frame(kernel = kernel_ls) %>%
  rowwise() %>%
  mutate(results = list(
    here("Shared", "Results", kernel, "pi_data.rds") %>%
      readRDS() %>%
      .[, type := ifelse(transfer == 0, "GWRR", "GWRT")] %>%
      .[, bias := pi_diff_est - pi_diff] %>%
      # only display the 25% (5.44), 50% (6.56), 75% (7.67) price ratio
      .[pRatio %in% c(5.44, 6.56, 7.67), ] %>%
      # === label price ratio
      .[, pLabelName := "Price Ratio (N/corn)"] %>%
      .[pRatio == 5.44, pLabel := "Low"] %>%
      .[pRatio == 6.56, pLabel := "Middle"] %>%
      .[pRatio == 7.67, pLabel := "High"] %>%
      .[, pLabel := factor(pLabel, levels = c("Low", "Middle", "High"))]
  )) %>%
  #* ===========================================================
  #* Plots of the value of GWR
  #* ===========================================================
  mutate(median_data_value = list(
    results %>%
      .[, .(pi_diff = median(pi_diff)),
        by = c("field_col", "pLabel", "type")
      ]
  )) %>%
  mutate(g_value = list(
    results %>%
      ggplot(data = .) +
      geom_histogram(
        aes(x = pi_diff),
        fill = NA,
        color = "blue",
        bins = 50,
        size = 0.2
      ) +
      geom_vline(
        data = median_data_value,
        aes(xintercept = pi_diff),
        color = "red",
        size = 0.5
      ) +
      geom_text(
        data = median_data_value, color = "red",
        aes(
          x = ifelse(pi_diff < 65, pi_diff + 5, pi_diff - 20),
          y = 150,
          label = paste0("Median = ", round(pi_diff, 2))
        ),
        angle = 0, hjust = -0.1, vjust = 0, size = 3
      ) +
      facet_grid(pLabel ~ type) +
      scale_y_continuous(expand = c(0, 0), limits = c(NA, 200)) +
      scale_x_continuous(breaks = 20 * (-2:3), limits = c(-45, 60)) +
      xlab("The value of VRA over URA ($ per ha)") +
      ylab("Number of Simulation Cases")
  )) %>%
  #* ===========================================================
  #* Plots of the bias in the value of GWR
  #* ===========================================================
  mutate(median_bias_data = list(
    results %>%
      .[, bias := pi_diff_est - pi_diff] %>%
      .[, .(bias = median(bias)),
        by = c("field_col", "pLabel", "type")
      ]
  )) %>%
  mutate(g_bias = list(
    results %>%
      .[, bias := pi_diff_est - pi_diff] %>%
      .[bias < 150, ] %>%
      ggplot(data = .) +
      geom_histogram(
        aes(x = bias),
        fill = NA,
        color = "blue",
        size = 0.2,
        bins = 50
      ) +
      geom_vline(
        data = median_bias_data, aes(xintercept = bias),
        color = "red",
        size = 0.5
      ) +
      geom_text(
        data = median_bias_data, color = "red",
        aes(
          x = ifelse(bias < 65, bias + 2, bias - 85), y = 100,
          label = paste0("Median = ", round(bias, 2))
        ),
        angle = 0, hjust = -0.1, vjust = 0, size = 3
      ) +
      facet_grid(pLabel ~ type) +
      scale_y_continuous(expand = c(0, 0)) +
      xlab("Bias in the Estimation of the Value of VRA over URA ($ per ha)") +
      ylab("Number of Simulation Cases")
  )) %>%
  select(kernel, g_value, g_bias)
```

# Appendix: Results with Alternative Kernel Functions {-}

There are many different kernel functions to define the distance-decay weightings for GWR model. In the main text, the Gaussian kernel function was use, which can be mathematically represented as follows:

\begin{equation}
w_{ab}=exp⁡(-0.5[\frac{d_{ab}}{h}]^2 ),
(\#eq:q)
\end{equation}

where $d_{ab}$ denotes the Euclidean distance between observation $b$ and regression location $a$, $w_{ab}$ denotes the kernel weight assigned to observation $b$, and $h$ denotes the bandwidth.

This appendix compares several other alternative kernel functions, including the Exponential, Boxcar, Bi-square, and Tri-cube, in additional to the Gaussian. The functional forms and graphical representations of these kernels can be found in Figure A\@ref(fig:kernel). The estimation results obtained using alternative kernel functions, apart from the Gaussian kernel, are presented in Figures A\@ref(fig:value-kernel-bs) through A\@ref(fig:bias-kernel-boxcar).

```{r, fig.id = "kernel", fig.cap = "List of Kernel functions"}
knitr::include_graphics("kernel_function_list.png")
```

For the case of Exponential kernel, which is a continuous kernel like the Gaussian, the optimal bandwidth selection follows a similar corrected AIC approach and results in a similar bandwidth of 18 meters. For the discontinuous kernels of Boxcar, Bi-square, and Tri-cube, however, the 18-meter bandwidth does not encompass a sufficient number of neighboring observations for reliable local regressions, resulting in unrealistic estimation outcomes. To address this issue, an empirical bandwidth of 100 meters is chosen for these discontinuous kernels to enable the inclusion of an adequate number of local observations. Other bandwidth values (such as 80 meters, 150 meters) are also conducted and the resulting estimation outcomes are found to be comparable.

Overall, the economic evaluation results of GWR models presented in this study are not significantly influenced by the selection of the kernel function in GWR estimation. Despite slight variations in calculated profit and bias among the different kernels, the qualitative consistency of the final conclusions remains intact regardless of the chosen kernel.

## Comparing the values of GWR-based VRA and SCAM-based URA {-}

Figures A\@ref(fig:value-kernel-bs) through A\@ref(fig:value-kernel-boxcar) show the distribution of the true economic value of GWR using four different kernels: Bi-square, Exponential, Tri-cube, and Boxcar.

\begin{equation}
\Delta^{GWR}=\Pi^{GWR}-\Pi^{SCAM}
(\#eq:label)
\end{equation}

Using the Gaussian kernel, we found that GWRR performs better as the price ratio increases, and GWRT performs better as the price ratio decreases (see Figure 3 of the main text). This holds true across all the other kernel function choices. Although there are some variations in the magnitudes of $\Delta^{GWR}$ among different kernel function choices, these differences do not significantly affect the conclusions drawn in the main text.

```{r, fig.id = "value-kernel-bs", fig.cap = "The value of GWR-based VRA over SCAM-based URA for GWRR and GWRT using the Bi-square kernel", fig.height = 3.5}
gg_appendix$g_value[[2]]
```

```{r, fig.id = "value-kernel-exponential", fig.cap = "The value of GWR-based VRA over SCAM-based URA for GWRR and GWRT using the Exponential kernel", fig.height = 3.5}
gg_appendix$g_value[[3]]
```

```{r, fig.id = "value-kernel-tricube", fig.cap = "The value of GWR-based VRA over SCAM-based URA for GWRR and GWRT using the Tri-cube kernel", fig.height = 3.5}
gg_appendix$g_value[[4]]
```

```{r, fig.id = "value-kernel-boxcar", fig.cap = "The value of GWR-based VRA over SCAM-based URA for GWRR and GWRT using the Boxcar kernel", fig.height = 3.5}
gg_appendix$g_value[[5]]
```

## Bias in the estimation of the value of GWR-based VRA {-}

Figures A\@ref(fig:bias-kernel-bs) through A\@ref(fig:bias-kernel-boxcar) show the distribution of the bias in the estimated economic value of GWR. Similar to the findings from using the Gaussian kernel presnted in Figure 6 under the Gaussian kernel, the GWRR consistently exhibits significant over-estimation of the value of GWR-based VRA across all other kernel function choices. Also, the GWRT demonstrates smaller over-estimation at low price ratios compared to GWRR, while the over-estimation increases as price ratio rises. The presence of a similar fat tail in the GWRT bias distribution is also evident. The magnitudes of the estimation bias vary across kernel function choices, but the differences are not substantial and do not affect qualitatively our conclusions drawn in the main text.

```{r, fig.id = "bias-kernel-bs", fig.cap = "Bias in the estimation of the value of GWR-based VRA over SCAM-based URA for GWRR and GWRT using the Bi-square kernel", fig.height = 3.5}
gg_appendix$g_bias[[2]]
```

```{r, fig.id = "bias-kernel-exponential", fig.cap = "Bias in the estimation of the value of GWR-based VRA over SCAM-based URA for GWRR and GWRT using the Exponential kernel", fig.height = 3.5}
gg_appendix$g_bias[[3]]
```

```{r, fig.id = "bias-kernel-tricube", fig.cap = "Bias in the estimation of the value of GWR-based VRA over SCAM-based URA for GWRR and GWRT using the Tri-cube kernel", fig.height = 3.5}
gg_appendix$g_bias[[4]]
```

```{r, fig.id = "bias-kernel-boxcar", fig.cap = "Bias in the estimation of the value of GWR-based VRA over SCAM-based URA for GWRR and GWRT using the Boxcar kernel", fig.height = 3.5}
gg_appendix$g_bias[[5]]
```

### 2023-06-16 Writing/JAAEA/1stRoundRevision/reply_to_reviewer_2.rmd
finalize appendix; clear the folder;

@@
 1. Subscript (j,k) changed to (j,i). k is already used in spline notation. 
+2. Title of figures. Explicitly add what low, middle, and high mean so the reader do not need to go back to the main text to search the definitions.
 
@@
 
-One of the most important questions in the literature relates to how variable rate technologies (VRT) can reduce negative externalities like fertilizer and chemical runoff and leaching.
+<span style = "color: blue;">One of the most important questions in the literature relates to how variable rate technologies (VRT) can reduce negative externalities like fertilizer and chemical runoff and leaching.
 Clearly, this is not the research objective, and addressing a much more burning question in the literature would involve additional terms in the equation on p.
 10, line 294 that represent the negative environmental externalities.
-The authors should clarify early on that “economically optimal” means “privately optimal” rather than “socially optimal.”
-Reply: That is correct.
-Thank you for the reminder.
-We modified the writing and made it more explicit that the economically optimal VRT is privately optimal which only considers farmer’s private profit.
-Environmental externalities were not considered in this study.
+The authors should clarify early on that “economically optimal” means “privately optimal” rather than “socially optimal.”</span>
+Reply: Thank you for the suggestion of clarifying the definition of "economically optimal".
+We added some explicit description in the introduction section (page xx, lines xxx) that the economical optimization in this study only includes farmers' private profit, and environmental externalities are not considered in this study.
 
@@
 Any intuition about the ratios of 4.2, 5.4, and 10.4?</span>
-Response: That is our ignorance. Thank you for pointing it out. We added the historical summary of p and w. We choose the historically high (10 or 7), middle, and low price ratio.
-Reply: Figure of historical price trend in the appendix; argue that our partial explanation is sufficient.
+Reply: Thank you for bringing up this point regarding the discussion of price information in the study.
+We have included a brief discussion of the historical corn and nitrogen prices in the results section (page x, lines xxx), explaining the three ratios represented the historically low, middle, and high price ratio scenarios.
+Additionally, we have created an appendix in the supplementary material (Appendix I: Historical Corn and Nitrogen Prices) to provide a more detailed description of the collection, calculation, and summary statistics of the historical price data.
+We also apologize for the typos of the price ratios 4.16, 5.44 and 10.35 in the previous version manuscript.
+The correct price ratios should be 5.44, 6.56, and 7.67.
+They were all corrected in the revised manuscript.
+For the underlying intuition regarding the dependence of relative performance of GWRR/GWRT to the nitrogen-corn price ratio, as explained in the paragraphs on pages 15-16 of the original manuscript, we believe the main difference arises from the specification of the $N^2$ coefficient in the models The GWRR model allows for a varying coefficient on $N^2$, leading to a wider range of estimated EONRs, while the GWRT model restricts the $N^2$ to be constant, leading to a narrower range of estimated EONRs.
+At higher nitrogen-corn price ratio, where nitrogen is relatively more expensive, the true range of EONRs should be larger, and therefore the economic penalty of GWRR's over-estimation of EONR range will be smaller.
+On the opposite, at lower nitrogen-corn price ratio, the true EONR range will be smaller, and the GWRT's under-estimation of EONR range is less of an issue.
+We believe this explanation adequately addresses the intuition behind the observed results.
+However, if the reviewer feels that further clarification is needed, please let us know, and we will be more than willing to provide additional discussion to enhance the understanding of our findings.
 

### 2023-06-16 Writing/manuscript_gwr.rmd
price history; a few other edits
finalize appendix; clear the folder;

@@
 They estimated site-specific yield response functions by applying GWR techniques on data from OFPEs [@bullock2019data], and reported dramatic results, estimating an average potential gain of \$65 ha$^{-1}$ from applying seed and N at optimal uniform rates (instead of at the rates the farmers would have chosen if not participating in the research), and an additional potential gain of \$58 ha$^{-1}$ when changing from optimal uniform application rates to optimal site-specific application rates.
-This is rather surprising given the often-reported poor statistical accuracy of GWR estimates [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation] and also much lower value of VRA over URA reported in previous studies (cite).
+This is rather surprising given the often-reported poor statistical accuracy of GWR estimates [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation] and also much lower value of variable rate application over uniform rate application reported in previous studies (cite).
 @rakshit2020 also applied GWR to on-farm experiment data.
@@
 
-The second source of over-estimation bias is endemic to any study that evaluates the value of variable rate application, not just @trevisan2021spatial.
+The second source of over-estimation bias is endemic to any study that evaluates the value of variable rate application (VRA), not just @trevisan2021spatial.
 In general, researchers take the following steps to estimate the value of VRA using OFPE data [e.g., @anselin2004spatial; @swinton1998evaluating; @bullock2002adding; @liu2006site]: (1) estimate site-specific yield response functions based on a method chosen by the researcher; (2) use the estimated yield response functions to estimate the economically optimal site-specific input rates (EOIRs) and economically optimal uniform input rates; (3) plug the estimated site-specific EOIRs and uniform EOIR into the estimated yield response functions to calculate estimated profits under both strategies; and (4) find the difference in the two strategies' estimated profits.
@@
 
-The primary objective of this study is examine the degree and direction of bias in the estimation of the economic value of GWR-based variable rate application (VRA) when GWR model is specified as quadratic when the true yield response function follows the quadratic-plateau functional form.
+The primary objective of this study is examine the degree and direction of bias in the estimation of the economic value of GWR-based site-specific nitrogen rate recommendations (or "variable rate application", VRA) when GWR model is specified as quadratic when the true yield response function follows the quadratic-plateau functional form.
 We evaluate two sets of GWR quadratic specifications used in @rakshit2020 and @trevisan2021spatial.
@@
 As part of identifying bias in the estimation of the economic value of VRA based on the GWR approaches, we evaluate their actual values.
-Finally, we also evaluate their relative performances compared to URA based on shape-constrained additive model approach.
+Finally, we also evaluate their relative performances compared to uniform rate application (URA) based on shape-constrained additive model approach.
+It should be noted that the economical optimization in this study only includes farmers' private profit, while the environmental externalities (such as fertilizer runoff and leaching) are not considered.
 
@@
 In each simulation, six trial N rates were assigned by calculating the 0%, 20%, 40%, 60%, 80%, and 100% quantiles of the simulation's true cell-specific optimal N rates.
-When using the historical average corn and N prices (past 20 years, 2002-2021), the means of these trial N rates across simulations were approximately, {80, 130, 154, 184, 219, and 270} kg ha$^{-1}$.
+When using the historical average corn and N prices (of the past two decades from 2002 to 2022), the means of these trial N rates across simulations were approximately {80, 130, 154, 184, 219, and 270} kg ha$^{-1}$, while the differences between simulations were small and negligible.
 
@@
 
-Figure \@ref(fig:pi-dif-dist) shows the distribution of $\Delta^{GWR}$, the true profit difference between the GWR-based VRA and the SCAM-based URA, at various price scenarios.
+Figure \@ref(fig:pi-dif-dist) shows the distribution of $\Delta^{GWR}$, the true profit difference between the GWR-based VRA and the SCAM-based URA, at three different price scenarios which represent the historically low (5.44), middle (6.56), and high (7.67) nitrogen-corn price ratio (\$/kg : \$/kg).
+Historical corn ($p$) and nitrogen fertilizer ($w$) prices from 2002 to 2022 were obtained from the USDA National Agricultural Statistics Service (NASS, 2022) and DTN Retail Fertilizer Trends (DTN, 2022), and were transformed into monthly data.
+The nitrogen-corn price ratios were calculated as the nitrogen fertilizer price ($w$) divided by corn price ($p$).
+Further information regarding the collection, calculation, and summary statistics of the price data can be found in Appendix I: Historical Corn and Nitrogen Prices in the supplementary material.
+
 The comparative advantage of GWRR and GWRT varies significantly depending on nitrogen-corn price ratio.
-Specifically, GWRR performs better as the price ratio increases (as nitrogen becomes more expensive relative to corn), while the opposite is the case for GWRT.
+Specifically, GWRR performs better as the price ratio increases (that is, as nitrogen becomes more expensive relative to corn), while the opposite is the case for GWRT.
 At the low price ratio of 5.44, VRA based on GWRR is no better than SCAM-based URA.

### 2023-06-16 Writing/supplementary_appendix.rmd
finalize appendix; clear the folder;

--- 2023-06-15 Writing/supplemenraty_appendix.rmd
@@
 ```{r include = FALSE}
-kernel_ls <- c("gaussian", "bisquare", "exponential", "tricube", "boxcar")
+kernel_ls <- c("gaussian", "exponential", "boxcar", "bisquare", "tricube")
 
@@
 
-# Appendix: Results with Alternative Kernel Functions {-}
+# Appendix I: Historical Corn and Nitrogen Prices {-}
+
+Figure A\@ref(fig:price) illustrates the historical prices of corn ($p$) and nitrogen fertilizer ($w$), along with the corresponding nitrogen-corn price ratios, during the two-decade period from 2002 to 2022.
+
+```{r, fig.id = "price", fig.cap = "Historical monthly variations in corn price, nitrogen fertilizer price, and the corresponding nitrogen-corn price ratio, 2002-2022"}
+knitr::include_graphics("price_ratio_history.png")
+```
+
+Corn prices were sourced from the USDA National Agricultural Statistics Service [@NASS2022] in monthly frequency from 2002 to 2022.
+As shown in the top panel of Figure A1, the corn prices fluctuated between \$0.07/kg and \$0.30/kg, with an average of $0.15/kg.
+
+Nitrogen prices were collected from two sources.
+The USDA National Agricultural Statistics Service provided yearly nitrogen fertilizer prices for the period 2002 to 2014.
+The DTN Retail Fertilizer Trends [@DTN2022] provided weekly nitrogen fertilizer prices from 2015 to 2022.
+To align with the monthly corn price data, the nitrogen price data from both sources were combined and converted into monthly data.
+Three most commonly used nitrogen fertilizer types were included: Liquid urea-ammonium nitrate with 28 percent nitrogen (UAN28), Liquid urea-ammonium nitrate with 32 percent nitrogen (UAN32), and anhydrous ammonia (ANHYD).
+All prices were all converted to the per kilogram (kg) of nitrogen basis.
+As shown in the middle panel of Figure A1, the nitrogen prices ranged from \$0.34/kg to \$2.37/kg, with an average of \$0.98/kg.
+
+The nitrogen-corn price ratios were calculated as the nitrogen fertilizer price ($w$) divided by corn price ($p$), and the results were shown in the bottom panel of Figure A1.
+This study took the values at the 25th, 50th, and 75th percentiles of the historical monthly price ratios (pooled over the three types of nitrogen fertilizer) from 2002 to 2022.
+These three values were used to represent the low (5.44), middle (6.56), and high (7.67) price ratio scenarios.
+For consistency purposes, in the profitability calculations the corn price was selected at approximately the Spring 2022 price of \$0.28/kg.
+Consequently, the corresponding nitrogen prices for the three price ratio scenarios were approximately 5.44×0.28 = \$1.52/kg, 6.56×0.28 = \$1.84/kg, and 10.35×0.28 = \$2.15/kg.
+It is important to note that when different corn prices are used, the resulting profits of GWR will vary accordingly, but the variation will be proportional to the result of selected corn price and does not qualitatively alter the final conclusions.
+
+# Appendix II: Results with Alternative Kernel Functions {-}
 
@@
 
-```{r, fig.id = "kernel", fig.cap = "List of Kernel functions"}
+```{r, fig.id = "kernel", fig.cap = "List of Kernel functions for GWR modeling.
+In the graphs of kernel function curves, the y-axis is the kernel weight, and the x-axis is the ratio of ($d_{ab}/h$).
+"}
 knitr::include_graphics("kernel_function_list.png")
@@
 
-Figures A\@ref(fig:value-kernel-bs) through A\@ref(fig:value-kernel-boxcar) show the distribution of the true economic value of GWR using four different kernels: Bi-square, Exponential, Tri-cube, and Boxcar.
+Figures A\@ref(fig:value-kernel-exp) through A\@ref(fig:value-kernel-tricube) show the distribution of the true economic value of GWR using four different kernels: Exponential, Boxcar, Bi-square, and Tri-cube.
 
@@
 
-```{r, fig.id = "value-kernel-bs", fig.cap = "The value of GWR-based VRA over SCAM-based URA for GWRR and GWRT using the Bi-square kernel", fig.height = 3.5}
+```{r, fig.id = "value-kernel-exp", fig.cap = "The true economic value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios (5.44 (low), 6.56 (middle), and 7.67 (high) $ kg^(-1)  / $ kg^(-1)), using Exponential kernel function", fig.height = 3.5}
 gg_appendix$g_value[[2]]
@@
 
-```{r, fig.id = "value-kernel-exponential", fig.cap = "The value of GWR-based VRA over SCAM-based URA for GWRR and GWRT using the Exponential kernel", fig.height = 3.5}
+```{r, fig.id = "value-kernel-boxcar", fig.cap = "The true economic value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios (5.44 (low), 6.56 (middle), and 7.67 (high) $ kg^(-1)  / $ kg^(-1)), using Boxcar kernel function", fig.height = 3.5}
 gg_appendix$g_value[[3]]
@@
 
-```{r, fig.id = "value-kernel-tricube", fig.cap = "The value of GWR-based VRA over SCAM-based URA for GWRR and GWRT using the Tri-cube kernel", fig.height = 3.5}
+```{r, fig.id = "value-kernel-bs", fig.cap = "The true economic value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios (5.44 (low), 6.56 (middle), and 7.67 (high) $ kg^(-1)  / $ kg^(-1)), using Bi-square kernel function", fig.height = 3.5}
 gg_appendix$g_value[[4]]
@@
 
-```{r, fig.id = "value-kernel-boxcar", fig.cap = "The value of GWR-based VRA over SCAM-based URA for GWRR and GWRT using the Boxcar kernel", fig.height = 3.5}
+```{r, fig.id = "value-kernel-tricube", fig.cap = "The true economic value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios (5.44 (low), 6.56 (middle), and 7.67 (high) $ kg^(-1)  / $ kg^(-1)), using Tri-cube kernel function", fig.height = 3.5}
 gg_appendix$g_value[[5]]
@@
 
-Figures A\@ref(fig:bias-kernel-bs) through A\@ref(fig:bias-kernel-boxcar) show the distribution of the bias in the estimated economic value of GWR.
-Similar to the findings from using the Gaussian kernel presnted in Figure 6 under the Gaussian kernel, the GWRR consistently exhibits significant over-estimation of the value of GWR-based VRA across all other kernel function choices.
+Figures A\@ref(fig:bias-kernel-exp) through A\@ref(fig:bias-kernel-tricube) show the distribution of the bias in the estimated economic value of GWR.
+Similar to the findings from using the Gaussian kernel presented in Figure 6 under the Gaussian kernel, the GWRR consistently exhibits significant over-estimation of the value of GWR-based VRA across all other kernel function choices.
 Also, the GWRT demonstrates smaller over-estimation at low price ratios compared to GWRR, while the over-estimation increases as price ratio rises.
@@
 
-```{r, fig.id = "bias-kernel-bs", fig.cap = "Bias in the estimation of the value of GWR-based VRA over SCAM-based URA for GWRR and GWRT using the Bi-square kernel", fig.height = 3.5}
+```{r, fig.id = "bias-kernel-exp", fig.cap = "Bias in the estimation of the value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios (5.44 (low), 6.56 (middle), and 7.67 (high) $ kg^(-1)  / $ kg^(-1)), using Exponential kernel function", fig.height = 3.5}
 gg_appendix$g_bias[[2]]
@@
 
-```{r, fig.id = "bias-kernel-exponential", fig.cap = "Bias in the estimation of the value of GWR-based VRA over SCAM-based URA for GWRR and GWRT using the Exponential kernel", fig.height = 3.5}
-gg_appendix$g_bias[[3]]
+```{r, fig.id = "bias-kernel-boxcar", fig.cap = "Bias in the estimation of the value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios (5.44 (low), 6.56 (middle), and 7.67 (high) $ kg^(-1)  / $ kg^(-1)), using Boxcar kernel function", fig.height = 3.5}
+gg_appendix$g_value[[3]]
 ```
 
-```{r, fig.id = "bias-kernel-tricube", fig.cap = "Bias in the estimation of the value of GWR-based VRA over SCAM-based URA for GWRR and GWRT using the Tri-cube kernel", fig.height = 3.5}
-gg_appendix$g_bias[[4]]
+```{r, fig.id = "bias-kernel-bs", fig.cap = "Bias in the estimation of the value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios (5.44 (low), 6.56 (middle), and 7.67 (high) $ kg^(-1)  / $ kg^(-1)), using Bi-square kernel function", fig.height = 3.5}
+gg_appendix$g_value[[4]]
 ```
 
-```{r, fig.id = "bias-kernel-boxcar", fig.cap = "Bias in the estimation of the value of GWR-based VRA over SCAM-based URA for GWRR and GWRT using the Boxcar kernel", fig.height = 3.5}
-gg_appendix$g_bias[[5]]
+```{r, fig.id = "bias-kernel-tricube", fig.cap = "Bias in the estimation of the value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios (5.44 (low), 6.56 (middle), and 7.67 (high) $ kg^(-1)  / $ kg^(-1)), using Tri-cube kernel function", fig.height = 3.5}
+gg_appendix$g_value[[5]]
 ```

### 2023-06-16 Writing/knit_appendix.R

@@ -1,1 +1,0 @@
-rmarkdown::render(here::here("GitControlled/Writing/Online-Appendix_supp.rmd"))

### 2023-06-21 Codes/01_price_data.rmd
reply to reviewer 1

# Objective

+ Create monthly nitrogen-corn price ratio data from 2002 to 2022

## Preparation

```{r}
# === Packages ===#
library(data.table)
library(tidyverse)
library(tidyr)
library(dplyr)
library(magrittr)
library(stringr)
library(ggplot2)
library(ggpubr)
library(here)
options(stringsAsFactors = FALSE)
```

## Load raw data

**NASS_fertilizer_price_yearly.csv**

+ source: NASS Quick Stat -> Survey -> Economics -> Prices Paid -> Nitrogen -> Price Paid
+ temporal resolution: yearly
+ period: 2002-2014

**NASS_fertilizer_index.csv**

+ source: NASS Quick Stat -> Survey -> Economics -> Prices Paid -> Nitrogen -> INDEX FOR PRICE PAID, 2011
+ temporal resolution: monthly
+ period: 1990-2022

**NASS_corn_price.csv**

+ source: NASS Quick Stat -> Survey -> Crops -> Field Crops -> Corn -> PRICE RECEIVED -> CORN, GRAIN - PRICE RECEIVED, MEASURED IN $ / BU
+ temporal resolution: monthly
+ period: 1908-2022

**DTN Fertilizer Trends_weekly.csv**

+ source: Quinn, R. (2022, March 2). DTN Retail Fertilizer Trends. DTN- Progressive Farmer. https://www.dtnpf.com/agriculture/web/ag/crops/article/2022/03/02/average-retail-fertilizer-prices
+ temporal resolution: weekly
+ period: 1908-2022

```{r}
#* corn price (1908-2022, monthly)
NASS_corn_monthly <-
  read.csv(here("Shared/Data/price_data/NASS_corn_price_monthly.csv")) %>%
  data.table() %>%
  .[, .(Year, Period, Value)] %>%
  .[Period != "MARKETING YEAR", ] %>%
  setnames("Value", "pCorn") %>%
  # === unit conversion: $/bushel to $/kg
  .[, pCorn := pCorn / 25.4] %>%
  print()

#* N fertilizer price (2002-2014, yearly)
NASS_N_yearly <-
  read.csv(here("Shared/Data/price_data/NASS_fertilizer_price_yearly.csv")) %>%
  data.table() %>%
  .[, .(Year, Data.Item, Value)] %>%
  setnames(c("Data.Item", "Value"), c("N_type", "pN")) %>%
  .[str_detect(N_type, "ANHYDROUS AMMONIA"), N_type := "ANHYD"] %>%
  .[str_detect(N_type, "28%"), N_type := "UAN28"] %>%
  .[str_detect(N_type, "32%"), N_type := "UAN32"] %>%
  # === convert to wide format
  dcast(Year ~ N_type, value.var = "pN") %>%
  # === unit conversion: raw $/ton to pure $/kg N
  .[, ANHYD := ANHYD / (2000 * 0.82) / 0.453592] %>%
  .[, UAN28 := UAN28 / (2000 * 0.28) / 0.453592] %>%
  .[, UAN32 := UAN32 / (2000 * 0.34) / 0.453592] %>%
  print()

#* N fertilizer price (2015-2022, weekly)
DTN_N_weekly <-
  read.csv(here("Shared/Data/price_data/DTN Fertilizer Trends_weekly.csv")) %>%
  data.table() %>%
  .[, Year := substr(Date.Range, nchar(Date.Range) - 3, nchar(Date.Range))] %>%
  .[, Week := substr(Date.Range, 1, nchar(Date.Range) - 5)] %>%
  .[, Month := substr(Date.Range, 1, 3)] %>%
  .[, Date.Range := NULL] %>%
  .[, Year := as.numeric(Year)] %>%
  .[, ANHYD := as.numeric(ANHYD)] %>%
  .[, UAN28 := as.numeric(UAN28)] %>%
  .[, UAN32 := as.numeric(UAN32)] %>%
  # === unit conversion: raw $/ton to pure $/kg N
  .[, ANHYD := ANHYD / (2000 * 0.82) / 0.453592] %>%
  .[, UAN28 := UAN28 / (2000 * 0.28) / 0.453592] %>%
  .[, UAN32 := UAN32 / (2000 * 0.34) / 0.453592] %>%
  print()
```

## Combine and build monthly data set

+ corn price: NASS monthly (2002-2022)
+ N price: NASS yearly (2002-2014) + DTN weekly (2015-2022)
+ N types: (ANHYD, UAN28, UAN32)

```{r}
#* month name data table
month_name <-
  data.table(
    Period = c(
      "JAN", "FEB", "MAR", "APR", "MAY", "JUN",
      "JUL", "AUG", "SEP", "OCT", "NOV", "DEC"
    ),
    Month = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12)
  )

#* pseudo monthly NASS N prices (2002-2014)
(
  NASS_N_monthly <-
    NASS_N_yearly %>%
    expand_grid(., month_name) %>%
    data.table()
)

#* monthly DTN N data (2015-2022)
(
  DTN_N_monthly <-
    DTN_N_weekly %>%
    dplyr::select(Year, Month, ANHYD, UAN28, UAN32) %>%
    # === aggregate weekly data to monthly
    .[, lapply(.SD, mean),
      .SDcols = c("ANHYD", "UAN28", "UAN32"),
      by = .(Year, Month)
    ] %>%
    .[, Month := toupper(Month)] %>%
    setnames("Month", "Period") %>%
    merge(., month_name, by = "Period")
)

#* N:Corn price ratio data
(
  price_ratio_data <-
    # === combine NASS and DNT data
    rbind(NASS_N_monthly, DTN_N_monthly) %>%
    # === merge corn price
    merge(NASS_corn_monthly, ., by = c("Year", "Period")) %>%
    # === convert to long format
    melt(id.vars = c("Year", "Period", "Month", "pCorn")) %>%
    setnames(c("variable", "value"), c("Ntype", "pN")) %>%
    # === price ratio
    .[, pRatio := pN / pCorn]
)

saveRDS(price_ratio_data, file = here("Shared/Data/price_ratio_data.rds"))
```

## Summary and graphing

```{r}
price_ratio_data <- readRDS(here("Shared/Data/price_ratio_data.rds"))
```

### summary statistics

```{r}
# corn price
# price_ratio_data$pCorn %>% quantile(na.rm = TRUE)
# N price (pool ANHYD, UAN28, UAN32 together)
# price_ratio_data$pN %>% quantile(na.rm = TRUE)
# price ratio (pool ANHYD, UAN28, UAN32 together)
price_ratio_data$pRatio %>% quantile(na.rm = TRUE, prob = c(0.05, 0.25, 0.5, 0.75, 0.95))
```

### 2023-06-21 Codes/02_data_preparation.rmd
reply to reviewer 1

# Objectives

+ Create simulated on-farm experiments, and estimates site-specific
+ Generate yield response coefficients by GWR model
+ Price history data

# Preparation

```{r}
# === Packages ===#
library(sp)
library(spdep)
library(spatialreg)
library(sf)
library(raster)
library(data.table)
library(tidyverse)
library(dplyr)
library(magrittr)
library(gstat)
library(GWmodel)
library(scam)
library(mgcv)
library(magic)
library(stringr)
library(ggplot2)
library(tictoc)
library(here)
options(stringsAsFactors = FALSE)
```

Source all the functions in the Functions folder

```{r}
#--- load all the functions ---#
fs::dir_ls(here("GitControlled/Codes/Functions"), full.names = TRUE) %>%
  lapply(., function(x) source(x))

#--- load price history data ---#
price_ratio_data <- readRDS(here("Shared/Data/price_ratio_data.rds"))
```

# Generate data for simulation

## Create a field

```{r}
field_data <-
  # ! This is where you set the experiment parameters
  CJ(
    plot_length = 12, # the length of a plot (in number of cells)
    plot_width = 3, # the width of a plot (in number of cells)
    cell_buffer = 1,
    aunit_length = 2, # the length of an analysis unit (in number of cells)
    aunit_width = 3, # the width of an analysis unit (in number of cells)
    cell = 6, # the length of a cell in meter
    #* how wide the field is
    field_col = c(144), # the number of cell columns
    #* how tall the field is
    field_row = 72, # the number of row columns
    sp_range = c(600),
    gstat_model = "Sph"
  ) %>%
  rowwise() %>%
  mutate(
    field_sf = list(
      make_field(
        field_col = field_col,
        field_row = field_row,
        aunit_length = aunit_length,
        aunit_width = aunit_width,
        cell = cell,
        cell_buffer = cell_buffer
      )
    ),
    #* price ratio scenarios
    pCorn = 7 / 25.4, # $/kg
    pRatio_ls = list(
      price_ratio_data$pRatio %>%
        quantile(na.rm = TRUE, prob = c(0.05, 0.25, 0.5, 0.75, 0.95)) %>%
        round(digits = 2)
    )
  )

#* save the fields
saveRDS(field_data, here("Shared/Data/field_data.rds"))
```

## Add trial design layout

```{r}
field_data <- readRDS(here("Shared/Data/field_data.rds"))

#* (use the fixed Latin Square design)
field_with_design <-
  field_data %>%
  rowwise() %>%
  mutate(design_layout = list(
    make_design_layout(plot_length, field_col)
  )) %>%
  dplyr::select(-plot_length) %>%
  unnest(cols = "design_layout") %>%
  filter(design_name == "Latin Square Fixed") %>%
  rowwise() %>%
  mutate(plot_block_id_data = list(
    gen_plot_block_ids(
      field_sf = field_sf,
      plot_length = plot_length,
      plot_width = plot_width,
      cols_plot_in_block = cols_plot_in_block,
      rows_plot_in_block = rows_plot_in_block,
      cell_buffer = cell_buffer
    )
  )) %>%
  mutate(field_sf = list(
    left_join(field_sf, plot_block_id_data, by = "cell_id")
  )) %>%
  dplyr::select(-plot_block_id_data) %>%
  mutate(
    data_file_name =
      paste0(
        stringr::str_replace_all(design_name, " ", ""),
        "_", field_col, ".rds"
      ) %>%
        here("Shared", "Data", .)
  )

#* save the fields with designs
saveRDS(field_with_design, here("Shared/Data/field_with_design.rds"))
```

## Generate true field parameters

```{r}
field_with_design <- readRDS(here("Shared/Data/field_with_design.rds"))

field_parameters <-
  readRDS(here("Shared/Data/field_data.rds")) %>%
  mutate(field_pars = list(
    gen_field_pars(
      sp_range = sp_range,
      gstat_model = gstat_model,
      field_sf = field_sf,
      nsim = 1000
    )
  ))

#* save the field parameters
saveRDS(field_parameters, here("Shared/Data/field_parameters.rds"))
```

## Create regression data

```{r}

field_parameters <- readRDS(here("Shared/Data/field_parameters.rds"))

tic()
lapply(
  1:nrow(field_with_design),
  function(x) gen_reg_data(x, field_with_design, field_parameters)
)
toc()
```

### 2023-06-21 Writing/manuscript_gwr.rmd
reply to reviewer 1

@@
 They estimated site-specific yield response functions by applying GWR techniques on data from OFPEs [@bullock2019data], and reported dramatic results, estimating an average potential gain of \$65 ha$^{-1}$ from applying seed and N at optimal uniform rates (instead of at the rates the farmers would have chosen if not participating in the research), and an additional potential gain of \$58 ha$^{-1}$ when changing from optimal uniform application rates to optimal site-specific application rates.
-This is rather surprising given the often-reported poor statistical accuracy of GWR estimates [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation] and also much lower value of variable rate application over uniform rate application reported in previous studies (cite).
+This is rather surprising given the often-reported poor statistical accuracy of GWR estimates [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation] and also much lower value of variable rate application (VRA) over uniform rate application (URA) reported in previous studies (cite).
 @rakshit2020 also applied GWR to on-farm experiment data.
@@
 
-The second source of over-estimation bias is endemic to any study that evaluates the value of variable rate application (VRA), not just @trevisan2021spatial.
+The second source of over-estimation bias is endemic to any study that evaluates the value of variable rate application, not just @trevisan2021spatial.
 In general, researchers take the following steps to estimate the value of VRA using OFPE data [e.g., @anselin2004spatial; @swinton1998evaluating; @bullock2002adding; @liu2006site]: (1) estimate site-specific yield response functions based on a method chosen by the researcher; (2) use the estimated yield response functions to estimate the economically optimal site-specific input rates (EOIRs) and economically optimal uniform input rates; (3) plug the estimated site-specific EOIRs and uniform EOIR into the estimated yield response functions to calculate estimated profits under both strategies; and (4) find the difference in the two strategies' estimated profits.
@@
 
-We pursue the objective by conducting Monte Carlo simulations in which we first generate and then analyze stylized OFPE data.
+We pursue the objective by conducting Monte Carlo simulations of 1000 rounds in which we first generate and then analyze stylized OFPE data.
 We cannot test which model specification results in more profitable site-specific nitrogen rate recommendations using real data because it is impossible to observe the true yield response functions using real-world data.
@@
 # Materials and Methods
+
+We conduct 1000 rounds of Monte Carlo simulation to answer our research questions. The process/components of the simulation analysis is detailed below.
 
@@
 An extensive literature examines the choice of functional form in yield response estimation [@cerrato1990comparison, @frank1990comparison, @bullock1994quadratic, @tembo2008crop].
-Our simulation assume that each cell $(j, k)$'s "true" yield response function is assumed to follow the commonly-used quadratic-plateau functional form:
+Our simulation assumes that each cell $(j, k)$'s "true" yield response function is assumed to follow the commonly-used quadratic-plateau functional form:
 

### 2023-06-21 Codes/0_data_preparation.R

@@ -1,170 +1,0 @@
-
-
-#'  This file creates simulated on-farm experiments, and estimates site-specific
-#'  yield response coefficients by GWR model.
-
-
-
-## ==============================================================
-##                          Preparation                        =
-## ==============================================================
-
-rm(list = ls())
-
-
-# === Packages ===#
-library(sp)
-library(spdep)
-library(spatialreg)
-library(sf)
-library(raster)
-library(data.table)
-library(tidyverse)
-library(dplyr)
-library(magrittr)
-library(gstat)
-library(GWmodel)
-library(scam)
-library(mgcv)
-library(magic)
-library(stringr)
-library(ggplot2)
-library(tictoc)
-library(here)
-options(stringsAsFactors = FALSE)
-
-
-
-# === Set working directory ===#
-setwd(here())
-
-# === load functions ===#
-#* source all the functions in the Functions folder
-fs::dir_ls(here("GitControlled", "Codes", "Functions"), full.names = TRUE) %>%
-    lapply(., function(x) source(x))
-
-
-# /*===========================================================
-#' # Create a field
-# /*===========================================================
-# ! Define field and plot characteristics here
-
-field_data <-
-    # ! This is where you set the experiment parameters
-    CJ(
-        plot_length = 12, # the length of a plot (in number of cells)
-        plot_width = 3, # the width of a plot (in number of cells)
-        cell_buffer = 1,
-        aunit_length = 2, # the length of an analysis unit (in number of cells)
-        aunit_width = 3, # the width of an analysis unit (in number of cells)
-        cell = 6, # the length of a cell in meter
-        #* how wide the field is
-        field_col = c(144), # the number of cell columns
-        #* how tall the field is
-        field_row = 72, # the number of row columns
-        sp_range = c(600),
-        gstat_model = "Sph"
-    ) %>%
-    rowwise() %>%
-    mutate(
-        field_sf = list(
-            make_field(
-                field_col = field_col,
-                field_row = field_row,
-                aunit_length = aunit_length,
-                aunit_width = aunit_width,
-                cell = cell,
-                cell_buffer = cell_buffer
-            )
-        ),
-        #* price ratio scenarios
-        pCorn = 7 / 25.4, # $/kg
-        pRatio_ls = list(c(4.16, 5.44, 6.56, 7.67, 10.35))
-    )
-
-#* save the fields
-saveRDS(field_data, here("Shared/Data/field_data.rds"))
[…]

### 2023-06-23 Writing/JAAEA/1stRoundRevision/reply_to_reviewer_2.rmd
Reviewer 2 comments completed

@@
 2. Title of figures. Explicitly add what low, middle, and high mean so the reader do not need to go back to the main text to search the definitions.
+3. Figure number on P. 17, line 335?
 
@@
 </span>  
-Reply: Very good point.
-What makes this study differ from previous studies is the model “value” is not measured by the accuracy of parameter estimates, but the ultimate economic return.
-We agree it is a good idea to add more review of previous studies and highlight our difference.
-More discussion, literature review, is added on page xx, lines xxx.
+Reply: Thank you for bringing up this important point.
+A significant aspect that sets this study apart from many previous studies lies in the evaluation of econometric models, where this study's measures are not based on the statistical accuracy of parameter estimates, but rather on the ultimate economic returns generated by the models.
+To emphasize this aspect, we have included an additional paragraph in the "Discussion and Conclusions" section (page x, lines xxx).
+It is worth noting that we were unable to identify a specific body of literature that exclusively focuses on assessing the value of general regression models.
+However, it is customary in the development of econometric models to evaluate their performance using statistical accuracy measures such as bias, mean squared error, and type I error, based on simulation data.
+We have referenced a few relevant studies of this nature to underscore the distinction of our economic value assessment approach.
 
@@
 <span style = "color: blue;">Where is there no in-text reference to, or explanation of, Figure 4? I do not know what to make of this lone figure.</span>  
-Reply: We apologize for this mistake.
-That figure was to compare the estimated and true GWR coefficients $\beta_1$ and $\beta_2$.
-But since we have already compared the estimated and true EONR's in the next figure, the coefficient comparisons do not seem necessary anymore, and we forgot to remove it from the final manuscript.
-It is now removed.
-(__Taro: I removed that figure.
-Is it OK, or you want to say something about it?__)
+Reply: We sincerely apologize for this oversight.
+The figure was originally included to compare the estimated and true GWR coefficients $\beta_1$ and $\beta_2$.
+However, as we have already compared the estimated and true EONRs in the subsequent figure, the coefficient comparisons are no longer necessary.
+Regrettably, we forgot to remove it from the final manuscript.
+We have now rectified this mistake and removed the figure accordingly.
+Thank you for bringing it to our attention.
+(__Taro: I removed that figure. Is it OK? Or you still want to keep it and say something about it?__)
 
@@
 Reply: Thank you for the suggestion.
-We added a few more explanations of the SCAM to make it more clear to the general JAAEA readers that it is a regression model that can fit a more flexible and non-linear response relationship, and also allows for shape constraints that can incorporate prior knowledge or theories.
-(see page xx, lines xxx of the revised manuscript.)
+We added a few more explanations of the SCAM (see page xx, lines xxx of the revised manuscript) to make it more clear to the general JAAEA readers that it is a regression model that can fit a more flexible and non-linear response relationship, and also allows for shape constraints that can incorporate prior knowledge or theories.
 
@@
 More information about this needs to be provided.</span>
-Reply: If we understand the question correctly, we believe it is asking about the robustness of GWR estimates to bandwidth selection.
-Choosing bandwidth is indeed a crucial step in GWR estimation, and there are many different bandwidth selection methods in the literature.
-In this study we used the corrected version of AIC approach [@fotheringham2017multiscale; @lu2017geographically] to determine the optimal bandwidth.
-It is a commonly used approach in practice, and also the same approach used by @rakshit2020 and @trevisan2021spatial which can make our simulation evaluations consistent.
-Since the corrected AIC method generates a unique bandwidth, we did not conduct any robustness check to bandwidths.
-We agree the GWR results could vary when choosing different bandwidths, but the choices of other bandwidth values other than the AIC-chosen one may be arbitrary.
-We added more discussions about bandwidth selection in page x, lines xxx of the revised manuscript.
+Reply: If we have correctly understood the question, it pertains to the robustness of GWR estimates with respect to bandwidth selection.
+We acknowledge that choosing the appropriate bandwidth is a critical step in GWR estimation, and the literature offers numerous methods for bandwidth selection.
+In our study, we employed the corrected version of the AIC approach as proposed by Fotheringham et al.
+[@fotheringham2017multiscale; @lu2017geographically] to determine the optimal bandwidth.
+This approach is widely used in practice and aligns with the methodology employed by Rakshit et al.
+[@rakshit2020] and Trevisan et al.
+[@trevisan2021spatial], thereby ensuring consistency in our simulation evaluations.
+
+As the corrected AIC method results in a unique bandwidth, we did not conduct additional robustness checks on alternative bandwidth values.
+While we acknowledge that GWR results may vary when using different bandwidths, selecting bandwidths other than the one determined by the AIC approach could introduce arbitrariness.
+Nevertheless, we have provided additional discussions about bandwidth selection in more depth in the revised manuscript on page x, lines xxx to provide more details and clarifications.
 
@@
 and the median benefit of VRA under GWRT is…?</span>
-Reply: Our apologies for the typos. We have corrected them and filled out the numbers. (See page x, line xx in the revised manuscript.)
+Reply: We apologize for the oversight in the sentences with blank numbers.
+We have rectified the issue by correcting the typos and providing the missing numbers.
+You can find the updated information on page x, line xx in the revised manuscript.
+Thank you for bringing this to our attention.
 
 <span style = "color: blue;">P. 15: You first discuss figure 6 and then move to figure 5. Put all figures in order.</span>  
-Reply: Thank you for pointing out the wrong order of the figures. We have corrected the order of Figures 5 and 6.
+Reply: Thank you for identifying the incorrect order of Figures 5 and 6.
+We apologize for the mistake, and we have corrected the order of the figures accordingly.
+The revised manuscript now reflects the correct sequence of Figures 5 and 6.
 
@@
 <span style = "color: blue;">P. 2, line 52: Basically or actually? Vagueness here makes it difficult to assess the degree to which OSU’s calculators are being used directly. </span>  
-Reply: The term "basically" used here does sounds a little oral and vague. We removed it in the revised manuscript (see page x, line xxx) to avoid any confusion.
+Reply: The term "basically" used in that context does appear informal and imprecise.
+In the revised manuscript, we have removed the term "basically" (see page x, line xxx) to ensure clarity and eliminate any potential confusion.
 
 <span style = "color: blue;">P. 2, line 54: To avoid confusing a general agricultural economics audience, I would use an abbreviation other than Rx for site-specific recommendations. </span>  
-Reply: In precision agriculture, the site-specific recommendation map  is commonly called "prescription" or "$R_x$" by researchers and the industry.
-There may be other abbreviations but they are not as popular as the "$R_x$".
-We added a brief note to explain that "$R_x$" means "prescription" in where "$R_x$" first shows up (page x, line xxx in revised manuscript) to make sure the abbreviation's meaning is clear to the general agricultural economics audience who are not familiar with precision agriculture.
+Reply: In precision agriculture, the site-specific recommendation map is commonly referred to as a "prescription" or denoted as "$R_x$" by both researchers and industry professionals.
+While there may be other abbreviations in use, they are not as widely recognized as "$R_x$".
+To ensure clarity for readers who may not be familiar with precision agriculture terminology, we have included a brief note explaining that "$R_x$" represents "prescription" when it is first mentioned (page x, line xxx in the revised manuscript).
+This clarification aims to make the meaning of the abbreviation clear to a broader agricultural economics audience.
 
 <span style = "color: blue;">P. 2, lines 49-60: All of these current commercial examples would work better as a footnote as they may become inaccurate in the next 3-10 years (or fewer). </span>  
-Reply: Thank you for the suggestion. We also agree putting those commercial examples in a footnote is a better idea. Those part of contents is now all in footnote 1 on page xx.
+Reply: Thank you for the suggestion.
+We agree that placing the commercial examples in a footnote is a better approach.
+As per your suggestion, all the relevant content has been moved to footnote 1 on page xx of the revised manuscript.
 
@@
 I would consider starting a new paragraph with the sentence beginning on line 97.</span>
-Reply: We followed the reviewer's suggestion and broke those discussion into two paragraphs.
-The second paragraph starts on page x, line xx.
-We also made some slight wording changes to the beginning of this paragraph.
+Reply: Thank you for the suggestion.
+We have followed this suggestion and divided the discussion into two paragraphs.
+The second paragraph now begins on page x, line xx.
+Additionally, we have made slight wording changes to the beginning of this paragraph to enhance clarity and coherence.
 
 <span style = "color: blue;">P. 7, line 137: This comment should have been removed by the authors prior to manuscript submission.</span>  
-Reply: This typo has been removed. Thank you for pointing it out.
+Reply: This typo has been removed. Thank you for bring it to our attention.
 
 <span style = "color: blue;">P. 9, line 189: The acronym DIFM is used before it’s spelled out in the sentence, but you should spell it out first and then use the acronym. </span>  
-Reply: Thank you for identifying this writing issue. The acronym DIFM is now put after the full name. See page x, line xx.
+Reply: Thank you for pointing out this writing issue. We have addressed it by placing the acronym DIFM after its full name, as suggested. The revised placement can be found on page x, line xx.
 
 <span style = "color: blue;">P. 10, line 212: The (j,k) index should be subscripted here.</span>  
-Reply: We very appreciate the reviewer's careful reading of the manuscript and pointing out this typo. It is not corrected to $\varepsilon_{j,k}$. (See page x, line xx.)
+Reply: We greatly appreciate the reviewer's meticulous review of the manuscript and for finding this typo.
+We have corrected it to use subscript notation (see page x, line xx).
+Furthermore, to eliminate the duplication of the spline index $k$, we have updated the cell index notation to ($j$, $i$) both in this section and throughout the rest of the manuscript.
 
@@
 The language here really matters so as to avoid confusion on the part of the readers.</span>
-Reply: The model described here is a single yield response function for the full field, in other words, not variable rate responses.
-We agree that the language used may cause confusion on whether it is a "single" response function or "single" shape constraint.
-To avoid the confusion, we removed the term "single".
-(See page x, line xx in the revised manuscript.)
+Reply: The model described here is a single yield response function for the full field.
+In other words, there is only one uniform response rather than variable responses.
+We acknowledge that the language used may have caused confusion regarding whether it refers to a "single" response function or a "single" shape constraint.
+To address this concern and eliminate any ambiguity, we have removed the term "single" from the manuscript (see page x, line xx in the revised version).
 
 <span style = "color: blue;">P. 11, line 235: It seems that 1-2 citations could be added (or are missing) after “well substantiated by agronomic research.”</span>  
-Reply: We followed the reviewer's comment and added two citations of agronomic studies to support this statement. (See page x, line xx in the revised manuscript.)
+Reply: We followed the comment and added two citations of agronomic studies to support this statement (see page x, line xx in the revised manuscript).
 
@@
 Reply: Thank you for the recommendation.
-We think the GWRR and GWRT look more concise than GWR-R and GWR-T, and have made the changes as suggested throughout the text.
-We also put all model names (GWR and SCAM) in superscripts of equations.
-We thank the reviewer's comment to make our notations more consistent throughout the manuscript.
+We also agree that "GWRR" and "GWRT" appear more concise than "GWR-R" and "GWR-T", and have made the changes as recommended.
+Additionally, we have placed all model names (GWR and SCAM) in superscripts in the equations.
+We appreciate the reviewer's comment, which has helped us improve the consistency of our notations across the manuscript.
 
@@
 Reply: Thank you for pointing out this formatting error.
-We have corrected all the acronym SCAM to uppercase throughout the text.
-In addition, we also changed all the acronyms in equations to uppercase as well.
+We have corrected the issue by ensuring that the acronym "SCAM" is consistently written in uppercase throughout the text.
+Additionally, we have capitalized all acronyms in equations as well.
 
 <span style = "color: blue;">P. 15, line 304: “but the its benefit is even negative at when the” should have the typos/redundant wording removed.</span>  
-Reply: Thank you for pointing out those typos. They have been corrected. (See page x, line xx in the revised manuscript.)
+Reply: Thank you for pointing out those typos. They have all been corrected (see page x, line xx in the revised manuscript).
 
 <span style = "color: blue;">P. 17, line 335: Figure 0?</span>  
-Reply: Our apologies for the typo. It should be Figure x. (__Taro: Which figure are you referring to here? I don't think it should be Figure 5.__)
+Reply: We apologize for the typographical error. It should be Figure x. (__Taro: Which figure are you referring to here? I don't think it should be Figure 5.__)
 
 <span style = "color: blue;">P. 18, line 362: Section title should just be “Discussion”. </span>  
-Reply: The title has been changed to “Discussion”. Furthermore, we combined this section with the conclusions section.
+Reply: The title has been changed to “Discussion”. Furthermore, we combined this section with the conclusions section, and the new title is "Discussion and conclusions".
 
 <span style = "color: blue;">P. 34, Figure 8 horizontal axis label: “Estiamated” should be “Estimated”. </span>
-Reply: We are very thankful for the reviewer to find out this typo. It was corrected by the revised manuscript.
+Reply: We greatly appreciate the reviewer for identifying this typo. It was corrected in the revised manuscript.
 
@@
 Specifically, what other statistical estimators should be reconsidered and how (specifically) should they be reassessed?</span>
-Reply: Thank you for pointing out the vagueness of this sentence.
-We added more details to explain that the other statistical methods that are commonly used in the site-specific yield response estimation literature include the regression with interaction terms of field characteristics, machine learning, etc.
-The approach of assessment is the similar simulation-based evaluation used by this study.
+Reply: We sincerely appreciate the reviewer's feedback regarding the vagueness of this sentence.
+We added more details to explain that the other commonly used statistical methods in the site-specific yield response estimation literature include the regression with interaction terms of field characteristics, machine learning, etc.
+The assessment approach will be simulation-based evaluation that is similar to the one used in this study.
+(See page x, line xx in the revised manuscript.)

### 2023-06-23 Writing/manuscript_gwr.rmd
Reviewer 2 comments completed

--- 2023-06-16 Writing/manuscript_gwr.rmd
@@
 They estimated site-specific yield response functions by applying GWR techniques on data from OFPEs [@bullock2019data], and reported dramatic results, estimating an average potential gain of \$65 ha$^{-1}$ from applying seed and N at optimal uniform rates (instead of at the rates the farmers would have chosen if not participating in the research), and an additional potential gain of \$58 ha$^{-1}$ when changing from optimal uniform application rates to optimal site-specific application rates.
-This is rather surprising given the often-reported poor statistical accuracy of GWR estimates [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation] and also much lower value of variable rate application over uniform rate application reported in previous studies (cite).
+This is rather surprising given the often-reported poor statistical accuracy of GWR estimates [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation] and also much lower value of variable rate application over uniform rate application reported in previous studies [@bullock1998does; @thrikawala1999economic; @koch2004economic].
 @rakshit2020 also applied GWR to on-farm experiment data.
@@
 Finally, we also evaluate their relative performances compared to uniform rate application (URA) based on shape-constrained additive model approach.
-It should be noted that the economical optimization in this study only includes farmers' private profit, while the environmental externalities (such as fertilizer runoff and leaching) are not considered.
+It should be noted that the economical optimization in this study only involves farmers' private profit, while the environmental externalities (such as fertilizer runoff and leaching) are not considered.
 
@@
 In total there were 1440 subplots available for experimental data analysis.
-The index $j \in {1, 2, \dots, 1440}$ identifies the field's subplots, and the index $k \in {1, \dots , 6}$ identifies the cells within a subplot.
-The couplet $(j, k)$ is used to identify individual cells.
+The index $j \in {1, 2, \dots, 1440}$ identifies the field's subplots, and the index $i \in {1, \dots , 6}$ identifies the cells within a subplot.
+The couplet $(j, i)$ is used to identify individual cells.
 
@@
 An extensive literature examines the choice of functional form in yield response estimation [@cerrato1990comparison, @frank1990comparison, @bullock1994quadratic, @tembo2008crop].
-Our simulation assume that each cell $(j, k)$'s "true" yield response function is assumed to follow the commonly-used quadratic-plateau functional form:
+Our simulation assume that each cell $(j, i)$'s "true" yield response function is assumed to follow the commonly-used quadratic-plateau functional form:
 
@@
 \begin{equation} \tag{1}
-y_{j,k} = f_{j, k} (N) = f(N, c_{j,k}) = 
+y_{j,i} = f_{j,i} (N) = f(N, c_{j,i}) = 
   \begin{cases}
-  \alpha_{j,k} + \beta_{j,k} N + \gamma_{j,k} N^2 + \varepsilon_{j,k} \, ,& N < \tau_{j,k} \\
-  \alpha_{j,k} + \beta_{j,k} \tau_{j,k} + \gamma_{j,k} \tau_{j,k}^2 + \varepsilon_{j,k} \, ,& N \ge \tau_{j,k}
+  \alpha_{j,i} + \beta_{j,i} N + \gamma_{j,i} N^2 + \varepsilon_{j,i} \, ,& N < \tau_{j,i} \\
+  \alpha_{j,i} + \beta_{j,i} \tau_{j,i} + \gamma_{j,i} \tau_{j,i}^2 + \varepsilon_{j,i} \, ,& N \ge \tau_{j,i}
   \end{cases}
@@
 
-where $c_{j,k} = (\alpha_{j,k},\beta_{j,k},\gamma_{j,k},\tau_{j,k})$ is the vector of yield response function parameters.
-$\tau_{j,k}$ can be interpreted as the critical value of N rate at which cell $(j, k)$'s yield reaches its plateau, where yield no longer increases with N rate.
-$\varepsilon_{j, k}$ is a stochastic error term.
+where $c_{j,i} = (\alpha_{j,i},\beta_{j,i},\gamma_{j,i},\tau_{j,i})$ is the vector of yield response function parameters.
+$\tau_{j,i}$ can be interpreted as the critical value of N rate at which cell $(j, i)$'s yield reaches its plateau, where yield no longer increases with N rate.
+$\varepsilon_{j, i}$ is a stochastic error term.
 The quadratic-plateau functional form implies a diminishing marginal product of N until a yield plateau, which are desirable properties for a yield response function [@frank1990comparison] and a pattern commonly observed in agronomic studies.
-Note that the cell-specific yield response function $f_{j, k} (N)$ is the reduced form of the meta response function $f$ when the characteristics vector takes on the value $c_{j, k}$.
+Note that the cell-specific yield response function $f_{j, i} (N)$ is the reduced form of the meta response function $f$ when the characteristics vector takes on the value $c_{j, i}$.
 In other words, all the soil or field properties that could affect yield response to N are embedded in the simulated parameters.
 
-The spatial distributions of cell-level parameters $\alpha_{j, k}$, $\beta_{j, k}$, $\gamma_{j,k}$, $\tau_{j, k}$, and the error term $\varepsilon_{j, k}$ were simulated by generating spatially correlated random fields using unconditional Gaussian geostatistical simulation based on the specified variograms [@dietrich1996fast, @wood1994simulation], and the simulation processes were conducted using the R package gstat [@graler16].
+The spatial distributions of cell-level parameters $\alpha_{j, i}$, $\beta_{j, i}$, $\gamma_{j,i}$, $\tau_{j, i}$, and the error term $\varepsilon_{j, i}$ were simulated by generating spatially correlated random fields using unconditional Gaussian geostatistical simulation based on the specified variograms [@dietrich1996fast, @wood1994simulation], and the simulation processes were conducted using the R package gstat [@graler16].
 Specifically, the model is spherical, the nugget variance is zero, and the range is 600 meters.
@@
 
-Letting $p$ represent the crop price and $w$ represent the price of nitrogen fertilizer, in each simulation the "true" economically optimal N rate for each cell $(j, k)$ was calculated as
+Letting $p$ represent the crop price and $w$ represent the price of nitrogen fertilizer, in each simulation the "true" economically optimal N rate for each cell $(j, i)$ was calculated as
 
 $$
-N^*_{j,k} \equiv argmax_N \Big[p\cdot f_{j,k}(N)-w\cdot N\Big].
+N^*_{j,i} \equiv argmax_N \Big[p\cdot f_{j,i}(N)-w\cdot N\Big].
 $$
@@
 
-In each simulation, for each cell $(j, k)$, the simulation's true yield $y_{j, k}$ was generated based on the cell's assigned application rate $N_{j,k}$, true response parameters $c_{j,k} = (\alpha_{j,k}, \beta_{j,k}, \gamma_{j,k}, \tau_{j,k})$, and error term $\varepsilon_{j,k}$.
-This procedure generated a field-level, cell-specific data set, $\{(y_{j, k},N_{j, k} ):j=1,\dots,1440;k=1,\dots, 6 \}$.
+In each simulation, for each cell $(j, i)$, the simulation's true yield $y_{j, i}$ was generated based on the cell's assigned application rate $N_{j,i}$, true response parameters $c_{j,i} = (\alpha_{j,i}, \beta_{j,i}, \gamma_{j,i}, \tau_{j,i})$, and error term $\varepsilon_{j,i}$.
+This procedure generated a field-level, cell-specific data set, $\{(y_{j, i},N_{j, i} ):j=1,\dots,1440;k=1,\dots, 6 \}$.
 To maintain consistency with real-world OFPEs, it was assumed that harvesting equipment could only record yields accurately at an 18m $\times$ 12m (subplot) resolution.
@@
 
-$$\Pi^{*SCAM} = 1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 \big[pf_{j, k} (\hat{N}^{*SCAM})-w\hat{N}^{*SCAM}\big]$$
+$$\Pi^{*SCAM} = 1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 \big[pf_{j, i} (\hat{N}^{*SCAM})-w\hat{N}^{*SCAM}\big]$$
 
-where $f_{j, k}(\cdot)$ denotes the true yield response function at cell $(j, k)$.
+where $f_{j, i}(\cdot)$ denotes the true yield response function at cell $(j, i)$.
 
@@
 
-$$\Pi^{GWR}=1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 [pf_{j, k} (\hat{N}^{*GWR}_j)-w\hat{N}^{*GWR}_j]$$
+$$\Pi^{GWR}=1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 [pf_{j, i} (\hat{N}^{*GWR}_j)-w\hat{N}^{*GWR}_j]$$
 
-where $f_{j, k} (\hat{N}^{*GWR}_j)$ denote the true yield generated at cell $(j, k)$ with subplot $j$'s GWR estimated N rate.
+where $f_{j, i} (\hat{N}^{*GWR}_j)$ denote the true yield generated at cell $(j, i)$ with subplot $j$'s GWR estimated N rate.
 
@@
 
-$$\hat{\Pi}^{*SCAM} = 1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 \big[p\hat{f}^{GWR}_{j, k} (\hat{N}^{*SCAM} )-w\hat{N}^{*SCAM}\big]$$
+$$\hat{\Pi}^{*SCAM} = 1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 \big[p\hat{f}^{GWR}_{j, i} (\hat{N}^{*SCAM} )-w\hat{N}^{*SCAM}\big]$$
 
-$$\hat{\Pi}^{*GWR}=1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 [p\hat{f}^{GWR}_{j, k} (\hat{N}^{*GWR}_{j} )-w\hat{N}^{*GWR}_{j}]$$
+$$\hat{\Pi}^{*GWR}=1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 [p\hat{f}^{GWR}_{j, i} (\hat{N}^{*GWR}_{j} )-w\hat{N}^{*GWR}_{j}]$$
 
@@
 
-Our results clealy show it can be dangerous to use GWR with quadratic functional form when yield-input relationship is quadratic plateau as done in @trevisan2021spatial.
-Their choice of quadratic functional form is likely due to the fact there is no readily usable statistical software or package that implements non-linear GWR.
+It is worthy of mentioning that, in most previous studies of model comparisons the model performances were predominantly measured by statistical accuracy of parameter estimates (such as bias, mean squared error, type I error, confidence intervals, and so on), for either the GWR models [@lu2017geographically, @harris2019simulation] or the econometric models in general [@christopeit2006local, @su2016identifying].
+While the statistical measures are fundamental criteria to evaluate model performances, what matters more in economic practices are whether and how much those statistical accuracy can translate into the ultimate economic values.
+Particularly, the magnitudes of this translation may depend on the application scenarios.
+This study differs from previous literature in that it reports the economic value of specific econometric models (GWR) with model functional form misspecification (quadratic estimation while the truth is quadratic-plateau) when being used in specific applications (corn site-specific nitrogen management) and under specific conditions (normal-sized production field, various market price scenarios, etc.) through a simulation-based approach.
+
+It is worth noting that previous studies comparing models have predominantly focused on measuring model performance based on statistical accuracy of parameter estimates, such as bias, mean squared error, type I error, and confidence intervals, for both GWR models [@lu2017geographically; @harris2019simulation] and general econometric models [@christopeit2006local, @su2016identifying].
+While these statistical measures are fundamental for evaluating model performance, in practical economic applications it is imperative to consider the translation of statistical accuracy into economic value.
+Moreover, the extent of this translation could vary depending on the specific application scenarios.
+This study distinguishes itself from previous literature by explicitly examining the economic value of specific econometric models (GWR) under a model functional form misspecification (quadratic instead of quadratic-plateau), in a specific application (corn site-specific nitrogen management), and under specific context scenarios (normal-sized production field, various market prices, etc.), through a simulation-based methodology.
+We encourage other model comparison studies in empirical economic research to also incorporate similar assessment of economic value.
+
+Our results clearly show it can be dangerous to use GWR with quadratic functional form when yield-input relationship is quadratic plateau as done in @trevisan2021spatial.
+Their choice of quadratic functional form is likely due to the fact that there is no readily usable statistical software or package that implements non-linear GWR.
 The only non-linear model available at the moment is the linear-plateau GWR by @lambert2022geographically.
@@
 
-Most important, whether using GWRT or GWRR, researchers must be cautious about their estimated value of VRA when model is assumed to be quadratic when the true underlying yield-input response is quadratic-plateau in relity.
+Most important, whether using GWRT or GWRR, researchers must be cautious about their estimated value of VRA when model is assumed to be quadratic when the true underlying yield-input response is quadratic-plateau in reality.
 Our results show that it is likely that they will over-estimate their true values and the bias can be misleadingly high with non-negligible probability.
@@
 Finally, it would be interesting to examine the pure performance of GWR.
-The objecive of this article was to evaluate GWR with quadratic functional form when the true yield-input relationship is quadratic-plateau.
+The objective of this article was to evaluate GWR with quadratic functional form when the true yield-input relationship is quadratic-plateau.
 Therefore, we evaluated GWR when model is misspecified in a particular manner.
-Once, GWR with quadratic-plateau model is developed, it would be interesting to see how it performs when the true yield reponse to input is quadratic-plateau.
+Once, GWR with quadratic-plateau model is developed, it would be interesting to see how it performs when the true yield response to input is quadratic-plateau.
 In this case, there is no functional form misspecification and the pure ability of GWR can be isolated.

### 2023-06-23 Writing/JAAEA/1stRoundRevision/reply_to_editor.rmd

@@
 output:
-  word_document: default
   html_document: default
@@
 
-Actually, the dominant functional form used in the literature is quadratic-plateau for non-GWR (regualr parametric) regression because agronomists have long known that it better represents corn-nitrogen relationship.
+Actually, the dominant functional form used in the literature is quadratic-plateau for <span style = "color: red;"> non-</span>GWR (regualr parametric) regression because agronomists have long known that it better represents corn-nitrogen relationship.
 Application of GWR is very new to the field and GWR is not currently flexible in funcional form.
-There is no readily available statistical software or packages that lets researchers to use quadratic-plateau functionl form under the GWR framework.
+There is no readily available statistical software or packages that lets researchers use the quadratic-plateau functionl form under the GWR framework.
 That is the primary reason that both Trevisan et al () and Rakshit et al () are using quadratic functional form.
 So, their choice of functional form is not coming from agronomic facts, rather from technical limitations.
-We are trying to point out this can be a problem with GWR just like it is a problem for regular regression framework.
-So, our paper is imporatnt because many use quadratic-plateau in regular regression framework, but the GWR promoted by the two studies use quadratic just because it is hard to do so.
-We believe it is imporatnt that this technical limitation is not trivial and would like to avoid practitioners or researcher to believe GWR is better than it truly is.
+We are trying to point out this can be dangerous with GWR just like it is a problem for regular regression framework.
+So, our paper is imporatnt because many use quadratic-plateau in regular regression framework for corn-nitrogen yield response function estimation, but the GWR promoted by the two studies use quadratic just because it is hard to do so.
+We believe that this technical limitation is not trivial and would like to avoid practitioners or researcher believing GWR is better than it truly is.
 We further suggest that it is important to develope a statistical package that allows to model yield-input relationship more flexibly.
@@
 
-Fiest, it is important to reiterate that we are not interested in evaluating GWR itself even though our writing did give that impression, rather we are interested in evaluating GWR with quadratic functional form when the true underlying relationship is quadratic-plateau.
+First, it is important to reiterate that we are not interested in evaluating GWR itself even though our writing did give that impression, rather we are interested in evaluating GWR with quadratic functional form when the true underlying relationship is quadratic-plateau.
 This point alone addresses lots of your and reviwer 1's comments (as we discussed above, this is an important problem to address).
@@
 In our DGP, we generate parameters (alpha, ...
-in equation )for individual $i$ in a spatially correlated manner (as opposed to what the reviewer thought).
+in equation )for individual $i$ in a spatially correlated manner (as opposed to what the reviewer 1 thought).
 So, aside from the functional form, the only difference is in the spatial pattern of parameters.

### 2023-06-23 Writing/supplementary_appendix.rmd

@@
 library(tidyverse)
+library(patchwork)
 library(flextable)
@@
     element_text(
-      size = 10, angle = 0, hjust = 0, vjust = 0, family = "Times"
+      size = 9, angle = 0, hjust = 0, vjust = 0, family = "Times"
     ),
@@
   #--- strip (for faceting) ---#
-  strip.text = element_text(size = 10),
+  strip.text = element_text(size = 10, family = "Times"),
   #--- plot title ---#
@@
 
-```{r include = FALSE}
+```{r results-plots, include = FALSE}
 kernel_ls <- c("gaussian", "exponential", "boxcar", "bisquare", "tricube")
@@
   mutate(results = list(
-    here("Shared", "Results", kernel, "pi_data.rds") %>%
+    here("Shared/Results", kernel, "pi_data.rds") %>%
       readRDS() %>%
@@
       .[pRatio == 7.67, pLabel := "High"] %>%
-      .[, pLabel := factor(pLabel, levels = c("Low", "Middle", "High"))]
+      .[, pLabel := factor(pLabel, levels = c("Low", "Middle", "High"))] %>%
+      .[, p_ratio_text := paste0("Price Ratio (N/Corn) \n = ", pRatio, " (", pLabel, ")")]
   )) %>%
@@
       .[, .(pi_diff = median(pi_diff)),
-        by = c("field_col", "pLabel", "type")
+        by = .(field_col, p_ratio_text, type)
       ]
@@
         ),
-        angle = 0, hjust = -0.1, vjust = 0, size = 3
+        angle = 0, hjust = -0.1, vjust = 0, size = 3,
+        family = "Times"
       ) +
-      facet_grid(pLabel ~ type) +
+      facet_grid(p_ratio_text ~ type) +
       scale_y_continuous(expand = c(0, 0), limits = c(NA, 200)) +
-      scale_x_continuous(breaks = 20 * (-2:3), limits = c(-45, 60)) +
+      scale_x_continuous(breaks = 20 * (-2:4), limits = c(-45, 80)) +
+      theme(
+        panel.spacing.y = unit(0.3, "cm")
+      ) +
       xlab("The value of VRA over URA ($ per ha)") +
@@
       .[, .(bias = median(bias)),
-        by = c("field_col", "pLabel", "type")
+        by = .(field_col, p_ratio_text, type)
       ]
@@
         ),
-        angle = 0, hjust = -0.1, vjust = 0, size = 3
+        angle = 0, hjust = -0.1, vjust = 0, size = 3,
+        family = "Times"
       ) +
-      facet_grid(pLabel ~ type) +
+      facet_grid(p_ratio_text ~ type) +
       scale_y_continuous(expand = c(0, 0)) +
+      theme(
+        panel.spacing.y = unit(0.3, "cm")
+      ) +
       xlab("Bias in the Estimation of the Value of VRA over URA ($ per ha)") +
@@
 
+```{r price-history-plot, include = FALSE}
+# read the data
+price_ratio_data <- readRDS(here("Shared/Data/price_ratio_data.rds"))
+
+# continuous time variable
+price_ratio_data[, Time := Year + Month / 12]
+
+# color legend
+color_legend <- c("Corn" = "black")
+
+# corn price
+g1 <-
+  ggplot(data = price_ratio_data) +
+  geom_line(aes(x = Time, y = pCorn), color = "black", linewidth = 0.6) +
+  ggtitle("Corn price ($/kg)") +
+  ylab("") +
+  xlab("Year") +
+  theme(
+    legend.title = element_blank(),
+    plot.title = element_text(hjust = 0.5, vjust = -1, size = 9),
+    axis.text = element_text(color = "black"),
+    axis.title.x = element_text(hjust = 1)
+  )
+
+# N price
+g2 <-
+  ggplot(data = price_ratio_data) +
+  geom_line(
+    aes(x = Time, y = pN, color = Ntype, linetype = Ntype),
+    linewidth = 0.6
+  ) +
+  scale_color_brewer(palette = "Dark2") +
+  ggtitle("Nitrogen price ($/kg)") +
+  ylab("") +
+  xlab("Year") +
+  labs(color = "Nitrogen type", linetype = "Nitrogen type") +
+  theme(
+    plot.title = element_text(hjust = 0.5, vjust = -1, size = 9),
+    axis.text = element_text(color = "black"),
+    axis.title.x = element_text(hjust = 1),
+    legend.key.width = unit(1, "cm")
+  )
+
+# price ratio
+g3 <-
+  ggplot(data = price_ratio_data) +
+  geom_line(
+    aes(x = Time, y = pRatio, color = Ntype, linetype = Ntype),
+    linewidth = 0.6
+  ) +
+  scale_color_brewer(palette = "Dark2") +
+  ggtitle("Nitrogen-Corn price ratio") +
+  ylab("") +
+  xlab("Year") +
+  labs(color = "Nitrogen type", linetype = "Nitrogen type") +
+  theme(
+    plot.title = element_text(hjust = 0.5, vjust = -1, size = 9),
+    axis.text = element_text(color = "black"),
+    axis.title.x = element_text(hjust = 1),
+    legend.key.width = unit(1, "cm")
+  )
+
+g_prices <- g1 / g2 / g3
+```
+
 Figure A\@ref(fig:price) illustrates the historical prices of corn ($p$) and nitrogen fertilizer ($w$), along with the corresponding nitrogen-corn price ratios, during the two-decade period from 2002 to 2022.
 
-```{r, fig.id = "price", fig.cap = "Historical monthly variations in corn price, nitrogen fertilizer price, and the corresponding nitrogen-corn price ratio, 2002-2022"}
-knitr::include_graphics("price_ratio_history.png")
+```{r, fig.id = "price", fig.cap = "Historical monthly variations in corn price, nitrogen fertilizer price, and the corresponding nitrogen-corn price ratio, 2002-2022", fig.width = 6, fig.height = 6}
+g_prices
 ```
@@
 
-```{r, fig.id = "value-kernel-exp", fig.cap = "The true economic value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios (5.44 (low), 6.56 (middle), and 7.67 (high) $ kg^(-1)  / $ kg^(-1)), using Exponential kernel function", fig.height = 3.5}
+```{r, fig.id = "value-kernel-exp", fig.cap = "The true economic value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios using the Exponential kernel function", fig.height = 6}
 gg_appendix$g_value[[2]]
@@
 
-```{r, fig.id = "value-kernel-boxcar", fig.cap = "The true economic value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios (5.44 (low), 6.56 (middle), and 7.67 (high) $ kg^(-1)  / $ kg^(-1)), using Boxcar kernel function", fig.height = 3.5}
+```{r, fig.id = "value-kernel-boxcar", fig.cap = "The true economic value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios using the Boxcar kernel function", fig.height = 6}
 gg_appendix$g_value[[3]]
@@
 
-```{r, fig.id = "value-kernel-bs", fig.cap = "The true economic value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios (5.44 (low), 6.56 (middle), and 7.67 (high) $ kg^(-1)  / $ kg^(-1)), using Bi-square kernel function", fig.height = 3.5}
+```{r, fig.id = "value-kernel-bs", fig.cap = "The true economic value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios using the Bi-square kernel function", fig.height = 6}
 gg_appendix$g_value[[4]]
@@
 
-```{r, fig.id = "value-kernel-tricube", fig.cap = "The true economic value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios (5.44 (low), 6.56 (middle), and 7.67 (high) $ kg^(-1)  / $ kg^(-1)), using Tri-cube kernel function", fig.height = 3.5}
+```{r, fig.id = "value-kernel-tricube", fig.cap = "The true economic value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios using the Tri-cube kernel function", fig.height = 6}
 gg_appendix$g_value[[5]]
 ```
+
+`r run_pagebreak()`
 
@@
 
-```{r, fig.id = "bias-kernel-exp", fig.cap = "Bias in the estimation of the value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios (5.44 (low), 6.56 (middle), and 7.67 (high) $ kg^(-1)  / $ kg^(-1)), using Exponential kernel function", fig.height = 3.5}
+```{r, fig.id = "bias-kernel-exp", fig.cap = "Bias in the estimation of the value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios using the Exponential kernel function", fig.height = 6}
 gg_appendix$g_bias[[2]]
@@
 
-```{r, fig.id = "bias-kernel-boxcar", fig.cap = "Bias in the estimation of the value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios (5.44 (low), 6.56 (middle), and 7.67 (high) $ kg^(-1)  / $ kg^(-1)), using Boxcar kernel function", fig.height = 3.5}
+```{r, fig.id = "bias-kernel-boxcar", fig.cap = "Bias in the estimation of the value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios using the Boxcar kernel function", fig.height = 6}
 gg_appendix$g_value[[3]]
@@
 
-```{r, fig.id = "bias-kernel-bs", fig.cap = "Bias in the estimation of the value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios (5.44 (low), 6.56 (middle), and 7.67 (high) $ kg^(-1)  / $ kg^(-1)), using Bi-square kernel function", fig.height = 3.5}
+```{r, fig.id = "bias-kernel-bs", fig.cap = "Bias in the estimation of the value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios using the Bi-square kernel function", fig.height = 6}
 gg_appendix$g_value[[4]]
@@
 
-```{r, fig.id = "bias-kernel-tricube", fig.cap = "Bias in the estimation of the value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios (5.44 (low), 6.56 (middle), and 7.67 (high) $ kg^(-1)  / $ kg^(-1)), using Tri-cube kernel function", fig.height = 3.5}
+```{r, fig.id = "bias-kernel-tricube", fig.cap = "Bias in the estimation of the value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios using the Tri-cube kernel function", fig.height = 6}
 gg_appendix$g_value[[5]]
 ```
+
+`r run_pagebreak()`
+
+# References
+
+<br />
+
+<div id="refs"></div>

### 2023-06-23 Writing/manuscript_gwr.rmd
finalized before Dave's editing

--- 2023-06-21 Writing/manuscript_gwr.rmd
@@
 ---
-title: "Economic Evaluation of Geographically Weighted Regression Analysis for Site-specific Nitrogen Management"
+title: "Economic Evaluation of Mis-speficied Geographically Weighted Regression Models for Site-specific Nitrogen Management"
 author:
@@
 But, inaccurate estimation of yield response function in this methodology can result in significant bias in the estimation of the value of VRA.
-This bias problem can be particularly severe when the method used tends to exaggerate the true heterogeneity in yield response functions, such as GWR.
+This bias problem can be particularly severe when the method used tends to exaggerate the true heterogeneity in yield response functions, such as GWR [@czarnota2015evaluating;].
 
@@
 At first, it appears that the specification used by @rakshit2020 is superior since it is more flexible than the specification used by @trevisan2021spatial.
-However, the flexibility can be a disadvantage rather than an advantage because the estimation of economically optimal nitrogen rate (EONR) is highly sensitive to the coefficient estimates on $N^2$, and GWR often provides inaccurate local estimation of that coefficient.
+However, the flexibility can be a disadvantage rather than an advantage because the estimation of economically optimal nitrogen rate (EONR) can be highly sensitive to the coefficient estimates on $N^2$, and GWR often provides inaccurate local estimation of that coefficient.
 It is critical to keep in mind that it is not our objective to measure the bias in the coefficient estimation by GWR, unlike [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation].
@@
 $$
-\begin{equation} \tag{1}
 y_{j,k} = f_{j, k} (N) = f(N, c_{j,k}) = 
@@
   \end{cases}
-\end{equation}
 $$

### 2023-06-23 Codes/3_make_figures_publication.R

@@ -182,7 +182,7 @@ g_value <-
 # facet_grid(round(pN, digits = 2) ~ .)
 
 est_data <-
-  readRDS(here("Shared", "Results", kernel_choice, "est_data.rds")) %>%
+  readRDS(here("Shared/Results/Gaussian/est_data.rds")) %>%
   unnest() %>%
   data.table() %>%
   .[, type := ifelse(transfer == 0, "GWR-R", "GWR-T")]
@@ -223,7 +223,7 @@ g_eonr_bias <-
 
 #* read the simulation data for a sigle simulationused for illustration
 single_sim <-
-  here("Shared", "Results", kernel_choice, "aunit_sim_single.rds") %>%
+  here("Shared/Results/Gaussian/aunit_sim_single.rds") %>%
   readRDS() %>%
   .[, type := ifelse(transfer == 0, "GWR-R", "GWR-T")]
 
@@ -341,7 +341,7 @@ pN <- pCorn * field_parameters$pRatio_ls[[1]][2] # medium price scenario
 #' # Prepare yield response curves
 # /*+++++++++++++++++++++++++++++++++++
 il_data_oe <-
-  readRDS(here("Shared", "Results", kernel_choice, "il_data_oe.rds")) %>%
+  readRDS(here("Shared/Results/Gaussian/il_data_oe.rds")) %>%
   .[,
     lapply(.SD, mean),
     by = aunit_id,

### 2023-06-23 Writing/manuscript_gwr.rmd

--- 2023-06-23 Writing/manuscript_gwr.rmd
@@
 They estimated site-specific yield response functions by applying GWR techniques on data from OFPEs [@bullock2019data], and reported dramatic results, estimating an average potential gain of \$65 ha$^{-1}$ from applying seed and N at optimal uniform rates (instead of at the rates the farmers would have chosen if not participating in the research), and an additional potential gain of \$58 ha$^{-1}$ when changing from optimal uniform application rates to optimal site-specific application rates.
-This is rather surprising given the often-reported poor statistical accuracy of GWR estimates [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation] and also much lower value of variable rate application over uniform rate application reported in previous studies [@bullock1998does; @thrikawala1999economic; @koch2004economic].
+This is rather surprising given the often-reported poor statistical accuracy of GWR estimates [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation] and also much lower value of variable rate application (VRA) over uniform rate application (URA) reported in previous studies (cite).
 @rakshit2020 also applied GWR to on-farm experiment data.
@@
 Finally, we also evaluate their relative performances compared to uniform rate application (URA) based on shape-constrained additive model approach.
-It should be noted that the economical optimization in this study only involves farmers' private profit, while the environmental externalities (such as fertilizer runoff and leaching) are not considered.
+It should be noted that the economical optimization in this study only includes farmers' private profit, while the environmental externalities (such as fertilizer runoff and leaching) are not considered.
 
-We pursue the objective by conducting Monte Carlo simulations in which we first generate and then analyze stylized OFPE data.
+We pursue the objective by conducting Monte Carlo simulations of 1000 rounds in which we first generate and then analyze stylized OFPE data.
 We cannot test which model specification results in more profitable site-specific nitrogen rate recommendations using real data because it is impossible to observe the true yield response functions using real-world data.
@@
 An extensive literature examines the choice of functional form in yield response estimation [@cerrato1990comparison, @frank1990comparison, @bullock1994quadratic, @tembo2008crop].
-Our simulation assume that each cell $(j, i)$'s "true" yield response function is assumed to follow the commonly-used quadratic-plateau functional form:
+Our simulation assumes that each cell $(j, k)$'s "true" yield response function is assumed to follow the commonly-used quadratic-plateau functional form:
 
@@
 
-It is worthy of mentioning that, in most previous studies of model comparisons the model performances were predominantly measured by statistical accuracy of parameter estimates (such as bias, mean squared error, type I error, confidence intervals, and so on), for either the GWR models [@lu2017geographically, @harris2019simulation] or the econometric models in general [@christopeit2006local, @su2016identifying].
-While the statistical measures are fundamental criteria to evaluate model performances, what matters more in economic practices are whether and how much those statistical accuracy can translate into the ultimate economic values.
-Particularly, the magnitudes of this translation may depend on the application scenarios.
-This study differs from previous literature in that it reports the economic value of specific econometric models (GWR) with model functional form misspecification (quadratic estimation while the truth is quadratic-plateau) when being used in specific applications (corn site-specific nitrogen management) and under specific conditions (normal-sized production field, various market price scenarios, etc.) through a simulation-based approach.
-
 It is worth noting that previous studies comparing models have predominantly focused on measuring model performance based on statistical accuracy of parameter estimates, such as bias, mean squared error, type I error, and confidence intervals, for both GWR models [@lu2017geographically; @harris2019simulation] and general econometric models [@christopeit2006local, @su2016identifying].

### 2023-06-24 Writing/manuscript_gwr.rmd
minor edit

@@
 **Abstract**: Geographically weighted regression (GWR) has been presented as a prominent tool to estimate site-specific yield response functions to derive site-specific input rate recommendations from data generated by on-farm precision experimentation (OFPE).
-However, the current application of GWR in this context assumes quadratic yield response function even though many of the yield-input relationships has been shown to be better represeted by the quadratic-plateau functional form.
-This is due to lack of readily available methods and satistical packages that allow researchers to estimate non-linear model undet the GWR framework, including quadratic-plateau.
+However, the current application of GWR in this context assumes quadratic yield response function even though many of the yield-input relationships has been shown to be better represented by the quadratic-plateau functional form.
+This is due to lack of readily available methods and satistical packages that allow researchers to estimate non-linear model under the GWR framework, including quadratic-plateau.
 The key objective of this paper is to investigate the possibility of bias in estimating the economic value of site-specific recommendation maps based on GWR with quadratic functional form assumption when in reality the true underlying yield-input relationship is quadratic-plateau.

### 2023-06-24 Writing/manuscript_gwr.rmd

@@
 However, the current application of GWR in this context assumes quadratic yield response function even though many of the yield-input relationships has been shown to be better represented by the quadratic-plateau functional form.
-This is due to lack of readily available methods and satistical packages that allow researchers to estimate non-linear model under the GWR framework, including quadratic-plateau.
+This is due to lack of readily available methods and statistical packages that allow researchers to estimate non-linear model under the GWR framework, including quadratic-plateau.
 The key objective of this paper is to investigate the possibility of bias in estimating the economic value of site-specific recommendation maps based on GWR with quadratic functional form assumption when in reality the true underlying yield-input relationship is quadratic-plateau.
@@
 We reveal that in many circumstances using GWR is far less profitable than claimed by previous studies, which provides a necessary cautionary message to researchers who might otherwise “over-sell” to other researchers the value of using GWR methods in empirical work involving the estimation of site-specific input management.
-We encourage the statistical community to extend the current GWR capability by allowing researchers to model yield-inpute response more flexibly than currently possible.
+We encourage the statistical community to extend the current GWR capability by allowing researchers to model yield-input response more flexibly than currently possible.
 
@@
 Midwestern row crop farmers to pay for 1-ha grid soil sampling and chemical analysis every three or four years [@morris2018strengths].
-The data are often used to derive fertilizer application recommendations, for example by applying comparatively simple formulas provided by university extension services (e.g., Culman, et al.
-2020).
+The data are often used to derive fertilizer application recommendations, for example by applying comparatively simple formulas provided by university extension services [e.g., @culman2020tri].
 But the expense of soil sampling and analysis is driving development of sensor technologies that gather data on site-specific field and crop characteristics or proxies of those characteristics, and the conversion of those data into recommended nitrogen fertilizer (N) application rate maps (usually called "prescriptions" or $R_x$s).^[For example, Trimble Agriculture's GreenSeeker and AgLeader's OptRx® systems use optical sensors mounted on fertilizer application booms to digitally record vegetative index imagery as farm machinery is driven through fields during early crop growth stages.
@@
 They estimated site-specific yield response functions by applying GWR techniques on data from OFPEs [@bullock2019data], and reported dramatic results, estimating an average potential gain of \$65 ha$^{-1}$ from applying seed and N at optimal uniform rates (instead of at the rates the farmers would have chosen if not participating in the research), and an additional potential gain of \$58 ha$^{-1}$ when changing from optimal uniform application rates to optimal site-specific application rates.
-This is rather surprising given the often-reported poor statistical accuracy of GWR estimates [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation] and also much lower value of variable rate application (VRA) over uniform rate application (URA) reported in previous studies (cite).
+This is rather surprising given the often-reported poor statistical accuracy of GWR estimates [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation] and also much lower value of variable rate application (VRA) over uniform rate application (URA) reported in previous studies [@bullock1998does; @thrikawala1999economic; @koch2004economic].
 @rakshit2020 also applied GWR to on-farm experiment data.
@@
 It is likely that their choice of quadratic functional form is merely a compromise because there did (does) not exist any statistical software of package that implements GWR with quadratic-plateau functional form.
-
 The second source of over-estimation bias is endemic to any study that evaluates the value of variable rate application, not just @trevisan2021spatial.
@@
 But, inaccurate estimation of yield response function in this methodology can result in significant bias in the estimation of the value of VRA.
-This bias problem can be particularly severe when the method used tends to exaggerate the true heterogeneity in yield response functions, such as GWR [@czarnota2015evaluating;].
+This bias problem can be particularly severe when the method used tends to exaggerate the true heterogeneity in yield response functions, such as GWR [@czarnota2015evaluating].
 
-The primary objective of this study is examine the degree and direction of bias in the estimation of the economic value of GWR-based site-specific nitrogen rate recommendations (or "variable rate application", VRA) when GWR model is specified as quadratic when the true yield response function follows the quadratic-plateau functional form.
+The primary objective of this study is examine the degree and direction of bias in the estimation of the economic value of GWR-based site-specific nitrogen rate recommendations (i.e., variable rate application of nitrogen) when GWR model is specified as quadratic when the true yield response function follows the quadratic-plateau functional form.
 We evaluate two sets of GWR quadratic specifications used in @rakshit2020 and @trevisan2021spatial.
@@
 An extensive literature examines the choice of functional form in yield response estimation [@cerrato1990comparison, @frank1990comparison, @bullock1994quadratic, @tembo2008crop].
-Our simulation assumes that each cell $(j, k)$'s "true" yield response function is assumed to follow the commonly-used quadratic-plateau functional form:
+Our simulation assumes that each cell $(j, i)$'s "true" yield response function is assumed to follow the commonly-used quadratic-plateau functional form:
 

### 2023-06-24 Writing/JAAEA/1stRoundRevision/reply_to_editor.rmd
minor edits

@@
 There is no readily available statistical software or packages that lets researchers use the quadratic-plateau functionl form under the GWR framework.
-That is the primary reason that both Trevisan et al () and Rakshit et al () are using quadratic functional form.
+That is the primary reason that both Trevisan et al.
+(2021) and Rakshit et al.
+(2020) are using quadratic functional form.
 So, their choice of functional form is not coming from agronomic facts, rather from technical limitations.
@@
 This is a problem of our writing and we apologize for that.
-Our objective is not to evaluate the problem of GWR itself, rather the current practice of using GWR with quadratic form when the true underlying true relationship is quadratic-plateau as in Trevisan et al ().
+Our objective is not to evaluate the problem of GWR itself, rather the current practice of using GWR with quadratic form when the true underlying true relationship is quadratic-plateau as in Trevisan et al.
+(2021).
 But, we agree fully that it is interesting to see how GWR performs when the assumed funtional form in regression and true functional form in the data generating process are the same.
@@
 It is not important in this paper to distinguish and isolate the sources of bias.
-Our interest is in showing the bias of using GWR with quadratic form (because of technical limitation) even though the underlying relatinship is quadratic-plateau (like corn-nitrogen) as done by Trevisan et al ().
+Our interest is in showing the bias of using GWR with quadratic form (because of technical limitation) even though the underlying relatinship is quadratic-plateau (like corn-nitrogen) as done by Trevisan et al.
+(2021).
 It is actually impossible in our paper to isolate them and we are not interested in doing so either.

### 2023-06-24 Writing/manuscript_gwr.rmd
minor edits

@@
 We show that both GWR approaches suffer significant positive bias, which can lead to large over-estimation of the economic value of applying GWR methods.
-We reveal that in many circumstances using GWR is far less profitable than claimed by previous studies, which provides a necessary cautionary message to researchers who might otherwise “over-sell” to other researchers the value of using GWR methods in empirical work involving the estimation of site-specific input management.
+We reveal that in many circumstances using GWR is far less profitable than claimed by previous studies, which provides a necessary cautionary message to researchers who might otherwise "over-sell" to other researchers the value of using GWR methods in empirical work involving the estimation of site-specific input management.
 We encourage the statistical community to extend the current GWR capability by allowing researchers to model yield-input response more flexibly than currently possible.
@@
 More important, both specifications by trevisan2021spatial and rakshit2020 tend to significantly over-estimate the economic value of VRA based on GWR.
-Their assumption of quadratic funcitonal form is one of the main culplits.
+Their assumption of quadratic functional form is one of the main culprits.
 When quadratic functional form is assumed, over-application of nitrogen is modeled to result in large economic loss due to yield loss when in reality over-application of nitrogen is not associated with any yield loss when the true yield-response function is quadratic-plateau.
@@
 The objective of this article was to evaluate GWR with quadratic functional form when the true yield-input relationship is quadratic-plateau.
-Therefore, we evaluated GWR when model is misspecified in a particular manner.
+Therefore, we evaluated GWR when model is mis-specified in a particular manner.
 Once, GWR with quadratic-plateau model is developed, it would be interesting to see how it performs when the true yield response to input is quadratic-plateau.
-In this case, there is no functional form misspecification and the pure ability of GWR can be isolated.
+In this case, there is no functional form mis-specification and the pure ability of GWR can be isolated.
 

### 2023-07-17 Writing/JAAEA/1stRoundRevision/reply_to_reviewer_2.rmd
final formatting correction
replies

--- 2023-06-15 Writing/JAAEA/1stRoundRevision/reply_to_reviewer_2.rmd
@@
 
-__Other changes__
-1. Subscript (j,k) changed to (j,i). k is already used in spline notation.
+Your comments are in blue, and our responses are in black.
 
-Your comments are in blue, and our responses are in black.
+First, we would like to express our sincere gratitude for the reviewer's careful examination and critique of our manuscript.
+The insightful comments and suggestions have significantly contributed to the paper's clarity, detail, and overall strength.
+In return, we have attempted to carefully address each of the comments and revise the manuscript in response.
 
@@
 All comments are designed to strengthen the research.</span>
-General reply: We would like to express our sincere gratitude for the reviewer's careful and thorough review of our research paper.
-The insightful comments and suggestions have significantly contributed to improving the clarity, detail, and overall strength of our manuscript.
-We truly appreciate the time and effort the reviewer has dedicated to this review process.
-We have carefully addressed each of the comments and incorporated the necessary revisions into the manuscript.
 
@@
 
-<span style = "color: blue;">General Comments</span>
+## <span style = "color: blue;">General Comments</span>
 
-<span style = "color: blue;">To some extent, this research is related to studies that examine the “value” of forecasting models by assessing their measure of inaccuracy.
-Given that determining the value of general regression methodologies is not overly common in the relevant literature here, why not add 1-2 paragraphs that ties your study to other studies that measure the “value” of certain econometric techniques?
+<span style = "color: blue;">To some extent, this research is related to studies that examine the "value" of forecasting models by assessing their measure of inaccuracy.
+Given that determining the value of general regression methodologies is not overly common in the relevant literature here, why not add 1-2 paragraphs that ties your study to other studies that measure the "value" of certain econometric techniques?
 </span>
-Reply: Very good point.
-What makes this study differ from previous studies is the model “value” is not measured by the accuracy of parameter estimates, but the ultimate economic return.
-We agree it is a good idea to add more review of previous studies and highlight our difference.
-More discussion, literature review, is added on page xx, lines xxx.
 
-One of the most important questions in the literature relates to how variable rate technologies (VRT) can reduce negative externalities like fertilizer and chemical runoff and leaching.
+Very good point.
+What makes this study differ from previous studies is that the model "value" is not measured by the accuracy of parameter estimates, but rather by the ultimate economic return.
+We have followed your suggestion above by expanding our review of previous studies to highlight what our research adds to the literature.
+Please see in particular section 2.3 of the revised manuscript.
+
+<span style = "color: blue;">One of the most important questions in the literature relates to how variable rate technologies (VRT) can reduce negative externalities like fertilizer and chemical runoff and leaching.
 Clearly, this is not the research objective, and addressing a much more burning question in the literature would involve additional terms in the equation on p.
 10, line 294 that represent the negative environmental externalities.
-The authors should clarify early on that “economically optimal” means “privately optimal” rather than “socially optimal.”
-Reply: That is correct.
-Thank you for the reminder.
-We modified the writing and made it more explicit that the economically optimal VRT is privately optimal which only considers farmer’s private profit.
-Environmental externalities were not considered in this study.
+The authors should clarify early on that "economically optimal" means "privately optimal" rather than "socially optimal."</span>
+
+Thank you for the suggestion.
+We have explicitly stated the following at the end of the Introduction section of the revised manuscript: *"While the environmental impacts of fertilizer management are of great social importance, for simplicity we confine our analysis to its private economic impacts."*
 
@@
 Any intuition about the ratios of 4.2, 5.4, and 10.4?</span>
-Response: That is our ignorance. Thank you for pointing it out. We added the historical summary of p and w. We choose the historically high (10 or 7), middle, and low price ratio.
-Reply: Figure of historical price trend in the appendix; argue that our partial explanation is sufficient.
+
+Good point.
+We have included a brief discussion of the historical corn and nitrogen prices in the first paragraph of the Results section, which is section 5.
+Additionally, we have included Appendix I: Historical Corn and Nitrogen Prices in the supplementary material to provide a more detailed description of the collection, calculation, and summary statistics of the historical price data.
+We also apologize for the typos of the price ratios 4.16, 5.44 and 10.35 in the previous version of the manuscript.
+The correct price ratios 5.44, 6.56, and 7.67 are used in the revised manuscript.
+The intuition underlying the dependence of the relative performances of GWRR and GWRT to the nitrogen-corn price ratio was explained in the paragraphs on pages 15-16 of the original manuscript, and that discussion has been included in the revised manuscript.
+The main difference arises from the models' specifications of the coefficient on $N^2$.
+The GWRR model allows for varying coefficient on $N^2$, leading to a wider range of estimated EONRs, while the GWRT model restricts the coefficient on $N^2$ to be constant, leading to a narrower range of estimated EONRs.
+When nitrogen is expensive relative to corn, the true range of EONRs should be larger, and therefore the economic penalty of GWRR's over-estimation of EONR range will be smaller.
+When the nitrogen-corn price ratio is lower, the true EONR range will be smaller, and GWRT's under-estimation of the EONR range is less of an issue.
+At the reviewer's request, we will be happy to further enhance the manuscript's discussion of this topic.
 
 <span style = "color: blue;">Where is there no in-text reference to, or explanation of, Figure 4? I do not know what to make of this lone figure.</span>
-Reply: We apologize for this mistake.
-That figure was to compare the estimated and true GWR coefficients $\beta_1$ and $\beta_2$.
-But since we have already compared the estimated and true EONR's in the next figure, the coefficient comparisons do not seem necessary anymore, and we forgot to remove it from the final manuscript.
-It is now removed.
-(__Taro: I removed that figure.
-Is it OK, or you want to say something about it?__)
+
+We apologize for the confusion.
+That figure was meant to compare the estimated and true GWR coefficients $\beta_1$ and $\beta_2$.
+But since we have already compared the estimated and true EONR's in another figure, so the figure 4 was redundant.
+We have removed it from the revised manuscript.
 
@@
 
-<span style = "color: blue;">Specific Comments</span>
+## <span style = "color: blue;">Specific Comments</span>
 
@@
 More importantly, VRT is just one component of precision ag; they are not synonymous.</span>
-Reply: We agree with the reviewer's comment that precision agriculture, site-specific farming, and variable-rate technology are not the same thing.
+
+Reply: We agree with the reviewer's comment that precision agriculture, site-specific farming, and variable-rate technology are not synonymous.
 Although in the literature those terms are often used interchangeably, they are not strictly speaking equivalent.
@@
 More broadly, at this point, besides the economics, why should we care about GWR relative to other spatial statistics methods?</span>
-Reply: We agree with the reviewer's comment that there are many nonparametric estimators that can estimate local yield responses, among which GWR is only one of them.
-However, the goal of this study is not to compare GWR with other estimators or to advocate the use of GWR.
-As stated  in the introduction section (page 1, lines 41-42xx; page 2, lines 61-65xx), the background of this study is that GWR model has gained attention in developing site-specific input recommendations due to its minimum requirement of costly field data collection.
-Our interest is to further test whether GWR is truly economically viable in this application and provide guidance for precision farming practice.
-The current study does not intend to involve other spatial statistics methods.
-But we do have plans to conduct similar simulation-based economic evaluations of other local response estimation methods (such as the spatial kriging smoothing) in future research.
+
+We agree with the reviewer's comment that GWR is only one of many nonparametric estimators of local yield responses.
+But our research goal was not to compare GWR with other estimators, nor to advocate the use of GWR.
+We have tried to make this much more clear in the Introduction of the revised manuscript.
+We explain as background that the GWR model has gained attention in developing site-specific input recommendations due to its minimal requirement of costly field characteristics data.
+We explain that our intent is to further test the value of having GWR available as a tool for the analysis of on-farm precision experimentation data and consequential input management recommendations.
+We do not intend to involve other spatial statistics methods in the current paper.
+But we do plan to conduct similar simulation-based economic evaluations of other local response estimation methods (such as the spatial kriging smoothing) in future research.
 
 <span style = "color: blue;">P. 9, line 192: Here, do you mean that you set the 1370 kg ha-1 to be the square root of the sill variances?</span>
-Reply: We apologize for the typo.
-Yes, it should be the square root of the sill variances since 1379 kg ha$^{-1}$ was the mean of standard deviations.
-Thank you for pointing out this typo.
-We have corrected that statement (see page x, line xx in the revised manuscript).
+
+Thanks for pointing out the typo.
+Yes, it should be the square root of the sill variances since 1379 kg ha−1 was the mean of the standard deviations.
+We have corrected that typo in the revised manuscript at (page x, line xx in the revised manuscript).
 
@@
 The general readers of JAAEA are likely to not know, either.</span>
-Reply: Thank you for the suggestion.
-We added a few more explanations of the SCAM to make it more clear to the general JAAEA readers that it is a regression model that can fit a more flexible and non-linear response relationship, and also allows for shape constraints that can incorporate prior knowledge or theories.
-(see page xx, lines xxx of the revised manuscript.)
+
+Thank you for the suggestion.
+In section 4.5.1 of the revised manuscript we have expanded our explanation of SCAM to clarify that it is a regression model that can fit a more flexible and non-linear response relationship and also allows for shape constraints that can incorporate prior knowledge or theories.
 
@@
 If so, use the same notation.</span>
-Reply: Thank you for pointing out this typo of notations. Yes, the $l$ and $k$ should be the same. We corrected the notations to use $k$ in the revised manuscript.
 
-<span style = "color: blue;">P.
-13, lines 268-270: How robust are the N ̂_(GWR-T,j )^*rates to variations in the AIC-chosen bandwidth parameters?
-More information about this needs to be provided.</span>
-Reply: If we understand the question correctly, we believe it is asking about the robustness of GWR estimates to bandwidth selection.
+Yes, the $l$ and $k$ should have been the same. We use $k$ in the revised manuscript.
+
+<span style = "color: blue;">P. 13, lines 268-270: How robust are the N^*_{GWR-T,j} rates to variations in the AIC-chosen bandwidth parameters? More information about this needs to be provided.</span>
+
+Reply: If we understand the question correctly, you are asking about the robustness of GWR estimates to bandwidth selection.
 Choosing bandwidth is indeed a crucial step in GWR estimation, and there are many different bandwidth selection methods in the literature.
@@
 and the median benefit of VRA under GWRT is…?</span>
-Reply: Our apologies for the typos. We have corrected them and filled out the numbers. (See page x, line xx in the revised manuscript.)
+
+Our apologies for the typos. We have corrected them and filled in the correct numbers. (See page x, line xx in the revised manuscript.)
 
 <span style = "color: blue;">P. 15: You first discuss figure 6 and then move to figure 5. Put all figures in order.</span>
-Reply: Thank you for pointing out the wrong order of the figures. We have corrected the order of Figures 5 and 6.
+
+We have corrected the order of the figures.
 
@@
 
-<span style = "color: blue;">
-Writing
-</span>
+## <span style = "color: blue;">Writing</span>
 
-<span style = "color: blue;">P. 2, line 45: This should be “data are”, not “data is”. </span>  
-Reply: This grammar error was corrected. The new sentence is now on page xx, line xx of the revised manuscript.
+<span style = "color: blue;">P. 2, line 45: This should be "data are", not "data is". </span>
 
-<span style = "color: blue;">P. 2, line 52: Basically or actually? Vagueness here makes it difficult to assess the degree to which OSU’s calculators are being used directly. </span>  
-Reply: The term "basically" used here does sounds a little oral and vague. We removed it in the revised manuscript (see page x, line xxx) to avoid any confusion.
+Corrected.
+
+<span style = "color: blue;">P. 2, line 52: Basically or actually? Vagueness here makes it difficult to assess the degree to which OSU's calculators are being used directly. </span>
+
+We removed the word "basically" in the pertinent part of the revised manuscript.
 
 <span style = "color: blue;">P. 2, line 54: To avoid confusing a general agricultural economics audience, I would use an abbreviation other than Rx for site-specific recommendations. </span>
-Reply: In precision agriculture, the site-specific recommendation map  is commonly called "prescription" or "$R_x$" by researchers and the industry.
-There may be other abbreviations but they are not as popular as the "$R_x$".
-We added a brief note to explain that "$R_x$" means "prescription" in where "$R_x$" first shows up (page x, line xxx in revised manuscript) to make sure the abbreviation's meaning is clear to the general agricultural economics audience who are not familiar with precision agriculture.
+
+Reply: In precision agriculture, the site-specific input management recommendation map is commonly called "prescription" or "Rx" by researchers and the industry.
+While we are certainly willing to defer to the editor's judgment, We have elected to keep this abbreviation in the revised manuscript, but have added a brief explanation of the notation.
+In the USA, at least, it is widely known that "Rx" means "prescription,"" and it is chiefly used in conversations about medicines and pharmacies.
 
 <span style = "color: blue;">P. 2, lines 49-60: All of these current commercial examples would work better as a footnote as they may become inaccurate in the next 3-10 years (or fewer). </span>
-Reply: Thank you for the suggestion. We also agree putting those commercial examples in a footnote is a better idea. Those part of contents is now all in footnote 1 on page xx.
+
+Thank you for the suggestion. We agree that placing the commercial examples in a footnote is a better idea. Please see footnote 1 of the revised manuscript.
 
@@
 I would consider starting a new paragraph with the sentence beginning on line 97.</span>
-Reply: We followed the reviewer's suggestion and broke those discussion into two paragraphs.
-The second paragraph starts on page x, line xx.
-We also made some slight wording changes to the beginning of this paragraph.
+
+We have followed the reviewer's suggestion and broken the discussion into two paragraphs In the revised manuscript.
 
 <span style = "color: blue;">P. 7, line 137: This comment should have been removed by the authors prior to manuscript submission.</span>
-Reply: This typo has been removed. Thank you for pointing it out.
 
-<span style = "color: blue;">P. 9, line 189: The acronym DIFM is used before it’s spelled out in the sentence, but you should spell it out first and then use the acronym. </span>  
-Reply: Thank you for identifying this writing issue. The acronym DIFM is now put after the full name. See page x, line xx.
+Corrected.
+
+<span style = "color: blue;">P. 9, line 189: The acronym DIFM is used before it's spelled out in the sentence, but you should spell it out first and then use the acronym. </span>
+
+The acronym DIFM has been placed after the full name in the revised manuscript.
 
 <span style = "color: blue;">P. 10, line 212: The (j,k) index should be subscripted here.</span>
-Reply: We very appreciate the reviewer's careful reading of the manuscript and pointing out this typo. It is not corrected to $\varepsilon_{j,k}$. (See page x, line xx.)
 
-<span style = "color: blue;">P. 11, line 221: The second “and” should be “an”. </span>  
-Reply: The typo is corrected. Thank you so much for finding this typo.
+Thanks for your careful reading. We have subscripted the indices in the revised manuscript where necessary.
+
+<span style = "color: blue;">P. 11, line 221: The second "and" should be "an". </span>
+
+Corrected.
 
@@
 The language here really matters so as to avoid confusion on the part of the readers.</span>
-Reply: The model described here is a single yield response function for the full field, in other words, not variable rate responses.
-We agree that the language used may cause confusion on whether it is a "single" response function or "single" shape constraint.
-To avoid the confusion, we removed the term "single".
-(See page x, line xx in the revised manuscript.)
 
-<span style = "color: blue;">P. 11, line 235: It seems that 1-2 citations could be added (or are missing) after “well substantiated by agronomic research.”</span>  
-Reply: We followed the reviewer's comment and added two citations of agronomic studies to support this statement. (See page x, line xx in the revised manuscript.)
+Here we are modeling a "full-field" response function.
+That is, the model assumes that yield response is uniform across the field.
+We agree that the language used could cause confusion about whether we were referring to the yield response function or the shape constraint as "single."  We removed the term "single" from the revised manuscript.
+Please see section 4.5.1 of the revised manuscript.
+
+<span style = "color: blue;">P. 11, line 235: It seems that 1-2 citations could be added (or are missing) after "well substantiated by agronomic research."</span>
+
+We have cited two additional of agronomic studies to support the statement in section 4.5.1 of the revised manuscript.
 
@@
 That is, f ̂_j^GWRR (∙) and f ̂_j^GWRT (∙).</span>
-Reply: Thank you for the recommendation.
-We think the GWRR and GWRT look more concise than GWR-R and GWR-T, and have made the changes as suggested throughout the text.
-We also put all model names (GWR and SCAM) in superscripts of equations.
-We thank the reviewer's comment to make our notations more consistent throughout the manuscript.
+
+Thank you for the recommendation.
+We have changed GWR-R and GWR-T GWRR and GWRT throughout the revised manuscript.
+We have also put all model names (GWR and SCAM) in superscripts in the pertinent equations.
 
 <span style = "color: blue;">P. 13, line 271: In keeping with your past usage, you should make sure the acronym SCAM is in uppercase throughout the text.</span>
-Reply: Thank you for pointing out this formatting error.
-We have corrected all the acronym SCAM to uppercase throughout the text.
-In addition, we also changed all the acronyms in equations to uppercase as well.
 
-<span style = "color: blue;">P. 15, line 304: “but the its benefit is even negative at when the” should have the typos/redundant wording removed.</span>  
-Reply: Thank you for pointing out those typos. They have been corrected. (See page x, line xx in the revised manuscript.)
+Done. We have put all acronyms in upper case throughout the revised manuscript.
+
+<span style = "color: blue;">P. 15, line 304: "but the its benefit is even negative at when the" should have the typos/redundant wording removed.</span>
+
+Done.
 
 <span style = "color: blue;">P. 17, line 335: Figure 0?</span>
-Reply: Our apologies for the typo. It should be Figure x. (__Taro: Which figure are you referring to here? I don't think it should be Figure 5.__)
 
-<span style = "color: blue;">P. 18, line 362: Section title should just be “Discussion”. </span>  
-Reply: The title has been changed to “Discussion”. Furthermore, we combined this section with the conclusions section.
+Our apologies for the typo. It should have been Figure 5 and this problem is fixed in our new manuscript.
 
-<span style = "color: blue;">P. 34, Figure 8 horizontal axis label: “Estiamated” should be “Estimated”. </span>
-Reply: We are very thankful for the reviewer to find out this typo. It was corrected by the revised manuscript.
+<span style = "color: blue;">P. 18, line 362: Section title should just be "Discussion". </span>
+
+We have combined what were the two final sections of the original manuscript into one section, headed “Discussion and Conclusions.”
+
+<span style = "color: blue;">P. 34, Figure 8 horizontal axis label: "Estiamated" should be "Estimated". </span>
+
+Corrected.
 
@@
 Specifically, what other statistical estimators should be reconsidered and how (specifically) should they be reassessed?</span>
-Reply: Thank you for pointing out the vagueness of this sentence.
-We added more details to explain that the other statistical methods that are commonly used in the site-specific yield response estimation literature include the regression with interaction terms of field characteristics, machine learning, etc.
-The approach of assessment is the similar simulation-based evaluation used by this study.
+
+We have edited the sentence in the revised manuscript, adding detail to explain that other statistical methods commonly used for site-specific yield response estimation literature include regression on field characteristics variables as interaction terms, machine learning, etc.
+The common assessment approach is to use simulation-based evaluation, much much as we do in our study.

### 2023-07-24 Writing/JAAEA/1stRoundRevision/reply_to_editor.rmd
modifications on replies

--- 2023-05-25 Writing/JAAEA/1stRoundRevision/reply_to_editor.rmd
@@
 output:
-  word_document: default
   html_document: default
+bibliography: PA.bib
 ---
@@
 
-Blur blur, . Your comments are in blue, and our responses are in black.
+Thank you for your thoughtful comments. Addressing them has made our paper much stronger. Below, your comments are in blue, and our responses are in black.
 
@@
 
-Actually, the dominant functional form used in the literature is quadratic-plateau for non-GWR (regualr parametric) regression because agronomists have long known that it better represents corn-nitrogen relationship.
-Application of GWR is very new to the field and GWR is not currently flexible in funcional form.
-There is no readily available statistical software or packages that lets researchers to use quadratic-plateau functionl form under the GWR framework.
-That is the primary reason that both Trevisan et al () and Rakshit et al () are using quadratic functional form.
-So, their choice of functional form is not coming from agronomic facts, rather from technical limitations.
-We are trying to point out this can be a problem with GWR just like it is a problem for regular regression framework.
-So, our paper is imporatnt because many use quadratic-plateau in regular regression framework, but the GWR promoted by the two studies use quadratic just because it is hard to do so.
-We believe it is imporatnt that this technical limitation is not trivial and would like to avoid practitioners or researcher to believe GWR is better than it truly is.
-We further suggest that it is important to develope a statistical package that allows to model yield-input relationship more flexibly.
+Actually, the dominant functional form used in the literature is quadratic-plateau for <span style = "color: red;"> non-</span>GWR (regualr parametric) regression because a agronomists have come to a consensus  that it better represents the corn-nitrogen relationship.
+Application of GWR is very new to the field, and no available software packages allow the user to conduct GWR assuming response functions that are non-linear in their parameters at the moment.
+This technical limitation is the primary reason that both Trevisan et al.
+(2021) and Rakshit et al.
+(2020) assumed a quadratic functional form of yield response.
+We are showing this can be dangerous with GWR, as it is in more traditional regression frameworks.
+Our paper's message is important--without understanding our evidence and arguments, practitioners or researchers could believe that GWR can provide more than it really can.
+One of our conclusions is that it is important for someone to develop a tool in a statistical package that allows application of GWR while modeling yield-input relationships more flexibly.
 
@@
 We fully agree with this point.
-We are assuming that readers know yield-nitrogen relationship is better represented by quadaratic-plateau and that point was kept implicit tghroughout the article.
-We made significant modifications to the manuscript so that we are not trying to blame GWR itself.
+We are assuming that readers know that the yield-nitrogen relationship is better represented by the quadaratic-plateau.
+We make this point explicitly in the revised manuscript, and it is an implicit motivator throughout the manuscript.
+But, following your responses to us, we have made significant modifications to the manuscript to show clearly that the problem is not with GWR itself, but rather is caused by the technical limitation of their being no GWR package that can handle functional forms that are nonlinear in their coefficients.
 
@@
 
-This is a problem of our writing and we apologize for that.
-Our objective is not to evaluate the problem of GWR itself, rather the current practice of using GWR with quadratic form when the true underlying true relationship is quadratic-plateau as in Trevisan et al ().
-But, we agree fully that it is interesting to see how GWR performs when the assumed funtional form in regression and true functional form in the data generating process are the same.
-However, please note that quadratic-plateu is a non-linear model and GWR with quadratic-plate cannot be estimated readily as of now.
+This was a real problem in the writing of the original manuscript, and we apologize.
+As we have written above, our objective is not to reveal any weakness inherent to GWR, but rather to point out that problems caused when software limitations cause the researcher to misspecify the functional form of the yield response function.
+But we agree fully that it is interesting to see how GWR performs when the assumed functional form in regression and true functional form in the data generating processes are the same.
+However, please note that quadratic-plateu is a non-linear model and GWR still cannot be readily used to estimate non-linear yield response.
 
-<span style = "color: blue;"> The other major critique of reviewer #1 is that the “true” DGP of the parameters does not correspond with a GWR.
-For example, reviewer #1 argues that the spatial distribution of parameters described in lines 173-193 does not correspond with a GWR DGP.
+<span style = "color: blue;"> Revierw #1's other major critique is that the “true” data generation process (DGP) of the parameters does not correspond with a GWR.
+For example, reviewer #1 argues that the spatial distribution of parameters described in the original manuscript's lines 173-193 does not correspond with a GWR DGP.
 Is there evidence from the agronomy literature that the DGP (aside from the functional form assumption) follows the process that you specify?
@@
 
-Fiest, it is important to reiterate that we are not interested in evaluating GWR itself even though our writing did give that impression, rather we are interested in evaluating GWR with quadratic functional form when the true underlying relationship is quadratic-plateau.
-This point alone addresses lots of your and reviwer 1's comments (as we discussed above, this is an important problem to address).
-We are critiqing the use of GWR with quadratic functional form when the true underlying relationship is quadratic-plateau.
+First, it is important to reiterate that we are not interested in evaluating GWR itself, even though we presented this idea very poorly in the original.
+Again, we are interested in evaluating GWR with a quadratic functional form when the true underlying relationship is quadratic-plateau.
+We believe that this point alone addresses many of the concerns addressed by both you and Reviewer 1.
 
-Second, the data generating process suggested by reviewer is not even very different from our DGP in principle even though you seem to have an impression that they are vastly different.
-
-While it may look complicated, the DGP suggested by the reviewer is basically the same as ours at the core (except functional form). Here is what the reviewer suggested.
+Second, while the DGPs may look complicated, close inspection shows that, other than the functional forms assumed, our DGP and Reviewer 1's suggested DGP are not as different as they may first appear.
+The reviewer suggested the following:
 
@@
 
-as shown in Leung, Y., Mei, C.
+, where $(X'W(s)X)^{-1}X'W(s)y = \beta$.
+As shown in Leung, Y., Mei, C.
 L., & Zhang, W.
 X.
-(2000), where $\beta_i$ is the coefficient specific to observation $i$.
+(2000),  $\beta_i$ is the coefficient specific to observation $i$.
 $W(s)$ ensures that $\beta$ are spatially correlated.
-The choice of $W(s)$ is arbitrary and if you use the same $W(s)$ used in DGP for GWR regression as well, then you would be cheating, giving an unfair advantage to GWR because we (researchers) never know $W(s)$ in reality just like we do not know the weight matrix in spatial econometric approaches like spatial error model.
-This is the "correct" GWR DGP only if you know what $W(s)$ is priori.
+The choice of $W(s)$ is arbitrary, and and there for it could be fairly called "cheating" to use the same $W(s)$ in the DGP and for the GWR both.
+This method gives an unfair advantage to GWR because the researcher cannot know the real $W(s)$.
+The situation is much like the one created becauase the researcher does not know the true weight matrix in spatial econometric approaches.
+This can only be called the "correct" GWR DGP only when $W(s)$ is known a priori.
 
-In our DGP, we generate parameters (alpha, ...
-in equation )for individual $i$ in a spatially correlated manner (as opposed to what the reviewer thought).
-So, aside from the functional form, the only difference is in the spatial pattern of parameters.
-It is kind of like, we are using a different $W(s)$ in the above equation, which is an arbitrary parameter chosen by the researcher running MC simulations in the first place.
+In our DGP, we generate spatially correlated parameters (alpha, ...
+in equation ) for individual $i$.
+(Reviewer 1 was under the impression that these parameters were not spatially correlated, but indeed they are.) So, aside from the functional form, the only difference in our DGPs is in the spatial pattern of parameters.
+It is much as if we were are using a $W(s)$ different from in the above equation, which is an arbitrary parameter chosen by the researcher running MC simulations in the first place.
 In this sense, our DGP is just as "valid" as the GWR DGP.
 
-Indeed, I would say our DGP is superior because ours is much more flexible.
-The DGP suggested by the reviewer cannot even accommodate non-linear model, while our DGP can use any functional relationship between $Y$ and $X$ as evident in our paper.
-Indeed, this is critical to our study because the data generating process <span style = "color: red;"> needs </span> to be quadratic-plateau to better represent the actual functional relationship exhibited by corn-nitogen response.
+In fact, we believe that our DGP is $superior$ to the the one suggested by Reviewer 1 because ours is more flexible.
+The DGP suggested by the Reviewer 1 cannot accommodate non-linear models, while our DGP can use any functional relationship between $Y$ and $X$.
+This is critical to our study because the DGP <span style = "color: red;"> needs </span> to include the quadratic-plateau functional form to better represent the actual functional relationship exhibited by corn-nitogen response.
 
-You are right that no agronomic studies suggest eigher our or the reviewer's DGP as a better DGP.
-However, our DGP has been used in an article in a prominent agronomy and precision agriculture journal (cite), meaning that our DGP was accepted by agronomists who reviewed them.
-On the other hand, the data generating process suggested by the reviewer has never been applied in the cotext of precision agriculture.
-Of course, we are not saying that our DGP is correct.
-And, this is not the main reason why we do not use the DGP suggested by the reviewer.
+You are right that no agronomic studies have examined whether our DGP or Reviewer 1's is superior.
+But whereas Reviewer 1's DGP has never been applied in the context of precision agriculture, ours has been used in several articles in prominent, peer-reviewed agronomy and precision agriculture journal [@kakimoto2022causal; @li2023economic].
+Of course, we are not claiming that our DGP is "correct."  But it is not inferior to the reviewer's DGP, and we have elected to keep it in our study.
 
-The reviewer clearly did not spend time trying to understand our DGP as the reviewer suggested him/herself.
-Also, the reviewer's criticism is based on his understanding that we are trying to test GWR itself and also test the its accuracy in parameter estimation, not EONR and profit estimation.
-Our impression of this reviewer from his/her comments is that he/she lacks domain knowledge and also economics.
+We take responsibility for the poor communication in our original manuscript that generated much of Reviewer 1's poor understanding of our study's methods and motivations.
+Reviewer 1's thought that our principal abjectives were test GWR itself and to test the accuracy in parameter estimation accuracy.
+We believe that in the revised manuscript we have made clear that our goal is to examine the economic effects of using GWR under misspecification of the yield response function.
 
@@
 
-It seems that you have an impression that the GWR DGP is the "correct" DGP if we are estimating with GWR.
-But, as I argued above, there is no such thing as the "correct" DGP.
-In GWR DGP, the choice of $W(s)$ is arbitrary and no researchers should know it.
-In that sense, you are destined to misspecify the underlying DGP in a realistic situation.
-The most important part of the DGP is by far the functinal form of yield and nitrogen.
+When using the GWR DGP, the researcher cannot know the "true" $W(s)$ matrix, and therefore misspecifying the underlying DGP is unavoidable.
+It is not possible to use the "correct" DGP, regardless of whether the underlying model is estimated with GWR.
+The point of our article is to point out the importance of the functional form assumption when GWR is used.
+If we were to follow Reviewer 1's suggestion that we use quadratic functional form as our true yield-nitrogen response, the whole point of the paper whould be lost.
 
 We will not use the GWR DGP process for two reasons.
-First, as we mentioned, we are not interested in criticizing GWR itself, but GWR with quadratic form when the true yield response function is better represented by quadratic-plateau (we aruged why this is important in our replies above).
+First, as we mentioned, we are not interested in criticizing GWR itself, but GWR with quadratic form when the true yield response function is better represented by quadratic-plateau (we argued why this is important in our replies above).
 Also, the GWR DGP process suggested by the reviewer is limited to linear-in-parmeter model (like quadratic model).
 It simply cannot be used for quadratic-plateau.
-If we were to use quadratic functional form for our true yield-nitrogen response, then this study is completely useless and loses its significance in the literature of precision agriculture.
 
@@
 
-It is not important in this paper to distinguish and isolate the sources of bias.
-Our interest is in showing the bias of using GWR with quadratic form (because of technical limitation) even though the underlying relatinship is quadratic-plateau (like corn-nitrogen) as done by Trevisan et al ().
-It is actually impossible in our paper to isolate them and we are not interested in doing so either.
+It is not our intention in this paper to distinguish and isolate the sources of bias.
+Our interest is in showing the bias of using GWR with a quadratic functional form of yield response (as does Trevisan,et al.
+(2021) ) even though the underlying relationship is quadratic-plateau.
 Also, please note that functional form is part of DGP and indeed the most important part of a DGP.
-There is no such thing as isolating the source of bias of funcitonal form assumption and DGP assumption.
+There is no such thing as isolating the source of bias of a functional form assumption and a DGP assumption.
 
-If our interest is understanding the problem of estiamtion inaccurcy by GWR alone, then we should have used quadratic-plateau in our GWR estimation so that the functional forms match.
-But, this is not our interest at least in this paper and it is also technically too cumbersome at the moment because there is no readily available statistical software to implement it.
-We are criticizing the practice that has been used by a researcher that can have false impression about how valuable GWR is for variable rate nitrogen application in the OFEP setting.
+If our interest were in understanding the problem of GWR estimation inaccuracy, we should have used quadratic-plateau in our GWR estimation so that the functional forms matched.
+But, this was not our intent, and anyway at this point in time it would be technically too cumbersome since there is no readily available statistical software to implement it.
+We are criticizing the practice that has been used by researchers that can give a false impression about how valuable GWR is in providing information for variable rate nitrogen application management in the OFPE setting.

### 2023-07-24 Writing/manuscript_gwr.rmd
modifications on replies

@@
 
-**Abstract**: Geographically weighted regression (GWR) has been presented as a prominent tool to estimate site-specific yield response functions to derive site-specific input rate recommendations from data generated by on-farm precision experimentation (OFPE).
-However, the current application of GWR in this context assumes quadratic yield response function even though many of the yield-input relationships has been shown to be better represented by the quadratic-plateau functional form.
-This is due to lack of readily available methods and statistical packages that allow researchers to estimate non-linear model under the GWR framework, including quadratic-plateau.
-The key objective of this paper is to investigate the possibility of bias in estimating the economic value of site-specific recommendation maps based on GWR with quadratic functional form assumption when in reality the true underlying yield-input relationship is quadratic-plateau.
-We consider two sets of functional-form specifications used by two recent published studies of site-specific input management that apply GWR to data from OFPE.
+**Abstract**: Geographically weighted regression (GWR) has been presented as a valuable tool for the estimation of site-specific yield response functions used to derive site-specific input rate recommendations from data generated by on-farm precision experimentation (OFPE).
+But applications of GWR in this context have assumed a quadratic yield response function, despite a scientific consensus that the yield-input relationships modeled are better represented by the quadratic-plateau functional form.
+The quadratic assumption has been made because no readily available statistical packages exist for GWR estimation with non-linear functional forms.
+The key objective of this paper is to investigate whether, when the true functional form of yield response is quadratic-plateau, assuming a quadratic form introduces bias into the GWR estimation of the economic value of site-specific recommendation maps.
+We consider two sets of functional-form specifications used by recently published studies of site-specific input management that apply GWR to data from OFPE.
 We show that both GWR approaches suffer significant positive bias, which can lead to large over-estimation of the economic value of applying GWR methods.
-We reveal that in many circumstances using GWR is far less profitable than claimed by previous studies, which provides a necessary cautionary message to researchers who might otherwise "over-sell" to other researchers the value of using GWR methods in empirical work involving the estimation of site-specific input management.
-We encourage the statistical community to extend the current GWR capability by allowing researchers to model yield-input response more flexibly than currently possible.
+We conclude that in many circumstances the information gleaned from using GWR may be far less valuable than has been claimed.
+We encourage the statistical community to develop tools in software packages providing GWR that allow more flexibility in functional form assumptions.
 
@@
 It is important to develop GWR with more flexible functional forms than currently possible if precision agriculture practitioner is interested in using GWR as one of the tools to estimate site-specific input use recommendation.
+
+# Background:  Estimation of Yield-to-input Response Relationships Using OFPE Data
 

### 2023-07-24 Writing/JAAEA/1stRoundRevision/reply_to_reviewer_2.rmd

@@
 Your comments are in blue, and our responses are in black.
-
-First, we would like to express our sincere gratitude for the reviewer's careful examination and critique of our manuscript.
-The insightful comments and suggestions have significantly contributed to the paper's clarity, detail, and overall strength.
-In return, we have attempted to carefully address each of the comments and revise the manuscript in response.
 
@@
 
+We would like to express our sincere gratitude for the reviewer’s careful examination and critique of our manuscript.
+The insightful comments and suggestions have significantly contributed to the paper’s clarity, detail, and overall strength.
+In return, we have attempted to carefully address each of the comments and revise the manuscript in response.
+
 <br>
@@
 
-Very good point.
-What makes this study differ from previous studies is that the model "value" is not measured by the accuracy of parameter estimates, but rather by the ultimate economic return.
+This is a very good point.
+What makes this study differ from previous studies is that the model “value” is not measured by the accuracy of parameter estimates, but rather by the ultimate economic return.
 We have followed your suggestion above by expanding our review of previous studies to highlight what our research adds to the literature.
@@
 
-Good point.
-We have included a brief discussion of the historical corn and nitrogen prices in the first paragraph of the Results section, which is section 5.
+Thank you for bringing up this point.
+We have included a brief discussion of the historical corn and nitrogen prices in the first paragraph of the Results section 5.1.
 Additionally, we have included Appendix I: Historical Corn and Nitrogen Prices in the supplementary material to provide a more detailed description of the collection, calculation, and summary statistics of the historical price data.
@@
 That figure was meant to compare the estimated and true GWR coefficients $\beta_1$ and $\beta_2$.
-But since we have already compared the estimated and true EONR's in another figure, so the figure 4 was redundant.
+But since we have already compared the estimated and true EONR's in another figure, the figure 4 was redundant.
 We have removed it from the revised manuscript.
@@
 
-Reply: We agree with the reviewer's comment that precision agriculture, site-specific farming, and variable-rate technology are not synonymous.
+We agree with the reviewer's comment that precision agriculture, site-specific farming, and variable-rate technology are not synonymous.
 Although in the literature those terms are often used interchangeably, they are not strictly speaking equivalent.
@@
 Thanks for pointing out the typo.
-Yes, it should be the square root of the sill variances since 1379 kg ha−1 was the mean of the standard deviations.
-We have corrected that typo in the revised manuscript at (page x, line xx in the revised manuscript).
+Yes, it should be the square root of the sill variances since 1370 kg ha−1 was the mean of the standard deviations.
+We have corrected that typo in the revised manuscript at the end of section 4.2.
 
@@
 
-Reply: If we understand the question correctly, you are asking about the robustness of GWR estimates to bandwidth selection.
+If we understand the question correctly, you are asking about the robustness of GWR estimates to bandwidth selection.
 Choosing bandwidth is indeed a crucial step in GWR estimation, and there are many different bandwidth selection methods in the literature.
@@
 We agree the GWR results could vary when choosing different bandwidths, but the choices of other bandwidth values other than the AIC-chosen one may be arbitrary.
-We added more discussions about bandwidth selection in page x, lines xxx of the revised manuscript.
+We added more discussions about bandwidth selection at the end of section 4.5.3 of the revised manuscript.
 
@@
 
-Our apologies for the typos. We have corrected them and filled in the correct numbers. (See page x, line xx in the revised manuscript.)
+Our apologies for the typos. We have corrected them and filled in the correct numbers. They can be found in the end of the 2nd paragraph of section 5.1 of the revised manuscript.
 
@@
 
-We have corrected the order of the figures.
+Thank you for identifying the incorrect order of figures.
+We apologize for the mistake, and we have corrected the order of the figures accordingly.
+The revised manuscript now reflects the correct sequence of Figures 5 and 6.
 
@@
 
-Corrected.
+This grammar error was corrected. The new sentence is now on section 2.2, the 1st paragraph, line 2 of the revised manuscript.
 
@@
 
-Reply: In precision agriculture, the site-specific input management recommendation map is commonly called "prescription" or "Rx" by researchers and the industry.
-While we are certainly willing to defer to the editor's judgment, We have elected to keep this abbreviation in the revised manuscript, but have added a brief explanation of the notation.
-In the USA, at least, it is widely known that "Rx" means "prescription,"" and it is chiefly used in conversations about medicines and pharmacies.
+In precision agriculture, the site-specific input management recommendation map is commonly called "prescription" or "Rx" by researchers and the industry.
+While we are certainly willing to defer to the editor's judgment, We have elected to keep this abbreviation in the revised manuscript, but have added a brief explanation of the notation (near the end of section 2.2).
+In the USA, at least, it is widely known that "Rx" means "prescription," and it is chiefly used in conversations about medicines and pharmacies.
 
@@
 
-Thank you for the suggestion. We agree that placing the commercial examples in a footnote is a better idea. Please see footnote 1 of the revised manuscript.
+Thank you for the suggestion. We agree that placing the commercial examples in a footnote is a better approach. Please see footnote 1 of the revised manuscript.
 
@@
 
-We have followed the reviewer's suggestion and broken the discussion into two paragraphs In the revised manuscript.
+We have followed the reviewer's suggestion and broken the discussion into two paragraphs in the revised manuscript.
 
@@
 
-Corrected.
+This typo has been removed. Thank you for bring it to our attention.
 
@@
 
-The acronym DIFM has been placed after the full name in the revised manuscript.
+Thank you for pointing out this writing issue. We have placed the acronym DIFM after the full name in the revised manuscript
 
@@
 
-Thanks for your careful reading. We have subscripted the indices in the revised manuscript where necessary.
+We greatly appreciate the reviewer’s meticulous review of the manuscript and for finding this typo.
+We have corrected it to use subscript notation (see line 3 of section 4.4).
+Furthermore, to eliminate the duplication of the spline index $k$, we have updated the cell index notation to $(j, i)$ both in this section and throughout the rest of the manuscript.
 
@@
 
-Corrected.
+The typo is corrected. Thank you so much for finding this typo.
 
@@
 
-Done. We have put all acronyms in upper case throughout the revised manuscript.
+Thank you for pointing out this formatting error.
+We have corrected the issue by ensuring that the acronym “SCAM” is consistently written in uppercase throughout the text.
+Additionally, we have capitalized all acronyms in equations as well.
 
@@
 
-Done.
+Thank you for pointing out those typos. They have all been corrected (see the end of the 2nd paragraph of section 5.1 of the revised manuscript).
 
@@
 
-Corrected.
+We greatly appreciate the reviewer for identifying this typo. It was corrected in the revised manuscript.
 
@@
 
-We have edited the sentence in the revised manuscript, adding detail to explain that other statistical methods commonly used for site-specific yield response estimation literature include regression on field characteristics variables as interaction terms, machine learning, etc.
-The common assessment approach is to use simulation-based evaluation, much much as we do in our study.
+We have edited the sentence in the revised manuscript (see the end of paragraph 4, section 6 in the revised manuscript), adding details to explain that other statistical methods commonly used for site-specific yield response estimation literature include regression on field characteristics variables as interaction terms, machine learning, etc.
+The common assessment approach is to use simulation-based evaluation, much as we do in our study.

### 2023-07-24 Writing/JAAEA/1stRoundRevision/reply_to_reviewer_2.rmd
change

@@
 
-We would like to express our sincere gratitude for the reviewer’s careful examination and critique of our manuscript.
-The insightful comments and suggestions have significantly contributed to the paper’s clarity, detail, and overall strength.
+We would like to express our sincere gratitude for the reviewer's careful examination and critique of our manuscript.
+The insightful comments and suggestions have significantly contributed to the paper's clarity, detail, and overall strength.
 In return, we have attempted to carefully address each of the comments and revise the manuscript in response.
@@
 
-We greatly appreciate the reviewer’s meticulous review of the manuscript and for finding this typo.
+We greatly appreciate the reviewer's meticulous review of the manuscript and for finding this typo.
 We have corrected it to use subscript notation (see line 3 of section 4.4).

### 2023-07-27 Codes/3_make_figures_publication.rmd
finalized revision

# Set figure theme 
```{r}
theme_fig <-
  theme_bw() +
  theme(
    axis.title.x =
      element_text(
        size = 12, angle = 0, hjust = .5, vjust = -0.3, family = "Times"
      ),
    axis.title.y =
      element_text(
        size = 12, angle = 90, hjust = .5, vjust = .9, family = "Times"
      ),
    axis.text.x =
      element_text(
        size = 9, angle = 0, hjust = .5, vjust = 1.5, family = "Times"
      ),
    axis.text.y =
      element_text(
        size = 9, angle = 0, hjust = 1, vjust = 0, family = "Times"
      ),
    axis.ticks =
      element_line(
        linewidth = 0.3, linetype = "solid"
      ),
    axis.ticks.length = unit(.15, "cm"),
    #--- legend ---#
    legend.text =
      element_text(
        size = 12, angle = 0, hjust = 0, vjust = 0.5, family = "Times"
      ),
    legend.title =
      element_text(
        size = 12, angle = 0, hjust = 0, vjust = 0, family = "Times"
      ),
    legend.key.size = unit(0.5, "cm"),
    #--- strip (for faceting) ---#
    strip.text = element_text(size = 12, family = "Times"),
    #--- plot title ---#
    plot.title = element_text(family = "Times", face = "bold", size = 12),
    #--- margin ---#
    # plot.margin = margin(0, 0, 0, 0, "cm"),
    #--- panel ---#
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    panel.border = element_rect(fill = NA)
  )
```

# Visualization the field and spatial units

```{r}
# fig.id = "field-layout",
# fig.cap = "Simulated field layout with spatial unit definitions",
# fig.dim = c(6, 6)

field_with_design <- readRDS(here("Shared/Data/field_with_design.rds"))
field_sf <- field_with_design[1, ]$field_sf[[1]]

plot_sf <-
  field_sf %>%
  nest_by(plot_id) %>%
  mutate(data = list(
    st_union(data)
  )) %>%
  unnest() %>%
  st_as_sf()

block_sf <-
  field_sf %>%
  nest_by(block_id) %>%
  mutate(data = list(
    st_union(data)
  )) %>%
  unnest() %>%
  st_as_sf()

block_text_sf <- st_centroid(block_sf)

#* Field: plots and blocks
g_field <-
  ggplot() +
  geom_sf(data = plot_sf, size = 0.2, fill = NA) +
  geom_sf(data = dplyr::filter(plot_sf, plot_id == 264), fill = "red", alpha = 0.5) +
  geom_sf(data = block_sf, fill = NA, linewidth = 1.5) +
  annotate("text", x = 830, y = 74, label = "plot", color = "red", size = 4, family = "Times") +
  geom_segment(
    aes(x = 830, xend = 830, y = 30, yend = -80),
    arrow = arrow(length = unit(0.5, "cm")),
    linewidth = 1,
    color = "red"
  ) +
  geom_sf_text(
    data = block_text_sf,
    aes(label = paste0("block ", block_id)),
    size = 5,
    family = "Times"
  ) +
  theme_void() +
  theme(plot.title = element_text(family = "Times")) +
  ggtitle("Panel (a): Plots and blocks in an experimental field")

## inside a plot
plot_sf_focus <- dplyr::filter(field_sf, plot_id == 1)

subplot_sf <-
  plot_sf_focus %>%
  nest_by(aunit_id, buffer) %>%
  mutate(data = list(
    st_union(data)
  )) %>%
  unnest() %>%
  st_as_sf() %>%
  mutate(label = ifelse(
    buffer == 1,
    "buffer",
    paste0("subplot-", aunit_id - 1)
  )) %>%
  mutate(buf_or_not = ifelse(label == "buffer", "buffer", "subplot"))

subplot_text_sf <- st_centroid(subplot_sf)

site_sf <- plot_sf_focus[7, ]

g_inside_plot <-
  ggplot() +
  geom_sf(data = plot_sf_focus, size = 0.2, fill = NA) +
  geom_sf_text(
    data = subplot_text_sf,
    aes(label = label),
    size = 3,
    family = "Times"
  ) +
  geom_sf(data = subplot_sf, linewidth = 1.2, fill = NA) +
  geom_sf(data = site_sf, fill = "red", alpha = 0.3) +
  annotate("text", x = 39, y = 429, label = "cell", family = "Times") +
  scale_fill_discrete(name = "") +
  theme_void() +
  theme(
    legend.position = "bottom",
    legend.text = element_text(size = 12),
    plot.title = element_text(family = "Times")
  ) +
  ggtitle("Panel (b): Subplots, buffers, and sites in a single plot")

g_layout <- g_field / g_inside_plot

ggsave(
  "GitControlled/Writing/Figures/g_layout.png",
  g_layout,
  width = 6,
  dpi = 600
)
```

# Experimental Design

```{r}

# fig.id = "field-N-design",
# fig.cap = "Experiment design of nitrogen (N) rates"

reg_data <-
  readRDS(here("Shared/Data/LatinSquareFixed_144.rds")) %>%
  pull(reg_data) %>%
  .[[1]] %>%
  .[1]

data <- reg_data$data[[1]]

N_levels <- reg_data$N_levels[[1]]

data <-
  data %>%
  .[, Nid := as.numeric(as.factor(Nid))] %>%
  .[, Ntg := N_levels[Nid]]

f <-
  left_join(field_sf, data[, .(aunit_id, Ntg)], by = "aunit_id") %>%
  data.table() %>%
  .[, Ntg := factor(Ntg)] %>%
  .[buffer == 1, Ntg := "buffer"] %>%
  .[, Ntg := factor(Ntg, levels = c("buffer", as.character(levels(Ntg)[-7])))] %>%
  st_as_sf()

g_exp <-
  ggplot() +
  geom_sf(data = f, aes(fill = (Ntg)), size = 0.1) +
  scale_fill_viridis_d(name = "N rate (kg/ha)", direction = -1) +
  theme_void() +
  theme(
    plot.title = element_text(hjust = 0.5, family = "Times"),
    legend.title = element_text(hjust = 0.5, family = "Times"),
    legend.position = "bottom",
    legend.key.size = unit(0.4, "cm"),
    legend.text = element_text(size = 10, family = "Times")
  )

ggsave(
  "GitControlled/Writing/Figures/g_exp.png",
  g_exp,
  width = 6,
  dpi = 600
)
```

# Read the results

```{r}
results <-
  here("Shared/Results/gaussian/pi_data.rds") %>%
  readRDS() %>%
  .[, type := ifelse(transfer == 0, "GWRR", "GWRT")] %>%
  .[, bias := pi_diff_est - pi_diff] %>%
  # only display the 25% (5.44), 50% (6.56), 75% (7.67) price ratio
  .[pRatio %in% c(5.44, 6.56, 7.67), ] %>%
  # === label price ratio
  .[, pLabelName := "Price Ratio (N/corn)"] %>%
  .[pRatio == 5.44, pLabel := "Low"] %>%
  .[pRatio == 6.56, pLabel := "Middle"] %>%
  .[pRatio == 7.67, pLabel := "High"] %>%
  .[, pLabel := factor(pLabel, levels = c("Low", "Middle", "High"))]
# fig.id = "pi-dif-dist",
# fig.cap = "The value of GWR-based VRA over SCAM-based URA for GWR-R and GWR-T"
```

# The value of GWR-based VRA over SCAM-based URA for GWR-R and GWR-T

```{r}
mean_data_value <-
  results %>%
  .[, .(pi_diff = median(pi_diff)),
    by = c("field_col", "pLabel", "type")
  ]

# saveRDS(mean_data_value, "Shared/Results/mean_data_value.rds")

g_value <-
  results %>%
  ggplot(data = .) +
  geom_histogram(
    aes(x = pi_diff),
    fill = NA,
    color = "blue",
    bins = 50,
    linewidth = 0.2
  ) +
  geom_vline(
    data = mean_data_value,
    aes(xintercept = pi_diff),
    color = "red",
    linewidth = 0.5
  ) +
  geom_text(
    data = mean_data_value, color = "red",
    aes(
      x = ifelse(pi_diff < 65, pi_diff + 5, pi_diff - 20), y = 150,
      label = paste0("Median = ", round(pi_diff, 2))
    ),
    angle = 0,
    hjust = -0.1,
    vjust = 0,
    size = 3,
    family = "Times"
  ) +
  facet_grid(pLabel ~ type) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_x_continuous(breaks = 20 * (-2:3), limits = c(-45, 60)) +
  xlab("The value of VRA over URA ($ per ha)") +
  ylab("Number of Simulation Cases") +
  theme_fig

ggsave(
  "GitControlled/Writing/Figures/g_value.png",
  g_value,
  width = 6,
  height = 5,
  dpi = 600
)
```

# EONR estimation tendency

```{r}
# ggplot(est_data) +
# geom_histogram(aes(x = opt_N_scam)) +
# facet_grid(round(pN, digits = 2) ~ .)

est_data <-
  readRDS(here("Shared/Results/Gaussian/est_data.rds")) %>%
  unnest() %>%
  data.table() %>%
  .[, type := ifelse(transfer == 0, "GWR-R", "GWR-T")]

eorn_ratio_data <-
  est_data %>%
  .[, pRatio := pN / pCorn] %>%
  # only display the 25% (5.44), 50% (6.56), 75% (7.67) price ratio
  .[pRatio %in% c(5.44, 6.56, 7.67), ] %>%
  # === label price ratio
  .[, pLabelName := "Price Ratio (N/corn)"] %>%
  .[pRatio == 5.44, pLabel := "Low"] %>%
  .[pRatio == 6.56, pLabel := "Middle"] %>%
  .[pRatio == 7.67, pLabel := "High"] %>%
  .[, pLabel := factor(pLabel, levels = c("Low", "Middle", "High"))] %>%
  .[, .(eonr_ratio = mean(opt_N_gwr / opt_N_scam)), by = .(type, sim, pLabel)]

g_eonr_bias <-
  ggplot(data = eorn_ratio_data) +
  geom_histogram(
    aes(x = eonr_ratio),
    color = "blue",
    fill = NA,
    bins = 50,
    size = 0.2
  ) +
  geom_vline(xintercept = 1, color = "red") +
  facet_grid(pLabel ~ type) +
  ylab("Number of Simulation Cases") +
  xlab("Average Ratio of Estimated EONR to true EONR") +
  theme_fig

ggsave(
  "GitControlled/Writing/Figures/g_eonr_bias.png",
  g_eonr_bias,
  width = 6,
  height = 5,
  dpi = 600
)
```

# Comparison of Estimated and True Coefficients

```{r}

# fig.id = "true-vs-estimated-coef-gwr-r",
# fig.cap = "Comparison of Estimated and True Coefficients"

#* read the simulation data for a sigle simulationused for illustration
single_sim <-
  here("Shared/Results/Gaussian/aunit_sim_single.rds") %>%
  readRDS() %>%
  .[, type := ifelse(transfer == 0, "GWR-R", "GWR-T")]

plot_data <-
  single_sim %>%
  .[type == "GWR-R", ] %>%
  .[, .(aunit_id, b1, b2, b1_hat, b2_hat)] %>%
  melt(id.var = "aunit_id") %>%
  .[, type := ifelse(str_detect(variable, "hat"), "Estimated", "True")] %>%
  .[, variable := gsub("_hat", "", variable)] %>%
  dcast(aunit_id + variable ~ type, value.var = "value")

g_b1 <-
  plot_data[variable == "b1", ] %>%
  ggplot(data = .) +
  geom_point(aes(y = Estimated, x = True), size = 0.3) +
  xlim(0, NA) +
  ylim(0, NA)

g_b2 <-
  plot_data[variable == "b2", ] %>%
  ggplot(data = .) +
  geom_point(aes(y = Estimated, x = True), size = 0.3) +
  geom_hline(yintercept = 0, color = "red") +
  xlim(NA, 0.1) +
  ylim(NA, 0.1) +
  theme_fig

g_comp_coef <- g_b1 / g_b2
```

# Comparison of Estimated and True EONR

```{r}
# fig.id = "true-vs-estimated-optn-gwr-r",
# fig.cap = "Comparison of Estimated and True EONR"

# est_data[sim == 1 & pn_pc == 10.35, ] %>%
#   .[, type := ifelse(transfer == 0, "GWR-R", "GWR-T")] %>%
#   ggplot(data = .) +
#     geom_histogram(aes(x = opt_N_gwr)) +
#     facet_grid(. ~ type)

g_comp_eonr <-
  single_sim %>%
  ggplot(data = .) +
  geom_point(aes(y = opt_N_gwr, x = opt_N), size = 0.3) +
  geom_abline(slope = 1, color = "red") +
  xlab("True Optimal Nitrogen Rate (kg/ha)") +
  ylab("Estimated Optimal Nitrogen Rate (kg/ha)") +
  facet_grid(. ~ type) +
  theme_fig +
  coord_equal()

ggsave(
  "GitControlled/Writing/Figures/g_comp_eonr.png",
  g_comp_eonr,
  width = 6,
  height = 5,
  dpi = 600
)
```

# Bias in the estimation of the value of GWR-based VRA over SCAM-based URA

```{r}
# fig.id = "bias-est-pi",
# fig.cap = "Bias in the estimation of the value of GWR-based VRA over SCAM-based URA for GWR-R and GWR-T"

# mean_data_bias[type == "GWR-T" & pLabel == 10.35, bias] %>% hist

median_bias_data <-
  results %>%
  .[, bias := pi_diff_est - pi_diff] %>%
  .[, .(bias = median(bias)),
    by = c("field_col", "pLabel", "type")
  ] %>%
  print()

g_bias <-
  results %>%
  .[, bias := pi_diff_est - pi_diff] %>%
  .[bias < 150, ] %>%
  ggplot(data = .) +
  geom_histogram(
    aes(x = bias),
    fill = NA,
    color = "blue",
    size = 0.2,
    bins = 50
  ) +
  geom_vline(
    data = median_bias_data, aes(xintercept = bias),
    color = "red",
    size = 0.5
  ) +
  geom_text(
    data = median_bias_data, color = "red",
    aes(
      x = ifelse(bias < 65, bias + 2, bias - 85), y = 100,
      label = paste0("Median = ", round(bias, 2)),
      family = "Times"
    ),
    angle = 0, hjust = -0.1, vjust = 0, size = 3
  ) +
  facet_grid(pLabel ~ type) +
  scale_y_continuous(expand = c(0, 0)) +
  xlab("Bias in the Estimation of the Value of VRA over URA ($ per ha)") +
  ylab("Number of Simulation Cases") +
  theme_fig

ggsave(
  "GitControlled/Writing/Figures/g_bias.png",
  g_bias,
  width = 6,
  height = 5,
  dpi = 600
)
```

# The cause of significant over-estimation of the value of GWR-based VRA

```{r}

# fig.id = "why-bias-many",
# fig.cap = "The cause of significant over-estimation of the value of GWR-based VRA"

# /*+++++++++++++++++++++++++++++++++++
#' # Prepare parameters
# /*+++++++++++++++++++++++++++++++++++
field_parameters <- readRDS(here("Shared/Data/field_parameters.rds"))

pCorn <- field_parameters$pCorn
pN <- pCorn * field_parameters$pRatio_ls[[1]][2] # medium price scenario

# /*+++++++++++++++++++++++++++++++++++
#' # Prepare yield response curves
# /*+++++++++++++++++++++++++++++++++++
il_data_oe <-
  readRDS(here("Shared/Results/Gaussian/il_data_oe.rds")) %>%
  .[,
    lapply(.SD, mean),
    by = aunit_id,
    .SDcols = c(
      "b0", "b1", "b2", "Nk",
      "b0_hat", "b1_hat", "b2_hat",
      "opt_N", "opt_N_gwr", "opt_N_scam"
    )
  ]

n_data <-
  data.table(
    N = seq(
      min(il_data_oe$opt_N_gwr) - 50,
      max(il_data_oe$opt_N_gwr, il_data_oe$opt_N_scam),
      length = 30
    )
  )

set.seed(710527)
aunit_id_ls <- sample(il_data_oe$aunit_id, 50)

gwr_curv_data <-
  expand_grid_df(il_data_oe, n_data) %>%
  .[, yield := (b0_hat + b1_hat * N + b2_hat * N^2) / 1000] %>%
  .[, profit := pCorn * yield * 1000 - pN * N] %>%
  .[aunit_id %in% aunit_id_ls, ]

# /*+++++++++++++++++++++++++++++++++++
#' # Prepare point data
# /*+++++++++++++++++++++++++++++++++++

point_data <-
  il_data_oe %>%
  .[, y_hat_gwr := (b0_hat + b1_hat * opt_N_gwr + b2_hat * opt_N_gwr^2) / 1000] %>%
  .[, y_hat_scam := (b0_hat + b1_hat * opt_N_scam + b2_hat * opt_N_scam^2) / 1000] %>%
  .[aunit_id %in% aunit_id_ls, ] %>%
  .[, .(aunit_id, y_hat_gwr, y_hat_scam, opt_N_gwr, opt_N_scam)] %>%
  melt(id.var = "aunit_id") %>%
  .[, var_type := fifelse(str_detect(variable, "y_hat"), "yield", "N")] %>%
  .[, type := fifelse(str_detect(variable, "gwr"), "GWR", "SCAM")] %>%
  .[, variable := NULL] %>%
  dcast(aunit_id + type ~ var_type, value.var = "value") %>%
  .[, profit := pCorn * yield * 1000 - pN * N]

# /*+++++++++++++++++++++++++++++++++++
#' # Figure
# /*+++++++++++++++++++++++++++++++++++
g_why_bias_many <-
  ggplot() +
  geom_line(
    data = gwr_curv_data,
    aes(y = yield, x = N, group = aunit_id),
    size = 0.3,
    color = "grey"
  ) +
  geom_point(
    data = point_data,
    aes(y = yield, x = N, color = type),
    size = 0.6
  ) +
  ylab("Estimated Yield (ton/ha)") +
  xlab("Nitrogen Rate (kg/ha)") +
  theme_fig +
  theme(
    legend.position = "bottom"
  ) +
  scale_color_discrete(name = "Estimated EONR")

ggsave(
  "GitControlled/Writing/Figures/g_why_bias_many.png",
  g_why_bias_many,
  width = 6,
  height = 5,
  dpi = 600
)
```

# An illustration of over-estimation of the value of GWR-based VRA over SCAM-based URA

```{r}
# fig.id = "why-bias-single",
# fig.cap = "An illustration of over-estimation of the value of GWR-based VRA over SCAM-based URA",
# fig.dim = c(6, 7)

# /*+++++++++++++++++++++++++++++++++++
#' # Preapare yeld response curves
# /*+++++++++++++++++++++++++++++++++++
true_curv_data <-
  il_data_oe %>%
  .[aunit_id %in% aunit_id_ls[1], ] %>%
  expand_grid_df(., n_data) %>%
  .[, y_true_curve_raw := (b0 + b1 * N + b2 * N^2) / 1000] %>%
  .[, y_true_curve_pl := (b0 + b1 * Nk + b2 * Nk^2) / 1000] %>%
  .[, yield := fifelse(N < Nk, y_true_curve_raw, y_true_curve_pl)] %>%
  .[, profit := pCorn * yield * 1000 - pN * N] %>%
  .[, .(yield, profit, N)] %>%
  .[, type := "True"]

gwr_curv_data_f <-
  gwr_curv_data[aunit_id %in% aunit_id_ls[1], ] %>%
  .[, .(yield, profit, N)] %>%
  .[, type := "GWR-estimated"]

curv_data <-
  rbind(true_curv_data, gwr_curv_data_f) %>%
  .[, type := factor(type, levels = c("True", "GWR-estimated"))]

# /*+++++++++++++++++++++++++++++++++++
#' # Prepare yield points data
# /*+++++++++++++++++++++++++++++++++++
true_yield_data <-
  il_data_oe %>%
  .[aunit_id %in% aunit_id_ls[1], ] %>%
  .[, .(b0, b1, b2, Nk, opt_N_gwr, opt_N_scam, opt_N)] %>%
  melt(id.vars = c("b0", "b1", "b2", "Nk")) %>%
  setnames("value", "N") %>%
  .[, y_true_raw := (b0 + b1 * N + b2 * N^2) / 1000] %>%
  .[, y_true_pl := (b0 + b1 * Nk + b2 * Nk^2) / 1000] %>%
  .[, yield := fifelse(N < Nk, y_true_raw, y_true_pl)] %>%
  .[, profit := pCorn * yield * 1000 - pN * N] %>%
  .[, type := fcase(
    variable == "opt_N_gwr", "GWR",
    variable == "opt_N_scam", "SCAM",
    variable == "opt_N", "True"
  )] %>%
  .[, .(yield, profit, N, type)]

point_data_gwr <-
  point_data[aunit_id %in% aunit_id_ls[1], ]

# /*+++++++++++++++++++++++++++++++++++
#' # Figure
# /*+++++++++++++++++++++++++++++++++++
g_yield <-
  ggplot() +
  geom_line(data = curv_data, aes(y = yield, x = N, linetype = type)) +
  geom_point(
    data = true_yield_data,
    aes(y = yield, x = N, color = type, shape = type)
  ) +
  geom_point(
    data = point_data_gwr,
    aes(y = yield, x = N, color = type, shape = type)
  ) +
  ylab("Yield (ton/ha)") +
  xlab("Nitrogen Rate (kg/ha)") +
  scale_color_discrete(name = "EONR") +
  scale_shape_discrete(name = "EONR") +
  scale_linetype_discrete(name = "Yield Response Fnctions") +
  ggtitle("(a) Estimated and True Yields") +
  theme_fig

g_profit <-
  ggplot() +
  geom_line(data = curv_data, aes(y = profit / 1000, x = N, linetype = type)) +
  geom_point(
    data = true_yield_data,
    aes(y = profit / 1000, x = N, color = type, shape = type)
  ) +
  geom_point(
    data = point_data_gwr,
    aes(y = profit / 1000, x = N, color = type, shape = type)
  ) +
  ylab("Partial Profit ($1000/ha)") +
  xlab("Nitrogen Rate (kg/ha)") +
  scale_color_discrete(name = "EONR") +
  scale_shape_discrete(name = "EONR") +
  scale_linetype_discrete(name = "Profit Response Fnctions") +
  ggtitle("(b) Estimated and True Profits") +
  theme_fig

g_why_bias_single <- g_yield / g_profit

ggsave(
  "GitControlled/Writing/Figures/g_why_bias_single.png",
  g_why_bias_single,
  width = 6.5,
  dpi = 600
)
```

### 2023-07-27 Writing/manuscript_gwr.rmd
finalized revision

@@
   fig.align = "center",
-  fig.retina = 5,
-  warning = F,
-  message = F,
-  cache = F,
-  echo = F,
+  fig.retina = 6,
+  warning = FALSE,
+  message = FALSE,
+  cache = FALSE,
+  echo = FALSE,
   fig.cap = TRUE
@@
 #* source all the functions in the Functions folder
-fs::dir_ls(here("GitControlled", "Codes", "Functions"), full.names = TRUE) %>%
+fs::dir_ls(here("GitControlled/Codes/Functions"), full.names = TRUE) %>%
   lapply(., function(x) source(x))
@@
 
-#* create figures
+mean_data_value <-
+  results %>%
+  .[, .(pi_diff = median(pi_diff)),
+    by = c("field_col", "pLabel", "type")
+  ]
+```
+
+```{r, include = FALSE}
+knitr::purl(here("GitControlled/Codes/3_make_figures_publication.rmd"), here("GitControlled/Codes/3_make_figures_publication.R"))
 source(here("GitControlled/Codes/3_make_figures_publication.R"))
+
 ```
@@
 But applications of GWR in this context have assumed a quadratic yield response function, despite a scientific consensus that the yield-input relationships modeled are better represented by the quadratic-plateau functional form.
-The quadratic assumption has been made because no readily available statistical packages exist for GWR estimation with non-linear functional forms.
+The quadratic assumption has been made because no readily available statistical packages exist for GWR estimation with nonlinear functional forms.
 The key objective of this paper is to investigate whether, when the true functional form of yield response is quadratic-plateau, assuming a quadratic form introduces bias into the GWR estimation of the economic value of site-specific recommendation maps.
@@
 
-**Acknowledgements**: This research was supported by a USDA-NIFA-AFRI Food Security Program Coordinated Agricultural Project, titled “Using Precision Technology in On-farm Field Trials to Enable Data-Intensive Fertilizer Management,” (Accession Number 2016-68004-24769), and also by the a USDA-NRCS Conservation Innovation Grant from the On-farm Trials Program, titled “Improving the Economic and Ecological Sustainability of US Crop Production through On-Farm Precision Experimentation” (Award Number NR213A7500013G021), and by USDA NIFA's Hatch Project 470-362.
+**Acknowledgements**: This research was supported by a USDA-NIFA-AFRI Food Security Program Coordinated Agricultural Project, titled "Using Precision Technology in On-farm Field Trials to Enable Data-Intensive Fertilizer Management," (Accession Number 2016-68004-24769), and also by the a USDA-NRCS Conservation Innovation Grant from the On-farm Trials Program, titled "Improving the Economic and Ecological Sustainability of US Crop Production through On-Farm Precision Experimentation" (Award Number NR213A7500013G021), and by USDA NIFA's Hatch Project 470-362.
 
@@
 
-Precision agriculture is a management strategy that adjusts farm management decisions according to the spatial and temporal variability of soil and crop conditions within a field.
-Over the past few decades, numerous technological innovations have been made in collecting detailed field information (e.g., yield mapping, soil sampling, remote sensing, etc.) and developing site-specific management recommendations based on the information.
-However, the long-standing question of whether the economic benefit of precision agriculture can offset the technology and information costs [@lowenberg1996revolution; @weiss1996precision] remains difficult to answer, particularly in the context of large-scale production systems [@mcfadden2022information].
+Precision agriculture technology allows input management strategies to adapt to the spatial and temporal variability of soil and crop conditions within a field.
+Over the past few decades, numerous technological innovations have been made for collecting detailed field information (e.g., yield mapping, soil sampling, remote sensing, etc.) and in developing site-specific management recommendations based on the information.
+But the long-standing question of whether the economic benefit of precision agriculture can offset the technology and information costs [@lowenberg1996revolution; @weiss1996precision] remains difficult to answer, particularly in the context of large-scale production systems [@mcfadden2022information].
 
-In recent years, on-farm precision experimentation (OFPE) has gained traction with both researchers and practitioners as a means of generating high-resolution spatial data to inform site-specific crop input management decisions [@bullock2019data; @lacoste2021farm].
-Accompanying interest is surging among researchers in identifying efficient statistical methods to estimate site-specific yield response functions, which have examined various methods, ranging from Geographically Weighted Regression (GWR) [@rakshit2020; @evans2020assessment; @trevisan2021spatial] to machine learning methods, including the random forest [@krause2020random, @de2023predicting], convolutional neural network [@barbosa2020modeling], and causal forest [@kakimoto2022causal] approaches.
-Among these methods applied to OFPE data, GWR is distinct in that it does not require potentially costly collection of site-specific field and soil information in estimating site-specific yield response functions.
+In recent years, on-farm precision experimentation (OFPE) has gained traction with agricultural researchers and practitioners as a means of generating high-resolution spatial data to inform site-specific crop input management [@bullock2019data; @lacoste2021farm].
+Accompanying interest is surging among researchers in identifying efficient statistical methods to estimate site-specific yield response functions with OFPE data.
+Researchers recently have examined various methods, ranging from Geographically Weighted Regression (GWR) [@rakshit2020; @evans2020assessment; @trevisan2021spatial] to machine learning techniques, including random forest [@krause2020random, @de2023predicting], convolutional neural network [@barbosa2020modeling], and causal forest [@kakimoto2022causal] approaches.
+Among these, reported research on the GWR approach have generated special interest because GWR can be used to estimate site-specific yield-to-input relationships without costly spatial field and soil data.
 
-On any given field, it is typical for U.S.
-Midwestern row crop farmers to pay for 1-ha grid soil sampling and chemical analysis every three or four years [@morris2018strengths].
-The data are often used to derive fertilizer application recommendations, for example by applying comparatively simple formulas provided by university extension services [e.g., @culman2020tri].
-But the expense of soil sampling and analysis is driving development of sensor technologies that gather data on site-specific field and crop characteristics or proxies of those characteristics, and the conversion of those data into recommended nitrogen fertilizer (N) application rate maps (usually called "prescriptions" or $R_x$s).^[For example, Trimble Agriculture's GreenSeeker and AgLeader's OptRx® systems use optical sensors mounted on fertilizer application booms to digitally record vegetative index imagery as farm machinery is driven through fields during early crop growth stages.
+@trevisan2021spatial demonstrated a method of providing site-specific management recommendations without such data.
+They estimated site-specific yield response functions by applying GWR techniques on OFPE data, and reported dramatic results, estimating an average potential gain of \$65 ha$^{-1}$ from applying seed and nitrogen (N) at optimal uniform rates instead of at the rates the farmers would have chosen if not participating in the research, and an additional potential gain of \$58 ha$^{-1}$ when changing from the optimal uniform application rate to optimal site-specific application rates.
+This might be seen as surprising given the often-reported poor statistical accuracy of GWR estimates [@griffith2008spatial; @harris2019simulation; @paez2011simulation; @da2016multiple] and also the much lower value of variable rate application (VRA)  management over uniform rate application (URA) management reported in previous studies [@bullock1998does; @koch2004economic; @thrikawala1999economic].
+
+We suspect that the value of GWR reported by @trevisan2021spatial is a result of over-estimation bias.
+There are two key sources of bias in their approach.
+First, they assumed a quadratic functional form of yield response, even though a consensus has evolved in the academic literature that the quadratic-plateau functional form better represents the yield-nitrogen relationship.
+It seems likely that they made this assumption primarily because no statistical software is readily usable to estimate GWR with nonlinear functional form.
+Second, as will be discussed in detail in the following section, their approach suffers from bias that is endemic to any study that tries to estimate the value of a statistical method in the OFPE context, which is that it is necessary because the true yield response function is unknowable and can only be estimated.
+
+The primary objective of this study is to examine the degree and direction of bias in the estimation of the economic value of GWR-based site-specific nitrogen rate recommendations (i.e., variable rate applications of nitrogen) when the yield response function assumed in the GWR model is specified as quadratic but is actually of quadratic-plateau functional form.
+We will do so using Monte Carlo simulations, which , since we define and know the true yield response function in the data generating process, allow us to measure the degree of bias.
+Unlike in @griffith2008spatial, @harris2019simulation, @paez2011simulation, and @da2016multiple, our objective is not to measure the bias in the coefficient estimation by GWR, but rather to measure economic effects of the statistical inaccuracy in estimating the coefficients of the model.
+We show that the misspecification tends to significantly over-estimate GWR's true value.
+
+# Background: Estimation of Yield-to-input Response Relationships Using OFPE Data
+
+## Conceptual Framework
+On-farm precision experimentation (OFPE) can provide detailed as-applied input and yield data at dense resolutions over entire fields, which if well analyzed may provide valuable information that can improve site-specific input application recommendations [@bullock2019data; @lacoste2021farm].
+Consider a yield response function $y = f(x, c)$, where following @bullock2000agronomic, $x$ is a vector of input management variables and $c$ is a vector of spatial variables describing field and soil characteristics^[For simplicity, we suppress discussion of the need to bring variance in weather data into yield response estimation.
+Obviously, generation and use of weather data is necessary to provide meaningful probabilistic analysis and input management advice.].
+Letting a field site $i$ be defined as a contiguous area characterized uniformly by a value $c_i$ of the vector of field and soil characteristics, its site-specific yield response function is the reduced form of the field's yield response function created when the value of the vector of characteristics variables is set at the site's value, $c_i$:  $f_i(x) \equiv f(x, c_i)$.
+This conceptualization suggests two methods of estimating a field's site-specific yield responses.
+The first is to estimate a "map" of the field characteristics, for example thought of as a set of the field's $n \geq 1$ sites' values of the characteristics vector: $\{c_1,\dots, c_n\}$.
+With that map, regressing yield on x and c generates an estimated "field-specific" yield response function $\hat{f}_(x,c)$.
+Estimates of site-specific yield response functions can then be obtained by inserting the value of the site's characteristic variables into the estimate of the field-specific response function: $\hat{f}_i(x) \equiv \hat{f}(x,c_i)$.
+Alternatively, a site-specific yield response function might be estimated simply by taking (input rate, yield) data from points around a site of interest, and regressing yield on input application rates to attain the estimate $\tilde{f}_i (x)$.
+Stated roughly, using GWR takes the latter approach, which has the advantage of not needing a costly map of field characteristics values.
+
+## Costs of Field Characteristics Data and The Appeal of GWR
+
+On any given field, it is typical for many row crop farmers to pay for 1-ha (2.5-ac) grid soil sampling and chemical analysis every three or four years [@morris2018strengths].
+The data are often used to derive fertilizer application recommendations, for example by applying comparatively simple formulas provided by university extension services (e.g., @culman2020tri).
+But the expense of soil sampling and analysis is driving development of sensor technologies that gather data on site-specific field and crop characteristics or proxies of those characteristics, and the conversion of those data into recommended input application rate maps (usually called "prescriptions" or "$R_x$s").
+For example, Trimble Agriculture's GreenSeeker and AgLeader's OptRx systems use optical sensors mounted on fertilizer application booms to digitally record vegetative index imagery as farm machinery is driven through fields during early crop growth stages.
 GreenSeeker then uses Oklahoma State University's Sensor-based N Rate Calculator to convert those data into recommended nitrogen fertilizer (N) $R_x$s.
@@
 The "decision tool" software FieldRevealTM allows users to upload EC data, elevation data, and vegetative index data, which FieldRevealTM's professional agronomists analyze to provide $R_x$s to farmers.
-FieldApex creates N $R_x$s using foliar vegetative index data from satellite imagery, and SlantRange uses drone imagery for similar purposes.]
+FieldApex creates N $R_x$s using foliar vegetative index data from satellite imagery, and SlantRange uses drone imagery for similar purposes.
+But deploying sophisticated sensors to gather field characteristics data is also costly, and the effects of their generation and use on farming profitability remains in question [@gardner2021economic].
 
-However, deploying sophisticated sensors to gather field characteristics data is also costly, and the effects of their generation and use on farming profitability remains in question [@gardner2021economic].
-Recognizing the significant costs of obtaining useful, high-resolution soil and field properties data, @trevisan2021spatial demonstrated a method of providing site-specific management recommendations without such data.
-They estimated site-specific yield response functions by applying GWR techniques on data from OFPEs [@bullock2019data], and reported dramatic results, estimating an average potential gain of \$65 ha$^{-1}$ from applying seed and N at optimal uniform rates (instead of at the rates the farmers would have chosen if not participating in the research), and an additional potential gain of \$58 ha$^{-1}$ when changing from optimal uniform application rates to optimal site-specific application rates.
-This is rather surprising given the often-reported poor statistical accuracy of GWR estimates [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation] and also much lower value of variable rate application (VRA) over uniform rate application (URA) reported in previous studies [@bullock1998does; @thrikawala1999economic; @koch2004economic].
-@rakshit2020 also applied GWR to on-farm experiment data.
-However, while they did estimate site-specific yield response functions, they did not derive site-specific economically optimal nitrogen rates based on them, and thus did not conduct economic analysis, unlike @trevisan2021spatial.
-@evans2020assessment explored using GWR with a linear model specification to detect low- and high-response areas, but like @rakshit2020, they also did not estimate site-specific economically optimal nitrogen rates.
+The appeal of GWR lies in its ability to estimate localized site-specific yield response functions without measuring these characteristics.
+It runs regressions locally at many points of the field to estimate yield response functions, where the locality is controlled by the bandwidth of the kernel function chosen by the researcher.
+Using OFPE data, @trevisan2021spatial assumed a quadratic yield response function, and reported large economic benefits associated with using GWR to generate site-specific seed and nitrogen rates recommendations.
+@rakshit2020 also estimated site-specific yield response functions by applying GWR to on-farm experiment data assuming a quadratic functional form of yield response.
+But they did not calculate site-specific economically optimal nitrogen rates, and so unlike @trevisan2021spatial did not conduct economic analysis.
+@evans2020assessment explored using GWR with a linear model specification to detect low- and high-response areas, but like @rakshit2020, did not estimate site-specific economically optimal nitrogen rates.
 
-While the results reported by @trevisan2021spatial look rosy and GWR looks like a promising method, there are two potentially dangerous factors that may have caused them to significantly over-estimate the value of GWR as a tool to estimate site-specific EONR.
-First, they used quadratic functional form in their GWR estimation even though it is widely accepted by scientific community that corn yield response to nitrogen is better approximated by quadratic-plateau functional form.
-It is likely that their choice of quadratic functional form is merely a compromise because there did (does) not exist any statistical software of package that implements GWR with quadratic-plateau functional form.
-The second source of over-estimation bias is endemic to any study that evaluates the value of variable rate application, not just @trevisan2021spatial.
-In general, researchers take the following steps to estimate the value of VRA using OFPE data [e.g., @anselin2004spatial; @swinton1998evaluating; @bullock2002adding; @liu2006site]: (1) estimate site-specific yield response functions based on a method chosen by the researcher; (2) use the estimated yield response functions to estimate the economically optimal site-specific input rates (EOIRs) and economically optimal uniform input rates; (3) plug the estimated site-specific EOIRs and uniform EOIR into the estimated yield response functions to calculate estimated profits under both strategies; and (4) find the difference in the two strategies' estimated profits.
+## Sources of Bias in Estimating the Value of VRA with Mis-specified Yield Response
+
+There are two potentially dangerous factors that may have caused significant over-estimation of the value of GWR as a tool to estimate site-specific economically optimal nitrogen application rates (EONRs) in @trevisan2021spatial.
+First, @trevisan2021spatial assumed a quadratic functional form in their GWR estimation even though there is a wide consensus among the scientific community that corn yield response to nitrogen is better represented by the quadratic-plateau functional form.
+It is likely that their choice of quadratic functional form was merely a compromise because no statistical software package implements GWR with a quadratic-plateau functional form.
+The second source of over-estimation bias is endemic to any study that evaluates the value of variable rate application.
+In general, researchers take the following steps to estimate the value of VRA using OFPE data [@anselin2004spatial, @bullock2002adding, @liu2006site, @swinton1998evaluating]: (1) estimate site-specific yield response functions based on a method chosen by the researcher; (2) use the estimated yield response functions to estimate the economically optimal site-specific input rates (EOIRs) and economically optimal uniform input rates; (3) plug the estimated site-specific EOIRs and uniform EOIR into the estimated yield response functions to calculate estimated profits under both strategies; and (4) find the difference in the two strategies' estimated profits.
 However, this approach can result in significant bias in the estimation of the value of VRA because of the step 3's assumption that the estimated yield response functions are the true yield response functions.
@@
 This assumption is generally unavoidable for researchers since they cannot observe any real field's true site-specific yield response functions.
-But, inaccurate estimation of yield response function in this methodology can result in significant bias in the estimation of the value of VRA.
-This bias problem can be particularly severe when the method used tends to exaggerate the true heterogeneity in yield response functions, such as GWR [@czarnota2015evaluating].
-
-The primary objective of this study is examine the degree and direction of bias in the estimation of the economic value of GWR-based site-specific nitrogen rate recommendations (i.e., variable rate application of nitrogen) when GWR model is specified as quadratic when the true yield response function follows the quadratic-plateau functional form.
-We evaluate two sets of GWR quadratic specifications used in @rakshit2020 and @trevisan2021spatial.
-Both of them assumed a quadratic response of yield to nitrogen rate ($N$).
-However, while @trevisan2021spatial estimated the coefficient on $N^2$ as a global parameter, @rakshit2020 estimated it locally for each point.
-At first, it appears that the specification used by @rakshit2020 is superior since it is more flexible than the specification used by @trevisan2021spatial.
-However, the flexibility can be a disadvantage rather than an advantage because the estimation of economically optimal nitrogen rate (EONR) can be highly sensitive to the coefficient estimates on $N^2$, and GWR often provides inaccurate local estimation of that coefficient.
-It is critical to keep in mind that it is not our objective to measure the bias in the coefficient estimation by GWR, unlike [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation].
-Rather, we are interested in the economic implications of the statistical inaccuracy in estimating the coefficients of the model in this study.
-As part of identifying bias in the estimation of the economic value of VRA based on the GWR approaches, we evaluate their actual values.
-Finally, we also evaluate their relative performances compared to uniform rate application (URA) based on shape-constrained additive model approach.
-It should be noted that the economical optimization in this study only involves farmers' private profit, while the environmental externalities (such as fertilizer runoff and leaching) are not considered.
-
-We pursue the objective by conducting Monte Carlo simulations of 1000 rounds in which we first generate and then analyze stylized OFPE data.
-We cannot test which model specification results in more profitable site-specific nitrogen rate recommendations using real data because it is impossible to observe the true yield response functions using real-world data.
-For the same reason, we cannot test whether @trevisan2021spatial over-estimates the actual value of VRA, either.
-But in the Monte Carlo simulations we specify yield response functions and generate stylized data from those functions, which enables us to quantify in the context of the simulations the value of GWR and the bias in GWR-based estimation of the value of VRA.
-Monte Carlo simulations are commonly used in this way to gain insights into the statistical and economic properties of trial designs and estimations methods [@mckinion2001analysis; @gebbers2010application; @bullock2020value; @alesso2021design].
-
-We found that the benefit of VRA over URA is rather small irrespective of the specification used, averaging only about \$5 ha$^{-1}$.
-More important, both specifications by trevisan2021spatial and rakshit2020 tend to significantly over-estimate the economic value of VRA based on GWR.
-Their assumption of quadratic functional form is one of the main culprits.
-When quadratic functional form is assumed, over-application of nitrogen is modeled to result in large economic loss due to yield loss when in reality over-application of nitrogen is not associated with any yield loss when the true yield-response function is quadratic-plateau.
-Our results suggest that the prospects of using GWR to generate site-specific input recommendations are bleaker than stated in @trevisan2021spatial.
-It is important to develop GWR with more flexible functional forms than currently possible if precision agriculture practitioner is interested in using GWR as one of the tools to estimate site-specific input use recommendation.
-
-# Background:  Estimation of Yield-to-input Response Relationships Using OFPE Data
+But inaccurate estimation of yield response function in this methodology can result in significant bias in the estimation of the value of VRA.
+This bias problem can be particularly severe when the method used tends to exaggerate the true heterogeneity in yield response functions.
+We suspect that the high value of VRA estimated by @trevisan2021spatial displays this bias., such as GWR [@czarnota2015evaluating].
 
@@
 
-We conduct 1000 rounds of Monte Carlo simulation to answer our research questions. The process/components of the simulation analysis is detailed below.
+We evaluated two sets of GWR quadratic specifications used in @rakshit2020 and @trevisan2021spatial, both of which assumed a quadratic response of yield to nitrogen rate ($N$).
+However, while @trevisan2021spatial estimated the coefficient on $N^2$ as a global parameter, @rakshit2020 estimated it locally for each point.
+We cannot use real data to test which model specification results in more profitable site-specific nitrogen rate recommendations because it is impossible to observe the true yield response functions using real-world data.
+For the same reason, neither can we test whether @trevisan2021spatial over-estimate the actual value of VRA.
+But in the Monte Carlo simulations we specified yield response functions and generated stylized data from those functions, which enabled us to quantify in the context of the simulations the value of GWR and the bias in GWR-based estimation of the value of VRA.
+Monte Carlo simulations are commonly used in this way to gain insights into the statistical and economic properties of trial designs and estimations methods [@alesso2021design; @bullock2020value; @gebbers2010application; @mckinion2001analysis].
+We conducted one thousand rounds of Monte Carlo simulation to answer our research questions.
+The process and components of the simulation analysis are detailed below.
 
@@
 
-Figure \@ref(fig:field-layout) shows the simulated field's layout and defines the spatial units of the simulated on-farm precision experiments in this study.
+Figure \@ref(fig:field-layout) shows a simulated field's layout and defines the spatial units of the simulated OFPEs.
 The basic spatial unit of the field is a 6m $\times$ 6m "cell", which is the resolution at which the field characteristics data (i.e., parameters of the "true" yield response function) were allowed to vary.
@@
 The field was 432m (72 cells) wide and 864m (144 cells) long, making its area 37.3 ha.
-Data from the 6-m-long headlands, side-lands (there are no transition zones on the north and south ends of the field), and 12-m-wide "transition zones" were not included in the data analyzed.
-In total there were 1440 subplots available for experimental data analysis.
+Data from the 6m-long headlands, side-lands (there are no transition zones on the north and south ends of the field), and 12m-wide "transition zones" were not included the analysis.
+In total, data from 1440 subplots available for experimental data analysis.
 The index $j \in {1, 2, \dots, 1440}$ identifies the field's subplots, and the index $i \in {1, \dots , 6}$ identifies the cells within a subplot.
@@
 An extensive literature examines the choice of functional form in yield response estimation [@cerrato1990comparison, @frank1990comparison, @bullock1994quadratic, @tembo2008crop].
-Our simulation assumes that each cell $(j, i)$'s "true" yield response function is assumed to follow the commonly-used quadratic-plateau functional form:
+Our simulation assumes that each cell $(j, i)$'s "true" yield response function  follows the commonly-used quadratic-plateau functional form:
 
@@
 
-The spatial distributions of cell-level parameters $\alpha_{j, i}$, $\beta_{j, i}$, $\gamma_{j,i}$, $\tau_{j, i}$, and the error term $\varepsilon_{j, i}$ were simulated by generating spatially correlated random fields using unconditional Gaussian geostatistical simulation based on the specified variograms [@dietrich1996fast, @wood1994simulation], and the simulation processes were conducted using the R package gstat [@graler16].
+The spatial distributions of cell-level parameters $\alpha_{j, i}$, $\beta_{j, i}$, $\gamma_{j,i}$, $\tau_{j, i}$, and the error term $\varepsilon_{j, i}$ were simulated by generating spatially correlated random fields using unconditional Gaussian geostatistical simulation based on the specified variograms [@dietrich1996fast, @wood1994simulation].
+The simulation processes were conducted using the R package gstat [@graler16].
 Specifically, the model is spherical, the nugget variance is zero, and the range is 600 meters.
@@
 The range of 600m means that observations separated by more than 600m are spatially uncorrelated.
-A higher range value indicates increased spatial dependence, meaning less abrupt differences are observed between the production function parameters of neighboring cells.
-The mean and sill variance of each parameter were specified to result in a realistic mean yield of $11,416$ kg ha$^{-1}$, and such that the cells' true economically optimal N rate ranged from $113$ kg ha$^{-1}$ to $273$ kg ha$^{-1}$ among all the simulations, a range into which most real-world N rate recommendations fall [e.g., @sawyer2018].
+A higher range value indicates increased spatial dependence, meaning that less abrupt differences tend to be observed between the production function parameters of neighboring cells.
+The mean and sill variance of each parameter were specified to result in a realistic mean yield of $11,416$ kg ha$^{-1}$, and such that the cells' true economically optimal N rates ranged from $113$ kg ha$^{-1}$ to $273$ kg ha$^{-1}$ across all the simulations, a range into which most real-world N rate recommendations fall [e.g., @sawyer2018].
 Note that the range of the optimal N rates of individual rounds of simulations are narrower.
@@
 To maintain consistency with real-world OFPEs, it was assumed that harvesting equipment could only record yields accurately at an 18m $\times$ 12m (subplot) resolution.
-Since every cell in a plot received the same N application rate, then so did every cell within a subplot, so $N_{j,1} = N_{j,2}= \dots = N_{j,6} = N_j$ for each subplot $j$.
+Since every cell in a plot received the same N application rate, then so did every cell within a subplot, and therefore $N_{j,1} = N_{j,2}= \dots = N_{j,6} = N_j$ for each subplot $j$.
 Letting $\mu_j$ denote the mean of the yields of the cells in subplot $j$, the analysis of each round's data was based on 1440 $(\mu_j,N_j )$ observations.
 
-## Estimation of Yield Response Function and EONR
+## Estimation of Yield Response Functions and EONRs
 
-Three approaches to estimate yield response functions and their associated EONRs were used.
-The first approach used the shape-constrained additive model (SCAM) to estimate a single yield response function for the entire field, and to estimate an economically optimal uniform nitrogen application rate for the field.
+Three approaches to estimating yield response functions and their associated EONRs were taken.
+The first approach used the shape-constrained additive model (SCAM) to estimate a single yield response function for the entire field, and with it estimate an economically optimal uniform nitrogen application rate for the field.
 The other two approaches both used GWR, but assumed different specifications in modeling the impact of nitrogen on yield.
@@
 
-In the lower benchmark situation, a researcher was assumed to run OFPEs to gather data and then to estimate a "full-field" uniform yield response function using the SCAM non-parametric regression framework [@pya2015shape].
-SCAM is a type of generalized additive model (GAM) [@hastie1986gam] which allows for more flexible and non-linear  relationships between the response variable and the predictors through a combination of smooth functions (also known as "splines").
-In comparison with the conventional GAM technique, SCAM allows for the imposing of shape constraints on the estimated relationship, which is particularly useful when prior knowledge or theoretical considerations suggest certain shape restrictions of the relationship.
-In the SCAM of this study, the yield response function was restricted to be monotonically increasing and concave with respect to the N application rate, which are traits well substantiated by agronomic research [@cerrato1990comparison; @bullock1994quadratic].
+In the lower benchmark situation, a researcher was assumed to work with farmers to run OFPEs, gather data, and then to estimate a "full-field" uniform yield response function using the SCAM non-parametric regression framework [@pya2015shape].
+SCAM is a type of generalized additive model (GAM) [@hastie1986gam] which allows for more flexible and nonlinear  relationships between the response variable and the predictors through a combination of smooth functions (also known as "splines").
+In comparison to the conventional GAM technique, SCAM allows for the imposition of shape constraints on the estimated relationship, which is particularly useful when prior knowledge or theoretical considerations call for such shape restrictions of the relationship.
+In using SCAM in this study, the yield response function was restricted to be monotonically increasing and concave with respect to the N application rate, which are traits well substantiated by agronomic research [@cerrato1990comparison; @bullock1994quadratic].
 When the chosen shape constraints are correct, SCAM is more statistically efficient than a fully non-parametric regression [@pya2015shape].
@@
 where $g_k(\cdot)$ is the $k$th spline basis and $\beta_k$ is its coefficient to be estimated.
-The $\beta_k$s were constrained such that the resulting relationship between $y_j$ and $N_j$ is such that $y_j$ monotonically increases as $N_j$ increases, but at a diminishing rate.
+The $\beta_k$s were constrained such that the resulting relationship between $y_j$ and $N_j$ is such that $y_j$ monotonically increases with $N_j$, but at a diminishing rate.
 
@@
 
-The coefficients $\alpha_j$, $\beta_j$, and $\eta_j$ were continuous functions of subplot $j$’s coordinates ($lon_j$, $lat_j$).
+The coefficients $\alpha_j$, $\beta_j$, and $\eta_j$ were continuous functions of subplot $j$'s coordinates ($lon_j$, $lat_j$).
 The GWRR estimation produced subplot-specific estimates of coefficients $\hat{\alpha}_j$, $\hat{\beta}_j$, and $\hat{\eta}_j$, and so of the yield response function $\hat{f}^{GWRR}_j(N)$ for $j = 1, 2, \dots, 1440$.
@@
 
-The GWRT model is also called as “mixed” GWR in the literature [@brunsdon1999some], where some parameters are fixed globally while others vary geographically.
-In our model, the coefficient on $N^2$ was estimated as a global parameter while the coefficient on $N$ was estimated subplot-specifically.
+The GWRT model is also called as "mixed" GWR in the literature [@brunsdon1999some], where some parameters are fixed globally while others vary geographically.
+We estimate the coefficient on $N^2$ as a global parameter and the coefficient on $N$ subplot-specifically.
 For each subplot $j \in {1, 2, \dots, 1440}$, the assumed yield response was,
@@
 
-The Gaussian kernel function was used when estimating both GWR models (other kernel functions were also tried and the final conclusions are quantitatively similar; see appendix).
-For the optimal kernel bandwidth selection, while there are several frequently used approaches in the literature such as cross-validation [@cleveland1979robust; @bowman1984alternative] and Akaike Information Criterion (AIC) [@akaike1973], this study used the corrected version of the AIC approach following the most recent GWR literature [@fotheringham2003geographically; @fotheringham2017multiscale; @lu2017geographically], which is also the same approach used by @rakshit2020 and @trevisan2021spatial.
-The optimal bandwidth differed slightly across each simulated experiment, and the average bandwidth was around 18 meters.
+The Gaussian kernel function was used when estimating both GWR models (Other kernel functions were also tried and the final conclusions were quantitatively similar; see the supplemenraty appendix.).
+There are several frequently used approaches in the literature to calculate the optimal kernal bandwidth, such as cross-validation [@cleveland1979robust; @bowman1984alternative] and the Akaike Information Criterion (AIC) [@akaike1973].
+Like @rakshit2020 and @trevisan2021spatial, we follow the most recent GWR literature by using the corrected version of the AIC approach [@fotheringham2003geographically; @fotheringham2017multiscale; @lu2017geographically].
+The optimal bandwidth differed slightly across each simulated experiment, and the average bandwidth was approximately 18 meters.
 
@@
 
-$$\Pi^{*SCAM} = 1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 \big[pf_{j, i} (\hat{N}^{*SCAM})-w\hat{N}^{*SCAM}\big]$$
+$$\Pi^{*SCAM} = \frac{1}{8640} \sum_{j=1}^{1440} \sum_{k=1}^6 \big[pf_{j, i} (\hat{N}^{*SCAM})-w\hat{N}^{*SCAM}\big]$$
 
@@
 
-$$\Pi^{GWR}=1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 [pf_{j, i} (\hat{N}^{*GWR}_j)-w\hat{N}^{*GWR}_j]$$
+$$\Pi^{GWR}=\frac{1}{8640} \sum_{j=1}^{1440} \sum_{k=1}^6 [pf_{j, i} (\hat{N}^{*GWR}_j)-w\hat{N}^{*GWR}_j]$$
 
@@
 
-The true value of the GWR-based VRA compared to the SCAM-based URA is defined by the difference of their partial profits:
+The true value of the GWR-based VRA compared to the SCAM-based URA is defined by the difference in their profits:
 
@@
 To find the bias in estimating the value of VRA, the profits of the SCAM-based URA and GWR-based VRA were calculated by substituting the estimated optimal nitrogen rates into the cell-specific yield response functions estimated by GWR.
-Estimated per-ha net revenues for SCAM-based URA and GWR-based VRA are found as follows:
+Estimated per-ha net revenues for SCAM-based URA and GWR-based VRA are calcualted as follows:
 
-$$\hat{\Pi}^{*SCAM} = 1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 \big[p\hat{f}^{GWR}_{j, i} (\hat{N}^{*SCAM} )-w\hat{N}^{*SCAM}\big]$$
+$$\hat{\Pi}^{*SCAM} = \frac{1}{8640} \sum_{j=1}^{1440} \sum_{k=1}^6 \big[p\hat{f}^{GWR}_{j, i} (\hat{N}^{*SCAM} )-w\hat{N}^{*SCAM}\big]$$
 
-$$\hat{\Pi}^{*GWR}=1/8640 \sum_{j=1}^{1440} \sum_{k=1}^6 [p\hat{f}^{GWR}_{j, i} (\hat{N}^{*GWR}_{j} )-w\hat{N}^{*GWR}_{j}]$$
+$$\hat{\Pi}^{*GWR}=\frac{1}{8640} \sum_{j=1}^{1440} \sum_{k=1}^6 [p\hat{f}^{GWR}_{j, i} (\hat{N}^{*GWR}_{j} )-w\hat{N}^{*GWR}_{j}]$$
 
@@
 
-Finally, the bias in the estimation of the value of GWR-based VRA was calculated as follows:
+The bias in the estimation of the value of GWR-based VRA was calculated as follows:
 
@@
 Historical corn ($p$) and nitrogen fertilizer ($w$) prices from 2002 to 2022 were obtained from the USDA National Agricultural Statistics Service (NASS, 2022) and DTN Retail Fertilizer Trends (DTN, 2022), and were transformed into monthly data.
-The nitrogen-corn price ratios were calculated as the nitrogen fertilizer price ($w$) divided by corn price ($p$).
-Further information regarding the collection, calculation, and summary statistics of the price data can be found in Appendix I: Historical Corn and Nitrogen Prices in the supplementary material.
+The nitrogen-corn price ratios were calculated as $w/p$.
+Further information regarding the collection, calculation, and summary statistics of the price data can be found in the supplementary appendix (Appendix 1: Historical Corn and Nitrogen Prices).
 
-The comparative advantage of GWRR and GWRT varies significantly depending on nitrogen-corn price ratio.
-Specifically, GWRR performs better as the price ratio increases (that is, as nitrogen becomes more expensive relative to corn), while the opposite is the case for GWRT.
+The comparative advantage of GWRR and GWRT varies significantly depending on the nitrogen-corn price ratio.
+Specifically, GWRR performs better as nitrogen becomes more expensive relative to corn, while the opposite is the case for GWRT.
 At the low price ratio of 5.44, VRA based on GWRR is no better than SCAM-based URA.
-However, when the price ratio increases to $6.56$, the median benefit of GWRR is `r round(mean_data_value[type == "GWRR" & pLabel == "6.56", pi_diff], digits = 2)`.
-At high price ratio of 7.67, the median benefit increases to `r round(mean_data_value[type == "GWRR" & pLabel == "7.67", pi_diff], digits = 2)`.
-On the other hand, the median benefit of VRA based on GWRT when the price ratio is low of 5.44 is `r round(mean_data_value[type == "GWRT" & pLabel == "5.44", pi_diff], digits = 2)`, but the benefit reduces to `r round(mean_data_value[type == "GWRT" & pLabel == "6.56", pi_diff], digits = 2)` when the price ratio is 6.56, and `r round(mean_data_value[type == "GWRT" & pLabel == "7.67", pi_diff], digits = 2)` when 7.67.
+But, when the price ratio increases to $6.56$, the median benefit of GWRR is $`r round(mean_data_value[type == "GWRR" & pLabel == "Middle", pi_diff], digits = 2)` per hectare.
+At the high price ratio of 7.67, the median benefit is $`r round(mean_data_value[type == "GWRR" & pLabel == "High", pi_diff], digits = 2)` per hectare.
+On the other hand, the median benefit of VRA based on GWRT at the low price ratio of 5.44 is $`r round(mean_data_value[type == "GWRT" & pLabel == "Low", pi_diff], digits = 2)` per hectare, but the benefit is reduced to $`r round(mean_data_value[type == "GWRT" & pLabel == "Middle", pi_diff], digits = 2)` per hectare when the price ratio is 6.56, and $`r round(mean_data_value[type == "GWRT" & pLabel == "High", pi_diff], digits = 2)` per hectare when 7.67.
 
 Figure \@ref(fig:bias-est-eonr) provides insights into this phenomenon, showing the distribution of the average ratio of estimated EONR to true EONR.
-A value lower than 1 means EONR is underestimated on average.
-GWRR tends to over-estimate EONR at lower price ratios, but the magnitude of over-estimation goes down as the price ratio goes up.
+A value lower than 1 means that EONR is underestimated on average.
+GWRR tends to over-estimate EONR at lower price ratios, but the magnitude of over-estimation falls as the price ratio rises.
 The opposite trend is true for GWRT.
@@
 The range of EONR estimates by GWRR is very wide because the coefficient on $N^2$ is allowed to vary site specifically in GWRR.
-Since the estimation of the coefficient on $N^2$ is highly inaccurate, the range of estimated EONRs is much wider than the range of true site-specific EONR.
-But, GWRT's range of EONR estimates is very narrow because the coefficient on $N^2$ is constrained to be equal across sites, making GWRT fail to capture the EONR's true heterogeneity.
+Since the estimation of the coefficient on $N^2$ is highly inaccurate, the range of estimated EONRs is much wider than the range of true site-specific EONRs.
+But, GWRT's range of EONR estimates is very narrow because the coefficient on $N^2$ is constrained to be equal across sites, making GWRT fail to capture the EONR's truea spatial heterogeneity.
 
@@
 For example, the value of 10 would mean that the estimated value of GWR-based VRA over-estimates its true value by $10 per ha.
-As the figure suggests, VRA based on GWRR appears to perform overwhelmingly better than it truly is, presenting significant positive bias across the price range.
+As the figure shows, GWRR-based VRA appears to perform better than it truly does, presenting significant positive bias across the relative price range.
 That is, researchers would tend to significantly over-estimate the value of VRA based on GWRR.
@@
 GWRT exhibits a different pattern of bias.
-At low price ratios, the GWRT approach has smaller bias compared to GWRR.
-This is partially because GWRT tends to understate the heterogeneity of site-specific yield response function as was seen in figure \@ref(fig:true-vs-estimated-optn-gwr-r).
+At low price ratios, the GWRT approach displays smaller bias compared to GWRR.
+This is partially because GWRT tends to understate the heterogeneity of the site-specific yield response functions as was seen in figure \@ref(fig:true-vs-estimated-optn-gwr-r).
 As the price ratio rises, bias increases.
@@
 Figure \@ref(fig:why-bias-single) focuses on a single cell and compares estimated and true yields between GWR and SCAM (panel (a)) and estimated and true profits between GWR and SCAM (panel (b)).
-The cell's true yield response functions plateaus at a nitrogen rate of about $140$ kg ha$^{-1}$, but the GWR-estimated yield response function suggests that yield should peak at a nitrogen rate of about $190$ kg ha$^{-1}$ and thereafter decline.
+The cell's true yield response functions plateaus at a nitrogen rate of about $140$ kg ha$^{-1}$, but the GWR-estimated yield response function suggests that yield should peak at a nitrogen rate of about $190$ kg ha$^{-1}$ and decline thereafter.
 In reality, the yield differential between GWR and SCAM is 0, while the estimated yield differential is about $0.25$ ton ha$^{-1}$, leading to the over-estimation of the value of GWR in panel (b).
@@
 
-# Discussion and conclusions
+# Discussion and Conclusions
 
-Our simulation results show that generating site-specific $R_x$s by applying the basic GWR model (GWRR) with quadratic functional form to OFPE data tends to have little economic value for site-specific $R_x$s when the true yield response function is quadratic-plateau.
+Our simulation results show that generating site-specific $R_x$s by applying the basic GWR model (GWRR) with a quadratic functional form to OFPE data tends to have little economic value for site-specific $R_x$s when the true yield response function is quadratic-plateau.
 The GWRR based VRA is on average no more profitable than SCAM-based URA under many price scenarios, particularly when nitrogen price is relatively low compared to the corn price.
-This finding reveals the economic consequences of the widely recognized statistical inaccuracy issue of GWR estimation [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation] and also the problem of assuming quadratic functional form when the true yield response function follows the quadratic-plateau functional form like corn-nitrogen relationship.
-Precision agriculture practitioners should be cautious when using GWR for site-specific $R_xs$.
-If GWR-based approach must be employed to find site-specific input recommendations (e.g., due to lack of field and soil information), our simulation results show that GWRT performs relatively better than GWRR, though its profitability improvement against URA is only moderate.
+This finding reveals the economic consequences of the widely recognized statistical inaccuracy issue of GWR estimation [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation] and also the problem of assuming quadratic functional form when the true yield response function follows the quadratic-plateau functional form, such as in the corn-nitrogen relationship.
+Precision agriculture practitioners should be cautious when using GWR for site-specific $R_x$s.
+If the GWR-based approach must be employed to find site-specific input recommendations (e.g., due to lack of field and soil information), our simulation results show that GWRT performs relatively better than GWRR, though its profitability improvement against URA is only moderate.
 
-It is worth noting that previous studies comparing models have predominantly focused on measuring model performance based on statistical accuracy of parameter estimates, such as bias, mean squared error, type I error, and confidence intervals, for both GWR models [@lu2017geographically; @harris2019simulation] and general econometric models [@christopeit2006local, @su2016identifying].
-While these statistical measures are fundamental for evaluating model performance, in practical economic applications it is imperative to consider the translation of statistical accuracy into economic value.
+Previous studies comparing models have predominantly focused on measuring model performance based on statistical accuracy of parameter estimates, such as bias, mean squared error, type I error, and confidence intervals, for both GWR models [@lu2017geographically; @harris2019simulation] and general econometric models [@christopeit2006local, @su2016identifying].
+While these statistical measures are fundamental for evaluating model performance, for practical reasons it is imperative to consider the translation of statistical accuracy into economic value.
 Moreover, the extent of this translation could vary depending on the specific application scenarios.
-This study distinguishes itself from previous literature by explicitly examining the economic value of specific econometric models (GWR) under a model functional form misspecification (quadratic instead of quadratic-plateau), in a specific application (corn site-specific nitrogen management), and under specific context scenarios (normal-sized production field, various market prices, etc.), through a simulation-based methodology.
+The research reported in the present article distinguishes itself from previous literature by explicitly examining the economic value of specific econometric models (GWR) under a model functional form misspecification (quadratic instead of quadratic-plateau), in a specific application (corn site-specific nitrogen management), and under specific context scenarios (normal-sized production field, various market prices, etc.), through a simulation-based methodology.
 We encourage other model comparison studies in empirical economic research to also incorporate similar assessment of economic value.
 
-Our results clearly show it can be dangerous to use GWR with quadratic functional form when yield-input relationship is quadratic plateau as done in @trevisan2021spatial.
-Their choice of quadratic functional form is likely due to the fact that there is no readily usable statistical software or package that implements non-linear GWR.
-The only non-linear model available at the moment is the linear-plateau GWR by @lambert2022geographically.
-Unfortunately, economically optimal input rate cannot be adjusted according to price using linear-plateau model as the economically optimal input rate occurs always at the kink.
+Our results clearly show that it can be dangerous to use GWR under the assumption of a quadratic functional form when the true yield-input relationship is quadratic plateau.
+@trevisan2021spatial had to choose the quadratic functional form because no readily usable statistical software or package could be used to implement nonlinear GWR.
+The only nonlinear model available at the moment is the linear-plateau GWR by @lambert2022geographically.
+Unfortunately, the estimation of the economically optimal input rate cannot be adjusted according to price using the linear-plateau model as the economically optimal input rate occurs always at the kink.
 Given that many yield-input relationships follow quadratic-plateau functional form for many crops, it would be fruitful to develop a GWR method with quadratic-plateau functional form.
 It should be also possible and interesting to build semi-parametric GWR where the yield response functions are estimated without assuming particular functional forms (like SCAM).
-It is also noted that the recently developed multi-scale GWR model [@fotheringham2017multiscale; @yu2020inference; @comber2022route] allows the bandwidth to be derived separately for each covariate in the model, which would potentially improve the performances of GWR estimates and be incorporated into future research.
+It is also noted that the recently developed multi-scale GWR model [@fotheringham2017multiscale; @yu2020inference; @comber2022route] allows the bandwidth to be derived separately for each covariate in the model, which would potentially improve the performances of GWR estimates and may need to be incorporated into future research.
 Please note, however, that multi-scale GWR models are not necessary in our simulations as we have only one covariate ($N$) in our simulations.
 
-Most important, whether using GWRT or GWRR, researchers must be cautious about their estimated value of VRA when model is assumed to be quadratic when the true underlying yield-input response is quadratic-plateau in reality.
+Most importantly, whether using GWRT or GWRR, researchers must be cautious about their estimated values of VRA when the model is assumed to be quadratic but the true underlying yield-input response is quadratic-plateau in reality.
 Our results show that it is likely that they will over-estimate their true values and the bias can be misleadingly high with non-negligible probability.
@@
 The objective of this article was to evaluate GWR with quadratic functional form when the true yield-input relationship is quadratic-plateau.
-Therefore, we evaluated GWR when model is mis-specified in a particular manner.
-Once, GWR with quadratic-plateau model is developed, it would be interesting to see how it performs when the true yield response to input is quadratic-plateau.
-In this case, there is no functional form mis-specification and the pure ability of GWR can be isolated.
+Therefore, we evaluated GWR when under a particular kind of model misspecification.
+After the development of software then can run GWR with a quadratic-plateau model, it would be interesting to see how it performs when the true yield response to input is quadratic-plateau.
+In this case, there is no functional form misspecification and the pure ability of GWR could be isolated.
 
@@
 
-```{r fig.id = "field-layout", fig.cap = "Simulated field layout with spatial unit definitions", fig.dim = c(6, 6)}
+```{r fig.id = "field-layout", fig.cap = "Simulated field layout with spatial unit definitions", fig.width = 7}
+# knitr::include_graphics(here::here("GitControlled/Writing/Figures/g_layout.png"))
 g_layout
@@
 
-```{r fig.id = "field-N-design", fig.cap = "Experiment design of nitrogen (N) rates", fig.dim = c(6, 3.5)}
+```{r fig.id = "field-N-design", fig.cap = "Experiment design of nitrogen (N) rates", out.width = "6in", fig.width = 6}
+# knitr::include_graphics(here::here("GitControlled/Writing/Figures/g_exp.png"))
 g_exp
@@
 
-```{r, fig.id = "pi-dif-dist", fig.cap = "The value of GWR-based VRA over SCAM-based URA for GWRR and GWRT", fig.height = 5, fig.width = 6}
+```{r, fig.id = "pi-dif-dist", fig.cap = "The value of GWR-based VRA over SCAM-based URA for GWRR and GWRT", out.width = "6.5in", fig.width = 6}
+# knitr::include_graphics(here::here("GitControlled/Writing/Figures/g_value.png"))
 g_value
@@
 
-```{r fig.id = "bias-est-eonr", fig.cap = "Average bias in the estimation of EONR by GWRR and GWRT", fig.height = 5, fig.width = 6}
-g_eonr_bias
+```{r fig.id = "bias-est-eonr", fig.cap = "Average bias in the estimation of EONR by GWRR and GWRT", fig.width = 6}
+# knitr::include_graphics(here::here("GitControlled/Writing/Figures/g_value.png"))
+g_value
 ```
 
-```{r fig.id = "true-vs-estimated-optn-gwr-r", fig.cap = "Comparison of Estimated and True EONR"}
+```{r fig.id = "true-vs-estimated-optn-gwr-r", fig.cap = "Comparison of Estimated and True EONR", fig.width = 6}
+# knitr::include_graphics(here::here("GitControlled/Writing/Figures/g_comp_eonr.png"))
 g_comp_eonr
@@
 
-```{r fig.id = "bias-est-pi", fig.cap = "Bias in the estimation of the value of GWR-based VRA over SCAM-based URA for GWRR and GWRT", fig.height = 5, fig.width = 6}
+```{r fig.id = "bias-est-pi", fig.cap = "Bias in the estimation of the value of GWR-based VRA over SCAM-based URA for GWRR and GWRT", fig.width = 6}
+# knitr::include_graphics(here::here("GitControlled/Writing/Figures/g_bias.png"))
 g_bias
@@
 
-```{r fig.id = "why-bias-many", fig.cap = "The cause of significant over-estimation of the value of GWR-based VRA"}
+```{r fig.id = "why-bias-many", fig.cap = "The cause of significant over-estimation of the value of GWR-based VRA", fig.width = 6}
+# knitr::include_graphics(here::here("GitControlled/Writing/Figures/g_why_bias_many.png"))
 g_why_bias_many
@@
 
-```{r fig.id = "why-bias-single", fig.cap = "An illustration of over-estimation of the value of GWR-based VRA over SCAM-based URA",fig.dim = c(6, 7)}
+```{r fig.id = "why-bias-single", fig.cap = "An illustration of over-estimation of the value of GWR-based VRA over SCAM-based URA",fig.width = 6.5, fig.height = 6}
+# knitr::include_graphics(here::here("GitControlled/Writing/Figures/g_why_bias_single.png"))
 g_why_bias_single
@@
 `r run_pagebreak()`
-
-# Appendix

### 2023-07-27 Codes/3_make_figures_publication.R

@@ -1,6 +1,52 @@
-# /*===========================================================
-#' # Visualization the field and spatial units
-# /*===========================================================
+## ------------------------------
+theme_fig <-
+  theme_bw() +
+  theme(
+    axis.title.x =
+      element_text(
+        size = 12, angle = 0, hjust = .5, vjust = -0.3, family = "Times"
+      ),
+    axis.title.y =
+      element_text(
+        size = 12, angle = 90, hjust = .5, vjust = .9, family = "Times"
+      ),
+    axis.text.x =
+      element_text(
+        size = 9, angle = 0, hjust = .5, vjust = 1.5, family = "Times"
+      ),
+    axis.text.y =
+      element_text(
+        size = 9, angle = 0, hjust = 1, vjust = 0, family = "Times"
+      ),
+    axis.ticks =
+      element_line(
+        linewidth = 0.3, linetype = "solid"
+      ),
+    axis.ticks.length = unit(.15, "cm"),
+    #--- legend ---#
+    legend.text =
+      element_text(
+        size = 12, angle = 0, hjust = 0, vjust = 0.5, family = "Times"
+      ),
+    legend.title =
+      element_text(
+        size = 12, angle = 0, hjust = 0, vjust = 0, family = "Times"
+      ),
+    legend.key.size = unit(0.5, "cm"),
+    #--- strip (for faceting) ---#
+    strip.text = element_text(size = 12, family = "Times"),
+    #--- plot title ---#
+    plot.title = element_text(family = "Times", face = "bold", size = 12),
+    #--- margin ---#
+    # plot.margin = margin(0, 0, 0, 0, "cm"),
+    #--- panel ---#
+    panel.grid.minor = element_blank(),
+    panel.background = element_blank(),
+    panel.border = element_rect(fill = NA)
+  )
+
+
+## ------------------------------
 # fig.id = "field-layout",
 # fig.cap = "Simulated field layout with spatial unit definitions",
 # fig.dim = c(6, 6)
@@ -32,25 +78,27 @@ block_text_sf <- st_centroid(block_sf)
 g_field <-
   ggplot() +
   geom_sf(data = plot_sf, size = 0.2, fill = NA) +
-  geom_sf(data = filter(plot_sf, plot_id == 264), fill = "red", alpha = 0.5) +
[…]

### 2023-07-27 Writing/knit.R

@@ -1,3 +1,13 @@
-rmarkdown::render(here::here("GitControlled/Writing/manuscript_gwr.rmd"))
-
 rmarkdown::render(here::here("GitControlled/Writing/JAAEA/1stRoundRevision/reply_to_editor.rmd"))
+
+pagedown::chrome_print(here::here("GitControlled/Writing/JAAEA/1stRoundRevision/reply_to_editor.html"))
+
+rmarkdown::render(here::here("GitControlled/Writing/JAAEA/1stRoundRevision/reply_to_reviewer_1.rmd"))
+
+pagedown::chrome_print(here::here("GitControlled/Writing/JAAEA/1stRoundRevision/reply_to_reviewer_1.html"))
+
+rmarkdown::render(here::here("GitControlled/Writing/JAAEA/1stRoundRevision/reply_to_reviewer_2.rmd"))
+
+pagedown::chrome_print(here::here("GitControlled/Writing/JAAEA/1stRoundRevision/reply_to_reviewer_2.html"))
+
+

### 2023-07-27 Writing/manuscript_gwr.rmd
citation problem fixed

@@
 Accompanying interest is surging among researchers in identifying efficient statistical methods to estimate site-specific yield response functions with OFPE data.
-Researchers recently have examined various methods, ranging from Geographically Weighted Regression (GWR) [@rakshit2020; @evans2020assessment; @trevisan2021spatial] to machine learning techniques, including random forest [@krause2020random, @de2023predicting], convolutional neural network [@barbosa2020modeling], and causal forest [@kakimoto2022causal] approaches.
+Researchers recently have examined various methods, ranging from Geographically Weighted Regression (GWR) [@rakshit2020; @evans2020assessment; @trevisan2021spatial] to machine learning techniques, including random forest [@krause2020random; @de2023predicting], convolutional neural network [@barbosa2020modeling], and causal forest [@kakimoto2022causal] approaches.
 Among these, reported research on the GWR approach have generated special interest because GWR can be used to estimate site-specific yield-to-input relationships without costly spatial field and soil data.
@@
 The second source of over-estimation bias is endemic to any study that evaluates the value of variable rate application.
-In general, researchers take the following steps to estimate the value of VRA using OFPE data [@anselin2004spatial, @bullock2002adding, @liu2006site, @swinton1998evaluating]: (1) estimate site-specific yield response functions based on a method chosen by the researcher; (2) use the estimated yield response functions to estimate the economically optimal site-specific input rates (EOIRs) and economically optimal uniform input rates; (3) plug the estimated site-specific EOIRs and uniform EOIR into the estimated yield response functions to calculate estimated profits under both strategies; and (4) find the difference in the two strategies' estimated profits.
+In general, researchers take the following steps to estimate the value of VRA using OFPE data [@anselin2004spatial; @bullock2002adding; @liu2006site; @swinton1998evaluating]: (1) estimate site-specific yield response functions based on a method chosen by the researcher; (2) use the estimated yield response functions to estimate the economically optimal site-specific input rates (EOIRs) and economically optimal uniform input rates; (3) plug the estimated site-specific EOIRs and uniform EOIR into the estimated yield response functions to calculate estimated profits under both strategies; and (4) find the difference in the two strategies' estimated profits.
 However, this approach can result in significant bias in the estimation of the value of VRA because of the step 3's assumption that the estimated yield response functions are the true yield response functions.
@@
 
-An extensive literature examines the choice of functional form in yield response estimation [@cerrato1990comparison, @frank1990comparison, @bullock1994quadratic, @tembo2008crop].
-Our simulation assumes that each cell $(j, i)$'s "true" yield response function  follows the commonly-used quadratic-plateau functional form:
+An extensive literature examines the choice of functional form in yield response estimation [@cerrato1990comparison; @frank1990comparison; @bullock1994quadratic; @tembo2008crop].
+Our simulation assumes that each cell $(j, i)$'s "true" yield response function follows the quadratic-plateau functional form because our main objective is to find the bias associated with using a quadratic funcitonal form in GWR when the true yield response fucntion follows the quadratic-plateau functional form:
 
@@
 
-The spatial distributions of cell-level parameters $\alpha_{j, i}$, $\beta_{j, i}$, $\gamma_{j,i}$, $\tau_{j, i}$, and the error term $\varepsilon_{j, i}$ were simulated by generating spatially correlated random fields using unconditional Gaussian geostatistical simulation based on the specified variograms [@dietrich1996fast, @wood1994simulation].
+The spatial distributions of cell-level parameters $\alpha_{j, i}$, $\beta_{j, i}$, $\gamma_{j,i}$, $\tau_{j, i}$, and the error term $\varepsilon_{j, i}$ were simulated by generating spatially correlated random fields using unconditional Gaussian geostatistical simulation based on the specified variograms [@dietrich1996fast; @wood1994simulation].
 The simulation processes were conducted using the R package gstat [@graler16].
@@
 
-Previous studies comparing models have predominantly focused on measuring model performance based on statistical accuracy of parameter estimates, such as bias, mean squared error, type I error, and confidence intervals, for both GWR models [@lu2017geographically; @harris2019simulation] and general econometric models [@christopeit2006local, @su2016identifying].
+Previous studies comparing models have predominantly focused on measuring model performance based on statistical accuracy of parameter estimates, such as bias, mean squared error, type I error, and confidence intervals, for both GWR models [@lu2017geographically; @harris2019simulation] and general econometric models [@christopeit2006local; @su2016identifying].
 While these statistical measures are fundamental for evaluating model performance, for practical reasons it is imperative to consider the translation of statistical accuracy into economic value.

### 2023-07-28 Writing/JAAEA/1stRoundRevision/reply_to_reviewer_2.rmd
finalized revision
proofread and final edits

@@
 ---
+title: "Reply"
 output: 
-  html_document: default
+  html_document:
+    theme:
+      version: 4
+bibliography: PA.bib
 ---
-# Reply to the Reviewer #2
 
@@
 
-This is a very good point.
-What makes this study differ from previous studies is that the model “value” is not measured by the accuracy of parameter estimates, but rather by the ultimate economic return.
-We have followed your suggestion above by expanding our review of previous studies to highlight what our research adds to the literature.
-Please see in particular section 2.3 of the revised manuscript.
+Thank you for bringing up this important point.
+What makes this study differ from previous studies is that the model “value” is not measured by the statistical accuracy of parameter estimates, but rather by the ultimate economic return.
+To emphasize this aspect, we have included an additional paragraph in the “5.
+Discussion and Conclusions” section (paragraph 2).
+It is worth noting that we are unable to identify a specific body of literature that exclusively focuses on assessing the value of general regression models.
+However, it is customary in the development of econometric models to evaluate their performance using statistical accuracy measures such as bias, mean squared error, and type I error, based on simulation data.
+We have referenced a few relevant studies of this nature to underscore the distinction of our economic value assessment approach.
 
@@
 Thank you for the suggestion.
-We have explicitly stated the following at the end of the Introduction section of the revised manuscript: *"While the environmental impacts of fertilizer management are of great social importance, for simplicity we confine our analysis to its private economic impacts."*
+We have explicitly stated the following in a footnote at the end of the Introduction section of the revised manuscript: *"While the environmental impacts of fertilizer management are of great social importance, for simplicity we confine our analysis to its private economic impacts."*
 
@@
 Thank you for bringing up this point.
-We have included a brief discussion of the historical corn and nitrogen prices in the first paragraph of the Results section 5.1.
+We have included a brief discussion of the historical corn and nitrogen prices in the first paragraph of the Results section 4.1.
 Additionally, we have included Appendix I: Historical Corn and Nitrogen Prices in the supplementary material to provide a more detailed description of the collection, calculation, and summary statistics of the historical price data.
@@
 Yes, it should be the square root of the sill variances since 1370 kg ha−1 was the mean of the standard deviations.
-We have corrected that typo in the revised manuscript at the end of section 4.2.
+We have corrected that typo in the revised manuscript at the end of section 3.2.
 
@@
 Thank you for the suggestion.
-In section 4.5.1 of the revised manuscript we have expanded our explanation of SCAM to clarify that it is a regression model that can fit a more flexible and non-linear response relationship and also allows for shape constraints that can incorporate prior knowledge or theories.
+In section 3.5.1 of the revised manuscript we have expanded our explanation of SCAM to clarify that it is a regression model that can fit a more flexible and non-linear response relationship and also allows for shape constraints that can incorporate prior knowledge or theories.
 
@@
 We agree the GWR results could vary when choosing different bandwidths, but the choices of other bandwidth values other than the AIC-chosen one may be arbitrary.
-We added more discussions about bandwidth selection at the end of section 4.5.3 of the revised manuscript.
+We added more discussions about bandwidth selection at the end of section 3.5.3 of the revised manuscript.
 
@@
 
-Our apologies for the typos. We have corrected them and filled in the correct numbers. They can be found in the end of the 2nd paragraph of section 5.1 of the revised manuscript.
+Our apologies for the typos. We have corrected them and filled in the correct numbers. They can be found in the end of the 2nd paragraph of section 4.1 of the revised manuscript.
 
@@
 We apologize for the mistake, and we have corrected the order of the figures accordingly.
-The revised manuscript now reflects the correct sequence of Figures 5 and 6.
+The revised manuscript now reflects the correct sequence of the two figures.
+Note that since the original Figure 4 was removed, the two figures are now the new Figure 4 and Figure 5.
 
@@
 In precision agriculture, the site-specific input management recommendation map is commonly called "prescription" or "Rx" by researchers and the industry.
-While we are certainly willing to defer to the editor's judgment, We have elected to keep this abbreviation in the revised manuscript, but have added a brief explanation of the notation (near the end of section 2.2).
+While we are certainly willing to defer to the editor's judgment, we have elected to keep this abbreviation in the revised manuscript, but have added a brief explanation of the notation (in the 1st paragraph of section 2.2).
 In the USA, at least, it is widely known that "Rx" means "prescription," and it is chiefly used in conversations about medicines and pharmacies.
@@
 
-Thank you for the suggestion. We agree that placing the commercial examples in a footnote is a better approach. Please see footnote 1 of the revised manuscript.
+Thank you for the suggestion.
+We agree that precision agriculture technologies are advancing rapidly.
+However, we believe that those commercial examples are essential to illustrate the current state of site-specific field data collection technologies, which will help readers understand the benefits of the GWR method.
+Therefore, we prefer to retain these examples in the main text.
+Nonetheless, we acknowledge that these contents may be a little lengthy, so we have moved them from the Introduction section to the Background section of 2.2 (1st paragraph).
 
@@
 
-We have followed the reviewer's suggestion and broken the discussion into two paragraphs in the revised manuscript.
+This paragraph's contents were broken into two pieces in the revised manuscript, one piece in the last paragraph of Introduction section, and the other piece in the first paragraph of section 2.3.
 
@@
 
-This typo has been removed. Thank you for bring it to our attention.
+This typo has been removed. Thank you for bringing it to our attention.
 
@@
 
-Thank you for pointing out this writing issue. We have placed the acronym DIFM after the full name in the revised manuscript
+Thank you for pointing out this writing issue. We have placed the acronym DIFM after the full name in the revised manuscript.
 
@@
 We greatly appreciate the reviewer's meticulous review of the manuscript and for finding this typo.
-We have corrected it to use subscript notation (see line 3 of section 4.4).
+We have corrected it to use subscript notation (see line 3 of section 3.4).
 Furthermore, to eliminate the duplication of the spline index $k$, we have updated the cell index notation to $(j, i)$ both in this section and throughout the rest of the manuscript.
@@
 We agree that the language used could cause confusion about whether we were referring to the yield response function or the shape constraint as "single."  We removed the term "single" from the revised manuscript.
-Please see section 4.5.1 of the revised manuscript.
+Please see section 3.5.1 of the revised manuscript.
 
@@
 
-We have cited two additional of agronomic studies to support the statement in section 4.5.1 of the revised manuscript.
+We have cited two additional of agronomic studies (Bullock and Bullock, 1994; Cerrato and Blackmer, 1990) to support the statement in section 5.5.1 of the revised manuscript.
 
@@
 
-Thank you for pointing out those typos. They have all been corrected (see the end of the 2nd paragraph of section 5.1 of the revised manuscript).
+Thank you for pointing out those typos. They have all been corrected (see the end of the 2nd paragraph of section 4.1 of the revised manuscript).
 
@@
 
-Our apologies for the typo. It should have been Figure 5 and this problem is fixed in our new manuscript.
+Our apologies for the typo. It should have been Figure 5 and this problem is fixed in our new manuscript (see the 2nd paragraph of section 4.2).
 
@@
 
-We greatly appreciate the reviewer for identifying this typo. It was corrected in the revised manuscript.
+We greatly appreciate the reviewer for identifying this typo. It was corrected in the revised manuscript (now Figure 7).
 
@@
 
-We have edited the sentence in the revised manuscript (see the end of paragraph 4, section 6 in the revised manuscript), adding details to explain that other statistical methods commonly used for site-specific yield response estimation literature include regression on field characteristics variables as interaction terms, machine learning, etc.
+We have edited the sentence in the revised manuscript (near the end of paragraph 4, section 5 in the revised manuscript), adding details to explain that other statistical methods commonly used for site-specific yield response estimation literature include regression on field characteristics variables as interaction terms, machine learning, etc.
 The common assessment approach is to use simulation-based evaluation, much as we do in our study.

### 2023-07-28 Writing/manuscript_gwr.rmd
proofread and final edits

@@
 The primary objective of this study is to examine the degree and direction of bias in the estimation of the economic value of GWR-based site-specific nitrogen rate recommendations (i.e., variable rate applications of nitrogen) when the yield response function assumed in the GWR model is specified as quadratic but is actually of quadratic-plateau functional form.
-We will do so using Monte Carlo simulations, which , since we define and know the true yield response function in the data generating process, allow us to measure the degree of bias.
-Unlike in @griffith2008spatial, @harris2019simulation, @paez2011simulation, and @da2016multiple, our objective is not to measure the bias in the coefficient estimation by GWR, but rather to measure economic effects of the statistical inaccuracy in estimating the coefficients of the model.
-We show that the misspecification tends to significantly over-estimate GWR's true value.
+We will do so using Monte Carlo simulations, which, since we define and know the true yield response function in the data generating process, allow us to measure the degree of bias.
+Unlike in @griffith2008spatial, @harris2019simulation, @paez2011simulation, and @da2016multiple, our objective is not to measure the bias in the coefficient estimation by GWR, but rather to measure economic effects^[While the environmental impacts of fertilizer management are of great social importance, for simplicity we confine our analysis to its private economic impacts.] of the statistical inaccuracy in estimating the coefficients of the model.
+We show that the misspecification tends to significantly over-estimate GWR's true economic value.
 
@@
 On-farm precision experimentation (OFPE) can provide detailed as-applied input and yield data at dense resolutions over entire fields, which if well analyzed may provide valuable information that can improve site-specific input application recommendations [@bullock2019data; @lacoste2021farm].
-Consider a yield response function $y = f(x, c)$, where following @bullock2000agronomic, $x$ is a vector of input management variables and $c$ is a vector of spatial variables describing field and soil characteristics^[For simplicity, we suppress discussion of the need to bring variance in weather data into yield response estimation.
+Consider a yield response function $y = f(\textbf{x}, \textbf{c})$, where following @bullock2000agronomic, $\textbf{x}$ is a vector of input management variables and $\textbf{c}$ is a vector of spatial variables describing field and soil characteristics^[For simplicity, we suppress discussion of the need to bring variance in weather data into yield response estimation.
 Obviously, generation and use of weather data is necessary to provide meaningful probabilistic analysis and input management advice.].
-Letting a field site $i$ be defined as a contiguous area characterized uniformly by a value $c_i$ of the vector of field and soil characteristics, its site-specific yield response function is the reduced form of the field's yield response function created when the value of the vector of characteristics variables is set at the site's value, $c_i$:  $f_i(x) \equiv f(x, c_i)$.
+Letting a field site $i$ be defined as a contiguous area characterized uniformly by a value $\textbf{c}_i$ of the vector of field and soil characteristics, its *site-specific yield response function* is the reduced form of the field's yield response function created when the value of the vector of characteristics variables is set at the site's value, $\textbf{c}_i$:  $f_i(\textbf{x}) \equiv f(\textbf{x}, \textbf{c}_i)$.
 This conceptualization suggests two methods of estimating a field's site-specific yield responses.
-The first is to estimate a "map" of the field characteristics, for example thought of as a set of the field's $n \geq 1$ sites' values of the characteristics vector: $\{c_1,\dots, c_n\}$.
-With that map, regressing yield on x and c generates an estimated "field-specific" yield response function $\hat{f}_(x,c)$.
-Estimates of site-specific yield response functions can then be obtained by inserting the value of the site's characteristic variables into the estimate of the field-specific response function: $\hat{f}_i(x) \equiv \hat{f}(x,c_i)$.
-Alternatively, a site-specific yield response function might be estimated simply by taking (input rate, yield) data from points around a site of interest, and regressing yield on input application rates to attain the estimate $\tilde{f}_i (x)$.
+The first is to estimate a "map" of the field characteristics, for example thought of as a set of the field's $n \geq 1$ sites' values of the characteristics vector: $\{\textbf{c}_1,\dots, \textbf{c}_n\}$.
+With that map, regressing yield on $\textbf{x}$ and $\textbf{c}$ generates an estimated "field-specific" yield response function $\hat{f}_(\textbf{x},\textbf{c})$.
+Estimates of site-specific yield response functions can then be obtained by inserting the value of the site's characteristic variables into the estimate of the field-specific response function: $\hat{f}_i(\textbf{x}) \equiv \hat{f}(\textbf{x},\textbf{c}_i)$.
+Alternatively, a site-specific yield response function might be estimated simply by taking (input rate, yield) data from points around a site of interest, and regressing yield on input application rates to attain the estimate $\tilde{f}_i (\textbf{x})$.
 Stated roughly, using GWR takes the latter approach, which has the advantage of not needing a costly map of field characteristics values.
 
-## Costs of Field Characteristics Data and The Appeal of GWR
+## Costs of Field Characteristics Data and the Appeal of GWR
 
@@
 The data are often used to derive fertilizer application recommendations, for example by applying comparatively simple formulas provided by university extension services (e.g., @culman2020tri).
-But the expense of soil sampling and analysis is driving development of sensor technologies that gather data on site-specific field and crop characteristics or proxies of those characteristics, and the conversion of those data into recommended input application rate maps (usually called "prescriptions" or "$R_x$s").
+**XL_changes_made: (I removed the "but" here) The expense of soil sampling and analysis is also driving development of new (I added the "new" here) sensor technologies** that gather data on site-specific field and crop characteristics or proxies of those characteristics, and the conversion of those data into recommended input application rate maps (usually called "prescriptions" or "$R_x$s").
 For example, Trimble Agriculture's GreenSeeker and AgLeader's OptRx systems use optical sensors mounted on fertilizer application booms to digitally record vegetative index imagery as farm machinery is driven through fields during early crop growth stages.
@@
 @rakshit2020 also estimated site-specific yield response functions by applying GWR to on-farm experiment data assuming a quadratic functional form of yield response.
-But they did not calculate site-specific economically optimal nitrogen rates, and so unlike @trevisan2021spatial did not conduct economic analysis.
+But they did not calculate site-specific economically optimal nitrogen rates, and so unlike @trevisan2021spatial, did not conduct economic analysis.
 @evans2020assessment explored using GWR with a linear model specification to detect low- and high-response areas, but like @rakshit2020, did not estimate site-specific economically optimal nitrogen rates.
@@
 However, this approach can result in significant bias in the estimation of the value of VRA because of the step 3's assumption that the estimated yield response functions are the true yield response functions.
-@trevisan2021spatial provided an example at step (3) by assuming that their GWR estimates provided "true" site-specific yield response functions.
+@trevisan2021spatial provided an example at step 3 by assuming that their GWR estimates provided "true" site-specific yield response functions.
 This assumption is generally unavoidable for researchers since they cannot observe any real field's true site-specific yield response functions.
 But inaccurate estimation of yield response function in this methodology can result in significant bias in the estimation of the value of VRA.
-This bias problem can be particularly severe when the method used tends to exaggerate the true heterogeneity in yield response functions.
-We suspect that the high value of VRA estimated by @trevisan2021spatial displays this bias., such as GWR [@czarnota2015evaluating].
+This bias problem can be particularly severe when the method used tends to exaggerate the true heterogeneity in yield response functions, such as GWR [@czarnota2015evaluating].
+We suspect that the high value of VRA estimated by @trevisan2021spatial displays this bias.
 
@@
 
-We evaluated two sets of GWR quadratic specifications used in @rakshit2020 and @trevisan2021spatial, both of which assumed a quadratic response of yield to nitrogen rate ($N$).
-However, while @trevisan2021spatial estimated the coefficient on $N^2$ as a global parameter, @rakshit2020 estimated it locally for each point.
+We evaluated two sets of GWR quadratic specifications used in @rakshit2020 and @trevisan2021spatial, both of which assumed a quadratic response of yield to nitrogen rate (N).
+However, while @trevisan2021spatial estimated the coefficient on N$^2$ as a global parameter, @rakshit2020 estimated it locally for each point.
 We cannot use real data to test which model specification results in more profitable site-specific nitrogen rate recommendations because it is impossible to observe the true yield response functions using real-world data.
@@
 Therefore, the yield data's resolution was 18m $\times$ 12m (3 cells $\times$ 2 cells, called a "subplot").
-The N rate unit consisted of five "subplots", that is, 18m $\times$ 72m (3 cells $\times$ 12 cells, called a "plot") to accommodate the variable-rate applicator's application resolution.
-A 12m "transition zone" was placed between two plots (that is, a 6m "transition zone" on each end of a plot), so that when the experimental N rate changed, the harvester had 12m to "clear" and begin to record accurately on a plot with an N rate different from its predecessor's.
+The N rate unit **(XL_changes_made:) was 18m $\times$ 72m (3 cells $\times$ 12 cells, called a "plot") to accommodate the variable-rate applicator's application resolution.
+However, a 12m "transition zone" was placed between two plots (that is, a 6m "transition zone" on each end of a plot), so that when the experimental N rate changed, the harvester had 12m to "clear" and begin to record accurately on a plot with an N rate different from its predecessor's.
+That means each N "plot" consisted of five effective "subplots" for data analysis.**
 
 The field was 432m (72 cells) wide and 864m (144 cells) long, making its area 37.3 ha.
-Data from the 6m-long headlands, side-lands (there are no transition zones on the north and south ends of the field), and 12m-wide "transition zones" were not included the analysis.
-In total, data from 1440 subplots available for experimental data analysis.
+Data from the 6m-long headlands, side-lands (there are no transition zones on the north and south ends of the field), and 12m-wide "transition zones" were not included in the analysis.
+In total, data from 1440 subplots were available for experimental data analysis.
 The index $j \in {1, 2, \dots, 1440}$ identifies the field's subplots, and the index $i \in {1, \dots , 6}$ identifies the cells within a subplot.
@@
 An extensive literature examines the choice of functional form in yield response estimation [@cerrato1990comparison; @frank1990comparison; @bullock1994quadratic; @tembo2008crop].
-Our simulation assumes that each cell $(j, i)$'s "true" yield response function follows the quadratic-plateau functional form because our main objective is to find the bias associated with using a quadratic funcitonal form in GWR when the true yield response fucntion follows the quadratic-plateau functional form:
+Our simulation assumed that each cell $(j, i)$'s "true" yield response function followed the quadratic-plateau functional form because our main objective was to find the bias associated with using a quadratic functional form in GWR when the true yield response function followed the quadratic-plateau functional form:
 
@@
 
-In each simulation, six trial N rates were assigned by calculating the 0%, 20%, 40%, 60%, 80%, and 100% quantiles of the simulation's true cell-specific optimal N rates.
-When using the historical average corn and N prices (of the past two decades from 2002 to 2022), the means of these trial N rates across simulations were approximately {80, 130, 154, 184, 219, and 270} kg ha$^{-1}$, while the differences between simulations were small and negligible.
+In each simulation, six trial N rates were assigned by calculating the 0%, 20%, 40%, 60%, 80%, and 100% quantiles of the simulation's true cell-specific **(XL_changes_made:) critical N rates ($\tau_{j,i})$)**.
+The means of these trial N rates across simulations were approximately {80, 130, 154, 184, 219, and 270} kg ha$^{-1}$, while the differences between simulations were small and negligible.
 
@@
 
-In each simulation, for each cell $(j, i)$, the simulation's true yield $y_{j, i}$ was generated based on the cell's assigned application rate $N_{j,i}$, true response parameters $c_{j,i} = (\alpha_{j,i}, \beta_{j,i}, \gamma_{j,i}, \tau_{j,i})$, and error term $\varepsilon_{j,i}$.
+In each simulation, for each cell $(j, i)$, the simulation's true yield $y_{j, i}$ was generated based on the cell's assigned application rate $N_{j,i}$, true response parameters $\textbf{c}_{j,i} = (\alpha_{j,i}, \beta_{j,i}, \gamma_{j,i}, \tau_{j,i})$, and error term $\varepsilon_{j,i}$.
 This procedure generated a field-level, cell-specific data set, $\{(y_{j, i},N_{j, i} ):j=1,\dots,1440;k=1,\dots, 6 \}$.
@@
 
-Let $\hat{f}^{SCAM}(\cdot)$ represent the estimated whole-yield yield response function ($\sum_{k=1}^K \hat{\beta}_k g_k(\cdot)$).
+Let $\hat{f}^{SCAM}(\cdot)$ represent the estimated whole-yield yield response function ($\hat{\alpha} + \sum_{k=1}^K \hat{\beta}_k g_k(\cdot)$).
 Given the information derived from the SCAM approach, the estimate of the economically optimal uniform N rate is,
@@
 
-The GWRR model is simply the basic GWR model [@fotheringham1996geography; @brunsdon1999some; @fotheringham2003geographically], where subplot-specific yield responses were modeled as quadratic functions of the nitrogen rate, which for each subplot $j \in {1, 2, \dots, 1440}$ was specified as,
+The GWRR model is simply the basic GWR model [@fotheringham1996geography; @brunsdon1999some; @fotheringham2003geographically], where subplot-specific yield responses were modeled as quadratic functions of the nitrogen rate.
+Each subplot $j \in {1, 2, \dots, 1440}$ was specified as,
 
-$$y_j= \alpha_j+ \beta_j N_j + \eta_j N_j^2+ \epsilon_j, \;\; j \in 1, 2, \dots, 1440.$$
+$$y_j= \alpha_j+ \beta_j N_j + \eta_j N_j^2+ \varepsilon_j, \;\; j \in 1, 2, \dots, 1440.$$
 
@@
 The GWRR estimation produced subplot-specific estimates of coefficients $\hat{\alpha}_j$, $\hat{\beta}_j$, and $\hat{\eta}_j$, and so of the yield response function $\hat{f}^{GWRR}_j(N)$ for $j = 1, 2, \dots, 1440$.
-The estimated economically optimal N application rate for subplot $j$ was calculated by solving the subplot's profit maximization problem:
+The estimated economically optimal N application rate for subplot $j$ was calculated by solving the subplot's profit maximization problem,
 
-$$\hat{N}^{*GWRR}_j \equiv argmax_N⁡[p\hat{f}^{GWRR}_j (N) -wN], \;\; j \in 1, 2, \dots, 1440.$$
+$$\hat{N}^{*GWRR}_j \equiv argmax_N⁡[ p \cdot \hat{f}^{GWRR}_j (N) - w\cdot N], \;\; j \in 1, 2, \dots, 1440.$$
 
@@
 The GWRT model is also called as "mixed" GWR in the literature [@brunsdon1999some], where some parameters are fixed globally while others vary geographically.
-We estimate the coefficient on $N^2$ as a global parameter and the coefficient on $N$ subplot-specifically.
+We estimated the coefficient on $N^2$ as a global parameter and the coefficient on $N$ subplot-specifically.
 For each subplot $j \in {1, 2, \dots, 1440}$, the assumed yield response was,
 
-$$y_j= \alpha_j+ \beta N_j + \eta N_j^2+ \epsilon_j ,$$
+$$y_j= \alpha_j+ \beta N_j + \eta N_j^2+ \varepsilon_j ,$$
 
@@
 
-The Gaussian kernel function was used when estimating both GWR models (Other kernel functions were also tried and the final conclusions were quantitatively similar; see the supplemenraty appendix.).
+The Gaussian kernel function was used when estimating both GWR models (other kernel functions were also tried and the final conclusions were quantitatively similar; see the supplemenraty appendix).
 There are several frequently used approaches in the literature to calculate the optimal kernal bandwidth, such as cross-validation [@cleveland1979robust; @bowman1984alternative] and the Akaike Information Criterion (AIC) [@akaike1973].
-Like @rakshit2020 and @trevisan2021spatial, we follow the most recent GWR literature by using the corrected version of the AIC approach [@fotheringham2003geographically; @fotheringham2017multiscale; @lu2017geographically].
+Like @rakshit2020 and @trevisan2021spatial, we followed the most recent GWR literature by using the corrected version of the AIC approach [@fotheringham2003geographically; @fotheringham2017multiscale; @lu2017geographically].
 The optimal bandwidth differed slightly across each simulated experiment, and the average bandwidth was approximately 18 meters.
@@
 
-$$\Pi^{*SCAM} = \frac{1}{8640} \sum_{j=1}^{1440} \sum_{k=1}^6 \big[pf_{j, i} (\hat{N}^{*SCAM})-w\hat{N}^{*SCAM}\big]$$
+$$\Pi^{SCAM} = \frac{1}{8640} \sum_{j=1}^{1440} \sum_{k=1}^6 \big[p \cdot f_{j, i} (\hat{N}^{*SCAM})-w \cdot \hat{N}^{*SCAM}\big]$$
+**(XL_changes_made:) and profits from the GWR approach (either GWRR or GWRT) were,**
+
+$$\Pi^{GWR}=\frac{1}{8640} \sum_{j=1}^{1440} \sum_{k=1}^6 [p \cdot f_{j, i} (\hat{N}^{*GWR}_j)-w \cdot \hat{N}^{*GWR}_j]$$
 
 where $f_{j, i}(\cdot)$ denotes the true yield response function at cell $(j, i)$.
-
-The true per-ha net revenues ("profits") resulting from applying the profit-maximizing cell-specific N rate plan estimated by GWR (either GWRR or GWRT) model were,
-
-$$\Pi^{GWR}=\frac{1}{8640} \sum_{j=1}^{1440} \sum_{k=1}^6 [pf_{j, i} (\hat{N}^{*GWR}_j)-w\hat{N}^{*GWR}_j]$$
-
-where $f_{j, i} (\hat{N}^{*GWR}_j)$ denote the true yield generated at cell $(j, i)$ with subplot $j$'s GWR estimated N rate.
 
@@
 
-To find the bias in estimating the value of VRA, the profits of the SCAM-based URA and GWR-based VRA were calculated by substituting the estimated optimal nitrogen rates into the cell-specific yield response functions estimated by GWR.
-Estimated per-ha net revenues for SCAM-based URA and GWR-based VRA are calcualted as follows:
+To find the bias in estimating the value of VRA, the estimated profits of the SCAM-based URA and GWR-based VRA were calculated by substituting the estimated optimal nitrogen rates into the cell-specific yield response functions estimated by GWR:
 
-$$\hat{\Pi}^{*SCAM} = \frac{1}{8640} \sum_{j=1}^{1440} \sum_{k=1}^6 \big[p\hat{f}^{GWR}_{j, i} (\hat{N}^{*SCAM} )-w\hat{N}^{*SCAM}\big]$$
+$$\hat{\Pi}^{SCAM} = \frac{1}{8640} \sum_{j=1}^{1440} \sum_{k=1}^6 \big[p \cdot \hat{f}^{GWR}_{j, i} (\hat{N}^{*SCAM} )-w \cdot \hat{N}^{*SCAM}\big]$$
 
-$$\hat{\Pi}^{*GWR}=\frac{1}{8640} \sum_{j=1}^{1440} \sum_{k=1}^6 [p\hat{f}^{GWR}_{j, i} (\hat{N}^{*GWR}_{j} )-w\hat{N}^{*GWR}_{j}]$$
+$$\hat{\Pi}^{GWR}=\frac{1}{8640} \sum_{j=1}^{1440} \sum_{k=1}^6 [p \cdot \hat{f}^{GWR}_{j, i} (\hat{N}^{*GWR}_{j} )-w \cdot \hat{N}^{*GWR}_{j}]$$
+where $\hat{f}^{GWR}_{j, i}(\cdot) = \hat{f}^{GWR}_j(\cdot)$ denotes the estimated yield response function by GWR (either GWRR or GWRT) at cell $(j, i)$ within subplot $j$.
 
@@
 
-$$\hat{\Delta}^{GWR} = \hat{\Pi}^{*GWR} - \hat{\Pi}^{*SCAM}$$
+$$\hat{\Delta}^{GWR} = \hat{\Pi}^{GWR} - \hat{\Pi}^{SCAM}$$
 
@@
 
-Figure \@ref(fig:pi-dif-dist) shows the distribution of $\Delta^{GWR}$, the true profit difference between the GWR-based VRA and the SCAM-based URA, at three different price scenarios which represent the historically low (5.44), middle (6.56), and high (7.67) nitrogen-corn price ratio (\$/kg : \$/kg).
-Historical corn ($p$) and nitrogen fertilizer ($w$) prices from 2002 to 2022 were obtained from the USDA National Agricultural Statistics Service (NASS, 2022) and DTN Retail Fertilizer Trends (DTN, 2022), and were transformed into monthly data.
+**(Taro:) I think we'd better to explain what "low", "middle", and "high" mean in the figure title.
+The readers can of course find them out from the main text, but it's better to explicitly show them there.
+The same applies for Figures 4, 5, 6 as well.
+Perhaps you can use the graphing codes I made for the supplementary appendix, where I added the price ratio labels in the figures.
+** Figure \@ref(fig:pi-dif-dist) shows the distribution of $\Delta^{GWR}$, the true profit difference between the GWR-based VRA and the SCAM-based URA, at three different price scenarios which represent the historically low (5.44), middle (6.56), and high (7.67) nitrogen-corn price ratio (\$/kg : \$/kg).
+Historical corn ($p$) and nitrogen fertilizer ($w$) prices from 2002 to 2022 were obtained from the USDA National Agricultural Statistics Service [@NASS2022] and DTN Retail Fertilizer Trends [@DTN2022], and were transformed into monthly data.
 The nitrogen-corn price ratios were calculated as $w/p$.
@@
 At the low price ratio of 5.44, VRA based on GWRR is no better than SCAM-based URA.
-But, when the price ratio increases to $6.56$, the median benefit of GWRR is $`r round(mean_data_value[type == "GWRR" & pLabel == "Middle", pi_diff], digits = 2)` per hectare.
+However, when the price ratio increases to $6.56$, the median benefit of GWRR is $`r round(mean_data_value[type == "GWRR" & pLabel == "Middle", pi_diff], digits = 2)` per hectare.
 At the high price ratio of 7.67, the median benefit is $`r round(mean_data_value[type == "GWRR" & pLabel == "High", pi_diff], digits = 2)` per hectare.
@@
 
-Figure \@ref(fig:bias-est-eonr) provides insights into this phenomenon, showing the distribution of the average ratio of estimated EONR to true EONR.
+**(Taro:) Wrong figure here.
+I changed it to g_eonr_bias.
+** Figure \@ref(fig:bias-est-eonr) provides insights into this phenomenon, showing the distribution of the average ratio of estimated EONR to true EONR.
 A value lower than 1 means that EONR is underestimated on average.
@@
 
-To illustrate the difference in the GWRR and GWRT outcomes, Figure \@ref(fig:true-vs-estimated-optn-gwr-r) presents for a single simulation round the estimated site-specific EONR plotted against the true site-specific EONR.
+To illustrate the difference in the GWRR and GWRT outcomes, **(Taro:) Please correct the "GWR-R" and "GWR-T" in figure title; also please show the price ratio used here (I believe it is the middle ratio) ** Figure \@ref(fig:true-vs-estimated-optn-gwr-r) presents for a single simulation round the estimated site-specific EONR plotted against the true site-specific EONR.
 The site-specific EONR estimates are both inaccurate, but differently inaccurate.
@@
 Since the estimation of the coefficient on $N^2$ is highly inaccurate, the range of estimated EONRs is much wider than the range of true site-specific EONRs.
-But, GWRT's range of EONR estimates is very narrow because the coefficient on $N^2$ is constrained to be equal across sites, making GWRT fail to capture the EONR's truea spatial heterogeneity.
+However, GWRT's range of EONR estimates is very narrow because the coefficient on $N^2$ is constrained to be equal across sites, making GWRT fail to capture the EONR's truea spatial heterogeneity.
 
@@
 Next, we examine the bias in the estimated value of GWR-based VRA.
-Figure \@ref(fig:bias-est-pi) shows the distribution of the bias in the estimation of the profit difference from GWR-based VRA and SCAM-based URA (profit difference between the GWR-based VRA and SCAM-based URA).
+Figure \@ref(fig:bias-est-pi) shows the distribution of the **(XL_changes_made) bias in the estimation of the value of GWR-based VRA ($\hat{\Delta}^{GWR} - \Delta^{GWR}$)**.
 For example, the value of 10 would mean that the estimated value of GWR-based VRA over-estimates its true value by $10 per ha.
@@
 At low price ratios, the GWRT approach displays smaller bias compared to GWRR.
-This is partially because GWRT tends to understate the heterogeneity of the site-specific yield response functions as was seen in figure \@ref(fig:true-vs-estimated-optn-gwr-r).
+This is partially because GWRT tends to understate the heterogeneity of the site-specific yield response functions as was seen in Figure \@ref(fig:true-vs-estimated-optn-gwr-r).
 As the price ratio rises, bias increases.
-This is due to the significant over-estimation of EONR by GWRT, as illustrated by figure \@ref(fig:bias-est-eonr).
+This is due to the significant over-estimation of EONR by GWRT, as illustrated by Figure \@ref(fig:bias-est-eonr).
 Unlike the GWRR approach, the distribution of the bias by the GWRT approach has a fat tail, indicating that there is a greater chance of encountering large positive bias in the estimated value of VRA over URA.
 
-Figure \@ref(fig:why-bias-many) illustrates how over-estimation of the value of VRA can occur.
+**(Taro:) Can you double check the figure?
+The values in the figure do not match the contents in the paragraph here.
+** Figure \@ref(fig:why-bias-many) illustrates how over-estimation of the value of VRA can occur.
 It shows yield response functions estimated by GWRT and estimated yields associated with the GWR-based EONR rates and SCAM-based EONR rates for 50 randomly chosen cells in a single simulation.
@@
 
-Our results clearly show that it can be dangerous to use GWR under the assumption of a quadratic functional form when the true yield-input relationship is quadratic plateau.
+Our results clearly show that it can be dangerous to use GWR under the assumption of a quadratic functional form when the true yield-input relationship is quadratic-plateau.
 @trevisan2021spatial had to choose the quadratic functional form because no readily usable statistical software or package could be used to implement nonlinear GWR.
 The only nonlinear model available at the moment is the linear-plateau GWR by @lambert2022geographically.
-Unfortunately, the estimation of the economically optimal input rate cannot be adjusted according to price using the linear-plateau model as the economically optimal input rate occurs always at the kink.
+Unfortunately, the estimation of the economically optimal input rate cannot be adjusted according to price using the linear-plateau model as the economically optimal input rate occurs always at the kink (critical input rate where yield plateau is reached).
 Given that many yield-input relationships follow quadratic-plateau functional form for many crops, it would be fruitful to develop a GWR method with quadratic-plateau functional form.
@@
 The objective of this article was to evaluate GWR with quadratic functional form when the true yield-input relationship is quadratic-plateau.
-Therefore, we evaluated GWR when under a particular kind of model misspecification.
-After the development of software then can run GWR with a quadratic-plateau model, it would be interesting to see how it performs when the true yield response to input is quadratic-plateau.
+Therefore, we evaluated GWR under a particular kind of model misspecification.
+After the development of software that can run GWR with a quadratic-plateau model, it would be interesting to see how it performs when the true yield response to input is quadratic-plateau.
 In this case, there is no functional form misspecification and the pure ability of GWR could be isolated.
@@
 ```{r fig.id = "bias-est-eonr", fig.cap = "Average bias in the estimation of EONR by GWRR and GWRT", fig.width = 6}
-# knitr::include_graphics(here::here("GitControlled/Writing/Figures/g_value.png"))
-g_value
+# knitr::include_graphics(here::here("GitControlled/Writing/Figures/g_eonr_bias.png"))
+g_eonr_bias
 ```

### 2023-07-28 Writing/supplementary_appendix.rmd
proofread and final edits

@@
 Corn prices were sourced from the USDA National Agricultural Statistics Service [@NASS2022] in monthly frequency from 2002 to 2022.
-As shown in the top panel of Figure A1, the corn prices fluctuated between \$0.07/kg and \$0.30/kg, with an average of $0.15/kg.
+As shown in the top panel of Figure A\@ref(fig:price), the corn prices fluctuated between \$0.07/kg and \$0.30/kg, with an average of $0.15/kg.
 
 Nitrogen prices were collected from two sources.
-The USDA National Agricultural Statistics Service provided yearly nitrogen fertilizer prices for the period 2002 to 2014.
+The USDA National Agricultural Statistics Service [@NASS2022] provided yearly nitrogen fertilizer prices for the period 2002 to 2014.
 The DTN Retail Fertilizer Trends [@DTN2022] provided weekly nitrogen fertilizer prices from 2015 to 2022.
@@
 Three most commonly used nitrogen fertilizer types were included: Liquid urea-ammonium nitrate with 28 percent nitrogen (UAN28), Liquid urea-ammonium nitrate with 32 percent nitrogen (UAN32), and anhydrous ammonia (ANHYD).
-All prices were all converted to the per kilogram (kg) of nitrogen basis.
-As shown in the middle panel of Figure A1, the nitrogen prices ranged from \$0.34/kg to \$2.37/kg, with an average of \$0.98/kg.
+All prices were converted to the per kilogram (kg) of nitrogen basis.
+As shown in the middle panel of Figure A\@ref(fig:price), the nitrogen prices ranged from \$0.34/kg to \$2.37/kg, with an average of \$0.98/kg.
 
-The nitrogen-corn price ratios were calculated as the nitrogen fertilizer price ($w$) divided by corn price ($p$), and the results were shown in the bottom panel of Figure A1.
-This study took the values at the 25th, 50th, and 75th percentiles of the historical monthly price ratios (pooled over the three types of nitrogen fertilizer) from 2002 to 2022.
-These three values were used to represent the low (5.44), middle (6.56), and high (7.67) price ratio scenarios.
+The nitrogen-corn price ratios were calculated as the nitrogen fertilizer price ($w$) divided by corn price ($p$), and the results were shown in the bottom panel of Figure A\@ref(fig:price).
+This study took three values at the 25th, 50th, and 75th percentiles of the historical monthly price ratios (pooled over the three types of nitrogen fertilizer) from 2002 to 2022 to represent the low (5.44), middle (6.56), and high (7.67) price ratio scenarios.
 For consistency purposes, in the profitability calculations the corn price was selected at approximately the Spring 2022 price of \$0.28/kg.
@@
 
-Figures A\@ref(fig:value-kernel-exp) through A\@ref(fig:value-kernel-tricube) show the distribution of the true economic value of GWR using four different kernels: Exponential, Boxcar, Bi-square, and Tri-cube.
+Figures A\@ref(fig:value-kernel-exp) through A\@ref(fig:value-kernel-tricube) show the distributions of the true economic value of GWR using four different kernels (Exponential, Boxcar, Bi-square, and Tri-cube):
 
 \begin{equation}
-\Delta^{GWR}=\Pi^{GWR}-\Pi^{SCAM}
+\Delta^{GWR}=\Pi^{GWR}-\Pi^{SCAM}.
 (\#eq:label)

### 2023-07-28 Codes/3_make_figures_publication.rmd
fix the issues of inconsistent description and figure on single cell bias

@@
       element_text(
-        size = 12, angle = 0, hjust = .5, vjust = -0.3, family = "Times"
+        size = 11, angle = 0, hjust = .5, vjust = -0.3, family = "Times"
       ),
@@
       element_text(
-        size = 12, angle = 90, hjust = .5, vjust = .9, family = "Times"
+        size = 11, angle = 90, hjust = .5, vjust = .9, family = "Times"
       ),
@@
       element_text(
-        size = 9, angle = 0, hjust = .5, vjust = 1.5, family = "Times"
+        size = 8, angle = 0, hjust = .5, vjust = 1.5, family = "Times"
       ),
@@
       element_text(
-        size = 9, angle = 0, hjust = 1, vjust = 0, family = "Times"
+        size = 8, angle = 0, hjust = 1, vjust = 0, family = "Times"
       ),
@@
       element_text(
-        size = 12, angle = 0, hjust = 0, vjust = 0.5, family = "Times"
+        size = 11, angle = 0, hjust = 0, vjust = 0.5, family = "Times"
       ),
@@
       element_text(
-        size = 12, angle = 0, hjust = 0, vjust = 0, family = "Times"
+        size = 11, angle = 0, hjust = 0, vjust = 0, family = "Times"
       ),
@@
     #--- strip (for faceting) ---#
-    strip.text = element_text(size = 12, family = "Times"),
+    strip.text = element_text(size = 8, family = "Times"),
     #--- plot title ---#
-    plot.title = element_text(family = "Times", face = "bold", size = 12),
+    plot.title = element_text(family = "Times", face = "bold", size = 11),
     #--- margin ---#
@@
   .[, pLabelName := "Price Ratio (N/corn)"] %>%
-  .[pRatio == 5.44, pLabel := "Low"] %>%
-  .[pRatio == 6.56, pLabel := "Middle"] %>%
-  .[pRatio == 7.67, pLabel := "High"] %>%
-  .[, pLabel := factor(pLabel, levels = c("Low", "Middle", "High"))]
-# fig.id = "pi-dif-dist",
-# fig.cap = "The value of GWR-based VRA over SCAM-based URA for GWR-R and GWR-T"
+  .[pRatio == 5.44, pLabel := "Low (5.44)"] %>%
+  .[pRatio == 6.56, pLabel := "Middle (6.56)"] %>%
+  .[pRatio == 7.67, pLabel := "High (7.67)"] %>%
+  .[, pLabel := factor(pLabel, levels = c("Low (5.44)", "Middle (6.56)", "High (7.67)"))]
 ```
@@
 ```{r}
+# fig.id = "pi-dif-dist",
+# fig.cap = "The value of GWR-based VRA over SCAM-based URA for GWR-R and GWR-T"
 mean_data_value <-
@@
   data.table() %>%
-  .[, type := ifelse(transfer == 0, "GWR-R", "GWR-T")]
+  .[, type := ifelse(transfer == 0, "GWRR", "GWRT")]
 
@@
   .[, pLabelName := "Price Ratio (N/corn)"] %>%
-  .[pRatio == 5.44, pLabel := "Low"] %>%
-  .[pRatio == 6.56, pLabel := "Middle"] %>%
-  .[pRatio == 7.67, pLabel := "High"] %>%
-  .[, pLabel := factor(pLabel, levels = c("Low", "Middle", "High"))] %>%
+  .[pRatio == 5.44, pLabel := "Low (5.44)"] %>%
+  .[pRatio == 6.56, pLabel := "Middle (6.56)"] %>%
+  .[pRatio == 7.67, pLabel := "High (7.67)"] %>%
+  .[, pLabel := factor(pLabel, levels = c("Low (5.44)", "Middle (6.56)", "High (7.67)"))] %>%
   .[, .(eonr_ratio = mean(opt_N_gwr / opt_N_scam)), by = .(type, sim, pLabel)]
@@
   readRDS() %>%
-  .[, type := ifelse(transfer == 0, "GWR-R", "GWR-T")]
+  .[, type := ifelse(transfer == 0, "GWRR", "GWRT")]
 
@@
   single_sim %>%
-  .[type == "GWR-R", ] %>%
+  .[type == "GWRR", ] %>%
   .[, .(aunit_id, b1, b2, b1_hat, b2_hat)] %>%
@@
 # est_data[sim == 1 & pn_pc == 10.35, ] %>%
-#   .[, type := ifelse(transfer == 0, "GWR-R", "GWR-T")] %>%
+#   .[, type := ifelse(transfer == 0, "GWRR", "GWRT")] %>%
 #   ggplot(data = .) +
@@
 
-# mean_data_bias[type == "GWR-T" & pLabel == 10.35, bias] %>% hist
+# mean_data_bias[type == "GWRT" & pLabel == 10.35, bias] %>% hist
 
@@
 
-set.seed(710527)
-aunit_id_ls <- sample(il_data_oe$aunit_id, 50)
-
 gwr_curv_data <-
@@
   .[, profit := pCorn * yield * 1000 - pN * N] %>%
-  .[aunit_id %in% aunit_id_ls, ]
+  .[, y_hat_gwr := (b0_hat + b1_hat * opt_N_gwr + b2_hat * opt_N_gwr^2) / 1000] %>%
+  .[, y_hat_scam := (b0_hat + b1_hat * opt_N_scam + b2_hat * opt_N_scam^2) / 1000]
+
+single_aunit <- 
+  gwr_curv_data[abs(opt_N-150) < 10, ] %>%
+  .[which.max(yield), aunit_id]
+
+set.seed(710527)
+aunit_id_ls <- c(sample(il_data_oe$aunit_id, 49), single_aunit)
+
+gwr_curv_data <- gwr_curv_data[aunit_id %in% aunit_id_ls, ]
 
@@
 point_data <-
-  il_data_oe %>%
-  .[, y_hat_gwr := (b0_hat + b1_hat * opt_N_gwr + b2_hat * opt_N_gwr^2) / 1000] %>%
-  .[, y_hat_scam := (b0_hat + b1_hat * opt_N_scam + b2_hat * opt_N_scam^2) / 1000] %>%
+  gwr_curv_data %>%
   .[aunit_id %in% aunit_id_ls, ] %>%
   .[, .(aunit_id, y_hat_gwr, y_hat_scam, opt_N_gwr, opt_N_scam)] %>%
+  unique(by = "aunit_id") %>%
   melt(id.var = "aunit_id") %>%
@@
   .[, variable := NULL] %>%
-  dcast(aunit_id + type ~ var_type, value.var = "value") %>%
+  data.table::dcast(aunit_id + type ~ var_type, value.var = "value") %>%
   .[, profit := pCorn * yield * 1000 - pN * N]
@@
 # /*+++++++++++++++++++++++++++++++++++
+
 true_curv_data <-
   il_data_oe %>%
-  .[aunit_id %in% aunit_id_ls[1], ] %>%
+  .[aunit_id %in% single_aunit, ] %>%
   expand_grid_df(., n_data) %>%
@@
 gwr_curv_data_f <-
-  gwr_curv_data[aunit_id %in% aunit_id_ls[1], ] %>%
+  gwr_curv_data[aunit_id %in% single_aunit, ] %>%
   .[, .(yield, profit, N)] %>%
@@
   il_data_oe %>%
-  .[aunit_id %in% aunit_id_ls[1], ] %>%
+  .[aunit_id %in% single_aunit, ] %>%
   .[, .(b0, b1, b2, Nk, opt_N_gwr, opt_N_scam, opt_N)] %>%
@@
 point_data_gwr <-
-  point_data[aunit_id %in% aunit_id_ls[1], ]
+  point_data[aunit_id %in% single_aunit, ]
 

### 2023-07-28 Writing/manuscript_gwr.rmd
fix the issues of inconsistent description and figure on single cell bias

@@
   #--- strip (for faceting) ---#
-  strip.text = element_text(size = 10),
+  strip.text = element_text(size = 9),
   #--- plot title ---#
@@
   .[, pLabelName := "Price Ratio (N/corn)"] %>%
-  .[pRatio == 5.44, pLabel := "Low"] %>%
-  .[pRatio == 6.56, pLabel := "Middle"] %>%
-  .[pRatio == 7.67, pLabel := "High"] %>%
-  .[, pLabel := factor(pLabel, levels = c("Low", "Middle", "High"))]
+  .[pRatio == 5.44, pLabel := "Low (5.44)"] %>%
+  .[pRatio == 6.56, pLabel := "Middle (6.56)"] %>%
+  .[pRatio == 7.67, pLabel := "High (7.67)"] %>%
+  .[, pLabel := factor(pLabel, levels = c("Low (5.44)", "Middle (6.56)", "High (7.67)"))]
 
@@
 source(here("GitControlled/Codes/3_make_figures_publication.R"))
-
 ```
@@
 We will do so using Monte Carlo simulations, which, since we define and know the true yield response function in the data generating process, allow us to measure the degree of bias.
-Unlike in @griffith2008spatial, @harris2019simulation, @paez2011simulation, and @da2016multiple, our objective is not to measure the bias in the coefficient estimation by GWR, but rather to measure economic effects^[While the environmental impacts of fertilizer management are of great social importance, for simplicity we confine our analysis to its private economic impacts.] of the statistical inaccuracy in estimating the coefficients of the model.
+Unlike in @griffith2008spatial, @harris2019simulation, @paez2011simulation, and @da2016multiple, our objective is not to measure the bias in the coefficient estimation by GWR, but rather to measure economic effects^[While the environmental impacts of fertilizer management are of great social importance, it is out of the scope of this study.] of the statistical inaccuracy in estimating the coefficients of the model.
 We show that the misspecification tends to significantly over-estimate GWR's true economic value.
@@
 The data are often used to derive fertilizer application recommendations, for example by applying comparatively simple formulas provided by university extension services (e.g., @culman2020tri).
-**XL_changes_made: (I removed the "but" here) The expense of soil sampling and analysis is also driving development of new (I added the "new" here) sensor technologies** that gather data on site-specific field and crop characteristics or proxies of those characteristics, and the conversion of those data into recommended input application rate maps (usually called "prescriptions" or "$R_x$s").
+The expense of soil sampling and analysis is also driving development of new (I added the "new" here) sensor technologies** that gather data on site-specific field and crop characteristics or proxies of those characteristics, and the conversion of those data into recommended input application rate maps (usually called "prescriptions" or "$R_x$s").
 For example, Trimble Agriculture's GreenSeeker and AgLeader's OptRx systems use optical sensors mounted on fertilizer application booms to digitally record vegetative index imagery as farm machinery is driven through fields during early crop growth stages.
@@
 The N rate unit **(XL_changes_made:) was 18m $\times$ 72m (3 cells $\times$ 12 cells, called a "plot") to accommodate the variable-rate applicator's application resolution.
-However, a 12m "transition zone" was placed between two plots (that is, a 6m "transition zone" on each end of a plot), so that when the experimental N rate changed, the harvester had 12m to "clear" and begin to record accurately on a plot with an N rate different from its predecessor's.
-That means each N "plot" consisted of five effective "subplots" for data analysis.**
+A 12m "transition zone" was placed between two plots (that is, a 6m "transition zone" on each end of a plot), so that when the experimental N rate changed, the harvester had 12m to "clear" and begin to record accurately on a plot with an N rate different from its predecessor's.
+This means that each N "plot" consists of five effective "subplots" for data analysis.
 
@@
 
-In each simulation, six trial N rates were assigned by calculating the 0%, 20%, 40%, 60%, 80%, and 100% quantiles of the simulation's true cell-specific **(XL_changes_made:) critical N rates ($\tau_{j,i})$)**.
+In each simulation, six trial N rates were assigned by calculating the 0%, 20%, 40%, 60%, 80%, and 100% quantiles of the simulation's true cell-specific  critical N rates ($\tau_{j,i})$.
 The means of these trial N rates across simulations were approximately {80, 130, 154, 184, 219, and 270} kg ha$^{-1}$, while the differences between simulations were small and negligible.
@@
 $$\Pi^{SCAM} = \frac{1}{8640} \sum_{j=1}^{1440} \sum_{k=1}^6 \big[p \cdot f_{j, i} (\hat{N}^{*SCAM})-w \cdot \hat{N}^{*SCAM}\big]$$
-**(XL_changes_made:) and profits from the GWR approach (either GWRR or GWRT) were,**
+
+and profits from the GWR approach (either GWRR or GWRT) were,
 
@@
 
-**(Taro:) I think we'd better to explain what "low", "middle", and "high" mean in the figure title.
-The readers can of course find them out from the main text, but it's better to explicitly show them there.
-The same applies for Figures 4, 5, 6 as well.
-Perhaps you can use the graphing codes I made for the supplementary appendix, where I added the price ratio labels in the figures.
-** Figure \@ref(fig:pi-dif-dist) shows the distribution of $\Delta^{GWR}$, the true profit difference between the GWR-based VRA and the SCAM-based URA, at three different price scenarios which represent the historically low (5.44), middle (6.56), and high (7.67) nitrogen-corn price ratio (\$/kg : \$/kg).
+Figure \@ref(fig:pi-dif-dist) shows the distribution of $\Delta^{GWR}$, the true profit difference between the GWR-based VRA and the SCAM-based URA, at three different price scenarios which represent the historically low (5.44), middle (6.56), and high (7.67) nitrogen-corn price ratio (\$/kg : \$/kg).
 Historical corn ($p$) and nitrogen fertilizer ($w$) prices from 2002 to 2022 were obtained from the USDA National Agricultural Statistics Service [@NASS2022] and DTN Retail Fertilizer Trends [@DTN2022], and were transformed into monthly data.
@@
 
-**(Taro:) Wrong figure here.
-I changed it to g_eonr_bias.
-** Figure \@ref(fig:bias-est-eonr) provides insights into this phenomenon, showing the distribution of the average ratio of estimated EONR to true EONR.
+Figure \@ref(fig:bias-est-eonr) provides insights into this phenomenon, showing the distribution of the average ratio of estimated EONR to true EONR.
 A value lower than 1 means that EONR is underestimated on average.
@@
 
-To illustrate the difference in the GWRR and GWRT outcomes, **(Taro:) Please correct the "GWR-R" and "GWR-T" in figure title; also please show the price ratio used here (I believe it is the middle ratio) ** Figure \@ref(fig:true-vs-estimated-optn-gwr-r) presents for a single simulation round the estimated site-specific EONR plotted against the true site-specific EONR.
+To illustrate the difference in the GWRR and GWRT outcomes, Figure \@ref(fig:true-vs-estimated-optn-gwr-r) presents for a single simulation round the estimated site-specific EONR plotted against the true site-specific EONR.
 The site-specific EONR estimates are both inaccurate, but differently inaccurate.
@@
 Next, we examine the bias in the estimated value of GWR-based VRA.
-Figure \@ref(fig:bias-est-pi) shows the distribution of the **(XL_changes_made) bias in the estimation of the value of GWR-based VRA ($\hat{\Delta}^{GWR} - \Delta^{GWR}$)**.
+Figure \@ref(fig:bias-est-pi) shows the distribution of the bias in the estimation of the value of GWR-based VRA ($\hat{\Delta}^{GWR} - \Delta^{GWR}$).
 For example, the value of 10 would mean that the estimated value of GWR-based VRA over-estimates its true value by $10 per ha.
@@
 
-**(Taro:) Can you double check the figure?
-The values in the figure do not match the contents in the paragraph here.
-** Figure \@ref(fig:why-bias-many) illustrates how over-estimation of the value of VRA can occur.
+Figure \@ref(fig:why-bias-many) illustrates how over-estimation of the value of VRA can occur.
 It shows yield response functions estimated by GWRT and estimated yields associated with the GWR-based EONR rates and SCAM-based EONR rates for 50 randomly chosen cells in a single simulation.
@@
 Figure \@ref(fig:why-bias-single) focuses on a single cell and compares estimated and true yields between GWR and SCAM (panel (a)) and estimated and true profits between GWR and SCAM (panel (b)).
-The cell's true yield response functions plateaus at a nitrogen rate of about $140$ kg ha$^{-1}$, but the GWR-estimated yield response function suggests that yield should peak at a nitrogen rate of about $190$ kg ha$^{-1}$ and decline thereafter.
-In reality, the yield differential between GWR and SCAM is 0, while the estimated yield differential is about $0.25$ ton ha$^{-1}$, leading to the over-estimation of the value of GWR in panel (b).
-Based on the true profit response curve, applying the GWR-based recommendation is about \$`r round(- true_yield_data[type != "True", diff(profit)], digits = 0)` ha$^{-1}$ more profitable than applying the SCAM-based recommendation.
+The cell's true yield response functions plateaus at a nitrogen rate of about $`r round(il_data_oe[aunit_id %in% single_aunit, Nk], digits = 0)`$ kg ha$^{-1}$, but the GWR-estimated yield response function suggests that yield should peak at a nitrogen rate of about $`r round(point_data_gwr[type == "GWR", N], digits = 0)`$ kg ha$^{-1}$ and decline thereafter.
+In reality, the yield differential between GWR and SCAM is 0, while the estimated yield differential is about `r round(point_data_gwr[type == "GWR", yield] - point_data_gwr[type == "SCAM", yield], digits = 2)` ton ha$^{-1}$, leading to the over-estimation of the value of GWR in panel (b).
+Based on the true profit response curve, applying the GWR-based recommendation is about \$`r round(- true_yield_data[type != "True", diff(profit)], digits = 0)` ha$^{-1}$ "less" profitable than applying the SCAM-based recommendation.
 This profit differential comes solely from the difference in nitrogen cost since GWR and SCAM yields are equal.
@@
 
-```{r fig.id = "true-vs-estimated-optn-gwr-r", fig.cap = "Comparison of Estimated and True EONR", fig.width = 6}
+```{r fig.id = "true-vs-estimated-optn-gwr-r", fig.cap = "Comparison of Estimated and True EONR at the middle price ratio of 6.56", fig.width = 6}
 # knitr::include_graphics(here::here("GitControlled/Writing/Figures/g_comp_eonr.png"))

### 2023-07-28 Codes/3_make_figures_publication.R

@@ -1,22 +1,22 @@
-## ------------------------------
+## -----------------------------------------------------
 theme_fig <-
   theme_bw() +
   theme(
     axis.title.x =
       element_text(
-        size = 12, angle = 0, hjust = .5, vjust = -0.3, family = "Times"
+        size = 11, angle = 0, hjust = .5, vjust = -0.3, family = "Times"
       ),
     axis.title.y =
       element_text(
-        size = 12, angle = 90, hjust = .5, vjust = .9, family = "Times"
+        size = 11, angle = 90, hjust = .5, vjust = .9, family = "Times"
       ),
     axis.text.x =
       element_text(
-        size = 9, angle = 0, hjust = .5, vjust = 1.5, family = "Times"
+        size = 8, angle = 0, hjust = .5, vjust = 1.5, family = "Times"
       ),
     axis.text.y =
       element_text(
-        size = 9, angle = 0, hjust = 1, vjust = 0, family = "Times"
+        size = 8, angle = 0, hjust = 1, vjust = 0, family = "Times"
       ),
     axis.ticks =
       element_line(
@@ -26,17 +26,17 @@ theme_fig <-
     #--- legend ---#
     legend.text =
       element_text(
-        size = 12, angle = 0, hjust = 0, vjust = 0.5, family = "Times"
+        size = 11, angle = 0, hjust = 0, vjust = 0.5, family = "Times"
       ),
     legend.title =
       element_text(
-        size = 12, angle = 0, hjust = 0, vjust = 0, family = "Times"
+        size = 11, angle = 0, hjust = 0, vjust = 0, family = "Times"
       ),
     legend.key.size = unit(0.5, "cm"),
     #--- strip (for faceting) ---#
-    strip.text = element_text(size = 12, family = "Times"),
+    strip.text = element_text(size = 8, family = "Times"),
     #--- plot title ---#
-    plot.title = element_text(family = "Times", face = "bold", size = 12),
+    plot.title = element_text(family = "Times", face = "bold", size = 11),
[…]

### 2023-07-28 Writing/manuscript_gwr.rmd
final proofread and typo corrections

@@
 The first is to estimate a "map" of the field characteristics, for example thought of as a set of the field's $n \geq 1$ sites' values of the characteristics vector: $\{\textbf{c}_1,\dots, \textbf{c}_n\}$.
-With that map, regressing yield on $\textbf{x}$ and $\textbf{c}$ generates an estimated "field-specific" yield response function $\hat{f}_(\textbf{x},\textbf{c})$.
+With that map, regressing yield on $\textbf{x}$ and $\textbf{c}$ generates an estimated "field-specific" yield response function $\hat{f}(\textbf{x},\textbf{c})$.
 Estimates of site-specific yield response functions can then be obtained by inserting the value of the site's characteristic variables into the estimate of the field-specific response function: $\hat{f}_i(\textbf{x}) \equiv \hat{f}(\textbf{x},\textbf{c}_i)$.
-Alternatively, a site-specific yield response function might be estimated simply by taking (input rate, yield) data from points around a site of interest, and regressing yield on input application rates to attain the estimate $\tilde{f}_i (\textbf{x})$.
+Alternatively, a site-specific yield response function might be estimated simply by taking (input rate, yield) data from points around a site of interest, and regressing yield on input application rates to attain the estimate $\hat{f}_i (\textbf{x})$.
 Stated roughly, using GWR takes the latter approach, which has the advantage of not needing a costly map of field characteristics values.
@@
 
-where $c_{j,i} = (\alpha_{j,i},\beta_{j,i},\gamma_{j,i},\tau_{j,i})$ is the vector of yield response function parameters.
+where $\textbf{c}_{j,i} = (\alpha_{j,i},\beta_{j,i},\gamma_{j,i},\tau_{j,i})$ is the vector of yield response function parameters.
 $\tau_{j,i}$ can be interpreted as the critical value of N rate at which cell $(j, i)$'s yield reaches its plateau, where yield no longer increases with N rate.
@@
 The quadratic-plateau functional form implies a diminishing marginal product of N until a yield plateau, which are desirable properties for a yield response function [@frank1990comparison] and a pattern commonly observed in agronomic studies.
-Note that the cell-specific yield response function $f_{j, i} (N)$ is the reduced form of the meta response function $f$ when the characteristics vector takes on the value $c_{j, i}$.
+Note that the cell-specific yield response function $f_{j, i} (N)$ is the reduced form of the meta response function $f$ when the characteristics vector takes on the value $\textbf{c}_{j, i}$.
 In other words, all the soil or field properties that could affect yield response to N are embedded in the simulated parameters.
@@
 In each simulation, for each cell $(j, i)$, the simulation's true yield $y_{j, i}$ was generated based on the cell's assigned application rate $N_{j,i}$, true response parameters $\textbf{c}_{j,i} = (\alpha_{j,i}, \beta_{j,i}, \gamma_{j,i}, \tau_{j,i})$, and error term $\varepsilon_{j,i}$.
-This procedure generated a field-level, cell-specific data set, $\{(y_{j, i},N_{j, i} ):j=1,\dots,1440;k=1,\dots, 6 \}$.
+This procedure generated a field-level, cell-specific data set, $\{(y_{j, i},N_{j, i} ):j=1,\dots,1440;i=1,\dots, 6 \}$.
 To maintain consistency with real-world OFPEs, it was assumed that harvesting equipment could only record yields accurately at an 18m $\times$ 12m (subplot) resolution.
@@
 
-$$\hat{N}^{*SCAM} \equiv argmax_N⁡ \big[p\cdot \hat{f}^{SCAM} (N)-w\cdot N\big]$$
+$$\hat{N}^{*SCAM} \equiv argmax_N⁡ \big[p\cdot \hat{f}^{SCAM} (N)-w\cdot N\big].$$
 
@@
 
-$$y_j= \alpha_j+ \beta N_j + \eta N_j^2+ \varepsilon_j ,$$
+$$y_j= \alpha_j+ \beta_j N_j + \eta N_j^2+ \varepsilon_j ,$$
 
@@
 To estimate the bias in the estimation of the economic value of GWR-based VRA, the true per-ha net revenues ("profits") of the SCAM-based URA and GWR-based VRA were calculated by substituting the estimated optimal nitrogen rates into the "true" yield response functions.
-Profits from the SCAM approach were
+Profits from the SCAM approach were:
 
-$$\Pi^{SCAM} = \frac{1}{8640} \sum_{j=1}^{1440} \sum_{k=1}^6 \big[p \cdot f_{j, i} (\hat{N}^{*SCAM})-w \cdot \hat{N}^{*SCAM}\big]$$
+$$\Pi^{SCAM} = \frac{1}{8640} \sum_{j=1}^{1440} \sum_{i=1}^6 \big[p \cdot f_{j, i} (\hat{N}^{*SCAM})-w \cdot \hat{N}^{*SCAM}\big]$$
 
-and profits from the GWR approach (either GWRR or GWRT) were,
+and profits from the GWR approach (either GWRR or GWRT) were:
 
-$$\Pi^{GWR}=\frac{1}{8640} \sum_{j=1}^{1440} \sum_{k=1}^6 [p \cdot f_{j, i} (\hat{N}^{*GWR}_j)-w \cdot \hat{N}^{*GWR}_j]$$
+$$\Pi^{GWR}=\frac{1}{8640} \sum_{j=1}^{1440} \sum_{i=1}^6 [p \cdot f_{j, i} (\hat{N}^{*GWR}_j)-w \cdot \hat{N}^{*GWR}_j]$$
 
@@
 
-$$\hat{\Pi}^{SCAM} = \frac{1}{8640} \sum_{j=1}^{1440} \sum_{k=1}^6 \big[p \cdot \hat{f}^{GWR}_{j, i} (\hat{N}^{*SCAM} )-w \cdot \hat{N}^{*SCAM}\big]$$
+$$\hat{\Pi}^{SCAM} = \frac{1}{8640} \sum_{j=1}^{1440} \sum_{i=1}^6 \big[p \cdot \hat{f}^{GWR}_{j, i} (\hat{N}^{*SCAM} )-w \cdot \hat{N}^{*SCAM}\big]$$
 
-$$\hat{\Pi}^{GWR}=\frac{1}{8640} \sum_{j=1}^{1440} \sum_{k=1}^6 [p \cdot \hat{f}^{GWR}_{j, i} (\hat{N}^{*GWR}_{j} )-w \cdot \hat{N}^{*GWR}_{j}]$$
+$$\hat{\Pi}^{GWR}=\frac{1}{8640} \sum_{j=1}^{1440} \sum_{i=1}^6 [p \cdot \hat{f}^{GWR}_{j, i} (\hat{N}^{*GWR}_{j} )-w \cdot \hat{N}^{*GWR}_{j}]$$
 where $\hat{f}^{GWR}_{j, i}(\cdot) = \hat{f}^{GWR}_j(\cdot)$ denotes the estimated yield response function by GWR (either GWRR or GWRT) at cell $(j, i)$ within subplot $j$.
 
-The estimated value of the GWR-based VRA compared to the SCAM-based URA is defined as
+The estimated value of the GWR-based VRA compared to the SCAM-based URA is defined as:
 
-$$\hat{\Delta}^{GWR} = \hat{\Pi}^{GWR} - \hat{\Pi}^{SCAM}$$
+$$\hat{\Delta}^{GWR} = \hat{\Pi}^{GWR} - \hat{\Pi}^{SCAM}.$$
 
-The bias in the estimation of the value of GWR-based VRA was calculated as follows:
+Finally, the bias in the estimation of the value of GWR-based VRA was calculated as follows:
 
-$$bias = \hat{\Delta}^{GWR} - \Delta^{GWR}$$
+$$bias = \hat{\Delta}^{GWR} - \Delta^{GWR}.$$
 
@@
 
-```{r, fig.id = "pi-dif-dist", fig.cap = "The value of GWR-based VRA over SCAM-based URA for GWRR and GWRT", out.width = "6.5in", fig.width = 6}
+```{r, fig.id = "pi-dif-dist", fig.cap = "The true economic value of GWR-based VRA over SCAM-based URA by two GWR models (GWRR and GWRT) and at three nitrogen-corn price ratios", out.width = "6.5in", fig.width = 6}
 # knitr::include_graphics(here::here("GitControlled/Writing/Figures/g_value.png"))
@@
 
-```{r fig.id = "bias-est-eonr", fig.cap = "Average bias in the estimation of EONR by GWRR and GWRT", fig.width = 6}
+```{r fig.id = "bias-est-eonr", fig.cap = "Average bias in the estimation of EONR by two GWR models (GWRR and GWRT) and at three nitrogen-corn price ratios", fig.width = 6}
 # knitr::include_graphics(here::here("GitControlled/Writing/Figures/g_eonr_bias.png"))
@@
 
-```{r fig.id = "true-vs-estimated-optn-gwr-r", fig.cap = "Comparison of Estimated and True EONR at the middle price ratio of 6.56", fig.width = 6}
+```{r fig.id = "true-vs-estimated-optn-gwr-r", fig.cap = "Comparison of GWR-Estimated and True EONR at the middle price ratio of 6.56", fig.width = 6}
 # knitr::include_graphics(here::here("GitControlled/Writing/Figures/g_comp_eonr.png"))
@@
 
-```{r fig.id = "bias-est-pi", fig.cap = "Bias in the estimation of the value of GWR-based VRA over SCAM-based URA for GWRR and GWRT", fig.width = 6}
+```{r fig.id = "bias-est-pi", fig.cap = "Bias in the estimation of the value of GWR-based VRA over SCAM-based URA by two GWR models (GWRR and GWRT) and at three nitrogen-corn price ratios", fig.width = 6}
 # knitr::include_graphics(here::here("GitControlled/Writing/Figures/g_bias.png"))

### 2023-07-28 Writing/manuscript_gwr.rmd
minor edits

--- 2023-07-28 Writing/manuscript_gwr.rmd
@@
 The data are often used to derive fertilizer application recommendations, for example by applying comparatively simple formulas provided by university extension services (e.g., @culman2020tri).
-The expense of soil sampling and analysis is also driving development of new (I added the "new" here) sensor technologies** that gather data on site-specific field and crop characteristics or proxies of those characteristics, and the conversion of those data into recommended input application rate maps (usually called "prescriptions" or "$R_x$s").
+The expense of soil sampling and analysis is also driving development of new sensor technologies that gather data on site-specific field and crop characteristics or proxies of those characteristics, and the conversion of those data into recommended input application rate maps (usually called "prescriptions" or "$R_x$s").
 For example, Trimble Agriculture's GreenSeeker and AgLeader's OptRx systems use optical sensors mounted on fertilizer application booms to digitally record vegetative index imagery as farm machinery is driven through fields during early crop growth stages.
@@
 Therefore, the yield data's resolution was 18m $\times$ 12m (3 cells $\times$ 2 cells, called a "subplot").
-The N rate unit **(XL_changes_made:) was 18m $\times$ 72m (3 cells $\times$ 12 cells, called a "plot") to accommodate the variable-rate applicator's application resolution.
+The N rate unit was 18m $\times$ 72m (3 cells $\times$ 12 cells, called a "plot") to accommodate the variable-rate applicator's application resolution.
 A 12m "transition zone" was placed between two plots (that is, a 6m "transition zone" on each end of a plot), so that when the experimental N rate changed, the harvester had 12m to "clear" and begin to record accurately on a plot with an N rate different from its predecessor's.
@@
 In reality, the yield differential between GWR and SCAM is 0, while the estimated yield differential is about `r round(point_data_gwr[type == "GWR", yield] - point_data_gwr[type == "SCAM", yield], digits = 2)` ton ha$^{-1}$, leading to the over-estimation of the value of GWR in panel (b).
-Based on the true profit response curve, applying the GWR-based recommendation is about \$`r round(- true_yield_data[type != "True", diff(profit)], digits = 0)` ha$^{-1}$ "less" profitable than applying the SCAM-based recommendation.
+Based on the true profit response curve, applying the GWR-based recommendation is about \$`r round(true_yield_data[type != "True", diff(profit)], digits = 0)` ha$^{-1}$ "less" profitable than applying the SCAM-based recommendation.
 This profit differential comes solely from the difference in nitrogen cost since GWR and SCAM yields are equal.

### 2023-07-28 Writing/JAAEA/1stRoundRevision/reply_to_editor_page#.txt
JAAEA re-submission; there are still some errors in the RMD file; final clean version is jaaea-2023-02-0015.R1_Proof_hi.pdf

--- 2023-07-24 Writing/JAAEA/1stRoundRevision/reply_to_editor.rmd
@@
----
-output:
-  html_document: default
-bibliography: PA.bib
----
-# Reply to the editor
+******   Reply to the editor   ******
 
-Thank you for your thoughtful comments. Addressing them has made our paper much stronger. Below, your comments are in blue, and our responses are in black.
+Thank you for your thoughtful comments. Addressing them has made our paper much stronger. Below are our detailed answers to your comments.
 
-<span style = "color: blue;"> Based on the reviews and your email response, I have decided to give you the opportunity to revise the manuscript and respond to reviewer comments.
+Comments:
+
+Based on the reviews and your email response, I have decided to give you the opportunity to revise the manuscript and respond to reviewer comments.
 One major point is that your true DGP assumed a quadratic plateau, but the estimated models use quadratic.
@@
 If the dominant approach in recent literature is to use quadratic functions, then it does seem valuable to quantify the bias from using quadratic rather than quadratic plateau.
-Please document clearly in the manuscript that quadratic is the common practice (__point 1__).
-However, the title of your paper is about an economic evaluation of GWR analysis, and the choice of quadratic or quadratic-plateau is not an issue with GWR and this needs to be clear (__point 2__).
-Also reading through your discussion section, the implications are primarily framed about how GWR performed, but it might completely be an issue with functional form, but the current simulations don't inform us about the source of bias.
-Ideally, you would compare a GWR model that is quadratic with a GWR model that is quadratic-plateau functional form (__point 3__).
-</span>
+Please document clearly in the manuscript that quadratic is the common practice (point 1).
+However, the title of your paper is about an economic evaluation of GWR analysis, and the choice of quadratic or quadratic-plateau is not an issue with GWR and this needs to be clear (point 2).
+Also reading through your discussion section, the implications are primarily framed about how GWR performed, but it might completely be an issue with functional form, but the current simulations don’t inform us about the source of bias.
+Ideally, you would compare a GWR model that is quadratic with a GWR model that is quadratic-plateau functional form (point 3).
 
-Reply to <span style = "color: blue;"> __point 1__ </span>:
+Reply to point 1 :
 
-Actually, the dominant functional form used in the literature is quadratic-plateau for <span style = "color: red;"> non-</span>GWR (regualr parametric) regression because a agronomists have come to a consensus  that it better represents the corn-nitrogen relationship.
+Actually, the dominant functional form used in the literature is quadratic-plateau for non-GWR (regualr parametric) regression because a agronomists have come to a consensus that it better represents the corn-nitrogen relationship.
 Application of GWR is very new to the field, and no available software packages allow the user to conduct GWR assuming response functions that are non-linear in their parameters at the moment.
@@
 We are showing this can be dangerous with GWR, as it is in more traditional regression frameworks.
-Our paper's message is important--without understanding our evidence and arguments, practitioners or researchers could believe that GWR can provide more than it really can.
+Our paper’s message is important–without understanding our evidence and arguments, practitioners or researchers could believe that GWR can provide more than it really can.
 One of our conclusions is that it is important for someone to develop a tool in a statistical package that allows application of GWR while modeling yield-input relationships more flexibly.
 
-Reply to <span style = "color: blue;"> __point 2__ </span>:
+Reply to point 2 :
 
@@
 
-Reply to <span style = "color: blue;"> __point 3__ </span>:
+Reply to point 3 :
 
@@
 
-<span style = "color: blue;"> Revierw #1's other major critique is that the “true” data generation process (DGP) of the parameters does not correspond with a GWR.
-For example, reviewer #1 argues that the spatial distribution of parameters described in the original manuscript's lines 173-193 does not correspond with a GWR DGP.
+Comments:
+
+Revierw #1’s other major critique is that the “true” data generation process (DGP) of the parameters does not correspond with a GWR.
+For example, reviewer #1 argues that the spatial distribution of parameters described in the original manuscript’s lines 173-193 does not correspond with a GWR DGP.
 Is there evidence from the agronomy literature that the DGP (aside from the functional form assumption) follows the process that you specify?
 Or alternatively, is there evidence from the agronomy literature that the DGP does not follow the GWR DGP described by reviewer #1 in comment #5?
-My guess is that the agronomy literature has little or nothing to say about this (compared to the functional form assumption), but maybe I'm wrong about that.
-If there is no evidence to support your proposed DGP or the GWR DGP as “true,” then it is difficult to critique GWR for not correctly estimating your proposed DGP (__specific point 1__).
+My guess is that the agronomy literature has little or nothing to say about this (compared to the functional form assumption), but maybe I’m wrong about that.
+If there is no evidence to support your proposed DGP or the GWR DGP as “true,” then it is difficult to critique GWR for not correctly estimating your proposed DGP (specific point 1).
 In your email response you state “Our choice of true yield response function is deliberate and just as valid as the data generating process Reviewer #1 recommends.” But if the DGP that you used and the DGP recommended by reviewer #1 are equally valid, then why critique GWR for not correctly estimating your DGP?
-To critique GWR, you need to argue that your DGP is more valid than the GWR DGP (__specific point 2__).
+To critique GWR, you need to argue that your DGP is more valid than the GWR DGP (specific point 2).
 Or you can estimate if GWR is robust to alternative, but equally valid, DGPs.
 
-</span>
+Reply:
 
@@
 
-Second, while the DGPs may look complicated, close inspection shows that, other than the functional forms assumed, our DGP and Reviewer 1's suggested DGP are not as different as they may first appear.
+Second, while the DGPs may look complicated, close inspection shows that, other than the functional forms assumed, our DGP and Reviewer 1’s suggested DGP are not as different as they may first appear.
 The reviewer suggested the following:
 
-$$
-\begin{aligned}
-y^* = X(X'W(s)X)^{-1}X'W(s)y + e^*
-\end{aligned}
-$$
+y∗=X(X′W(s)X)^{−1}X′W(s)y+e∗
 
@@
 
-$$
-\begin{aligned}
-y_i = X_i\beta_i + e_i
-\end{aligned}
-$$
+yi=Xiβi+ei,
 
-, where $(X'W(s)X)^{-1}X'W(s)y = \beta$.
+where (X′W(s)X)^{−1}X′W(s)y=β.
 As shown in Leung, Y., Mei, C.
@@
 X.
-(2000),  $\beta_i$ is the coefficient specific to observation $i$.
-$W(s)$ ensures that $\beta$ are spatially correlated.
-The choice of $W(s)$ is arbitrary, and and there for it could be fairly called "cheating" to use the same $W(s)$ in the DGP and for the GWR both.
-This method gives an unfair advantage to GWR because the researcher cannot know the real $W(s)$.
+(2000), βi is the coefficient specific to observation i.
+W(s) ensures that β are spatially correlated.
+The choice of W(s) is arbitrary, and and there for it could be fairly called “cheating” to use the same W(s) in the DGP and for the GWR both.
+This method gives an unfair advantage to GWR because the researcher cannot know the real W(s).
 The situation is much like the one created becauase the researcher does not know the true weight matrix in spatial econometric approaches.
-This can only be called the "correct" GWR DGP only when $W(s)$ is known a priori.
+This can only be called the “correct” GWR DGP only when W(s) is known a priori.
 
-In our DGP, we generate spatially correlated parameters (alpha, ...
-in equation ) for individual $i$.
+In our DGP, we generate spatially correlated parameters (alpha, beta, tau, … in equation) for individual i.
 (Reviewer 1 was under the impression that these parameters were not spatially correlated, but indeed they are.) So, aside from the functional form, the only difference in our DGPs is in the spatial pattern of parameters.
-It is much as if we were are using a $W(s)$ different from in the above equation, which is an arbitrary parameter chosen by the researcher running MC simulations in the first place.
-In this sense, our DGP is just as "valid" as the GWR DGP.
+It is much as if we were are using a W(s) different from in the above equation, which is an arbitrary parameter chosen by the researcher running MC simulations in the first place.
+In this sense, our DGP is just as “valid” as the GWR DGP.
 
-In fact, we believe that our DGP is $superior$ to the the one suggested by Reviewer 1 because ours is more flexible.
-The DGP suggested by the Reviewer 1 cannot accommodate non-linear models, while our DGP can use any functional relationship between $Y$ and $X$.
-This is critical to our study because the DGP <span style = "color: red;"> needs </span> to include the quadratic-plateau functional form to better represent the actual functional relationship exhibited by corn-nitogen response.
+In fact, we believe that our DGP is superior to the the one suggested by Reviewer 1 because ours is more flexible.
+The DGP suggested by the Reviewer 1 cannot accommodate non-linear models, while our DGP can use any functional relationship between Y and X.
+This is critical to our study because the DGP needs to include the quadratic-plateau functional form to better represent the actual functional relationship exhibited by corn-nitogen response.
 
-You are right that no agronomic studies have examined whether our DGP or Reviewer 1's is superior.
-But whereas Reviewer 1's DGP has never been applied in the context of precision agriculture, ours has been used in several articles in prominent, peer-reviewed agronomy and precision agriculture journal [@kakimoto2022causal; @li2023economic].
-Of course, we are not claiming that our DGP is "correct."  But it is not inferior to the reviewer's DGP, and we have elected to keep it in our study.
+You are right that no agronomic studies have examined whether our DGP or Reviewer 1’s is superior.
+But whereas Reviewer 1’s DGP has never been applied in the context of precision agriculture, ours has been used in several articles in prominent, peer-reviewed agronomy and precision agriculture journal (Kakimoto et al.
+2022; Li, Mieno, and Bullock 2023).
+Of course, we are not claiming that our DGP is “correct.” But it is not inferior to the reviewer’s DGP, and we have elected to keep it in our study.
 
-We take responsibility for the poor communication in our original manuscript that generated much of Reviewer 1's poor understanding of our study's methods and motivations.
-Reviewer 1's thought that our principal abjectives were test GWR itself and to test the accuracy in parameter estimation accuracy.
+We take responsibility for the poor communication in our original manuscript that generated much of Reviewer 1’s poor understanding of our study’s methods and motivations.
+Reviewer 1’s thought that our principal abjectives were test GWR itself and to test the accuracy in parameter estimation accuracy.
 We believe that in the revised manuscript we have made clear that our goal is to examine the economic effects of using GWR under misspecification of the yield response function.
 
-Reply to <span style = "color: blue;"> __specific point 1__ </span>:
+Reply to specific point 1 :
 
-When using the GWR DGP, the researcher cannot know the "true" $W(s)$ matrix, and therefore misspecifying the underlying DGP is unavoidable.
-It is not possible to use the "correct" DGP, regardless of whether the underlying model is estimated with GWR.
+When using the GWR DGP, the researcher cannot know the “true” W(s) matrix, and therefore misspecifying the underlying DGP is unavoidable.
+It is not possible to use the “correct” DGP, regardless of whether the underlying model is estimated with GWR.
 The point of our article is to point out the importance of the functional form assumption when GWR is used.
-If we were to follow Reviewer 1's suggestion that we use quadratic functional form as our true yield-nitrogen response, the whole point of the paper whould be lost.
+If we were to follow Reviewer 1’s suggestion that we use quadratic functional form as our true yield-nitrogen response, the whole point of the paper whould be lost.
 
@@
 
-Reply to <span style = "color: blue;"> __specific point 2__ </span>:
+Reply to specific point 2 :
 
@@
 This is not to say, GWR is always bad.
-But, it is enough to warrant researchers and practitioners that GWR <span style = "color: red;"> may </span> fail.
-If we show that GWR does not work well with "a" valid DGP, then it is enought to warn people about its potential danger.
+But, it is enough to warrant researchers and practitioners that GWR may fail.
+If we show that GWR does not work well with “a” valid DGP, then it is enought to warn people about its potential danger.
 
-<span style = "color: blue;"> In general, it is important in your paper to clarify how much of the bias you estimate is due to the functional form assumption versus the assumption about the DGP.
+Comments:
+
+In general, it is important in your paper to clarify how much of the bias you estimate is due to the functional form assumption versus the assumption about the DGP.
 Also, you need to more clearly defend the DGP you choose as the “true” DGP or compare results with alternative DGPs.
 It seems to me that you will need to rethink your simulations so that you can more clearly sort out the sources of bias.
-</span>
 
@@
 We are criticizing the practice that has been used by researchers that can give a false impression about how valuable GWR is in providing information for variable rate nitrogen application management in the OFPE setting.
+
+References:
+
+Kakimoto, Shunkei, Taro Mieno, Takashi ST Tanaka, and David S Bullock.
+2022.
+“Causal Forest Approach for Site-Specific Input Management via on-Farm Precision Experimentation.” Computers and Electronics in Agriculture 199: 107164.
+Li, Xiaofei, Taro Mieno, and David S Bullock. 2023. “The Economic Performances of Different Trial Designs in on-Farm Precision Experimentation: A Monte Carlo Evaluation.” Precision Agriculture, 1–22.

### 2023-07-28 Writing/JAAEA/1stRoundRevision/reply_to_reviewer_2_page#.txt
JAAEA re-submission; there are still some errors in the RMD file; final clean version is jaaea-2023-02-0015.R1_Proof_hi.pdf

--- 2023-07-28 Writing/JAAEA/1stRoundRevision/reply_to_reviewer_2.rmd
@@
----
-title: "Reply"
-output: 
-  html_document:
-    theme:
-      version: 4
-bibliography: PA.bib
----
+Reply to Reviewer 2:
 
-Your comments are in blue, and our responses are in black.
-
-<span style = "color: blue;">This study examines the economic value associated with three statistical methods used to generate site-specific nitrogen application rates: 1) geographically weighted regressions using the method of Rakshit et al.
+This study examines the economic value associated with three statistical methods used to generate site-specific nitrogen application rates: 1) geographically weighted regressions using the method of Rakshit et al.
 (2020) denoted as GWR-R, 2) geographically weighted regressions using the method of Trevisan et al.
@@
 For convenience, my review below is organized into a set of general comments, specific comments, and comments related to the exposition and writing, with each being arranged in order of page number.
-All comments are designed to strengthen the research.</span>
+All comments are designed to strengthen the research.
 
-We would like to express our sincere gratitude for the reviewer's careful examination and critique of our manuscript.
-The insightful comments and suggestions have significantly contributed to the paper's clarity, detail, and overall strength.
+Reply: We would like to express our sincere gratitude for the reviewer’s careful examination and critique of our manuscript.
+The insightful comments and suggestions have significantly contributed to the paper’s clarity, detail, and overall strength.
 In return, we have attempted to carefully address each of the comments and revise the manuscript in response.
 
-<br>
+General Comments
 
-## <span style = "color: blue;">General Comments</span>
+To some extent, this research is related to studies that examine the “value” of forecasting models by assessing their measure of inaccuracy.
+Given that determining the value of general regression methodologies is not overly common in the relevant literature here, why not add 1-2 paragraphs that ties your study to other studies that measure the “value” of certain econometric techniques?
 
-<span style = "color: blue;">To some extent, this research is related to studies that examine the "value" of forecasting models by assessing their measure of inaccuracy.
-Given that determining the value of general regression methodologies is not overly common in the relevant literature here, why not add 1-2 paragraphs that ties your study to other studies that measure the "value" of certain econometric techniques?
-</span>
-
-Thank you for bringing up this important point.
+Reply: Thank you for bringing up this important point.
 What makes this study differ from previous studies is that the model “value” is not measured by the statistical accuracy of parameter estimates, but rather by the ultimate economic return.
 To emphasize this aspect, we have included an additional paragraph in the “5.
-Discussion and Conclusions” section (paragraph 2).
+Discussion and Conclusions” section (page 22, lines 419-432).
 It is worth noting that we are unable to identify a specific body of literature that exclusively focuses on assessing the value of general regression models.
@@
 
-<span style = "color: blue;">One of the most important questions in the literature relates to how variable rate technologies (VRT) can reduce negative externalities like fertilizer and chemical runoff and leaching.
+One of the most important questions in the literature relates to how variable rate technologies (VRT) can reduce negative externalities like fertilizer and chemical runoff and leaching.
 Clearly, this is not the research objective, and addressing a much more burning question in the literature would involve additional terms in the equation on p.
 10, line 294 that represent the negative environmental externalities.
-The authors should clarify early on that "economically optimal" means "privately optimal" rather than "socially optimal."</span>
+The authors should clarify early on that “economically optimal” means “privately optimal” rather than “socially optimal.”
 
-Thank you for the suggestion.
-We have explicitly stated the following in a footnote at the end of the Introduction section of the revised manuscript: *"While the environmental impacts of fertilizer management are of great social importance, for simplicity we confine our analysis to its private economic impacts."*
+Reply: Thank you for the suggestion.
+We have explicitly stated the following in a footnote at the end of the Introduction section of the revised manuscript (page 5): “While the environmental impacts of fertilizer management are of great social importance, for simplicity we confine our analysis to its private economic impacts.”
 
-<span style = "color: blue;">It strikes me as odd that, even with a minor clause on line 207 of p.
+It strikes me as odd that, even with a minor clause on line 207 of p.
 10, there is no real discussion of the corn price or nitrogen price in the methods section.
@@
 What is the underlying intuition regarding the dependence of the relative performance of GWRR/GWRT to the corn-to-nitrogen price ratio (though this is partially explained in the paragraph on pages 15-16)?
-Any intuition about the ratios of 4.2, 5.4, and 10.4?</span>
+Any intuition about the ratios of 4.2, 5.4, and 10.4?
 
-Thank you for bringing up this point.
-We have included a brief discussion of the historical corn and nitrogen prices in the first paragraph of the Results section 4.1.
+Reply: Thank you for bringing up this point.
+We have included a brief discussion of the historical corn and nitrogen prices in the first paragraph of the Results section 4.1 (page 18, lines 336-343).
 Additionally, we have included Appendix I: Historical Corn and Nitrogen Prices in the supplementary material to provide a more detailed description of the collection, calculation, and summary statistics of the historical price data.
@@
 The correct price ratios 5.44, 6.56, and 7.67 are used in the revised manuscript.
-The intuition underlying the dependence of the relative performances of GWRR and GWRT to the nitrogen-corn price ratio was explained in the paragraphs on pages 15-16 of the original manuscript, and that discussion has been included in the revised manuscript.
-The main difference arises from the models' specifications of the coefficient on $N^2$.
-The GWRR model allows for varying coefficient on $N^2$, leading to a wider range of estimated EONRs, while the GWRT model restricts the coefficient on $N^2$ to be constant, leading to a narrower range of estimated EONRs.
-When nitrogen is expensive relative to corn, the true range of EONRs should be larger, and therefore the economic penalty of GWRR's over-estimation of EONR range will be smaller.
-When the nitrogen-corn price ratio is lower, the true EONR range will be smaller, and GWRT's under-estimation of the EONR range is less of an issue.
-At the reviewer's request, we will be happy to further enhance the manuscript's discussion of this topic.
+The intuition underlying the dependence of the relative performances of GWRR and GWRT to the nitrogen-corn price ratio was explained in the paragraphs on pages 15-16 of the original manuscript, and that discussion has been included in the revised manuscript (page 19, lines 352-366).
+The main difference arises from the models’ specifications of the coefficient on N2.
+The GWRR model allows for varying coefficient on N2, leading to a wider range of estimated EONRs, while the GWRT model restricts the coefficient on N2 to be constant, leading to a narrower range of estimated EONRs.
+When nitrogen is expensive relative to corn, the true range of EONRs should be larger, and therefore the economic penalty of GWRR’s over-estimation of EONR range will be smaller.
+When the nitrogen-corn price ratio is lower, the true EONR range will be smaller, and GWRT’s under-estimation of the EONR range is less of an issue.
+At the reviewer’s request, we will be happy to further enhance the manuscript’s discussion of this topic.
 
-<span style = "color: blue;">Where is there no in-text reference to, or explanation of, Figure 4? I do not know what to make of this lone figure.</span>
+Where is there no in-text reference to, or explanation of, Figure 4? I do not know what to make of this lone figure.
 
-We apologize for the confusion.
-That figure was meant to compare the estimated and true GWR coefficients $\beta_1$ and $\beta_2$.
-But since we have already compared the estimated and true EONR's in another figure, the figure 4 was redundant.
+Reply: We apologize for the confusion.
+That figure was meant to compare the estimated and true GWR coefficients β1 and β2.
+But since we have already compared the estimated and true EONR’s in another figure, the figure 4 was redundant.
 We have removed it from the revised manuscript.
 
-<br>
+Specific Comments
+P.
+1, line 23: Site-specific farming, these days, does not have to be very precise, although the early literature conflated precision ag and site-specific farming.
+More importantly, VRT is just one component of precision ag; they are not synonymous.
 
-## <span style = "color: blue;">Specific Comments</span>
+Reply: We agree with the reviewer’s comment that precision agriculture, site-specific farming, and variable-rate technology are not synonymous.
+Although in the literature those terms are often used interchangeably, they are not strictly speaking equivalent.
+We removed the statement in the parentheses “also known as site-specific farming, or variable-rate technology” to avoid misleading the audiences.
 
-<span style = "color: blue;">P.
-1, line 23: Site-specific farming, these days, does not have to be very precise, although the early literature conflated precision ag and site-specific farming.
-More importantly, VRT is just one component of precision ag; they are not synonymous.</span>
-
-We agree with the reviewer's comment that precision agriculture, site-specific farming, and variable-rate technology are not synonymous.
-Although in the literature those terms are often used interchangeably, they are not strictly speaking equivalent.
-We removed the statement in the parentheses "also known as site-specific farming, or variable-rate technology" to avoid misleading the audiences.
-
-<span style = "color: blue;">P.
+P.
 5, lines 89-90: By this point, it would have been useful to add 1-2 sentences or a footnote about parallels with nonparametric estimators.
@@
 It would be helpful to provide more background on this.
-More broadly, at this point, besides the economics, why should we care about GWR relative to other spatial statistics methods?</span>
+More broadly, at this point, besides the economics, why should we care about GWR relative to other spatial statistics methods?
 
-We agree with the reviewer's comment that GWR is only one of many nonparametric estimators of local yield responses.
+Reply: We agree with the reviewer’s comment that GWR is only one of many nonparametric estimators of local yield responses.
 But our research goal was not to compare GWR with other estimators, nor to advocate the use of GWR.
 We have tried to make this much more clear in the Introduction of the revised manuscript.
-We explain as background that the GWR model has gained attention in developing site-specific input recommendations due to its minimal requirement of costly field characteristics data.
+We explain as background that the GWR model has gained attention in developing site-specific input recommendations due to its minimal requirement of costly field characteristics data (pages 7-8, lines 116-127).
 We explain that our intent is to further test the value of having GWR available as a tool for the analysis of on-farm precision experimentation data and consequential input management recommendations.
@@
 
-<span style = "color: blue;">P. 9, line 192: Here, do you mean that you set the 1370 kg ha-1 to be the square root of the sill variances?</span>
+P. 9, line 192: Here, do you mean that you set the 1370 kg ha-1 to be the square root of the sill variances?
 
-Thanks for pointing out the typo.
+Reply: Thanks for pointing out the typo.
 Yes, it should be the square root of the sill variances since 1370 kg ha−1 was the mean of the standard deviations.
-We have corrected that typo in the revised manuscript at the end of section 3.2.
+We have corrected that typo in the revised manuscript at the end of section 3.2 (page 12, line 224).
 
-<span style = "color: blue;">P.
+P.
 11, line 220: At the first mention of shape-constrained additive models (SCAM), there should be a few sentences of explanation, either in the body or as a footnote.
 Even after the partial explanation on lines 232-233, it is still somewhat unclear and warrants more detail.
-The general readers of JAAEA are likely to not know, either.</span>
+The general readers of JAAEA are likely to not know, either.
 
-Thank you for the suggestion.
-In section 3.5.1 of the revised manuscript we have expanded our explanation of SCAM to clarify that it is a regression model that can fit a more flexible and non-linear response relationship and also allows for shape constraints that can incorporate prior knowledge or theories.
+Reply: Thank you for the suggestion.
+In section 3.5.1 (pages 14-15) of the revised manuscript we have expanded our explanation of SCAM to clarify that it is a regression model that can fit a more flexible and non-linear response relationship and also allows for shape constraints that can incorporate prior knowledge or theories.
 
-<span style = "color: blue;">Pp.
-11-12, lines 238-245: To check, l=K, i.e., the total number of splines from the equation on line 238 equals the total number of splines used for f ̂_SCAM (∙)?
-If so, use the same notation.</span>
+Pp. 11-12, lines 238-245: To check, l=K, i.e., the total number of splines from the equation on line 238 equals the total number of splines used for f ̂_SCAM (∙)? If so, use the same notation.
 
-Yes, the $l$ and $k$ should have been the same. We use $k$ in the revised manuscript.
+Reply:  Yes, the l and k should have been the same. We use k in the revised manuscript (page 15, lines 275, 279).
 
-<span style = "color: blue;">P. 13, lines 268-270: How robust are the N^*_{GWR-T,j} rates to variations in the AIC-chosen bandwidth parameters? More information about this needs to be provided.</span>
+P. 13, lines 268-270: How robust are the N^*_{GWR-T,j} rates to variations in the AIC-chosen bandwidth parameters? More information about this needs to be provided.
 
-If we understand the question correctly, you are asking about the robustness of GWR estimates to bandwidth selection.
+Reply:  If we understand the question correctly, you are asking about the robustness of GWR estimates to bandwidth selection.
 Choosing bandwidth is indeed a crucial step in GWR estimation, and there are many different bandwidth selection methods in the literature.
-In this study we used the corrected version of AIC approach [@fotheringham2017multiscale; @lu2017geographically] to determine the optimal bandwidth.
-It is a commonly used approach in practice, and also the same approach used by @rakshit2020 and @trevisan2021spatial which can make our simulation evaluations consistent.
+In this study we used the corrected version of AIC approach (Fotheringham, Yang, and Kang 2017; Lu et al.
+2017) to determine the optimal bandwidth.
+It is a commonly used approach in practice, and also the same approach used by Rakshit et al.
+(2020) and Trevisan, Bullock, and Martin (2021) which can make our simulation evaluations consistent.
 Since the corrected AIC method generates a unique bandwidth, we did not conduct any robustness check to bandwidths.
 We agree the GWR results could vary when choosing different bandwidths, but the choices of other bandwidth values other than the AIC-chosen one may be arbitrary.
-We added more discussions about bandwidth selection at the end of section 3.5.3 of the revised manuscript.
+We added more discussions about bandwidth selection at the end of section 3.5.3 of the revised manuscript (page 16, lines 303-310).
 
-<span style = "color: blue;">P.
-15, lines 303-305: Why are the numbers from these sentences blank?
-In particular, the median benefit of VRA under GWRR is ?
-and the median benefit of VRA under GWRT is…?</span>
+P. 15, lines 303-305: Why are the numbers from these sentences blank? In particular, the median benefit of VRA under GWRR is ? and the median benefit of VRA under GWRT is…?
 
-Our apologies for the typos. We have corrected them and filled in the correct numbers. They can be found in the end of the 2nd paragraph of section 4.1 of the revised manuscript.
+Reply:  Our apologies for the typos.
+We have corrected them and filled in the correct numbers.
+They can be found in the end of the 2nd paragraph of section 4.1 of the revised manuscript (page 19, lines 348-351).
 
-<span style = "color: blue;">P. 15: You first discuss figure 6 and then move to figure 5. Put all figures in order.</span>
+P. 15: You first discuss figure 6 and then move to figure 5. Put all figures in order.
 
-Thank you for identifying the incorrect order of figures.
+Reply:  Thank you for identifying the incorrect order of figures.
 We apologize for the mistake, and we have corrected the order of the figures accordingly.
@@
 
-<br>
+Writing
+P. 2, line 45: This should be “data are”, not “data is”.
 
-## <span style = "color: blue;">Writing</span>
+Reply:  This grammar error was corrected. The new sentence is now on section 2.2, page 6, line 98 of the revised manuscript.
 
-<span style = "color: blue;">P. 2, line 45: This should be "data are", not "data is". </span>
+P. 2, line 52: Basically or actually? Vagueness here makes it difficult to assess the degree to which OSU’s calculators are being used directly.
 
-This grammar error was corrected. The new sentence is now on section 2.2, the 1st paragraph, line 2 of the revised manuscript.
+Reply:  We removed the word “basically” in the pertinent part of the revised manuscript.
 
-<span style = "color: blue;">P. 2, line 52: Basically or actually? Vagueness here makes it difficult to assess the degree to which OSU's calculators are being used directly. </span>
+P. 2, line 54: To avoid confusing a general agricultural economics audience, I would use an abbreviation other than Rx for site-specific recommendations.
 
-We removed the word "basically" in the pertinent part of the revised manuscript.
+Reply:  In precision agriculture, the site-specific input management recommendation map is commonly called “prescription” or “Rx” by researchers and the industry.
+While we are certainly willing to defer to the editor’s judgment, we have elected to keep this abbreviation in the revised manuscript, but have added a brief explanation of the notation (in the 1st paragraph of section 2.2, page 7, line 103).
+In the USA, at least, it is widely known that “Rx” means “prescription,” and it is chiefly used in conversations about medicines and pharmacies.
 
-<span style = "color: blue;">P. 2, line 54: To avoid confusing a general agricultural economics audience, I would use an abbreviation other than Rx for site-specific recommendations. </span>
+P. 2, lines 49-60: All of these current commercial examples would work better as a footnote as they may become inaccurate in the next 3-10 years (or fewer).
 
-In precision agriculture, the site-specific input management recommendation map is commonly called "prescription" or "Rx" by researchers and the industry.
-While we are certainly willing to defer to the editor's judgment, we have elected to keep this abbreviation in the revised manuscript, but have added a brief explanation of the notation (in the 1st paragraph of section 2.2).
-In the USA, at least, it is widely known that "Rx" means "prescription," and it is chiefly used in conversations about medicines and pharmacies.
-
-<span style = "color: blue;">P. 2, lines 49-60: All of these current commercial examples would work better as a footnote as they may become inaccurate in the next 3-10 years (or fewer). </span>
-
-Thank you for the suggestion.
+Reply:  Thank you for the suggestion.
 We agree that precision agriculture technologies are advancing rapidly.
@@
 Therefore, we prefer to retain these examples in the main text.
-Nonetheless, we acknowledge that these contents may be a little lengthy, so we have moved them from the Introduction section to the Background section of 2.2 (1st paragraph).
+Nonetheless, we acknowledge that these contents may be a little lengthy, so we have moved them from the Introduction section to the Background section of 2.2 (1st paragraph, page 7, lines 104-115).
 
-<span style = "color: blue;">P.
-5, lines 91-114: This page-long paragraph should be split up into at least two paragraphs.
-The length is taxing.
-I would consider starting a new paragraph with the sentence beginning on line 97.</span>
+P. 5, lines 91-114: This page-long paragraph should be split up into at least two paragraphs. The length is taxing. I would consider starting a new paragraph with the sentence beginning on line 97.
 
-This paragraph's contents were broken into two pieces in the revised manuscript, one piece in the last paragraph of Introduction section, and the other piece in the first paragraph of section 2.3.
+Reply:  This paragraph’s contents were broken into two pieces in the revised manuscript, one piece in the last paragraph of Introduction section (pages 4-5, lines 64-73), and the other piece in the first paragraph of section 2.3 (pages 8-9, lines 130-153).
 
-<span style = "color: blue;">P. 7, line 137: This comment should have been removed by the authors prior to manuscript submission.</span>
+P. 7, line 137: This comment should have been removed by the authors prior to manuscript submission.
 
-This typo has been removed. Thank you for bringing it to our attention.
+Reply:  This typo has been removed. Thank you for bringing it to our attention.
 
-<span style = "color: blue;">P. 9, line 189: The acronym DIFM is used before it's spelled out in the sentence, but you should spell it out first and then use the acronym. </span>
+P. 9, line 189: The acronym DIFM is used before it’s spelled out in the sentence, but you should spell it out first and then use the acronym.
 
-Thank you for pointing out this writing issue. We have placed the acronym DIFM after the full name in the revised manuscript.
+Reply:  Thank you for pointing out this writing issue. We have placed the acronym DIFM after the full name in the revised manuscript.
 
-<span style = "color: blue;">P. 10, line 212: The (j,k) index should be subscripted here.</span>
+P. 10, line 212: The (j,k) index should be subscripted here.
 
-We greatly appreciate the reviewer's meticulous review of the manuscript and for finding this typo.
-We have corrected it to use subscript notation (see line 3 of section 3.4).
-Furthermore, to eliminate the duplication of the spline index $k$, we have updated the cell index notation to $(j, i)$ both in this section and throughout the rest of the manuscript.
+Reply:  We greatly appreciate the reviewer’s meticulous review of the manuscript and for finding this typo.
+We have corrected it to use subscript notation (see section 3.4, page 13, line 244).
+Furthermore, to eliminate the duplication of the spline index k, we have updated the cell index notation to (j,i) both in this section and throughout the rest of the manuscript.
 
-<span style = "color: blue;">P. 11, line 221: The second "and" should be "an". </span>
+P. 11, line 221: The second “and” should be “an”.
 
-The typo is corrected. Thank you so much for finding this typo.
+Reply:  The typo is corrected. Thank you so much for finding this typo.
 
-<span style = "color: blue;">P.
-11, line 232: Are you using one shape constraint or more than one shape constraint?
-The language here really matters so as to avoid confusion on the part of the readers.</span>
+P. 11, line 232: Are you using one shape constraint or more than one shape constraint? The language here really matters so as to avoid confusion on the part of the readers.
 
-Here we are modeling a "full-field" response function.
+Reply:  Here we are modeling a “full-field” response function.
 That is, the model assumes that yield response is uniform across the field.
-We agree that the language used could cause confusion about whether we were referring to the yield response function or the shape constraint as "single."  We removed the term "single" from the revised manuscript.
-Please see section 3.5.1 of the revised manuscript.
+We agree that the language used could cause confusion about whether we were referring to the yield response function or the shape constraint as “single.” We removed the term “single” from the revised manuscript.
+Please see section 3.5.1 of the revised manuscript (page 14, lines 261-266).
 
-<span style = "color: blue;">P. 11, line 235: It seems that 1-2 citations could be added (or are missing) after "well substantiated by agronomic research."</span>
+P. 11, line 235: It seems that 1-2 citations could be added (or are missing) after “well substantiated by agronomic research.”
 
-We have cited two additional of agronomic studies (Bullock and Bullock, 1994; Cerrato and Blackmer, 1990) to support the statement in section 5.5.1 of the revised manuscript.
+Reply:  We have cited two additional of agronomic studies (Bullock and Bullock, 1994; Cerrato and Blackmer, 1990) to support the statement in section 3.5.1 of the revised manuscript (page 14, line 271).
 
-<span style = "color: blue;">P.
+P.
 12, line 253: I know what you mean by the notation f ̂_(GWR-R,j) (N), but the hyphen in the notation almost seems like a subtraction sign.
 I would recommend changing GWR-R and GWR-T to GWRR and GWRT and then having superscripts here.
-That is, f ̂_j^GWRR (∙) and f ̂_j^GWRT (∙).</span>
+That is, f ̂_j^GWRR (∙) and f ̂_j^GWRT (∙).
 
-Thank you for the recommendation.
+Reply:  Thank you for the recommendation.
 We have changed GWR-R and GWR-T GWRR and GWRT throughout the revised manuscript.
@@
 
-<span style = "color: blue;">P. 13, line 271: In keeping with your past usage, you should make sure the acronym SCAM is in uppercase throughout the text.</span>
+P. 13, line 271: In keeping with your past usage, you should make sure the acronym SCAM is in uppercase throughout the text.
 
-Thank you for pointing out this formatting error.
+Reply:  Thank you for pointing out this formatting error.
 We have corrected the issue by ensuring that the acronym “SCAM” is consistently written in uppercase throughout the text.
@@
 
-<span style = "color: blue;">P. 15, line 304: "but the its benefit is even negative at when the" should have the typos/redundant wording removed.</span>
+P. 15, line 304: “but the its benefit is even negative at when the” should have the typos/redundant wording removed.
 
-Thank you for pointing out those typos. They have all been corrected (see the end of the 2nd paragraph of section 4.1 of the revised manuscript).
+Reply:  Thank you for pointing out those typos. They have all been corrected end of the 2nd paragraph of section 4.1 of the revised manuscript (page 19, lines 348-351).
 
-<span style = "color: blue;">P. 17, line 335: Figure 0?</span>
+P. 17, line 335: Figure 0?
 
-Our apologies for the typo. It should have been Figure 5 and this problem is fixed in our new manuscript (see the 2nd paragraph of section 4.2).
+Reply:  Our apologies for the typo. It should have been Figure 5 and this problem is fixed in our new manuscript (see the 2nd paragraph of section 4.2, page 20, line 379).
 
-<span style = "color: blue;">P. 18, line 362: Section title should just be "Discussion". </span>
+P. 18, line 362: Section title should just be “Discussion”.
 
-We have combined what were the two final sections of the original manuscript into one section, headed “Discussion and Conclusions.”
+Reply:  We have combined what were the two final sections of the original manuscript into one section, headed “Discussion and Conclusions.”
 
-<span style = "color: blue;">P. 34, Figure 8 horizontal axis label: "Estiamated" should be "Estimated". </span>
+P. 34, Figure 8 horizontal axis label: “Estiamated” should be “Estimated”.
 
-We greatly appreciate the reviewer for identifying this typo. It was corrected in the revised manuscript (now Figure 7).
+Reply:  We greatly appreciate the reviewer for identifying this typo. It was corrected in the revised manuscript (now Figure 7).
 
-<span style = "color: blue;">Pp.
+Pp.
 19-20, lines 398-400: Can this sentence be sharpened?
 Right now, it is a bit too vague to be completely useful as a guide to researchers in this area.
-Specifically, what other statistical estimators should be reconsidered and how (specifically) should they be reassessed?</span>
+Specifically, what other statistical estimators should be reconsidered and how (specifically) should they be reassessed?
 
-We have edited the sentence in the revised manuscript (near the end of paragraph 4, section 5 in the revised manuscript), adding details to explain that other statistical methods commonly used for site-specific yield response estimation literature include regression on field characteristics variables as interaction terms, machine learning, etc.
+Reply:  We have edited the sentence in the revised manuscript (section 5, page 24, lines 457-462), adding details to explain that other statistical methods commonly used for site-specific yield response estimation literature include regression on field characteristics variables as interaction terms, machine learning, etc.
 The common assessment approach is to use simulation-based evaluation, much as we do in our study.
+
+References:
+
+Fotheringham, A Stewart, Wenbai Yang, and Wei Kang. 2017. “Multiscale Geographically Weighted Regression (MGWR).” Annals of the American Association of Geographers 107 (6): 1247–65.
+Lu, Binbin, Chris Brunsdon, Martin Charlton, and Paul Harris.
+2017.
+“Geographically Weighted Regression with Parameter-Specific Distance Metrics.” International Journal of Geographical Information Science 31 (5): 982–98.
+Rakshit, Suman, Adrian Baddeley, Katia Stefanova, Karyn Reeves, Kefei Chen, Zhanglong Cao, Fiona Evans, and Mark Gibberd.
+2020.
+“Novel Approach to the Analysis of Spatially-Varying Treatment Effects in on-Farm Experiments.” Field Crops Research 255: 107783.
+Trevisan, RG, DS Bullock, and NF Martin. 2021. “Spatial Variability of Crop Responses to Agronomic Inputs in on-Farm Precision Experimentation.” Precision Agriculture 22 (2): 342–63.

### 2023-11-05 Writing/JAAEA/2ndRoundRevision/reply_to_reviewer_2.rmd
replies started

---
title: "Reply"
output: 
  html_document: default
---

Your comments are in blue.  Our responses are in black.

# General Comments

+ <span style = "color: blue;">I still believe this research is related to studies that examine the economic value of forecasting models by assessing the economic effects stemming from inaccuracy (e.g.,
reduction in a business’ profits by assuming a mean-squared-error loss function instead of an
asymmetric loss, for example). Although there have been improvements in references to the
agronomy and statistical literatures, it would still be useful to add 1-2 sentences in the
conclusion that reference the broader economics literature on this topic. </span>

Response: We do not address this as you suggested.

+ <span style = "color: blue;"> As mentioned in my previous review, the term "economically optimal" has different meanings among agricultural economists. The new footnote (footnote 1 on p. 5) is appreciated, but here you should specify that "economically optimal" in the context of the article does not mean "socially optimal."</span>

Response:

+ <span style = "color: blue;"> None of the figure numbers appear in the text; instead, each figure reference is followed by "Error! Reference source not found." These all should be corrected. </span>

Response: We apologize for these mistakes. We have corrected theses errors.

+ In Section 3, to reduce confusion, you should consider using the word "Simulated" in the
section heads (i.e., 3.1 Simulated Field Layout, 3.2 Simulated True Cell-Specific Yield
Response Function, 3.3 Simulated Trial Design, and 3.4 Simulated Yield Data).

Response:

+ All of the figures have their dimensions and DPI listed (1422x812mm). This information is
not necessary and should have been removed prior to submission.

Response:

Specific Comments

+ P. 4, lines 58-59: This statement, while perhaps likely, is just speculation. The authors should
either check with Trevisan et al. (2021) that this was the reason (and then remove "It seems
likely") or just delete the sentence entirely.
o The same comment applies to P. 8, lines 134-136.

Response:

+ P. 6, lines 91-95: Implicitly, you seem to be suggesting that the set of points from which you
would take (input rate, yield) data is smaller than n, the total number of sites associated with
the characteristics vector. Either way, this should be clarified in the text.

Response:

+ P. 9, lines 146-148: This seems overly negative of Trevisan et al. (2021), as well as clunky
wording ("provided an example at step 3"). Since you say this assumption is unavoidable, it is done by all studies, including the ones you mention above: Anselin et al, Bullock et al, Liu et al, and Swinton and Lowenberg-DeBoer. You should remove this sentence entirely because it really adds nothing. Later on in the paragraph, you address the thing that's more important: inaccurate estimation of yield response using GWR, because it exaggerates the true heterogeneity in the yield response functions, leads to comparatively worse bias.

Response:

+ P. 10, lines 185-186: This almost sounds misleading; "were available for analysis" seems to
suggest you were using real-world data. You should re-write this as "In total, simulated data from 1,440 subplots were used for analysis."

Response:

+ P. 10, line 199: In this sentence, you should mention which specific statistical distribution the
error term follows, despite the fact that you mention Gaussian random fields below.

Response:

+ P. 12, line 212: It would be useful to add a footnote here explaining why the range of 600m
was chosen.

Response:

+ P. 12, line 229: Given that JAAEA is an economics journal and not an agronomy journal, you
should rewrite "Latin square trial design schema" as "trial design" here, and at the end of the
next sentence, write "each column of the block (i.e., a Latin square)."

Response:

+ P. 14, line 254: For additional clarity, you could point out that the EOUNA rate is just the
value of N that solves 𝑝 ⋅ 𝑓(𝑁) - 𝑤 ⋅ 𝑁, where 𝑓(𝑁) is SCAM-estimated.

Response:

+ P. 15, lines 277-279: Add a sentence (perhaps in a footnote) mentioning how this shape
constraint is actually imposed.

Response:

+ PP. 22-23, lines 439-441: This sentence should be removed because it seems speculative.
More importantly, researchers do not "have" to implement a methodology because it is
conveniently available in standard software; instead, they could code their own models,
methods, etc.

Response:

+ P. 33, Figure 2: In the notes to this figure, you should add that the 1,440 subplots are
illustrated as 24 rows x 12 columns, each containing 5 subplots (24 x 12 x 5 = 1,440). Also
add that there are 72 rows x 120 columns of cells (72 x 120 = 8,640).

Response:

Writing

+ P. 4, line 45: Replace "dramatic" with "seemingly implausibly large"

Response:

+ P. 4, line 54: Replace "suspect" with "hypothesize"
o Same comment for "suspect" on P. 9, line 153

Response:

+ P. 5, line 77: You do not need to write (OFPE) again here since you have already introduced
the acronym.

Response:

+ P. 8, line 124: You should place the first instance of "(EONR)" here after "economically
optimal nitrogen rates" rather than line 132.

Response:

+ P. 8, line 130: Replace "dangerous" with "problematic"
o Same comment for P. 22, line 438

Response:

+ P. 8, line 145: Remove the word "the" in front of "step"

Response:

+ P. 11, lines 200-201: Replace "are desirable properties" with "is a desirable property"

Response:

+ P. 13, line 233: Replace "due the" with "due to the"

Response:

+ P. 14, line 262: This is the first and only mention in the paper of a benchmark. Given that,
what is a "lower" benchmark?

Response:

+ P. 16, line 295: Replace "as" with "the"

Response:

+ P. 19, line 269: Replace "truea" with "true"

Response:

+ P. 22, line 453: Remove the word "please"

Response:

+ P. 24, lines 468-474: Remove the clause "After the development of software that..."
Additionally, you should add quotation marks to both instances of "pure" in this paragraph.
Response:

### 2023-11-05 Writing/JAAEA/2ndRoundRevision/reply_to_reviewer_2.rmd
create some new files

@@
 output: 
-  html_document: default
+  html_document:
+    theme:
+      version: 4
+bibliography: PA.bib
 ---
 
-Your comments are in blue.  Our responses are in black.
+Your comments are in blue, and our responses are in black.
 
-# General Comments
+<span style = "color: blue;">This study examines the economic value associated with three statistical methods used to generate site-specific nitrogen application rates: 1) geographically weighted regressions using the method of Rakshit et al.
+(2020) denoted as GWR-R, 2) geographically weighted regressions using the method of Trevisan et al.
+(2021) denoted as GWR-T, and 3) shape-constrained additive models (SCAM).
+Using straightforward Monte Carlo simulations, the two GWR methods are used to determine the economically optimal nitrogen rate (EONR) and profits from variable rate applications (VRA), while the SCAM methodology is used to determine the EONRs and profits for uniform rate applications (URA).
+These rates are based on estimations of site-specific corn yield functions for six cells across 1,440 subplots.
+The authors find the GWR-T outperforms GWR-R when the nitrogen price (relative to corn) is low, but GWR-R outperforms GWR-T when the nitrogen price is relatively high.
+This is because of the relative over- and underestimation of the EONRs.
+The study also finds that both GWR-T and GWR-R may have substantially overestimated the economic value of VRA; the net benefit of VRA over URA is much smaller, roughly $2 per acre (just over $5 per hectare, on average).
+For convenience, my review below is organized into a set of general comments, specific comments, and comments related to the exposition and writing, with each being arranged in order of page number.
+All comments are designed to strengthen the research.</span>
 
-+ <span style = "color: blue;">I still believe this research is related to studies that examine the economic value of forecasting models by assessing the economic effects stemming from inaccuracy (e.g.,
-reduction in a business’ profits by assuming a mean-squared-error loss function instead of an
-asymmetric loss, for example). Although there have been improvements in references to the
-agronomy and statistical literatures, it would still be useful to add 1-2 sentences in the
-conclusion that reference the broader economics literature on this topic. </span>
+We would like to express our sincere gratitude for the reviewer's careful examination and critique of our manuscript.
+The insightful comments and suggestions have significantly contributed to the paper's clarity, detail, and overall strength.
+In return, we have attempted to carefully address each of the comments and revise the manuscript in response.
 
-Response: We do not address this as you suggested.
+<br>
 
-+ <span style = "color: blue;"> As mentioned in my previous review, the term "economically optimal" has different meanings among agricultural economists.
-The new footnote (footnote 1 on p.
-5) is appreciated, but here you should specify that "economically optimal" in the context of the article does not mean "socially optimal."</span>
+## <span style = "color: blue;">General Comments</span>
 
-Response:
+<span style = "color: blue;">To some extent, this research is related to studies that examine the "value" of forecasting models by assessing their measure of inaccuracy.
+Given that determining the value of general regression methodologies is not overly common in the relevant literature here, why not add 1-2 paragraphs that ties your study to other studies that measure the "value" of certain econometric techniques?
+</span>
 
-+ <span style = "color: blue;"> None of the figure numbers appear in the text; instead, each figure reference is followed by "Error! Reference source not found." These all should be corrected. </span>
+Thank you for bringing up this important point.
+What makes this study differ from previous studies is that the model “value” is not measured by the statistical accuracy of parameter estimates, but rather by the ultimate economic return.
+To emphasize this aspect, we have included an additional paragraph in the “5.
+Discussion and Conclusions” section (paragraph 2).
+It is worth noting that we are unable to identify a specific body of literature that exclusively focuses on assessing the value of general regression models.
+However, it is customary in the development of econometric models to evaluate their performance using statistical accuracy measures such as bias, mean squared error, and type I error, based on simulation data.
+We have referenced a few relevant studies of this nature to underscore the distinction of our economic value assessment approach.
 
-Response: We apologize for these mistakes. We have corrected theses errors.
+<span style = "color: blue;">One of the most important questions in the literature relates to how variable rate technologies (VRT) can reduce negative externalities like fertilizer and chemical runoff and leaching.
+Clearly, this is not the research objective, and addressing a much more burning question in the literature would involve additional terms in the equation on p.
+10, line 294 that represent the negative environmental externalities.
+The authors should clarify early on that "economically optimal" means "privately optimal" rather than "socially optimal."</span>
 
-+ In Section 3, to reduce confusion, you should consider using the word "Simulated" in the
-section heads (i.e., 3.1 Simulated Field Layout, 3.2 Simulated True Cell-Specific Yield
-Response Function, 3.3 Simulated Trial Design, and 3.4 Simulated Yield Data).
+Thank you for the suggestion.
+We have explicitly stated the following in a footnote at the end of the Introduction section of the revised manuscript: *"While the environmental impacts of fertilizer management are of great social importance, for simplicity we confine our analysis to its private economic impacts."*
 
-Response:
+<span style = "color: blue;">It strikes me as odd that, even with a minor clause on line 207 of p.
+10, there is no real discussion of the corn price or nitrogen price in the methods section.
+What are the summary statistics and/or assumptions about p and w?
+What is the underlying intuition regarding the dependence of the relative performance of GWRR/GWRT to the corn-to-nitrogen price ratio (though this is partially explained in the paragraph on pages 15-16)?
+Any intuition about the ratios of 4.2, 5.4, and 10.4?</span>
 
-+ All of the figures have their dimensions and DPI listed (1422x812mm). This information is
-not necessary and should have been removed prior to submission.
+Thank you for bringing up this point.
+We have included a brief discussion of the historical corn and nitrogen prices in the first paragraph of the Results section 4.1.
+Additionally, we have included Appendix I: Historical Corn and Nitrogen Prices in the supplementary material to provide a more detailed description of the collection, calculation, and summary statistics of the historical price data.
+We also apologize for the typos of the price ratios 4.16, 5.44 and 10.35 in the previous version of the manuscript.
+The correct price ratios 5.44, 6.56, and 7.67 are used in the revised manuscript.
+The intuition underlying the dependence of the relative performances of GWRR and GWRT to the nitrogen-corn price ratio was explained in the paragraphs on pages 15-16 of the original manuscript, and that discussion has been included in the revised manuscript.
+The main difference arises from the models' specifications of the coefficient on $N^2$.
+The GWRR model allows for varying coefficient on $N^2$, leading to a wider range of estimated EONRs, while the GWRT model restricts the coefficient on $N^2$ to be constant, leading to a narrower range of estimated EONRs.
+When nitrogen is expensive relative to corn, the true range of EONRs should be larger, and therefore the economic penalty of GWRR's over-estimation of EONR range will be smaller.
+When the nitrogen-corn price ratio is lower, the true EONR range will be smaller, and GWRT's under-estimation of the EONR range is less of an issue.
+At the reviewer's request, we will be happy to further enhance the manuscript's discussion of this topic.
 
-Response:
+<span style = "color: blue;">Where is there no in-text reference to, or explanation of, Figure 4? I do not know what to make of this lone figure.</span>
 
-Specific Comments
+We apologize for the confusion.
+That figure was meant to compare the estimated and true GWR coefficients $\beta_1$ and $\beta_2$.
+But since we have already compared the estimated and true EONR's in another figure, the figure 4 was redundant.
+We have removed it from the revised manuscript.
 
-+ P. 4, lines 58-59: This statement, while perhaps likely, is just speculation. The authors should
-either check with Trevisan et al. (2021) that this was the reason (and then remove "It seems
-likely") or just delete the sentence entirely.
-o The same comment applies to P. 8, lines 134-136.
+<br>
 
-Response:
+## <span style = "color: blue;">Specific Comments</span>
 
-+ P. 6, lines 91-95: Implicitly, you seem to be suggesting that the set of points from which you
-would take (input rate, yield) data is smaller than n, the total number of sites associated with
-the characteristics vector. Either way, this should be clarified in the text.
+<span style = "color: blue;">P.
+1, line 23: Site-specific farming, these days, does not have to be very precise, although the early literature conflated precision ag and site-specific farming.
+More importantly, VRT is just one component of precision ag; they are not synonymous.</span>
 
-Response:
+We agree with the reviewer's comment that precision agriculture, site-specific farming, and variable-rate technology are not synonymous.
+Although in the literature those terms are often used interchangeably, they are not strictly speaking equivalent.
+We removed the statement in the parentheses "also known as site-specific farming, or variable-rate technology" to avoid misleading the audiences.
 
-+ P. 9, lines 146-148: This seems overly negative of Trevisan et al. (2021), as well as clunky
-wording ("provided an example at step 3").
-Since you say this assumption is unavoidable, it is done by all studies, including the ones you mention above: Anselin et al, Bullock et al, Liu et al, and Swinton and Lowenberg-DeBoer.
-You should remove this sentence entirely because it really adds nothing.
-Later on in the paragraph, you address the thing that's more important: inaccurate estimation of yield response using GWR, because it exaggerates the true heterogeneity in the yield response functions, leads to comparatively worse bias.
+<span style = "color: blue;">P.
+5, lines 89-90: By this point, it would have been useful to add 1-2 sentences or a footnote about parallels with nonparametric estimators.
+Using multiple data points to derive local estimates, as in kernel density estimation, is nothing new.
+It would be helpful to provide more background on this.
+More broadly, at this point, besides the economics, why should we care about GWR relative to other spatial statistics methods?</span>
 
-Response:
+We agree with the reviewer's comment that GWR is only one of many nonparametric estimators of local yield responses.
+But our research goal was not to compare GWR with other estimators, nor to advocate the use of GWR.
+We have tried to make this much more clear in the Introduction of the revised manuscript.
+We explain as background that the GWR model has gained attention in developing site-specific input recommendations due to its minimal requirement of costly field characteristics data.
+We explain that our intent is to further test the value of having GWR available as a tool for the analysis of on-farm precision experimentation data and consequential input management recommendations.
+We do not intend to involve other spatial statistics methods in the current paper.
+But we do plan to conduct similar simulation-based economic evaluations of other local response estimation methods (such as the spatial kriging smoothing) in future research.
 
-+ P. 10, lines 185-186: This almost sounds misleading; "were available for analysis" seems to
-suggest you were using real-world data. You should re-write this as "In total, simulated data from 1,440 subplots were used for analysis."
+<span style = "color: blue;">P. 9, line 192: Here, do you mean that you set the 1370 kg ha-1 to be the square root of the sill variances?</span>
 
-Response:
+Thanks for pointing out the typo.
+Yes, it should be the square root of the sill variances since 1370 kg ha−1 was the mean of the standard deviations.
+We have corrected that typo in the revised manuscript at the end of section 3.2.
 
-+ P. 10, line 199: In this sentence, you should mention which specific statistical distribution the
-error term follows, despite the fact that you mention Gaussian random fields below.
+<span style = "color: blue;">P.
+11, line 220: At the first mention of shape-constrained additive models (SCAM), there should be a few sentences of explanation, either in the body or as a footnote.
+Even after the partial explanation on lines 232-233, it is still somewhat unclear and warrants more detail.
+The general readers of JAAEA are likely to not know, either.</span>
 
-Response:
+Thank you for the suggestion.
+In section 3.5.1 of the revised manuscript we have expanded our explanation of SCAM to clarify that it is a regression model that can fit a more flexible and non-linear response relationship and also allows for shape constraints that can incorporate prior knowledge or theories.
 
-+ P. 12, line 212: It would be useful to add a footnote here explaining why the range of 600m
-was chosen.
+<span style = "color: blue;">Pp.
+11-12, lines 238-245: To check, l=K, i.e., the total number of splines from the equation on line 238 equals the total number of splines used for f ̂_SCAM (∙)?
+If so, use the same notation.</span>
 
-Response:
+Yes, the $l$ and $k$ should have been the same. We use $k$ in the revised manuscript.
 
-+ P. 12, line 229: Given that JAAEA is an economics journal and not an agronomy journal, you
-should rewrite "Latin square trial design schema" as "trial design" here, and at the end of the
-next sentence, write "each column of the block (i.e., a Latin square)."
+<span style = "color: blue;">P. 13, lines 268-270: How robust are the N^*_{GWR-T,j} rates to variations in the AIC-chosen bandwidth parameters? More information about this needs to be provided.</span>
 
-Response:
+If we understand the question correctly, you are asking about the robustness of GWR estimates to bandwidth selection.
+Choosing bandwidth is indeed a crucial step in GWR estimation, and there are many different bandwidth selection methods in the literature.
+In this study we used the corrected version of AIC approach [@fotheringham2017multiscale; @lu2017geographically] to determine the optimal bandwidth.
+It is a commonly used approach in practice, and also the same approach used by @rakshit2020 and @trevisan2021spatial which can make our simulation evaluations consistent.
+Since the corrected AIC method generates a unique bandwidth, we did not conduct any robustness check to bandwidths.
+We agree the GWR results could vary when choosing different bandwidths, but the choices of other bandwidth values other than the AIC-chosen one may be arbitrary.
+We added more discussions about bandwidth selection at the end of section 3.5.3 of the revised manuscript.
 
-+ P. 14, line 254: For additional clarity, you could point out that the EOUNA rate is just the
-value of N that solves 𝑝 ⋅ 𝑓(𝑁) - 𝑤 ⋅ 𝑁, where 𝑓(𝑁) is SCAM-estimated.
+<span style = "color: blue;">P.
+15, lines 303-305: Why are the numbers from these sentences blank?
+In particular, the median benefit of VRA under GWRR is ?
+and the median benefit of VRA under GWRT is…?</span>
 
-Response:
+Our apologies for the typos. We have corrected them and filled in the correct numbers. They can be found in the end of the 2nd paragraph of section 4.1 of the revised manuscript.
 
-+ P. 15, lines 277-279: Add a sentence (perhaps in a footnote) mentioning how this shape
-constraint is actually imposed.
+<span style = "color: blue;">P. 15: You first discuss figure 6 and then move to figure 5. Put all figures in order.</span>
 
-Response:
+Thank you for identifying the incorrect order of figures.
+We apologize for the mistake, and we have corrected the order of the figures accordingly.
+The revised manuscript now reflects the correct sequence of the two figures.
+Note that since the original Figure 4 was removed, the two figures are now the new Figure 4 and Figure 5.
 
-+ PP. 22-23, lines 439-441: This sentence should be removed because it seems speculative.
-More importantly, researchers do not "have" to implement a methodology because it is
-conveniently available in standard software; instead, they could code their own models,
-methods, etc.
+<br>
 
-Response:
+## <span style = "color: blue;">Writing</span>
 
-+ P. 33, Figure 2: In the notes to this figure, you should add that the 1,440 subplots are
-illustrated as 24 rows x 12 columns, each containing 5 subplots (24 x 12 x 5 = 1,440). Also
-add that there are 72 rows x 120 columns of cells (72 x 120 = 8,640).
+<span style = "color: blue;">P. 2, line 45: This should be "data are", not "data is". </span>
 
-Response:
+This grammar error was corrected. The new sentence is now on section 2.2, the 1st paragraph, line 2 of the revised manuscript.
 
-Writing
+<span style = "color: blue;">P. 2, line 52: Basically or actually? Vagueness here makes it difficult to assess the degree to which OSU's calculators are being used directly. </span>
 
-+ P. 4, line 45: Replace "dramatic" with "seemingly implausibly large"
+We removed the word "basically" in the pertinent part of the revised manuscript.
 
-Response:
+<span style = "color: blue;">P. 2, line 54: To avoid confusing a general agricultural economics audience, I would use an abbreviation other than Rx for site-specific recommendations. </span>
 
-+ P. 4, line 54: Replace "suspect" with "hypothesize"
-o Same comment for "suspect" on P. 9, line 153
+In precision agriculture, the site-specific input management recommendation map is commonly called "prescription" or "Rx" by researchers and the industry.
+While we are certainly willing to defer to the editor's judgment, we have elected to keep this abbreviation in the revised manuscript, but have added a brief explanation of the notation (in the 1st paragraph of section 2.2).
+In the USA, at least, it is widely known that "Rx" means "prescription," and it is chiefly used in conversations about medicines and pharmacies.
 
-Response:
+<span style = "color: blue;">P. 2, lines 49-60: All of these current commercial examples would work better as a footnote as they may become inaccurate in the next 3-10 years (or fewer). </span>
 
-+ P. 5, line 77: You do not need to write (OFPE) again here since you have already introduced
-the acronym.
+Thank you for the suggestion.
+We agree that precision agriculture technologies are advancing rapidly.
+However, we believe that those commercial examples are essential to illustrate the current state of site-specific field data collection technologies, which will help readers understand the benefits of the GWR method.
+Therefore, we prefer to retain these examples in the main text.
+Nonetheless, we acknowledge that these contents may be a little lengthy, so we have moved them from the Introduction section to the Background section of 2.2 (1st paragraph).
 
-Response:
+<span style = "color: blue;">P.
+5, lines 91-114: This page-long paragraph should be split up into at least two paragraphs.
+The length is taxing.
+I would consider starting a new paragraph with the sentence beginning on line 97.</span>
 
-+ P. 8, line 124: You should place the first instance of "(EONR)" here after "economically
-optimal nitrogen rates" rather than line 132.
+This paragraph's contents were broken into two pieces in the revised manuscript, one piece in the last paragraph of Introduction section, and the other piece in the first paragraph of section 2.3.
 
-Response:
+<span style = "color: blue;">P. 7, line 137: This comment should have been removed by the authors prior to manuscript submission.</span>
 
-+ P. 8, line 130: Replace "dangerous" with "problematic"
-o Same comment for P. 22, line 438
+This typo has been removed. Thank you for bringing it to our attention.
 
-Response:
+<span style = "color: blue;">P. 9, line 189: The acronym DIFM is used before it's spelled out in the sentence, but you should spell it out first and then use the acronym. </span>
 
-+ P. 8, line 145: Remove the word "the" in front of "step"
+Thank you for pointing out this writing issue. We have placed the acronym DIFM after the full name in the revised manuscript.
 
-Response:
+<span style = "color: blue;">P. 10, line 212: The (j,k) index should be subscripted here.</span>
 
-+ P. 11, lines 200-201: Replace "are desirable properties" with "is a desirable property"
+We greatly appreciate the reviewer's meticulous review of the manuscript and for finding this typo.
+We have corrected it to use subscript notation (see line 3 of section 3.4).
+Furthermore, to eliminate the duplication of the spline index $k$, we have updated the cell index notation to $(j, i)$ both in this section and throughout the rest of the manuscript.
 
-Response:
+<span style = "color: blue;">P. 11, line 221: The second "and" should be "an". </span>
 
-+ P. 13, line 233: Replace "due the" with "due to the"
+The typo is corrected. Thank you so much for finding this typo.
 
-Response:
+<span style = "color: blue;">P.
+11, line 232: Are you using one shape constraint or more than one shape constraint?
+The language here really matters so as to avoid confusion on the part of the readers.</span>
 
-+ P. 14, line 262: This is the first and only mention in the paper of a benchmark. Given that,
-what is a "lower" benchmark?
+Here we are modeling a "full-field" response function.
+That is, the model assumes that yield response is uniform across the field.
+We agree that the language used could cause confusion about whether we were referring to the yield response function or the shape constraint as "single."  We removed the term "single" from the revised manuscript.
+Please see section 3.5.1 of the revised manuscript.
 
-Response:
+<span style = "color: blue;">P. 11, line 235: It seems that 1-2 citations could be added (or are missing) after "well substantiated by agronomic research."</span>
 
-+ P. 16, line 295: Replace "as" with "the"
+We have cited two additional of agronomic studies (Bullock and Bullock, 1994; Cerrato and Blackmer, 1990) to support the statement in section 3.5.1 of the revised manuscript.
 
-Response:
+<span style = "color: blue;">P.
+12, line 253: I know what you mean by the notation f ̂_(GWR-R,j) (N), but the hyphen in the notation almost seems like a subtraction sign.
+I would recommend changing GWR-R and GWR-T to GWRR and GWRT and then having superscripts here.
+That is, f ̂_j^GWRR (∙) and f ̂_j^GWRT (∙).</span>
 
-+ P. 19, line 269: Replace "truea" with "true"
+Thank you for the recommendation.
+We have changed GWR-R and GWR-T GWRR and GWRT throughout the revised manuscript.
+We have also put all model names (GWR and SCAM) in superscripts in the pertinent equations.
 
-Response:
+<span style = "color: blue;">P. 13, line 271: In keeping with your past usage, you should make sure the acronym SCAM is in uppercase throughout the text.</span>
 
-+ P. 22, line 453: Remove the word "please"
+Thank you for pointing out this formatting error.
+We have corrected the issue by ensuring that the acronym “SCAM” is consistently written in uppercase throughout the text.
+Additionally, we have capitalized all acronyms in equations as well.
 
-Response:
+<span style = "color: blue;">P. 15, line 304: "but the its benefit is even negative at when the" should have the typos/redundant wording removed.</span>
 
-+ P. 24, lines 468-474: Remove the clause "After the development of software that..."
-Additionally, you should add quotation marks to both instances of "pure" in this paragraph.
-Response:
+Thank you for pointing out those typos. They have all been corrected (see the end of the 2nd paragraph of section 4.1 of the revised manuscript).
+
+<span style = "color: blue;">P. 17, line 335: Figure 0?</span>
+
+Our apologies for the typo. It should have been Figure 5 and this problem is fixed in our new manuscript (see the 2nd paragraph of section 4.2).
+
+<span style = "color: blue;">P. 18, line 362: Section title should just be "Discussion". </span>
+
+We have combined what were the two final sections of the original manuscript into one section, headed “Discussion and Conclusions.”
+
+<span style = "color: blue;">P. 34, Figure 8 horizontal axis label: "Estiamated" should be "Estimated". </span>
+
+We greatly appreciate the reviewer for identifying this typo. It was corrected in the revised manuscript (now Figure 7).
+
+<span style = "color: blue;">Pp.
+19-20, lines 398-400: Can this sentence be sharpened?
+Right now, it is a bit too vague to be completely useful as a guide to researchers in this area.
+Specifically, what other statistical estimators should be reconsidered and how (specifically) should they be reassessed?</span>
+
+We have edited the sentence in the revised manuscript (near the end of paragraph 4, section 5 in the revised manuscript), adding details to explain that other statistical methods commonly used for site-specific yield response estimation literature include regression on field characteristics variables as interaction terms, machine learning, etc.
+The common assessment approach is to use simulation-based evaluation, much as we do in our study.

### 2023-11-05 Writing/JAAEA/2ndRoundRevision/reply_to_reviewer_2.rmd
replies

--- 2023-11-05 Writing/JAAEA/2ndRoundRevision/reply_to_reviewer_2.rmd
@@
 
-Response: We apologize for these mistakes. We have corrected theses errors.
+Response:
 
-+ In Section 3, to reduce confusion, you should consider using the word "Simulated" in the
-section heads (i.e., 3.1 Simulated Field Layout, 3.2 Simulated True Cell-Specific Yield
-Response Function, 3.3 Simulated Trial Design, and 3.4 Simulated Yield Data).
++ <span style = "color: blue;"> In Section 3, to reduce confusion, you should consider using the word "Simulated" in the section heads (i.e., 3.1 Simulated Field Layout, 3.2 Simulated True Cell-Specific Yield Response Function, 3.3 Simulated Trial Design, and 3.4 Simulated Yield Data).
+</span>
+
+Response: Instead of making the suggested changes, we simply renamed the Methods section to "Methods: Monte Carlo Simulations," so that it is clear that all the subsequent sections are about simulations.
+
++ <span style = "color: blue;"> All of the figures have their dimensions and DPI listed (1422x812mm). This information is not necessary and should have been removed prior to submission. </span>
+
+Response: We apologize this mistake. This has been fixed in this version of the manuscript.
+
+# Specific Comments
+
++ <span style = "color: blue;"> P.
+4, lines 58-59: This statement, while perhaps likely, is just speculation.
+The authors should either check with Trevisan et al.
+(2021) that this was the reason (and then remove "It seems likely") or just delete the sentence entirely.
+The same comment applies to P.
+8, lines 134-136.
+</span>
+
+Response: You are correct and we have removed the sentence entirely.
+
++ <span style = "color: blue;">P.
+6, lines 91-95: Implicitly, you seem to be suggesting that the set of points from which you would take (input rate, yield) data is smaller than n, the total number of sites associated with the characteristics vector.
+Either way, this should be clarified in the text.</span>
+
+Response: We have modified the sentence to the following so that it describes what GWR does more accurately:
+
+  - Old: "Alternatively, a site-specific yield response function might be estimated simply by taking (input rate, yield) data from points around a site of interest"
+  - New: "Alternatively, a site-specific yield response function might be estimated simply by giving greater weights to the points around a site of interest"
+
++ <span style = "color: blue;"> P.
+9, lines 146-148: This seems overly negative of Trevisan et al.
+(2021), as well as clunky wording ("provided an example at step 3").
+Since you say this assumption is unavoidable, it is done by all studies, including the ones you mention above: Anselin et al, Bullock et al, Liu et al, and Swinton and Lowenberg-DeBoer.
+You should remove this sentence entirely because it really adds nothing.
+Later on in the paragraph, you address the thing that's more important: inaccurate estimation of yield response using GWR, because it exaggerates the true heterogeneity in the yield response functions, leads to comparatively worse bias.
+</span>
+
+Response: We dropped the sentence.
+
++ <span style = "color: blue;"> P.
+10, lines 185-186: This almost sounds misleading; "were available for analysis" seems to suggest you were using real-world data.
+You should re-write this as "In total, simulated data from 1,440 subplots were used for analysis." </span>
+
+Response: We edited the sentence according to your suggestion.
+
++ <span style = "color: blue;"> P.
+10, line 199: In this sentence, you should mention which specific statistical distribution the error term follows, despite the fact that you mention Gaussian random fields below.
+</span>
+
+Response: It follows a normal distribution in a way it is spatially correlated. This has been made clear in the manuscript (see page ??, line ??).
+
++ <span style = "color: blue;">P. 12, line 212: It would be useful to add a footnote here explaining why the range of 600m was chosen.</span>
 
@@
 
-+ All of the figures have their dimensions and DPI listed (1422x812mm). This information is
-not necessary and should have been removed prior to submission.
++ <span style = "color: blue;">P.
+12, line 229: Given that JAAEA is an economics journal and not an agronomy journal, you should rewrite "Latin square trial design schema" as "trial design" here, and at the end of the next sentence, write "each column of the block (i.e., a Latin square)." </span>
+
+Response: We followed your suggestions and texts were modified accordingly.
+
++ <span style = "color: blue;">P.
+14, line 254: For additional clarity, you could point out that the EONR rate is just the value of N that solves $\\cdot f(N) - \omega\dcot N$, where $f(N)$ is SCAM-estimated.
+</span>
 
@@
 
-Specific Comments
-
-+ P. 4, lines 58-59: This statement, while perhaps likely, is just speculation. The authors should
-either check with Trevisan et al. (2021) that this was the reason (and then remove "It seems
-likely") or just delete the sentence entirely.
-o The same comment applies to P. 8, lines 134-136.
++ <span style = "color: blue;"> P. 15, lines 277-279: Add a sentence (perhaps in a footnote) mentioning how this shape constraint is actually imposed. </span>
 
@@
 
-+ P. 6, lines 91-95: Implicitly, you seem to be suggesting that the set of points from which you
-would take (input rate, yield) data is smaller than n, the total number of sites associated with
-the characteristics vector. Either way, this should be clarified in the text.
++ <span style = "color: blue;">PP.
+22-23, lines 439-441: This sentence should be removed because it seems speculative.
+More importantly, researchers do not "have" to implement a methodology because it is conveniently available in standard software; instead, they could code their own models, methods, etc.
+</span>
 
@@
 
-+ P. 9, lines 146-148: This seems overly negative of Trevisan et al. (2021), as well as clunky
-wording ("provided an example at step 3").
-Since you say this assumption is unavoidable, it is done by all studies, including the ones you mention above: Anselin et al, Bullock et al, Liu et al, and Swinton and Lowenberg-DeBoer.
-You should remove this sentence entirely because it really adds nothing.
-Later on in the paragraph, you address the thing that's more important: inaccurate estimation of yield response using GWR, because it exaggerates the true heterogeneity in the yield response functions, leads to comparatively worse bias.
-
-Response:
-
-+ P. 10, lines 185-186: This almost sounds misleading; "were available for analysis" seems to
-suggest you were using real-world data. You should re-write this as "In total, simulated data from 1,440 subplots were used for analysis."
-
-Response:
-
-+ P. 10, line 199: In this sentence, you should mention which specific statistical distribution the
-error term follows, despite the fact that you mention Gaussian random fields below.
-
-Response:
-
-+ P. 12, line 212: It would be useful to add a footnote here explaining why the range of 600m
-was chosen.
-
-Response:
-
-+ P. 12, line 229: Given that JAAEA is an economics journal and not an agronomy journal, you
-should rewrite "Latin square trial design schema" as "trial design" here, and at the end of the
-next sentence, write "each column of the block (i.e., a Latin square)."
-
-Response:
-
-+ P. 14, line 254: For additional clarity, you could point out that the EOUNA rate is just the
-value of N that solves 𝑝 ⋅ 𝑓(𝑁) - 𝑤 ⋅ 𝑁, where 𝑓(𝑁) is SCAM-estimated.
-
-Response:
-
-+ P. 15, lines 277-279: Add a sentence (perhaps in a footnote) mentioning how this shape
-constraint is actually imposed.
-
-Response:
-
-+ PP. 22-23, lines 439-441: This sentence should be removed because it seems speculative.
-More importantly, researchers do not "have" to implement a methodology because it is
-conveniently available in standard software; instead, they could code their own models,
-methods, etc.
-
-Response:
-
-+ P. 33, Figure 2: In the notes to this figure, you should add that the 1,440 subplots are
-illustrated as 24 rows x 12 columns, each containing 5 subplots (24 x 12 x 5 = 1,440). Also
-add that there are 72 rows x 120 columns of cells (72 x 120 = 8,640).
++ <span style = "color: blue;">P.
+33, Figure 2: In the notes to this figure, you should add that the 1,440 subplots are illustrated as 24 rows x 12 columns, each containing 5 subplots (24 x 12 x 5 = 1,440).
+Also add that there are 72 rows x 120 columns of cells (72 x 120 = 8,640).
+</span>
 

### 2023-11-05 Writing/manuscript_gwr.rmd
replies

@@
 First, they assumed a quadratic functional form of yield response, even though a consensus has evolved in the academic literature that the quadratic-plateau functional form better represents the yield-nitrogen relationship.
-It seems likely that they made this assumption primarily because no statistical software is readily usable to estimate GWR with nonlinear functional form.
 Second, as will be discussed in detail in the following section, their approach suffers from bias that is endemic to any study that tries to estimate the value of a statistical method in the OFPE context, which is that it is necessary because the true yield response function is unknowable and can only be estimated.
@@
 However, this approach can result in significant bias in the estimation of the value of VRA because of the step 3's assumption that the estimated yield response functions are the true yield response functions.
-@trevisan2021spatial provided an example at step 3 by assuming that their GWR estimates provided "true" site-specific yield response functions.
 This assumption is generally unavoidable for researchers since they cannot observe any real field's true site-specific yield response functions.
@@
 
-# Materials and Methods
+# Methods: Monte Carlo Simulations
 
-We evaluated two sets of GWR quadratic specifications used in @rakshit2020 and @trevisan2021spatial, both of which assumed a quadratic response of yield to nitrogen rate (N).
+This study conducte Monte Carlo simulations to evaluate two sets of GWR quadratic specifications used in @rakshit2020 and @trevisan2021spatial in terms of their economic performance and also bias in estiamting the value of VRA over URA.
+Both specifications assume a quadratic response of yield to nitrogen rate (N).
 However, while @trevisan2021spatial estimated the coefficient on N$^2$ as a global parameter, @rakshit2020 estimated it locally for each point.
@@
 For the same reason, neither can we test whether @trevisan2021spatial over-estimate the actual value of VRA.
-But in the Monte Carlo simulations we specified yield response functions and generated stylized data from those functions, which enabled us to quantify in the context of the simulations the value of GWR and the bias in GWR-based estimation of the value of VRA.
+But in the Monte Carlo simulations we specify yield response functions and generated stylized data from those functions, which enable us to quantify in the context of the simulations the value of GWR and the bias in GWR-based estimation of the value of VRA.
 Monte Carlo simulations are commonly used in this way to gain insights into the statistical and economic properties of trial designs and estimations methods [@alesso2021design; @bullock2020value; @gebbers2010application; @mckinion2001analysis].
-We conducted one thousand rounds of Monte Carlo simulation to answer our research questions.
+We conduct one thousand rounds of Monte Carlo simulation to answer our research questions.
 The process and components of the simulation analysis are detailed below.
+
+Our simulations are run using R \citep{}, and all the R programs are publicly accessible at the following GitHub direcotr: https://github.com/tmieno2/GWR_value.
 
@@
 
-Figures \@ref(fig:field-layout) and \@ref(fig:field-N-design) illustrate the Latin square trial design schema assumed in each simulation.
-The field was partitioned into a 4-block $\times$ 2-block grid, in which each block was partitioned into a 6-plot $\times$ 6-plot grid with each of six N rates assigned to exactly one plot in each row and each column of the block.
+Figures \@ref(fig:field-layout) and \@ref(fig:field-N-design) illustrate the Latin square trial design assumed in each simulation.
+The field was partitioned into a 4-block $\times$ 2-block grid, in which each block was partitioned into a 6-plot $\times$ 6-plot grid with each of six N rates assigned to exactly one plot in each row and each column of the block (i.e., a Latin square).
 The design ensured that no adjacent N plots were assigned the same N rate.

### 2023-11-05 Writing/manuscript_gwr.rmd
addressed minor writing comments

--- 2023-11-05 Writing/manuscript_gwr.rmd
@@
 We will do so using Monte Carlo simulations, which, since we define and know the true yield response function in the data generating process, allow us to measure the degree of bias.
-Unlike in @griffith2008spatial, @harris2019simulation, @paez2011simulation, and @da2016multiple, our objective is not to measure the bias in the coefficient estimation by GWR, but rather to measure economic effects^[While the environmental impacts of fertilizer management are of great social importance, it is out of the scope of this study.] of the statistical inaccuracy in estimating the coefficients of the model.
+Unlike in @griffith2008spatial, @harris2019simulation, @paez2011simulation, and @da2016multiple, our objective is not to measure the bias in the coefficient estimation by GWR, but rather to measure economic effects^[While the environmental impacts of fertilizer management are of great social importance, it is out of the scope of this study.
+The "economically optimal" in the context of this study does not mean "socially optimal", but is rather limited to the economic optimization of farmers' private production.] of the statistical inaccuracy in estimating the coefficients of the model.
 We show that the misspecification tends to significantly over-estimate GWR's true economic value.
@@
 Data from the 6m-long headlands, side-lands (there are no transition zones on the north and south ends of the field), and 12m-wide "transition zones" were not included in the analysis.
-In total, data from 1440 subplots were available for experimental data analysis.
+In total, simulated data from 1440 subplots were used for data analysis.
 The index $j \in {1, 2, \dots, 1440}$ identifies the field's subplots, and the index $i \in {1, \dots , 6}$ identifies the cells within a subplot.
@@
 $\tau_{j,i}$ can be interpreted as the critical value of N rate at which cell $(j, i)$'s yield reaches its plateau, where yield no longer increases with N rate.
-$\varepsilon_{j, i}$ is a stochastic error term.
+$\varepsilon_{j, i}$ is a stochastic error term following a normal distribution and is spatially autocorrelated.
 The quadratic-plateau functional form implies a diminishing marginal product of N until a yield plateau, which are desirable properties for a yield response function [@frank1990comparison] and a pattern commonly observed in agronomic studies.

### 2023-11-05 Writing/JAAEA/2ndRoundRevision/reply_to_reviewer_2.rmd
test
more replies added

@@
 
-Response:
+Response: We added an explanation that the 600m range was chosen based on empirical data of our existing on-farm trials (see page ??, lines ??).
 
@@
 
-Response:
+Response: Expalining how the shape constraint is imposed would take more than a page of mathematical explanations.
+We added a footnote that  cites Pya's journal article titled "Shape constrained additive models" published in Statistics and computing.
 
@@
 
-Response:
+Response: There is no speculation in this sentence.
+We are stating a drawback of linear-plateau model.
+What we state is a irrefutable fact and important in real world practice of estimating yield response function.
 
@@
 
-+ P. 4, line 45: Replace "dramatic" with "seemingly implausibly large"
++ <span style = "color: blue;">P. 4, line 45: Replace "dramatic" with "seemingly implausibly large"</span>
 
-Response:
+Response: We followed your suggestion.
 
-+ P. 4, line 54: Replace "suspect" with "hypothesize"
-o Same comment for "suspect" on P. 9, line 153
++ <span style = "color: blue;">P. 4, line 54: Replace "suspect" with "hypothesize". Same comment for "suspect" on P. 9, line 153</span>
 
-Response:
+Response: We followed your suggestion.
 
-+ P. 5, line 77: You do not need to write (OFPE) again here since you have already introduced
-the acronym.
++ <span style = "color: blue;">P. 5, line 77: You do not need to write (OFPE) again here since you have already introduced
+the acronym.</span>
 
-Response:
+Response: We followed your suggestion.
 
-+ P. 8, line 124: You should place the first instance of "(EONR)" here after "economically
-optimal nitrogen rates" rather than line 132.
++ <span style = "color: blue;">P. 8, line 124: You should place the first instance of "(EONR)" here after "economically
+optimal nitrogen rates" rather than line 132.</span>
 
-Response:
+Response: We followed your suggestion.
 
-+ P. 8, line 130: Replace "dangerous" with "problematic"
-o Same comment for P. 22, line 438
++ <span style = "color: blue;">P. 8, line 130: Replace "dangerous" with "problematic" Same comment for P. 22, line 438 </span>
 
-Response:
+Response: We followed your suggestion.
 
@@
 
-Response:
+Response: We followed your suggestion.
 
@@
 
-Response:
+Response: We have changed the wording to "In this scenario."
 
@@
 Additionally, you should add quotation marks to both instances of "pure" in this paragraph.
-Response:
+
+Response: We followed your suggestion.

### 2023-11-05 Writing/manuscript_gwr.rmd
more replies added

@@
 A higher range value indicates increased spatial dependence, meaning that less abrupt differences tend to be observed between the production function parameters of neighboring cells.
+The choice of 600m range in this study was based on empirical data generated through eight on-farm randomized N field trials conducted by the Data-Intensive Farm Management Project (DIFM) project in 2018 [@bullock2019data].
 The mean and sill variance of each parameter were specified to result in a realistic mean yield of $11,416$ kg ha$^{-1}$, and such that the cells' true economically optimal N rates ranged from $113$ kg ha$^{-1}$ to $273$ kg ha$^{-1}$ across all the simulations, a range into which most real-world N rate recommendations fall [e.g., @sawyer2018].
 Note that the range of the optimal N rates of individual rounds of simulations are narrower.
-In defining the magnitude of the error term, we utilized the experimental data generated through eight on-farm randomized N field trials conducted by the Data-Intensive Farm Management Project (DIFM) project in 2018 [@bullock2019data].
+The magnitude of the error term $\varepsilon_{j, i}$ was also based on the DIFM project empirical data.
 Using the data from each of the eight actual trials, separate regressions of yield on N were run, and standard deviations of the residuals were calculated.
@@
 where $g_k(\cdot)$ is the $k$th spline basis and $\beta_k$ is its coefficient to be estimated.
-The $\beta_k$s were constrained such that the resulting relationship between $y_j$ and $N_j$ is such that $y_j$ monotonically increases with $N_j$, but at a diminishing rate.
+The $\beta_k$s were constrained such that the resulting relationship between $y_j$ and $N_j$ is such that $y_j$ monotonically increases with $N_j$, but at a diminishing rate^[Please see @pya2015shape for technical details on how to implement this constraint under the GAM framework.].
 

### 2023-11-05 Writing/manuscript_gwr.rmd
minor changes

--- 2023-11-05 Writing/manuscript_gwr.rmd
@@
 @trevisan2021spatial demonstrated a method of providing site-specific management recommendations without such data.
-They estimated site-specific yield response functions by applying GWR techniques on OFPE data, and reported dramatic results, estimating an average potential gain of \$65 ha$^{-1}$ from applying seed and nitrogen (N) at optimal uniform rates instead of at the rates the farmers would have chosen if not participating in the research, and an additional potential gain of \$58 ha$^{-1}$ when changing from the optimal uniform application rate to optimal site-specific application rates.
+They estimated site-specific yield response functions by applying GWR techniques on OFPE data, and reported implausibly large results, estimating an average potential gain of \$65 ha$^{-1}$ from applying seed and nitrogen (N) at optimal uniform rates instead of at the rates the farmers would have chosen if not participating in the research, and an additional potential gain of \$58 ha$^{-1}$ when changing from the optimal uniform application rate to optimal site-specific application rates.
 This might be seen as surprising given the often-reported poor statistical accuracy of GWR estimates [@griffith2008spatial; @harris2019simulation; @paez2011simulation; @da2016multiple] and also the much lower value of variable rate application (VRA)  management over uniform rate application (URA) management reported in previous studies [@bullock1998does; @koch2004economic; @thrikawala1999economic].
 
-We suspect that the value of GWR reported by @trevisan2021spatial is a result of over-estimation bias.
+We hypothesize that the value of GWR reported by @trevisan2021spatial is a result of over-estimation bias.
 There are two key sources of bias in their approach.
@@
 ## Conceptual Framework
-On-farm precision experimentation (OFPE) can provide detailed as-applied input and yield data at dense resolutions over entire fields, which if well analyzed may provide valuable information that can improve site-specific input application recommendations [@bullock2019data; @lacoste2021farm].
+OFPE can provide detailed as-applied input and yield data at dense resolutions over entire fields, which if well analyzed may provide valuable information that can improve site-specific input application recommendations [@bullock2019data; @lacoste2021farm].
 Consider a yield response function $y = f(\textbf{x}, \textbf{c})$, where following @bullock2000agronomic, $\textbf{x}$ is a vector of input management variables and $\textbf{c}$ is a vector of spatial variables describing field and soil characteristics^[For simplicity, we suppress discussion of the need to bring variance in weather data into yield response estimation.
@@
 @rakshit2020 also estimated site-specific yield response functions by applying GWR to on-farm experiment data assuming a quadratic functional form of yield response.
-But they did not calculate site-specific economically optimal nitrogen rates, and so unlike @trevisan2021spatial, did not conduct economic analysis.
+But they did not calculate site-specific economically optimal nitrogen rates (EONRs), and so unlike @trevisan2021spatial, did not conduct economic analysis.
 @evans2020assessment explored using GWR with a linear model specification to detect low- and high-response areas, but like @rakshit2020, did not estimate site-specific economically optimal nitrogen rates.
@@
 
-There are two potentially dangerous factors that may have caused significant over-estimation of the value of GWR as a tool to estimate site-specific economically optimal nitrogen application rates (EONRs) in @trevisan2021spatial.
+There are two potentially problematic factors that may have caused significant over-estimation of the value of GWR as a tool to estimate site-specific economically optimal nitrogen application rates in @trevisan2021spatial.
 First, @trevisan2021spatial assumed a quadratic functional form in their GWR estimation even though there is a wide consensus among the scientific community that corn yield response to nitrogen is better represented by the quadratic-plateau functional form.
@@
 In general, researchers take the following steps to estimate the value of VRA using OFPE data [@anselin2004spatial; @bullock2002adding; @liu2006site; @swinton1998evaluating]: (1) estimate site-specific yield response functions based on a method chosen by the researcher; (2) use the estimated yield response functions to estimate the economically optimal site-specific input rates (EOIRs) and economically optimal uniform input rates; (3) plug the estimated site-specific EOIRs and uniform EOIR into the estimated yield response functions to calculate estimated profits under both strategies; and (4) find the difference in the two strategies' estimated profits.
-However, this approach can result in significant bias in the estimation of the value of VRA because of the step 3's assumption that the estimated yield response functions are the true yield response functions.
+However, this approach can result in significant bias in the estimation of the value of VRA because of step 3's assumption that the estimated yield response functions are the true yield response functions.
 This assumption is generally unavoidable for researchers since they cannot observe any real field's true site-specific yield response functions.
@@
 This bias problem can be particularly severe when the method used tends to exaggerate the true heterogeneity in yield response functions, such as GWR [@czarnota2015evaluating].
-We suspect that the high value of VRA estimated by @trevisan2021spatial displays this bias.
+We hypothesize that the high value of VRA estimated by @trevisan2021spatial displays this bias.
 
@@
 $\varepsilon_{j, i}$ is a stochastic error term following a normal distribution and is spatially autocorrelated.
-The quadratic-plateau functional form implies a diminishing marginal product of N until a yield plateau, which are desirable properties for a yield response function [@frank1990comparison] and a pattern commonly observed in agronomic studies.
+The quadratic-plateau functional form implies a diminishing marginal product of N until a yield plateau, which is a desirable property for a yield response function [@frank1990comparison] and a pattern commonly observed in agronomic studies.
 Note that the cell-specific yield response function $f_{j, i} (N)$ is the reduced form of the meta response function $f$ when the characteristics vector takes on the value $\textbf{c}_{j, i}$.
@@
 The design ensured that no adjacent N plots were assigned the same N rate.
-Furthermore, the order of N rates in each row of every block was specified to avoid relatively large changes in N rates (due the technological limitations of N application equipment commonly witnessed in real-world OFPE).
+Furthermore, the order of N rates in each row of every block was specified to avoid relatively large changes in N rates (due to the technological limitations of N application equipment commonly witnessed in real-world OFPE).
 
@@
 
-In the lower benchmark situation, a researcher was assumed to work with farmers to run OFPEs, gather data, and then to estimate a "full-field" uniform yield response function using the SCAM non-parametric regression framework [@pya2015shape].
+In this scenario, a researcher was assumed to work with farmers to run OFPEs, gather data, and then to estimate a "full-field" uniform yield response function using the SCAM non-parametric regression framework [@pya2015shape].
 SCAM is a type of generalized additive model (GAM) [@hastie1986gam] which allows for more flexible and nonlinear  relationships between the response variable and the predictors through a combination of smooth functions (also known as "splines").
@@
 
-The GWRT model is also called as "mixed" GWR in the literature [@brunsdon1999some], where some parameters are fixed globally while others vary geographically.
+The GWRT model is also called the "mixed" GWR in the literature [@brunsdon1999some], where some parameters are fixed globally while others vary geographically.
 We estimated the coefficient on $N^2$ as a global parameter and the coefficient on $N$ subplot-specifically.
@@
 Since the estimation of the coefficient on $N^2$ is highly inaccurate, the range of estimated EONRs is much wider than the range of true site-specific EONRs.
-However, GWRT's range of EONR estimates is very narrow because the coefficient on $N^2$ is constrained to be equal across sites, making GWRT fail to capture the EONR's truea spatial heterogeneity.
+However, GWRT's range of EONR estimates is very narrow because the coefficient on $N^2$ is constrained to be equal across sites, making GWRT fail to capture the EONR's true spatial heterogeneity.
 
@@
 
-Our results clearly show that it can be dangerous to use GWR under the assumption of a quadratic functional form when the true yield-input relationship is quadratic-plateau.
+Our results clearly show that it can be problematic to use GWR under the assumption of a quadratic functional form when the true yield-input relationship is quadratic-plateau.
 @trevisan2021spatial had to choose the quadratic functional form because no readily usable statistical software or package could be used to implement nonlinear GWR.
@@
 It is also noted that the recently developed multi-scale GWR model [@fotheringham2017multiscale; @yu2020inference; @comber2022route] allows the bandwidth to be derived separately for each covariate in the model, which would potentially improve the performances of GWR estimates and may need to be incorporated into future research.
-Please note, however, that multi-scale GWR models are not necessary in our simulations as we have only one covariate ($N$) in our simulations.
+Note, however, that multi-scale GWR models are not necessary in our simulations as we have only one covariate ($N$) in our simulations.
 
@@
 
-Finally, it would be interesting to examine the pure performance of GWR.
+Finally, it would be interesting to examine the "pure" performance of GWR.
 The objective of this article was to evaluate GWR with quadratic functional form when the true yield-input relationship is quadratic-plateau.
 Therefore, we evaluated GWR under a particular kind of model misspecification.
-After the development of software that can run GWR with a quadratic-plateau model, it would be interesting to see how it performs when the true yield response to input is quadratic-plateau.
-In this case, there is no functional form misspecification and the pure ability of GWR could be isolated.
+It would be interesting to see how it performs when the true yield response to input is quadratic-plateau.
+In this case, there is no functional form misspecification and the "pure" ability of GWR could be isolated.
 

### 2023-11-05 Writing/JAAEA/2ndRoundRevision/reply_to_reviewer_2.rmd
minor changes
modified

@@
 
-Writing
+# Writing
 
@@
 
-+ P. 8, line 145: Remove the word "the" in front of "step"
++ <span style = "color: blue;">P. 8, line 145: Remove the word "the" in front of "step"</span>
 
@@
 
-+ P. 11, lines 200-201: Replace "are desirable properties" with "is a desirable property"
++ <span style = "color: blue;">P. 11, lines 200-201: Replace "are desirable properties" with "is a desirable property" </span>
 
@@
 
-+ P. 13, line 233: Replace "due the" with "due to the"
++ <span style = "color: blue;">P. 13, line 233: Replace "due the" with "due to the"</span>
 
@@
 
-+ P. 14, line 262: This is the first and only mention in the paper of a benchmark. Given that,
-what is a "lower" benchmark?
++ <span style = "color: blue;">P. 14, line 262: This is the first and only mention in the paper of a benchmark. Given that, what is a "lower" benchmark?</span>
 
@@
 
-+ P. 16, line 295: Replace "as" with "the"
++ <span style = "color: blue;">P. 16, line 295: Replace "as" with "the"</span>
 
@@
 
-+ P. 19, line 269: Replace "truea" with "true"
++ <span style = "color: blue;">P. 19, line 269: Replace "truea" with "true"</span>
 
@@
 
-+ P. 22, line 453: Remove the word "please"
++ <span style = "color: blue;">P. 22, line 453: Remove the word "please"</span>
 
@@
 
-+ P. 24, lines 468-474: Remove the clause "After the development of software that..."
-Additionally, you should add quotation marks to both instances of "pure" in this paragraph.
++ <span style = "color: blue;">P.
+24, lines 468-474: Remove the clause "After the development of software that..." Additionally, you should add quotation marks to both instances of "pure" in this paragraph.</span>
 

### 2023-11-05 Writing/JAAEA/2ndRoundRevision/reply_to_reviewer_1.rmd
replies to reviewer 1 added

---
title: "Reply"
output: 
  html_document: default
---

Your comments are in blue, and our responses are in black.

1. <span style = "color: blue;"> The statement in the Abstract "...because no readily available statistical packages exist for GWR estimation with nonlinear functional forms" is inaccurate. A 2022 Precision Agriculture article includes a Linear Response Plateau GWR package in the supplemental materials. </span>

**Response**: This is good to know because the authors do not mention this at all in the paper. But, they only provide bare matlab codes without any readme file. I would not call this readily available. However, we will drop the sentence. (We understand that you told us we cannot ignore this comment, but we just wanted to point this out because we are keeping that sentence.)

2. <span style = "color: blue;">A flat response could have produced the "high values" of VRA reported by Trevisan et al., not the method used to estimate yield response. A quadratic functional form (and even a quad-response with a plateau) will likely produce optimal n-rates outside the experimental n-rates if the response is flat.</span>

**Response**: We completely agree with the first part. We, however, limit the estimated optimal N rates to be inside the range of the experimental range (e.g., if higher than the highest experimental rate, then the EONR was set to the highest experimental rate). Therefore, the second statement is no corret. With that said, if we were to allow the optimal N rate to go beyond the range of the experimental rates, then the bias would have been even greater than what we report in the manuscript. Finally, as we mentioned, we do not intend to isolate the impact of functional misspecification and the use of GWR in causing bias in estimating the value of VRA.

We realized that we did not state thaa we limited the estimted EONR to the range of the experimental rates. We added the following sentence to the manuscript on page ??, line ??":

"It should be noted that in some locations the estimated EONRs would be below or above the bound of trial N rates. For those locations, the minimum or maximum trial N rate was used as the corner solution of that location’s EONR. For example, if the estimated EONR was 40 kg/ha, the minimum trial N rate 80 kg/ha will be used as the EONR instead."

3. <span style = "color: blue;">The quad-response with plateau "true" d.g.p is a red herring. One would arrive at the same result if a regular quadratic response function was used. If a QRP were ESTIMATED, the results would be different from a standard quad-response function if the data exhibited a plateau.</span>

**Response**: Ignored as suggested.

4. <span style = "color: blue;"> The authors generate the "true" site-specific parameters using a Gaussian random field. It does not appear that the authors allowed correlations between the model parameters. In practice, response parameters are typically correlated. How does this affect the simulation results? It is unclear if the simulated random field ensured that parameters of the linear and quadratic n-rates were constrained to be positive and negative, respectively. How was this verified?</span>

**Response**:

This comment clearly shows that this reviewer did not pay attention to our replies to his comments. In our reply to his comments, we clearly stated that the site-specific parameters are indeed spatially correlated. We also ensured that the coefficients on the linear and quadratic n-rates were constrained to be positive and negative. This is not a hard task. We share all the codes written in R on a publicly accessible repository. Anybody can check how this was done in our paper.

5. <span style = "color: blue;">Page 11, Line 206: was this random field generated once and then used for 1,000 MC iterations, or was the field generated for each MC iteration? What about the errors? What were the nugget, sill, etc., for each simulated parameter?  </span>

**Response**:

Site-specific parameters and errors were generated for each of the 1000 MC iterations. So all simulation instanes have different spatial patterns of EONR. Parameters of the variogram (nugget, sill, etc) stays the same across the simulations, meaning that the spatial dependence of the site-specific parameters are the same.

6. <span style = "color: blue;">Replicability. How would one proceed if one were to replicate what the authors did? For example, "Note that the range of the optimal N rates of individual rounds were narrower." What does this mean? Yield Data generation. What distribution were the e's? The Methods need to be more clearly documented if others want to replicate the study.</span>

**Response**:

We agree that we can provide more information on how the data is generated. The error term is follows the normal distribution with spatial correlation (a sentence on this added on page ??, line ??).

However, we emphasize that we are dedicated for reproducibility of our work and all the computer programs are made publicly available at the GitHub repository dedicated for this project (The url of this repository is shared in the manuscript in page ??, line??). It is simply impossible to describe all the details of the simulations. Reproducibility can be achieved only when the full computer programs are shared, which we do.

7. <span style = "color: blue;">Then correct d.g.p.'s for each model should be used to generate yield data, optimal EONR, and profit. Each competing model would use the data from its challengers to estimate the parameters. These results would then be compared to the "true" N* and profit values.</span>

**Response**: Ignored as suggested

8. <span style = "color: blue;"> Consider Page 17, line 328. You have f_GWR(N_SCAM) and f_GWR(N_GWR). However, what of f_SCAM(N_SCAM) and f_SCAN(N_GWR)? Why is a whole field, uniform-rate type model used as a benchmark?</span>

**Response**: Ignored as suggested

9. <span style = "color: blue;"> The cost of committing a type-II error would indicate the value of information lost using GWR. The PiHat comparisons are a step forward toward this, but the comparisons are incomplete. The logic of using SCAM needs to be argued more convincingly. One could re-do the analysis using a different, less complicated whole-field response model without loss of generality. </span>

**Response**: Ignored as suggested

10. <span style = "color: blue;">Why was SCAM used to estimate a whole-field response? Why not QRP? The SCAM comparison with GWR (and with a quad-response) is not apples-to-apples.</span>

**Response**: Ignored as suggested

11. <span style = "color: blue;">If the GWR d.g.p., was used as the true d.g.p., for example, y* = X(X'W(s)X)-1X'W(s)y + e*, with W(s) GWR weights and e~N(0, sig2e), then GWR should perform better. The manuscript needs a scenario that finds GWR bias in profit when the true d.g.p. is GWR.</span>

<span style = "color: blue;">Other notes:
The text had no figure numbers, so it was hard to tell which figures we were supposed to see. What did appear in the manuscript was "Error! Reference source not found."</span>

**Response**: Ignored as suggested

### 2023-11-05 Writing/manuscript_gwr.rmd
replies to reviewer 1 added

@@
 **Abstract**: Geographically weighted regression (GWR) has been presented as a valuable tool for the estimation of site-specific yield response functions used to derive site-specific input rate recommendations from data generated by on-farm precision experimentation (OFPE).
-But applications of GWR in this context have assumed a quadratic yield response function, despite a scientific consensus that the yield-input relationships modeled are better represented by the quadratic-plateau functional form.
-The quadratic assumption has been made because no readily available statistical packages exist for GWR estimation with nonlinear functional forms.
+But most of the applications of GWR in this context have assumed a quadratic yield response function, despite a scientific consensus that the yield-input relationships modeled are better represented by the quadratic-plateau functional form.
 The key objective of this paper is to investigate whether, when the true functional form of yield response is quadratic-plateau, assuming a quadratic form introduces bias into the GWR estimation of the economic value of site-specific recommendation maps.

### 2023-11-05 Writing/manuscript_gwr.rmd
modified

--- 2023-11-05 Writing/manuscript_gwr.rmd
@@
 
+It should be noted that in some locations the estimated EONRs would be below or above the bound of trial N rates.
+For those locations, the minimum or maximum trial N rate was used as the corner solution of that location’s EONR.
+For example, if the estimated EONR was 40 kg/ha, the minimum trial N rate 80 kg/ha will be used as the EONR instead.
+
 ### GWR-Trevisan (GWRT)

### 2023-11-05 Writing/JAAEA/2ndRoundRevision/reply_to_reviewer_2.rmd

@@
 
-Response:
+Response: We apologize for the figure number errors.
+Those were generated by the online PDF compiling tool of JAAEA submision website.
+We will communicate with the journal editor and technician to solve the errors.
 
@@
 
-Response:
+Response: Here at the beginning of this session, we only briefly introduce the procedure of estimating uniform EONR.
+The more detailed explanation of how EONR is calculated by solving for maximization of p\cdot \hat{f}^{SCAM} (N)-w\cdot N was described in the later part (see line 281??)
 
@@
 
-Response:
+Response: We added the following details to the Figure 2 notes: "The experimental field contains a total of 288 N trial plots, arranged in 24 rows $\times$ 12 columns.
+Each N plot contains 5 effective yield subplots (as illustrated in Figure 1, Panel b), and the total number of subplots is 1,440.
+The total number of effective cells are 8,640 (72 rows $\times$ 120 columns)".
 

### 2023-11-05 Writing/JAAEA/2ndRoundRevision/reply_to_reviewer_1.rmd
more replies

@@
 
-This comment clearly shows that this reviewer did not pay attention to our replies to his comments.
+This comment clearly shows that this reviewer did not pay attention to our replies to his comments (the first round review, comment 1).
 In our reply to his comments, we clearly stated that the site-specific parameters are indeed spatially correlated.
-We also ensured that the coefficients on the linear and quadratic n-rates were constrained to be positive and negative.
+We also ensured that the coefficients on the linear and quadratic N-rates were constrained to be positive and negative.
 This is not a hard task.
@@
 
-Site-specific parameters and errors were generated for each of the 1000 MC iterations.
-So all simulation instanes have different spatial patterns of EONR.
-Parameters of the variogram (nugget, sill, etc) stays the same across the simulations, meaning that the spatial dependence of the site-specific parameters are the same.
+Site-specific parameters and errors were generated for each of the 1,000 Monte Carlo iterations, resulting in distinct spatial patterns of Economic Optimum Nitrogen Rate (EONR) for each simulation instance.
+However, the parameters of the variogram (such as nugget and sill) remain consistent across simulations, ensuring that the spatial dependence of the site-specific parameters is the same.
+
+Clarifying sentences were added to page ??, line ??.
 
@@
 
-We agree that we can provide more information on how the data is generated. The error term is follows the normal distribution with spatial correlation (a sentence on this added on page ??, line ??).
+We agree that we can provide more information on how the data is generated. The error term follows the normal distribution with spatial correlation (a sentence on this added on page ??, line ??).
 

### 2023-11-05 Writing/manuscript_gwr.rmd
more replies

@@
 The mean value of the eight standard deviations was $1370$ kg ha$^{-1}$, which was the square root value of the sill variances assigned to the simulations' error terms.
+Site-specific parameters and errors were generated for each of the 1,000 Monte Carlo iterations, resulting in distinct spatial patterns of EONR for each simulation instance.
+However, the parameters of the variogram (such as nugget and sill) remain consistent across simulations, ensuring that the spatial dependence of the site-specific parameters is the same.
 

### 2023-11-05 Writing/JAAEA/2ndRoundRevision/reply_to_reviewer_1.rmd
more replies

--- 2023-11-05 Writing/JAAEA/2ndRoundRevision/reply_to_reviewer_1.rmd
@@
 
-Site-specific parameters and errors were generated for each of the 1000 MC iterations.
-So all simulation instanes have different spatial patterns of EONR.
-Parameters of the variogram (nugget, sill, etc) stays the same across the simulations, meaning that the spatial dependence of the site-specific parameters are the same.
+Site-specific parameters and errors were generated for each of the 1,000 Monte Carlo iterations, resulting in distinct spatial patterns of Economic Optimum Nitrogen Rate (EONR) for each simulation instance.
+However, the parameters of the variogram (such as nugget and sill) remain consistent across simulations, ensuring that the spatial dependence of the site-specific parameters is the same.
 

### 2023-11-05 Writing/manuscript_gwr.rmd
more replies

--- 2023-11-05 Writing/manuscript_gwr.rmd
@@
 
-Finally, it would be interesting to examine the "pure" performance of GWR.
-The objective of this article was to evaluate GWR with quadratic functional form when the true yield-input relationship is quadratic-plateau.
-Therefore, we evaluated GWR under a particular kind of model misspecification.
-It would be interesting to see how it performs when the true yield response to input is quadratic-plateau.
-In this case, there is no functional form misspecification and the "pure" ability of GWR could be isolated.
-
 <!-- # Conclusions

### 2023-11-11 Writing/manuscript_gwr.rmd
some changes made by Xiaofei

--- 2023-11-05 Writing/manuscript_gwr.rmd
@@
 ---
-title: "Economic Evaluation of Mis-speficied Geographically Weighted Regression Models for Site-specific Nitrogen Management"
+title: "Bias in the Estimation of the Value of VRA over URA: A case of Mis-speficied Geographically Weighted Regression Models"
 author:
@@
 
-In recent years, on-farm precision experimentation (OFPE) has gained traction with agricultural researchers and practitioners as a means of generating high-resolution spatial data to inform site-specific crop input management [@bullock2019data; @lacoste2021farm].
+While as-applied yield and input data are relatively easy to collect by modern farming machinery, gathering detailed soil characteristics data is often costly.
+On any given field, it is typical for many row crop farmers to pay for 1-ha (2.5-ac) grid soil sampling and chemical analysis every three or four years [@morris2018strengths].
+The high expense of soil sampling and analysis is also driving development of new sensor technologies that gather data on site-specific field and crop characteristics or proxies of those characteristics, for example, mounted optical sensors for vegetative index (Trimble Agriculture's GreenSeeker and AgLeader's OptRx), towed soil sensor for electroconductivity data (Veris Technologies), etc.
+Those data are then converted into recommended input application rate maps (usually called "prescriptions" or "$R_x$s") by applying formulas provided by agricultural companies (e.g., FieldRevealTM, FieldApex) or university extension services (e.g., @culman2020tri).
+But deploying sophisticated sensors to gather field characteristics data is also costly, and the effects of their generation and use on farming profitability remains in question [@gardner2021economic].
+
+In recent years, on-farm precision experimentation (OFPE) has gained traction with agricultural researchers and practitioners as a means of generating inexpensive, high-resolution yield and input trial data to inform site-specific crop input management [@bullock2019data; @lacoste2021farm].
 Accompanying interest is surging among researchers in identifying efficient statistical methods to estimate site-specific yield response functions with OFPE data.
-Researchers recently have examined various methods, ranging from Geographically Weighted Regression (GWR) [@rakshit2020; @evans2020assessment; @trevisan2021spatial] to machine learning techniques, including random forest [@krause2020random; @de2023predicting], convolutional neural network [@barbosa2020modeling], and causal forest [@kakimoto2022causal] approaches.
-Among these, reported research on the GWR approach have generated special interest because GWR can be used to estimate site-specific yield-to-input relationships without costly spatial field and soil data.
+Researchers recently have examined various methods, ranging from spatial econometrics [@anselin2004spatial; @liu2006site], Geographically Weighted Regression (GWR) [@rakshit2020; @evans2020assessment; @trevisan2021spatial] to machine learning techniques (suhc as random forest [@krause2020random; @de2023predicting], convolutional neural network [@barbosa2020modeling], and causal forest [@kakimoto2022causal]).
+Among these mehtods, however, most still require detailed soil sampling or field characteristics data together with the OFPE (yield, input) data for the site-specific estimation.
+The GWR model, on the other hand, runs a localized regression by taking only (yield, input) data from neighboring points around a site of interest, where the locality is controlled by the bandwidth of the kernel function chosen by the researcher.
+Therefore, it can estimate site-specific yield response functions without the costly soil and field characteristics data, and is appealing in OFPE data analysis.
+
+@evans2020assessment explored using GWR with a linear model specification to detect low- and high-response areas, but like @rakshit2020, did not estimate site-specific economically optimal nitrogen rates.
+
+@rakshit2020 also estimated site-specific yield response functions by applying GWR to on-farm experiment data assuming a quadratic functional form of yield response.
+But they did not calculate site-specific economically optimal nitrogen rates (EONRs), and so unlike @trevisan2021spatial, did not conduct economic analysis.
+
+Using OFPE data, @trevisan2021spatial assumed a quadratic yield response function, and reported large economic benefits associated with using GWR to generate site-specific seed and nitrogen rates recommendations.
 
@@
 They estimated site-specific yield response functions by applying GWR techniques on OFPE data, and reported implausibly large results, estimating an average potential gain of \$65 ha$^{-1}$ from applying seed and nitrogen (N) at optimal uniform rates instead of at the rates the farmers would have chosen if not participating in the research, and an additional potential gain of \$58 ha$^{-1}$ when changing from the optimal uniform application rate to optimal site-specific application rates.
+
 This might be seen as surprising given the often-reported poor statistical accuracy of GWR estimates [@griffith2008spatial; @harris2019simulation; @paez2011simulation; @da2016multiple] and also the much lower value of variable rate application (VRA) management over uniform rate application (URA) management reported in previous studies [@bullock1998does; @koch2004economic; @thrikawala1999economic].
 
-We hypothesize that the value of GWR reported by @trevisan2021spatial is a result of over-estimation bias.
-There are two key sources of bias in their approach.
-First, they assumed a quadratic functional form of yield response, even though a consensus has evolved in the academic literature that the quadratic-plateau functional form better represents the yield-nitrogen relationship.
-Second, as will be discussed in detail in the following section, their approach suffers from bias that is endemic to any study that tries to estimate the value of a statistical method in the OFPE context, which is that it is necessary because the true yield response function is unknowable and can only be estimated.
+* The central interest is the economic performance of GWR. We measure it by the profit improvement of GWR-based VRA over URA. We do not focus on statistical performance, as that is not the 
+final goal
 
-The primary objective of this study is to examine the degree and direction of bias in the estimation of the economic value of GWR-based site-specific nitrogen rate recommendations (i.e., variable rate applications of nitrogen) when the yield response function assumed in the GWR model is specified as quadratic but is actually of quadratic-plateau functional form.
-We will do so using Monte Carlo simulations, which, since we define and know the true yield response function in the data generating process, allow us to measure the degree of bias.
-Unlike in @griffith2008spatial, @harris2019simulation, @paez2011simulation, and @da2016multiple, our objective is not to measure the bias in the coefficient estimation by GWR, but rather to measure economic effects^[While the environmental impacts of fertilizer management are of great social importance, it is out of the scope of this study.
-The "economically optimal" in the context of this study does not mean "socially optimal", but is rather limited to the economic optimization of farmers' private production.] of the statistical inaccuracy in estimating the coefficients of the model.
-We show that the misspecification tends to significantly over-estimate GWR's true economic value.
-
-# Background: Estimation of Yield-to-input Response Relationships Using OFPE Data
-
-## Conceptual Framework
-OFPE can provide detailed as-applied input and yield data at dense resolutions over entire fields, which if well analyzed may provide valuable information that can improve site-specific input application recommendations [@bullock2019data; @lacoste2021farm].
-Consider a yield response function $y = f(\textbf{x}, \textbf{c})$, where following @bullock2000agronomic, $\textbf{x}$ is a vector of input management variables and $\textbf{c}$ is a vector of spatial variables describing field and soil characteristics^[For simplicity, we suppress discussion of the need to bring variance in weather data into yield response estimation.
-Obviously, generation and use of weather data is necessary to provide meaningful probabilistic analysis and input management advice.].
-Letting a field site $i$ be defined as a contiguous area characterized uniformly by a value $\textbf{c}_i$ of the vector of field and soil characteristics, its *site-specific yield response function* is the reduced form of the field's yield response function created when the value of the vector of characteristics variables is set at the site's value, $\textbf{c}_i$:  $f_i(\textbf{x}) \equiv f(\textbf{x}, \textbf{c}_i)$.
-This conceptualization suggests two methods of estimating a field's site-specific yield responses.
-The first is to estimate a "map" of the field characteristics, for example thought of as a set of the field's $n \geq 1$ sites' values of the characteristics vector: $\{\textbf{c}_1,\dots, \textbf{c}_n\}$.
-With that map, regressing yield on $\textbf{x}$ and $\textbf{c}$ generates an estimated "field-specific" yield response function $\hat{f}(\textbf{x},\textbf{c})$.
-Estimates of site-specific yield response functions can then be obtained by inserting the value of the site's characteristic variables into the estimate of the field-specific response function: $\hat{f}_i(\textbf{x}) \equiv \hat{f}(\textbf{x},\textbf{c}_i)$.
-Alternatively, a site-specific yield response function might be estimated simply by taking (input rate, yield) data from points around a site of interest, and regressing yield on input application rates to attain the estimate $\hat{f}_i (\textbf{x})$.
-Stated roughly, using GWR takes the latter approach, which has the advantage of not needing a costly map of field characteristics values.
-
-## Costs of Field Characteristics Data and the Appeal of GWR
-
-On any given field, it is typical for many row crop farmers to pay for 1-ha (2.5-ac) grid soil sampling and chemical analysis every three or four years [@morris2018strengths].
-The data are often used to derive fertilizer application recommendations, for example by applying comparatively simple formulas provided by university extension services (e.g., @culman2020tri).
-The expense of soil sampling and analysis is also driving development of new sensor technologies that gather data on site-specific field and crop characteristics or proxies of those characteristics, and the conversion of those data into recommended input application rate maps (usually called "prescriptions" or "$R_x$s").
-For example, Trimble Agriculture's GreenSeeker and AgLeader's OptRx systems use optical sensors mounted on fertilizer application booms to digitally record vegetative index imagery as farm machinery is driven through fields during early crop growth stages.
-GreenSeeker then uses Oklahoma State University's Sensor-based N Rate Calculator to convert those data into recommended nitrogen fertilizer (N) $R_x$s.
-Veris Technologies manufactures sensor equipment that can be towed through fields to gather apparent electroconductivity (EC) data, which can be used to infer properties of soil content.
-The "decision tool" software FieldRevealTM allows users to upload EC data, elevation data, and vegetative index data, which FieldRevealTM's professional agronomists analyze to provide $R_x$s to farmers.
-FieldApex creates N $R_x$s using foliar vegetative index data from satellite imagery, and SlantRange uses drone imagery for similar purposes.
-But deploying sophisticated sensors to gather field characteristics data is also costly, and the effects of their generation and use on farming profitability remains in question [@gardner2021economic].
-
-The appeal of GWR lies in its ability to estimate localized site-specific yield response functions without measuring these characteristics.
-It runs regressions locally at many points of the field to estimate yield response functions, where the locality is controlled by the bandwidth of the kernel function chosen by the researcher.
-Using OFPE data, @trevisan2021spatial assumed a quadratic yield response function, and reported large economic benefits associated with using GWR to generate site-specific seed and nitrogen rates recommendations.
-@rakshit2020 also estimated site-specific yield response functions by applying GWR to on-farm experiment data assuming a quadratic functional form of yield response.
-But they did not calculate site-specific economically optimal nitrogen rates (EONRs), and so unlike @trevisan2021spatial, did not conduct economic analysis.
-@evans2020assessment explored using GWR with a linear model specification to detect low- and high-response areas, but like @rakshit2020, did not estimate site-specific economically optimal nitrogen rates.
+* Why we use simulation
 
@@
 We hypothesize that the high value of VRA estimated by @trevisan2021spatial displays this bias.
+
+We hypothesize that the economic value of GWR reported by @trevisan2021spatial is a result of over-estimation bias.
+There are two key sources of bias in their approach.
+First, they assumed a quadratic functional form of yield response, even though a consensus has evolved in the academic literature that the quadratic-plateau functional form better represents the yield-nitrogen relationship.
+Second, as will be discussed in detail in the following section, their approach suffers from bias that is endemic to any study that tries to estimate the value of a statistical method in the OFPE context, which is that it is necessary because the true yield response function is unknowable and can only be estimated.
+
+The primary objective of this study is to examine the degree and direction of bias in the estimation of the economic value of GWR-based site-specific nitrogen rate recommendations (i.e., variable rate applications of nitrogen) when the yield response function assumed in the GWR model is specified as quadratic but is actually of quadratic-plateau functional form.
+We will do so using Monte Carlo simulations, which, since we define and know the true yield response function in the data generating process, allow us to measure the degree of bias.
+Unlike in @griffith2008spatial, @harris2019simulation, @paez2011simulation, and @da2016multiple, our objective is not to measure the bias in the coefficient estimation by GWR, but rather to measure economic effects^[While the environmental impacts of fertilizer management are of great social importance, it is out of the scope of this study.
+The "economically optimal" in the context of this study does not mean "socially optimal", but is rather limited to the economic optimization of farmers' private production.] of the statistical inaccuracy in estimating the coefficients of the model.
+We show that the misspecification tends to significantly over-estimate GWR's true economic value.
+
+## Conceptual Framework: Estimation of Yield-to-input Response Relationships Using OFPE Data
+OFPE can provide detailed as-applied input and yield data at dense resolutions over entire fields, which if well analyzed may provide valuable information that can improve site-specific input application recommendations [@bullock2019data; @lacoste2021farm].
+Consider a yield response function $y = f(\textbf{x}, \textbf{c})$, where following @bullock2000agronomic, $\textbf{x}$ is a vector of input management variables and $\textbf{c}$ is a vector of spatial variables describing field and soil characteristics^[For simplicity, we suppress discussion of the need to bring variance in weather data into yield response estimation.
+Obviously, generation and use of weather data is necessary to provide meaningful probabilistic analysis and input management advice.].
+Letting a field site $i$ be defined as a contiguous area characterized uniformly by a value $\textbf{c}_i$ of the vector of field and soil characteristics, its *site-specific yield response function* is the reduced form of the field's yield response function created when the value of the vector of characteristics variables is set at the site's value, $\textbf{c}_i$:  $f_i(\textbf{x}) \equiv f(\textbf{x}, \textbf{c}_i)$.
+This conceptualization suggests two methods of estimating a field's site-specific yield responses.
+The first is to estimate a "map" of the field characteristics, for example thought of as a set of the field's $n \geq 1$ sites' values of the characteristics vector: $\{\textbf{c}_1,\dots, \textbf{c}_n\}$.
+With that map, regressing yield on $\textbf{x}$ and $\textbf{c}$ generates an estimated "field-specific" yield response function $\hat{f}(\textbf{x},\textbf{c})$.
+Estimates of site-specific yield response functions can then be obtained by inserting the value of the site's characteristic variables into the estimate of the field-specific response function: $\hat{f}_i(\textbf{x}) \equiv \hat{f}(\textbf{x},\textbf{c}_i)$.
+Alternatively, a site-specific yield response function might be estimated simply by taking (input rate, yield) data from points around a site of interest $i$, and regressing yield on input application rates to attain the estimate $\hat{f}_i (\textbf{x})$.
+Stated roughly, using GWR takes the latter approach, which has the advantage of not needing a costly map of field characteristics values.
 

### 2023-11-11 Writing/manuscript_gwr.rmd
rewrote the introduction

@@
 Over the past few decades, numerous technological innovations have been made for collecting detailed field information (e.g., yield mapping, soil sampling, remote sensing, etc.) and in developing site-specific management recommendations based on the information.
-But the long-standing question of whether the economic benefit of precision agriculture can offset the technology and information costs [@lowenberg1996revolution; @weiss1996precision] remains difficult to answer, particularly in the context of large-scale production systems [@mcfadden2022information].
+In recent years, on-farm precision experimentation (OFPE) has gained traction with agricultural researchers and practitioners as a means of generating inexpensive, high-resolution yield and input trial data to inform site-specific crop input management [@bullock2019data; @lacoste2021farm].
+One of the crucial and long-stanging research question is how valuable variable rate application (VRA) of input (e.g., fertilizer, seed) over the traditional uniform rate application (URA).
+This is because the answer to this question determines whether farmers should invest in expensive technologies, conduct soil sampling, or purchase third-party variable rate prescription map.
 
-While as-applied yield and input data are relatively easy to collect by modern farming machinery, gathering detailed soil characteristics data is often costly.
-On any given field, it is typical for many row crop farmers to pay for 1-ha (2.5-ac) grid soil sampling and chemical analysis every three or four years [@morris2018strengths].
+Unforuntealy, the estimation of the value of VRA over URA is inherently biased.
+In general, researchers take the following steps to estimate the value of VRA using OFPE data [@anselin2004spatial; @bullock2002adding; @liu2006site; @swinton1998evaluating]: (1) estimate site-specific yield response functions based on a method chosen by the researcher; (2) use the estimated yield response functions to estimate the economically optimal site-specific input rates (EOIRs) and economically optimal uniform input rates; (3) plug the estimated site-specific EOIRs and uniform EOIR into the estimated yield response functions to calculate estimated profits under both strategies; and (4) find the difference in the two strategies' estimated profits.
+The core source of bias lies in step (3).
+It implicitly assumes that the estimated site-specific yield response functions are true.
+Unfortunately, this assumption is not avoidable in general since we will never know the true site-specific yield response functions.
+Consequently, when the estimated site-specific yield response functions are inaccurate and significanly different from the true site-specific yield response functions, it is not hard to imagine that estimation of the value of VRA over URA is also biased.
+The direction of bias can be either negative or positive.
+One way to exercebate the bias is functional form mis-specificaiton because it can immediately introduce mis-reppresentation of the true yield response functions.
+
+There are mainly two strands of approaches in obtaining VRA recommendations using OFPE data.
+First strand uses soil sampling and/or field characteristics (e.g., topography) data together with the OFPE (yield, input) data to estimate site-specific yield response functions.
+Many different statistical methods have been used under this approach, ranging from spatial econometrics [@anselin2004spatial; @liu2006site] to machine learning methods, suhc as random forest [@krause2020random; @de2023predicting], convolutional neural network [@barbosa2020modeling], and causal forest [@kakimoto2022causal].
+The second strand is a characteristic-agnostic approach, represented by geographically weighted regression (GWR), which runs a localized regression by taking only yield- input data from neighboring points around a site of interest [@rakshit2020; @evans2020assessment; @trevisan2021spatial].
+Therefore, it can estimate site-specific yield response functions without site-specific characteristics.
+The benefit of this approach is that it does not require soil sampling or sensing, which can be highly costly^[On any given field, it is typical for many row crop farmers to pay for 1-ha (2.5-ac) grid soil sampling and chemical analysis every three or four years [@morris2018strengths].
 The high expense of soil sampling and analysis is also driving development of new sensor technologies that gather data on site-specific field and crop characteristics or proxies of those characteristics, for example, mounted optical sensors for vegetative index (Trimble Agriculture's GreenSeeker and AgLeader's OptRx), towed soil sensor for electroconductivity data (Veris Technologies), etc.
 Those data are then converted into recommended input application rate maps (usually called "prescriptions" or "$R_x$s") by applying formulas provided by agricultural companies (e.g., FieldRevealTM, FieldApex) or university extension services (e.g., @culman2020tri).
-But deploying sophisticated sensors to gather field characteristics data is also costly, and the effects of their generation and use on farming profitability remains in question [@gardner2021economic].
+But deploying sophisticated sensors to gather field characteristics data is also costly, and the effects of their generation and use on farming profitability remains in question [@gardner2021economic]].
 
-In recent years, on-farm precision experimentation (OFPE) has gained traction with agricultural researchers and practitioners as a means of generating inexpensive, high-resolution yield and input trial data to inform site-specific crop input management [@bullock2019data; @lacoste2021farm].
-Accompanying interest is surging among researchers in identifying efficient statistical methods to estimate site-specific yield response functions with OFPE data.
-Researchers recently have examined various methods, ranging from spatial econometrics [@anselin2004spatial; @liu2006site], Geographically Weighted Regression (GWR) [@rakshit2020; @evans2020assessment; @trevisan2021spatial] to machine learning techniques (suhc as random forest [@krause2020random; @de2023predicting], convolutional neural network [@barbosa2020modeling], and causal forest [@kakimoto2022causal]).
-Among these mehtods, however, most still require detailed soil sampling or field characteristics data together with the OFPE (yield, input) data for the site-specific estimation.
-The GWR model, on the other hand, runs a localized regression by taking only (yield, input) data from neighboring points around a site of interest, where the locality is controlled by the bandwidth of the kernel function chosen by the researcher.
-Therefore, it can estimate site-specific yield response functions without the costly soil and field characteristics data, and is appealing in OFPE data analysis.
-
-@evans2020assessment explored using GWR with a linear model specification to detect low- and high-response areas, but like @rakshit2020, did not estimate site-specific economically optimal nitrogen rates.
-
-@rakshit2020 also estimated site-specific yield response functions by applying GWR to on-farm experiment data assuming a quadratic functional form of yield response.
-But they did not calculate site-specific economically optimal nitrogen rates (EONRs), and so unlike @trevisan2021spatial, did not conduct economic analysis.
-
-Using OFPE data, @trevisan2021spatial assumed a quadratic yield response function, and reported large economic benefits associated with using GWR to generate site-specific seed and nitrogen rates recommendations.
-
-@trevisan2021spatial demonstrated a method of providing site-specific management recommendations without such data.
-They estimated site-specific yield response functions by applying GWR techniques on OFPE data, and reported implausibly large results, estimating an average potential gain of \$65 ha$^{-1}$ from applying seed and nitrogen (N) at optimal uniform rates instead of at the rates the farmers would have chosen if not participating in the research, and an additional potential gain of \$58 ha$^{-1}$ when changing from the optimal uniform application rate to optimal site-specific application rates.
-
-This might be seen as surprising given the often-reported poor statistical accuracy of GWR estimates [@griffith2008spatial; @harris2019simulation; @paez2011simulation; @da2016multiple] and also the much lower value of variable rate application (VRA) management over uniform rate application (URA) management reported in previous studies [@bullock1998does; @koch2004economic; @thrikawala1999economic].
-
-* The central interest is the economic performance of GWR. We measure it by the profit improvement of GWR-based VRA over URA. We do not focus on statistical performance, as that is not the 
-final goal
-
-* Why we use simulation
-
-## Sources of Bias in Estimating the Value of VRA with Mis-specified Yield Response
-
-There are two potentially problematic factors that may have caused significant over-estimation of the value of GWR as a tool to estimate site-specific economically optimal nitrogen application rates in @trevisan2021spatial.
-First, @trevisan2021spatial assumed a quadratic functional form in their GWR estimation even though there is a wide consensus among the scientific community that corn yield response to nitrogen is better represented by the quadratic-plateau functional form.
-It is likely that their choice of quadratic functional form was merely a compromise because no statistical software package implements GWR with a quadratic-plateau functional form.
-The second source of over-estimation bias is endemic to any study that evaluates the value of variable rate application.
-In general, researchers take the following steps to estimate the value of VRA using OFPE data [@anselin2004spatial; @bullock2002adding; @liu2006site; @swinton1998evaluating]: (1) estimate site-specific yield response functions based on a method chosen by the researcher; (2) use the estimated yield response functions to estimate the economically optimal site-specific input rates (EOIRs) and economically optimal uniform input rates; (3) plug the estimated site-specific EOIRs and uniform EOIR into the estimated yield response functions to calculate estimated profits under both strategies; and (4) find the difference in the two strategies' estimated profits.
-However, this approach can result in significant bias in the estimation of the value of VRA because of step 3's assumption that the estimated yield response functions are the true yield response functions.
-This assumption is generally unavoidable for researchers since they cannot observe any real field's true site-specific yield response functions.
-But inaccurate estimation of yield response function in this methodology can result in significant bias in the estimation of the value of VRA.
-This bias problem can be particularly severe when the method used tends to exaggerate the true heterogeneity in yield response functions, such as GWR [@czarnota2015evaluating].
-We hypothesize that the high value of VRA estimated by @trevisan2021spatial displays this bias.
-
-We hypothesize that the economic value of GWR reported by @trevisan2021spatial is a result of over-estimation bias.
-There are two key sources of bias in their approach.
-First, they assumed a quadratic functional form of yield response, even though a consensus has evolved in the academic literature that the quadratic-plateau functional form better represents the yield-nitrogen relationship.
-Second, as will be discussed in detail in the following section, their approach suffers from bias that is endemic to any study that tries to estimate the value of a statistical method in the OFPE context, which is that it is necessary because the true yield response function is unknowable and can only be estimated.
+Among the GWR studies, @trevisan2021spatial estimated site-specific yield response functions by applying GWR on OFPE data, and reported implausibly large estimate of the potential gain of \$58 ha$^{-1}$ when changing from the optimal uniform application rate to optimal site-specific application rates.
+This is surprising given the much lower value of variable rate application (VRA) management over uniform rate application (URA) management reported in previous studies [@bullock1998does; @koch2004economic; @thrikawala1999economic].
+We hypothesize that their estimate of the value of GWR-based VRA over URA are significantly positively biased.
+First, they most likely mis-specified the model of corn yield reponse to nitrogen.
+It has been widely shown in agronomic studies that corn yield exhibits quadratic-plaeau response.
+However, they used quadratic model.
+GWR has also been criticized for its poor statistical accuracy of coefficient estimation [@griffith2008spatial; @harris2019simulation; @paez2011simulation; @da2016multiple].
+We hypothesize that the combination of these two factors may have results in significant over-estimation of the value of VRA over URA.
 
@@
 The "economically optimal" in the context of this study does not mean "socially optimal", but is rather limited to the economic optimization of farmers' private production.] of the statistical inaccuracy in estimating the coefficients of the model.
-We show that the misspecification tends to significantly over-estimate GWR's true economic value.
-
-## Conceptual Framework: Estimation of Yield-to-input Response Relationships Using OFPE Data
-OFPE can provide detailed as-applied input and yield data at dense resolutions over entire fields, which if well analyzed may provide valuable information that can improve site-specific input application recommendations [@bullock2019data; @lacoste2021farm].
-Consider a yield response function $y = f(\textbf{x}, \textbf{c})$, where following @bullock2000agronomic, $\textbf{x}$ is a vector of input management variables and $\textbf{c}$ is a vector of spatial variables describing field and soil characteristics^[For simplicity, we suppress discussion of the need to bring variance in weather data into yield response estimation.
-Obviously, generation and use of weather data is necessary to provide meaningful probabilistic analysis and input management advice.].
-Letting a field site $i$ be defined as a contiguous area characterized uniformly by a value $\textbf{c}_i$ of the vector of field and soil characteristics, its *site-specific yield response function* is the reduced form of the field's yield response function created when the value of the vector of characteristics variables is set at the site's value, $\textbf{c}_i$:  $f_i(\textbf{x}) \equiv f(\textbf{x}, \textbf{c}_i)$.
-This conceptualization suggests two methods of estimating a field's site-specific yield responses.
-The first is to estimate a "map" of the field characteristics, for example thought of as a set of the field's $n \geq 1$ sites' values of the characteristics vector: $\{\textbf{c}_1,\dots, \textbf{c}_n\}$.
-With that map, regressing yield on $\textbf{x}$ and $\textbf{c}$ generates an estimated "field-specific" yield response function $\hat{f}(\textbf{x},\textbf{c})$.
-Estimates of site-specific yield response functions can then be obtained by inserting the value of the site's characteristic variables into the estimate of the field-specific response function: $\hat{f}_i(\textbf{x}) \equiv \hat{f}(\textbf{x},\textbf{c}_i)$.
-Alternatively, a site-specific yield response function might be estimated simply by taking (input rate, yield) data from points around a site of interest $i$, and regressing yield on input application rates to attain the estimate $\hat{f}_i (\textbf{x})$.
-Stated roughly, using GWR takes the latter approach, which has the advantage of not needing a costly map of field characteristics values.
+We show that the mis-specified GWR indeed tends to significantly over-estimate GWR's true economic value.
 
@@
 `r run_pagebreak()`
+
+# Conceptual Framework: Estimation of Yield-to-input Response Relationships Using OFPE Data
+
+OFPE can provide detailed as-applied input and yield data at dense resolutions over entire fields, which if well analyzed may provide valuable information that can improve site-specific input application recommendations [@bullock2019data; @lacoste2021farm].
+Consider a yield response function $y = f(\textbf{x}, \textbf{c})$, where following @bullock2000agronomic, $\textbf{x}$ is a vector of input management variables and $\textbf{c}$ is a vector of spatial variables describing field and soil characteristics^[For simplicity, we suppress discussion of the need to bring variance in weather data into yield response estimation.
+Obviously, generation and use of weather data is necessary to provide meaningful probabilistic analysis and input management advice.].
+Letting a field site $i$ be defined as a contiguous area characterized uniformly by a value $\textbf{c}_i$ of the vector of field and soil characteristics, its *site-specific yield response function* is the reduced form of the field's yield response function created when the value of the vector of characteristics variables is set at the site's value, $\textbf{c}_i$:  $f_i(\textbf{x}) \equiv f(\textbf{x}, \textbf{c}_i)$.
+This conceptualization suggests two methods of estimating a field's site-specific yield responses.
+The first is to estimate a "map" of the field characteristics, for example thought of as a set of the field's $n \geq 1$ sites' values of the characteristics vector: $\{\textbf{c}_1,\dots, \textbf{c}_n\}$.
+With that map, regressing yield on $\textbf{x}$ and $\textbf{c}$ generates an estimated "field-specific" yield response function $\hat{f}(\textbf{x},\textbf{c})$.
+Estimates of site-specific yield response functions can then be obtained by inserting the value of the site's characteristic variables into the estimate of the field-specific response function: $\hat{f}_i(\textbf{x}) \equiv \hat{f}(\textbf{x},\textbf{c}_i)$.
+Alternatively, a site-specific yield response function might be estimated simply by taking (input rate, yield) data from points around a site of interest $i$, and regressing yield on input application rates to attain the estimate $\hat{f}_i (\textbf{x})$.
+Stated roughly, using GWR takes the latter approach, which has the advantage of not needing a costly map of field characteristics values.

### 2023-11-11 Writing/manuscript_gwr.rmd
modified introduction

@@
 
-Precision agriculture technology allows input management strategies to adapt to the spatial and temporal variability of soil and crop conditions within a field.
-Over the past few decades, numerous technological innovations have been made for collecting detailed field information (e.g., yield mapping, soil sampling, remote sensing, etc.) and in developing site-specific management recommendations based on the information.
-In recent years, on-farm precision experimentation (OFPE) has gained traction with agricultural researchers and practitioners as a means of generating inexpensive, high-resolution yield and input trial data to inform site-specific crop input management [@bullock2019data; @lacoste2021farm].
-One of the crucial and long-stanging research question is how valuable variable rate application (VRA) of input (e.g., fertilizer, seed) over the traditional uniform rate application (URA).
-This is because the answer to this question determines whether farmers should invest in expensive technologies, conduct soil sampling, or purchase third-party variable rate prescription map.
+Precision agriculture technology enables the tailoring of input management strategies to the unique spatial and temporal variations in soil and crop conditions within a field.
+In recent decades, there has been a surge in technological advancements for collecting comprehensive field data (such as yield mapping, soil sampling, and remote sensing), which has facilitated the development of site-specific management recommendations.
+Recently, on-farm precision experimentation (OFPE) has emerged as a popular method among agricultural researchers and practitioners.
+It provides a cost-effective way to gather high-resolution data on yields and input trials, which is crucial for informing site-specific crop input management [@bullock2019data; @lacoste2021farm for reference].
+One of the enduring research questions in this domain is the value of variable rate application (VRA) of inputs like fertilizer and seeds compared to traditional uniform rate application (URA).
+This is a pivotal question, as the answer determines whether the investment in costly precision agriculture technologies, conducting soil sampling, or purchasing variable rate prescription maps is justifiable for farmers.
 
-Unforuntealy, the estimation of the value of VRA over URA is inherently biased.
-In general, researchers take the following steps to estimate the value of VRA using OFPE data [@anselin2004spatial; @bullock2002adding; @liu2006site; @swinton1998evaluating]: (1) estimate site-specific yield response functions based on a method chosen by the researcher; (2) use the estimated yield response functions to estimate the economically optimal site-specific input rates (EOIRs) and economically optimal uniform input rates; (3) plug the estimated site-specific EOIRs and uniform EOIR into the estimated yield response functions to calculate estimated profits under both strategies; and (4) find the difference in the two strategies' estimated profits.
+Unfortunately, the estimation of the value of variable rate application (VRA) over uniform rate application (URA) is intrinsically subject to bias.
+Generally, researchers undertake the following steps to estimate the value of VRA using on-farm precision experimentation (OFPE) data [@anselin2004spatial; @bullock2002adding; @liu2006site; @swinton1998evaluating]: (1) estimate site-specific yield response functions based on a method chosen by the researcher; (2) use the estimated yield response functions to estimate the economically optimal site-specific input rates (EOIRs) and economically optimal uniform input rates; (3) plug the estimated site-specific EOIRs and uniform EOIR into the estimated yield response functions to calculate estimated profits under both strategies; and (4) find the difference in the two strategies' estimated profits.
 The core source of bias lies in step (3).
-It implicitly assumes that the estimated site-specific yield response functions are true.
-Unfortunately, this assumption is not avoidable in general since we will never know the true site-specific yield response functions.
-Consequently, when the estimated site-specific yield response functions are inaccurate and significanly different from the true site-specific yield response functions, it is not hard to imagine that estimation of the value of VRA over URA is also biased.
-The direction of bias can be either negative or positive.
-One way to exercebate the bias is functional form mis-specificaiton because it can immediately introduce mis-reppresentation of the true yield response functions.
+The primary source of bias originates from step (3), where it is implicitly assumed that the estimated site-specific yield response functions are accurate representations of reality.
+This is a challenging assumption because the true site-specific yield response functions are ultimately unknowable.
+As such, when the estimated functions diverge significantly from the true functions, it follows that the estimated value of VRA over URA will also be biased.
+This bias could manifest as either an underestimation or overestimation of VRA's value.
+The bias can be exacerbated by mis-specification of the functional form, as this can lead to immediate misrepresentation of the true yield response, further skewing the estimated value of VRA.
 
-There are mainly two strands of approaches in obtaining VRA recommendations using OFPE data.
-First strand uses soil sampling and/or field characteristics (e.g., topography) data together with the OFPE (yield, input) data to estimate site-specific yield response functions.
-Many different statistical methods have been used under this approach, ranging from spatial econometrics [@anselin2004spatial; @liu2006site] to machine learning methods, suhc as random forest [@krause2020random; @de2023predicting], convolutional neural network [@barbosa2020modeling], and causal forest [@kakimoto2022causal].
-The second strand is a characteristic-agnostic approach, represented by geographically weighted regression (GWR), which runs a localized regression by taking only yield- input data from neighboring points around a site of interest [@rakshit2020; @evans2020assessment; @trevisan2021spatial].
-Therefore, it can estimate site-specific yield response functions without site-specific characteristics.
-The benefit of this approach is that it does not require soil sampling or sensing, which can be highly costly^[On any given field, it is typical for many row crop farmers to pay for 1-ha (2.5-ac) grid soil sampling and chemical analysis every three or four years [@morris2018strengths].
+Two primary approaches exist for deriving variable rate application (VRA) recommendations from on-farm precision experimentation (OFPE) data.
+The first approach integrates soil sampling and/or field characteristic data (such as topography) with OFPE data (yield, input) to estimate site-specific yield response functions.
+A variety of statistical methods are employed within this framework, including spatial econometrics [@anselin2004spatial; @liu2006site] and various machine learning techniques like random forests [@krause2020random; @de2023predicting], convolutional neural networks [@barbosa2020modeling], and causal forests [@kakimoto2022causal].
+The second approach is characteristic-agnostic, represented by geographically weighted regression (GWR).
+This technique performs localized regressions using yield and input data from surrounding points near the site of interest [@rakshit2020; @evans2020assessment; @trevisan2021spatial].
+Consequently, it can estimate site-specific yield response functions without needing data on specific site characteristics.
+The advantage here is the circumvention of potentially expensive soil sampling or sensing operations^[On any given field, it is typical for many row crop farmers to pay for 1-ha (2.5-ac) grid soil sampling and chemical analysis every three or four years [@morris2018strengths].
 The high expense of soil sampling and analysis is also driving development of new sensor technologies that gather data on site-specific field and crop characteristics or proxies of those characteristics, for example, mounted optical sensors for vegetative index (Trimble Agriculture's GreenSeeker and AgLeader's OptRx), towed soil sensor for electroconductivity data (Veris Technologies), etc.
@@
 
-Among the GWR studies, @trevisan2021spatial estimated site-specific yield response functions by applying GWR on OFPE data, and reported implausibly large estimate of the potential gain of \$58 ha$^{-1}$ when changing from the optimal uniform application rate to optimal site-specific application rates.
-This is surprising given the much lower value of variable rate application (VRA) management over uniform rate application (URA) management reported in previous studies [@bullock1998does; @koch2004economic; @thrikawala1999economic].
-We hypothesize that their estimate of the value of GWR-based VRA over URA are significantly positively biased.
-First, they most likely mis-specified the model of corn yield reponse to nitrogen.
-It has been widely shown in agronomic studies that corn yield exhibits quadratic-plaeau response.
-However, they used quadratic model.
-GWR has also been criticized for its poor statistical accuracy of coefficient estimation [@griffith2008spatial; @harris2019simulation; @paez2011simulation; @da2016multiple].
-We hypothesize that the combination of these two factors may have results in significant over-estimation of the value of VRA over URA.
+Among the GWR studies, @trevisan2021spatial utilized GWR to estimate site-specific yield response functions from OFPE data and reported an unusually high potential gain of $58 per hectare from transitioning from the optimal uniform application rate to optimal site-specific application rates.
+Such a figure is notably higher than what has been suggested by previous studies on the value of variable rate application (VRA) over uniform rate application (URA) [@bullock1998does; @koch2004economic; @thrikawala1999economic].
+We suspect that their reported estimate for the benefit of GWR-based VRA over URA may be significantly over-estimated for a couple of reasons.
+First, their model for corn yield response to nitrogen is mostly likely mis-specified.
+Numerous past agronomic studies recognize that corn yield follows a quadratic-plateau response to nitrogen, yet a simple quadratic model was employed by @trevisan2021spatial.
+Second, GWR itself has faced criticism regarding the statistical reliability of its coefficient estimations [@griffith2008spatial; @harris2019simulation; @paez2011simulation; @da2016multiple].
+We hypothesize that the intersection of these two issues—the model mis-specification and the inherent limitations of GWR—may have led to a substantial overestimation of the economic value of switching from URA to VRA.
 
-The primary objective of this study is to examine the degree and direction of bias in the estimation of the economic value of GWR-based site-specific nitrogen rate recommendations (i.e., variable rate applications of nitrogen) when the yield response function assumed in the GWR model is specified as quadratic but is actually of quadratic-plateau functional form.
-We will do so using Monte Carlo simulations, which, since we define and know the true yield response function in the data generating process, allow us to measure the degree of bias.
-Unlike in @griffith2008spatial, @harris2019simulation, @paez2011simulation, and @da2016multiple, our objective is not to measure the bias in the coefficient estimation by GWR, but rather to measure economic effects^[While the environmental impacts of fertilizer management are of great social importance, it is out of the scope of this study.
-The "economically optimal" in the context of this study does not mean "socially optimal", but is rather limited to the economic optimization of farmers' private production.] of the statistical inaccuracy in estimating the coefficients of the model.
-We show that the mis-specified GWR indeed tends to significantly over-estimate GWR's true economic value.
+The primary objective of this study is to examine the degree and direction of bias in the estimation of the economic value of GWR-based variable nitrogen rate recommendations, especially when the yield response to nitrogen is incorrectly specified as quadratic in the GWR model instead of the correct quadratic-plateau function.
+We will employ Monte Carlo simulations, which allow us to accurately define and know the true yield response function within our data-generating process, providing a means to quantify the degree of bias present.
+
+Differing from the works of @griffith2008spatial, @harris2019simulation, @paez2011simulation, and @da2016multiple, our goal is not to critique the bias in GWR's coefficient estimates per se.
+Instead, we seek to assess the economic repercussions^[Note that while the environmental consequences of fertilizer management carry significant societal importance, they fall outside the purview of this study.
+Herein, "economically optimal" pertains strictly to the maximization of private production profitability for farmers and does not imply "socially optimal."] stemming from functional form mis-specifcatin combined with statistical inaccuracies in the coefficient estimation of the model.
+Wd found that a mis-specified GWR model tends to result in substantial over-estimation of the economic value of GWR-based VRA over URA.
 

### 2023-11-12 Writing/manuscript_gwr.rmd
minor edit
Updates from Overleaf

@@
 First, their model for corn yield response to nitrogen is mostly likely mis-specified.
-Numerous past agronomic studies recognize that corn yield follows a quadratic-plateau response to nitrogen, yet a simple quadratic model was employed by @trevisan2021spatial.
+Numerous past agronomic studies recognize that corn yield follows a quadratic-plateau response to nitrogen.
+Ideally, the GWR model should be specified with quadratic-plateau or more flexible functional forms.
+However, no software package is readily usable to estimate GWR with nonlinear functional form.
+A simple quadratic model was employed by @trevisan2021spatial.
 Second, GWR itself has faced criticism regarding the statistical reliability of its coefficient estimations [@griffith2008spatial; @harris2019simulation; @paez2011simulation; @da2016multiple].
@@
 
-The primary objective of this study is to examine the degree and direction of bias in the estimation of the economic value of GWR-based variable nitrogen rate recommendations, especially when the yield response to nitrogen is incorrectly specified as quadratic in the GWR model instead of the correct quadratic-plateau function.
+(Taro: I feel the primary objective should be two-folded.
+As Nathan summarized in his email, they should be (1) the true economic value of GWR-based VRA and, (2) the bias in the estimation of that value.
+But, you make the final call.) The primary objective of this study is to examine the degree and direction of bias in the estimation of the economic value of GWR-based variable nitrogen rate recommendations, especially when the yield response to nitrogen is incorrectly specified as quadratic in the GWR model instead of the correct quadratic-plateau function.
 We will employ Monte Carlo simulations, which allow us to accurately define and know the true yield response function within our data-generating process, providing a means to quantify the degree of bias present.
@@
 Herein, "economically optimal" pertains strictly to the maximization of private production profitability for farmers and does not imply "socially optimal."] stemming from functional form mis-specifcatin combined with statistical inaccuracies in the coefficient estimation of the model.
-Wd found that a mis-specified GWR model tends to result in substantial over-estimation of the economic value of GWR-based VRA over URA.
+We found that functional form mis-specified GWR model tends to result in substantial over-estimation of the economic value of GWR-based VRA over URA.
 
@@
 
-This study conducte Monte Carlo simulations to evaluate two sets of GWR quadratic specifications used in @rakshit2020 and @trevisan2021spatial in terms of their economic performance and also bias in estiamting the value of VRA over URA.
+This study conduct Monte Carlo simulations to evaluate two sets of GWR quadratic specifications used in @rakshit2020 and @trevisan2021spatial in terms of their economic performance and also bias in estiamting the economic value of VRA over URA.
 Both specifications assume a quadratic response of yield to nitrogen rate (N).
@@
 We cannot use real data to test which model specification results in more profitable site-specific nitrogen rate recommendations because it is impossible to observe the true yield response functions using real-world data.
-For the same reason, neither can we test whether @trevisan2021spatial over-estimate the actual value of VRA.
-But in the Monte Carlo simulations we specify yield response functions and generated stylized data from those functions, which enable us to quantify in the context of the simulations the value of GWR and the bias in GWR-based estimation of the value of VRA.
+For the same reason, neither can we test whether the quadratic GWR models over-estimate the actual economic value of VRA.
+But in the Monte Carlo simulations we specify yield response functions and generated stylized data from those functions, which enable us to quantify in the context of the simulations the true economic value of GWR-based VRA and the bias in the estimation of that value.
 Monte Carlo simulations are commonly used in this way to gain insights into the statistical and economic properties of trial designs and estimations methods [@alesso2021design; @bullock2020value; @gebbers2010application; @mckinion2001analysis].
@@
 
-## Trial Design
-
-Figures \@ref(fig:field-layout) and \@ref(fig:field-N-design) illustrate the Latin square trial design assumed in each simulation.
-The field was partitioned into a 4-block $\times$ 2-block grid, in which each block was partitioned into a 6-plot $\times$ 6-plot grid with each of six N rates assigned to exactly one plot in each row and each column of the block (i.e., a Latin square).
-The design ensured that no adjacent N plots were assigned the same N rate.
-Furthermore, the order of N rates in each row of every block was specified to avoid relatively large changes in N rates (due to the technological limitations of N application equipment commonly witnessed in real-world OFPE).
-
-Letting $p$ represent the crop price and $w$ represent the price of nitrogen fertilizer, in each simulation the "true" economically optimal N rate for each cell $(j, i)$ was calculated as
+Letting $p$ represent the crop price and $w$ represent the price of nitrogen fertilizer, in each simulation the "true" economically optimal N rate for each cell $(j, i)$ was calculated as:
 
@@
 
-In each simulation, six trial N rates were assigned by calculating the 0%, 20%, 40%, 60%, 80%, and 100% quantiles of the simulation's true cell-specific  critical N rates ($\tau_{j,i})$.
+Figure ??
+illustrates the spatial distribution map of cell-level $N^*_{j,i}$ for one example simulation.
+Note that the true $N^*_{j,i}$s are not observable by producers or researchers, and are not used in the profit calculation in this study.
+
+## Trial Design
+
+Figures \@ref(fig:field-layout) and \@ref(fig:field-N-design) illustrate the Latin square trial design assumed in each simulation.
+The field was partitioned into a 4-block $\times$ 2-block grid, in which each block was partitioned into a 6-plot $\times$ 6-plot grid with each of six N rates assigned to exactly one plot in each row and each column of the block (i.e., a Latin square).
+A special patterned Latin square [@li2023trial] was utilized to ensure that no adjacent N plots were assigned the same N rate, and furthermore, the order of N rates in each row of every block was specified to avoid relatively large changes in N rates (due to the technological limitations of N application equipment commonly witnessed in real-world OFPE).
+
+In each simulation, six trial N rates were assigned by calculating the 0%, 20%, 40%, 60%, 80%, and 100% quantiles of the simulation's true cell-specific plateau N rates ($\tau_{j,i})$.
+Moreover, the lower and upper bounds of trial N rates were expanded by 20 kg ha$^{-1}$ to ensure the range of trial N rates can fully cover all cells' plateau points as well as the response curve segments near the plateau points.
 The means of these trial N rates across simulations were approximately {80, 130, 154, 184, 219, and 270} kg ha$^{-1}$, while the differences between simulations were small and negligible.
@@
 In each simulation, for each cell $(j, i)$, the simulation's true yield $y_{j, i}$ was generated based on the cell's assigned application rate $N_{j,i}$, true response parameters $\textbf{c}_{j,i} = (\alpha_{j,i}, \beta_{j,i}, \gamma_{j,i}, \tau_{j,i})$, and error term $\varepsilon_{j,i}$.
-This procedure generated a field-level, cell-specific data set, $\{(y_{j, i},N_{j, i} ):j=1,\dots,1440;i=1,\dots, 6 \}$.
+This procedure generated a field-level, cell-specific data set, $\{(y_{j, i},N_{j, i} ): j=1, \dots, 1440; i=1, \dots, 6 \}$.
 To maintain consistency with real-world OFPEs, it was assumed that harvesting equipment could only record yields accurately at an 18m $\times$ 12m (subplot) resolution.
@@
 
-## The value of GWR-based VRA over SCAM-based URA
+## Economic value of GWR-based VRA
 
-To estimate the bias in the estimation of the economic value of GWR-based VRA, the true per-ha net revenues ("profits") of the SCAM-based URA and GWR-based VRA were calculated by substituting the estimated optimal nitrogen rates into the "true" yield response functions.
-Profits from the SCAM approach were:
+The true economic value of the GWR model was measured by the per-ha net revenue ("profit") increase resulting from the utilization of VRA based on the GWR model in comparison to the URA.
+The true profit of GWR-based VRA (either GWRR or GWRT) was generated by substituting the GWR-estimated site-specific optimal N rates ($\hat{N}^{*GWR}_j$) into the true yield response functions:
 
-$$\Pi^{SCAM} = \frac{1}{8640} \sum_{j=1}^{1440} \sum_{i=1}^6 \big[p \cdot f_{j, i} (\hat{N}^{*SCAM})-w \cdot \hat{N}^{*SCAM}\big]$$
+$$\Pi^{GWR}=\frac{1}{8640} \sum_{j=1}^{1440} \sum_{i=1}^6 [p \cdot f_{j, i} (\hat{N}^{*GWR}_j)-w \cdot \hat{N}^{*GWR}_j],$$
 
-and profits from the GWR approach (either GWRR or GWRT) were:
+where $f_{j, i}(\cdot)$ denotes the true yield response function at cell $(j, i)$. Similarly, the true profit of URA was based on the SCAM-estimated uniform optimal N rate (\hat{N}^{*SCAM} ):
 
-$$\Pi^{GWR}=\frac{1}{8640} \sum_{j=1}^{1440} \sum_{i=1}^6 [p \cdot f_{j, i} (\hat{N}^{*GWR}_j)-w \cdot \hat{N}^{*GWR}_j]$$
+$$\Pi^{SCAM} = \frac{1}{8640} \sum_{j=1}^{1440} \sum_{i=1}^6 \big[p \cdot f_{j, i} (\hat{N}^{*SCAM})-w \cdot \hat{N}^{*SCAM}\big].$$
 
-where $f_{j, i}(\cdot)$ denotes the true yield response function at cell $(j, i)$.
-
-The true value of the GWR-based VRA compared to the SCAM-based URA is defined by the difference in their profits:
+The true economic value of the GWR-based VRA was then calculated as:
 
@@
 
-To find the bias in estimating the value of VRA, the estimated profits of the SCAM-based URA and GWR-based VRA were calculated by substituting the estimated optimal nitrogen rates into the cell-specific yield response functions estimated by GWR:
+In practice, since the true responses $f_{j, i}(\cdot)$ are unknown, the calculation of the economic value of GWR-based VRA is often based on assumption that the GWR-estimated yield response functions are true.
+In this study, the estimated profits of VRA (based on GWR) and URA (based on SCAM) based on the GWR-estimated responses were:
 
-$$\hat{\Pi}^{SCAM} = \frac{1}{8640} \sum_{j=1}^{1440} \sum_{i=1}^6 \big[p \cdot \hat{f}^{GWR}_{j, i} (\hat{N}^{*SCAM} )-w \cdot \hat{N}^{*SCAM}\big]$$
+$$\hat{\Pi}^{GWR}=\frac{1}{8640} \sum_{j=1}^{1440} \sum_{i=1}^6 [p \cdot \hat{f}^{GWR}_{j, i} (\hat{N}^{*GWR}_{j} )-w \cdot \hat{N}^{*GWR}_{j}],$$
 
-$$\hat{\Pi}^{GWR}=\frac{1}{8640} \sum_{j=1}^{1440} \sum_{i=1}^6 [p \cdot \hat{f}^{GWR}_{j, i} (\hat{N}^{*GWR}_{j} )-w \cdot \hat{N}^{*GWR}_{j}]$$
-where $\hat{f}^{GWR}_{j, i}(\cdot) = \hat{f}^{GWR}_j(\cdot)$ denotes the estimated yield response function by GWR (either GWRR or GWRT) at cell $(j, i)$ within subplot $j$.
+$$\hat{\Pi}^{SCAM} = \frac{1}{8640} \sum_{j=1}^{1440} \sum_{i=1}^6 \big[p \cdot \hat{f}^{GWR}_{j, i} (\hat{N}^{*SCAM} )-w \cdot \hat{N}^{*SCAM}\big],$$
 
-The estimated value of the GWR-based VRA compared to the SCAM-based URA is defined as:
+where $\hat{f}^{GWR}_{j, i}(\cdot) = \hat{f}^{GWR}_j(\cdot)$ denotes the GWR-estimated yield response function at cell $(j, i)$ within subplot $j$.
+
+The estimated economic value of the GWR-based VRA was:
 
@@
 
-Finally, the bias in the estimation of the value of GWR-based VRA was calculated as follows:
+Because $\hat{f}^{GWR}_{j,i}(\cdot)$ is mis-specified in functional form and deviating from the true response $f_{j,i}(\cdot)$, the estimated economic value of GWR-based VRA $\hat{\Delta}^{GWR}$ is likely biased from the true economic value $\Delta^{GWR}$.
+That bias in the estimation was calculated as:
 

### 2023-11-12 Writing/manuscript_gwr.rmd
comments to editor modified

--- 2023-11-11 Writing/manuscript_gwr.rmd
@@
 It provides a cost-effective way to gather high-resolution data on yields and input trials, which is crucial for informing site-specific crop input management [@bullock2019data; @lacoste2021farm for reference].
-One of the enduring research questions in this domain is the value of variable rate application (VRA) of inputs like fertilizer and seeds compared to traditional uniform rate application (URA).
+One of the enduring research goal in this domain is the estimation of the value of variable rate application (VRA) of inputs like fertilizer and seeds compared to traditional uniform rate application (URA).
 This is a pivotal question, as the answer determines whether the investment in costly precision agriculture technologies, conducting soil sampling, or purchasing variable rate prescription maps is justifiable for farmers.
@@
 Generally, researchers undertake the following steps to estimate the value of VRA using on-farm precision experimentation (OFPE) data [@anselin2004spatial; @bullock2002adding; @liu2006site; @swinton1998evaluating]: (1) estimate site-specific yield response functions based on a method chosen by the researcher; (2) use the estimated yield response functions to estimate the economically optimal site-specific input rates (EOIRs) and economically optimal uniform input rates; (3) plug the estimated site-specific EOIRs and uniform EOIR into the estimated yield response functions to calculate estimated profits under both strategies; and (4) find the difference in the two strategies' estimated profits.
-The core source of bias lies in step (3).
-The primary source of bias originates from step (3), where it is implicitly assumed that the estimated site-specific yield response functions are accurate representations of reality.
-This is a challenging assumption because the true site-specific yield response functions are ultimately unknowable.
+The primary source of bias originates from step (3), where it is implicitly assumed that the "estimated" site-specific yield response functions are indeed true in reality.
+This assumption is unavoidable because the true site-specific yield response functions are ultimately unknowable.
 As such, when the estimated functions diverge significantly from the true functions, it follows that the estimated value of VRA over URA will also be biased.
 This bias could manifest as either an underestimation or overestimation of VRA's value.
-The bias can be exacerbated by mis-specification of the functional form, as this can lead to immediate misrepresentation of the true yield response, further skewing the estimated value of VRA.
+The bias can be exacerbated by mis-specification of the functional form, as this can lead to immediate mis-representation of the true yield response, further skewing the estimated value of VRA.
 
-Two primary approaches exist for deriving variable rate application (VRA) recommendations from on-farm precision experimentation (OFPE) data.
+Two primary approaches exist for deriving variable rate application (VRA) recommendations from OFPE data.
 The first approach integrates soil sampling and/or field characteristic data (such as topography) with OFPE data (yield, input) to estimate site-specific yield response functions.
+In this approach, interacations of inputs and soil/field characteristics are explicilty modeled.
+One can then plug in site-specific soil/field characteristics to the estimated model to represent site-specific yield response functions.
 A variety of statistical methods are employed within this framework, including spatial econometrics [@anselin2004spatial; @liu2006site] and various machine learning techniques like random forests [@krause2020random; @de2023predicting], convolutional neural networks [@barbosa2020modeling], and causal forests [@kakimoto2022causal].
@@
 
-Among the GWR studies, @trevisan2021spatial utilized GWR to estimate site-specific yield response functions from OFPE data and reported an unusually high potential gain of $58 per hectare from transitioning from the optimal uniform application rate to optimal site-specific application rates.
+GWR has been presented as a valuable tool for the estimation of site-specific yield response functions used to derive site-specific input rate recommendations from data generated by OFPE [@rakshit2020; @trevisan2021spatial].
+@trevisan2021spatial, in particular, reported an unusually high potential gain of $58 per hectare from transitioning from the optimal uniform application rate to optimal site-specific application rates.
 Such a figure is notably higher than what has been suggested by previous studies on the value of variable rate application (VRA) over uniform rate application (URA) [@bullock1998does; @koch2004economic; @thrikawala1999economic].
-We suspect that their reported estimate for the benefit of GWR-based VRA over URA may be significantly over-estimated for a couple of reasons.
+We suspect that their reported estimate for the benefit of GWR-based VRA over URA may be significantly over-estimated for the very reasons mentioned earlier.
 First, their model for corn yield response to nitrogen is mostly likely mis-specified.
@@
 Herein, "economically optimal" pertains strictly to the maximization of private production profitability for farmers and does not imply "socially optimal."] stemming from functional form mis-specifcatin combined with statistical inaccuracies in the coefficient estimation of the model.
-Wd found that a mis-specified GWR model tends to result in substantial over-estimation of the economic value of GWR-based VRA over URA.
+We found that a mis-specified GWR model tends to result in substantial over-estimation of the economic value of GWR-based VRA over URA.
 
@@
 
-Our simulations are run using R \citep{}, and all the R programs are publicly accessible at the following GitHub direcotr: https://github.com/tmieno2/GWR_value.
+Our simulations are run using R [@R], and all the R programs are publicly accessible at the following GitHub direcotry: https://github.com/tmieno2/GWR_value.
 

### 2023-11-12 Writing/manuscript_gwr.rmd
minor edits

--- 2023-11-12 Writing/manuscript_gwr.rmd
@@
 
-Among the GWR studies, @trevisan2021spatial utilized GWR to estimate site-specific yield response functions from OFPE data and reported an unusually high potential gain of $58 per hectare from transitioning from the optimal uniform application rate to optimal site-specific application rates.
+GWR has been presented as a valuable tool for the estimation of site-specific yield response functions used to derive site-specific input rate recommendations from data generated by OFPE [@rakshit2020; @trevisan2021spatial].
+@trevisan2021spatial, in particular, reported an unusually high potential gain of $58 per hectare from transitioning from the optimal uniform application rate to optimal site-specific application rates.
 Such a figure is notably higher than what has been suggested by previous studies on the value of variable rate application (VRA) over uniform rate application (URA) [@bullock1998does; @koch2004economic; @thrikawala1999economic].
-We suspect that their reported estimate for the benefit of GWR-based VRA over URA may be significantly over-estimated for a couple of reasons.
+We suspect that their reported estimate for the benefit of GWR-based VRA over URA may be significantly over-estimated for the very reasons mentioned earlier.
 First, their model for corn yield response to nitrogen is mostly likely mis-specified.
-Numerous past agronomic studies recognize that corn yield follows a quadratic-plateau response to nitrogen.
-Ideally, the GWR model should be specified with quadratic-plateau or more flexible functional forms.
-However, no software package is readily usable to estimate GWR with nonlinear functional form.
-A simple quadratic model was employed by @trevisan2021spatial.
+Numerous past agronomic studies recognize that corn yield follows a quadratic-plateau response to nitrogen, yet a simple quadratic model was employed by @trevisan2021spatial.
 Second, GWR itself has faced criticism regarding the statistical reliability of its coefficient estimations [@griffith2008spatial; @harris2019simulation; @paez2011simulation; @da2016multiple].
@@
 Herein, "economically optimal" pertains strictly to the maximization of private production profitability for farmers and does not imply "socially optimal."] stemming from functional form mis-specifcatin combined with statistical inaccuracies in the coefficient estimation of the model.
-We found that functional form mis-specified GWR model tends to result in substantial over-estimation of the economic value of GWR-based VRA over URA.
+We found that a mis-specified GWR model tends to result in substantial over-estimation of the economic value of GWR-based VRA over URA.
 

### 2023-11-12 Writing/manuscript_gwr.rmd
Updates from Overleaf

--- 2023-11-12 Writing/manuscript_gwr.rmd
@@
 
+(Nathan kept asking us to revise the language throughout the manuscript to make it clear that we are comparing "a difference between quadratic GWR and a more flexible functional form with no spatial heterogeneity".)
+
 **Keywords**: on-farm precision experimentation, site-specific input management, geographically weighted regression, economically optimal nitrogen rate
@@
 But, you make the final call.) The primary objective of this study is to examine the degree and direction of bias in the estimation of the economic value of GWR-based variable nitrogen rate recommendations, especially when the yield response to nitrogen is incorrectly specified as quadratic in the GWR model instead of the correct quadratic-plateau function.
-We will employ Monte Carlo simulations, which allow us to accurately define and know the true yield response function within our data-generating process, providing a means to quantify the degree of bias present.
+(Nathan's emphasis: "a difference between quadratic GWR and a more flexible functional form with no spatial heterogeneity".
+Shall we put it here?)  We will employ Monte Carlo simulations, which allow us to accurately define and know the true yield response function within our data-generating process, providing a means to quantify the degree of bias present.
 
@@
 For many cells, the SCAM-based estimated EONR is significantly higher than the actual yield-maximizing N rate, resulting in an estimated yield far lower because of the quadratic functional form assumption.
-Figure \@ref(fig:why-bias-single) focuses on a single cell and compares estimated and true yields between GWR and SCAM (panel (a)) and estimated and true profits between GWR and SCAM (panel (b)).
-The cell's true yield response functions plateaus at a nitrogen rate of about $`r round(il_data_oe[aunit_id %in% single_aunit, Nk], digits = 0)`$ kg ha$^{-1}$, but the GWR-estimated yield response function suggests that yield should peak at a nitrogen rate of about $`r round(point_data_gwr[type == "GWR", N], digits = 0)`$ kg ha$^{-1}$ and decline thereafter.
-In reality, the yield differential between GWR and SCAM is 0, while the estimated yield differential is about `r round(point_data_gwr[type == "GWR", yield] - point_data_gwr[type == "SCAM", yield], digits = 2)` ton ha$^{-1}$, leading to the over-estimation of the value of GWR in panel (b).
-Based on the true profit response curve, applying the GWR-based recommendation is about \$`r round(true_yield_data[type != "True", diff(profit)], digits = 0)` ha$^{-1}$ "less" profitable than applying the SCAM-based recommendation.
-This profit differential comes solely from the difference in nitrogen cost since GWR and SCAM yields are equal.
-However, if calculations are based on the cell's GWR-based estimation of the response function, profits from the GWR-based recommendation are measured to exceed those from the SCAM-based recommendation by about \$`r round(- point_data_gwr[, diff(profit)], digits = 0)` ha$^{-1}$.
-Beyond the difference in nitrogen cost, the falsely estimated yield boost by GWR contributes to the profit differential, thus significantly over-estimating the actual value of GWR.
+(Taro: Can you double check the above paragraph?
+I don't remember who wrote it.
+But it does not seem clear to me.) Figure \@ref(fig:why-bias-single) panel (a) illustrates a single cell's true quadratic-plateau yield response and estimated yield response by the mis-specified quadratic GWR.
+The cell's true yield response plateaus at a nitrogen rate of about $`r round(il_data_oe[aunit_id %in% single_aunit, Nk], digits = 0)`$ kg ha$^{-1}$, but the GWR-estimated yield response function suggests that yield should peak at a nitrogen rate of about $`r round(point_data_gwr[type == "GWR", N], digits = 0)`$ kg ha$^{-1}$ and decline thereafter.
+The true yield differential between recommended N rates by GWR and SCAM is 0, while the estimated yield differential is about `r round(point_data_gwr[type == "GWR", yield] - point_data_gwr[type == "SCAM", yield], digits = 2)` ton ha$^{-1}$, leading to the over-estimation of the GWR yield benefit.
+Panel (b) illustrates the corresponding true and estimated profit response curves.
+Based on the true profit response, applying the GWR-based recommendation is about \$`r round(true_yield_data[type != "True", diff(profit)], digits = 0)` ha$^{-1}$ less profitable than the SCAM-based recommendation, where this profit differential comes solely from the difference in nitrogen cost since GWR and SCAM yields are equal.
+However, if calculations are based on the cell's GWR-estimated response, profit from the GWR-based recommendation exceeds that from the SCAM-based recommendation by about \$`r round(- point_data_gwr[, diff(profit)], digits = 0)` ha$^{-1}$, which is much larger than the true value of \$`r round(true_yield_data[type != "True", diff(profit)], digits = 0)` ha$^{-1}$.
+Beyond the difference in nitrogen cost, the falsely estimated yield boost by GWR contributes to the profit differential, thus significantly over-estimating the actual value of GWR-based VRA.
+
+estimated and true yields resulting from GWR-based and SCAM-based EONRs, where the estimated yields are predicted using the estimated yield response function by .
+
+(panel a) or profits (panel b) of GWR and SCAM EONR, where the estimated.
 
@@
 
-Most importantly, whether using GWRT or GWRR, researchers must be cautious about their estimated values of VRA when the model is assumed to be quadratic but the true underlying yield-input response is quadratic-plateau in reality.
+Most importantly, whether using GWRT or GWRR, researchers must be cautious about their estimated values of VRA when the model is assumed to be quadratic but the true underlying yield-input response is quadratic-plateau.
 Our results show that it is likely that they will over-estimate their true values and the bias can be misleadingly high with non-negligible probability.

### 2023-11-12 Writing/manuscript_gwr.rmd
updates

@@
 ---
-title: "Bias in the Estimation of the Value of VRA over URA: A case of Mis-speficied Geographically Weighted Regression Models"
+title: "Bias in the Estimation of the Value of VRA over URA: A Case of Mis-speficied Geographically Weighted Regression Models"
 author:
@@
 
-(Nathan kept asking us to revise the language throughout the manuscript to make it clear that we are comparing "a difference between quadratic GWR and a more flexible functional form with no spatial heterogeneity".)
-
 **Keywords**: on-farm precision experimentation, site-specific input management, geographically weighted regression, economically optimal nitrogen rate
@@
 Numerous past agronomic studies recognize that corn yield follows a quadratic-plateau response to nitrogen, yet a simple quadratic model was employed by @trevisan2021spatial.
+Similarly, @rakshit2020 also used quadratic model.
+Ideally, the GWR model should be specified with quadratic-plateau or more flexible functional forms.
+However, no software package is readily usable to estimate GWR with quadratic-plateau fucntional form.
 Second, GWR itself has faced criticism regarding the statistical reliability of its coefficient estimations [@griffith2008spatial; @harris2019simulation; @paez2011simulation; @da2016multiple].
@@
 But, you make the final call.) The primary objective of this study is to examine the degree and direction of bias in the estimation of the economic value of GWR-based variable nitrogen rate recommendations, especially when the yield response to nitrogen is incorrectly specified as quadratic in the GWR model instead of the correct quadratic-plateau function.
-(Nathan's emphasis: "a difference between quadratic GWR and a more flexible functional form with no spatial heterogeneity".
-Shall we put it here?)  We will employ Monte Carlo simulations, which allow us to accurately define and know the true yield response function within our data-generating process, providing a means to quantify the degree of bias present.
+We will employ Monte Carlo simulations, which allow us to accurately define and know the true yield response function within our data-generating process, providing a means to quantify the degree of bias present.
 
@@
 
-This study conduct Monte Carlo simulations to evaluate two sets of GWR quadratic specifications used in @rakshit2020 and @trevisan2021spatial in terms of their economic performance and also bias in estiamting the economic value of VRA over URA.
+This study conducts Monte Carlo simulations to evaluate the bias in the estimation of the value of VRA over URA when VRA is derived from quadratic GWR model when the true yield response function follows quadratic-plateau functional form.
+We consider two sets of GWR specifications: one used in @rakshit2020 and the other in @trevisan2021spatial.
 Both specifications assume a quadratic response of yield to nitrogen rate (N).
 However, while @trevisan2021spatial estimated the coefficient on N$^2$ as a global parameter, @rakshit2020 estimated it locally for each point.
-We cannot use real data to test which model specification results in more profitable site-specific nitrogen rate recommendations because it is impossible to observe the true yield response functions using real-world data.
-For the same reason, neither can we test whether the quadratic GWR models over-estimate the actual economic value of VRA.
-But in the Monte Carlo simulations we specify yield response functions and generated stylized data from those functions, which enable us to quantify in the context of the simulations the true economic value of GWR-based VRA and the bias in the estimation of that value.
+
+We cannot use real data to achieve this objective because we never observe the true site-specific yield response functions.
+But in the Monte Carlo simulations, we can specify yield response functions and generate data from those functions, which enables us to quantify the true economic value of the mis-specified GWR-based VRA over URA and the bias in the estimation of that value in the context of the simulations.
 Monte Carlo simulations are commonly used in this way to gain insights into the statistical and economic properties of trial designs and estimations methods [@alesso2021design; @bullock2020value; @gebbers2010application; @mckinion2001analysis].
@@
 The process and components of the simulation analysis are detailed below.
-
 Our simulations are run using R [@R], and all the R programs are publicly accessible at the following GitHub direcotry: https://github.com/tmieno2/GWR_value.
@@
 In each simulation, six trial N rates were assigned by calculating the 0%, 20%, 40%, 60%, 80%, and 100% quantiles of the simulation's true cell-specific plateau N rates ($\tau_{j,i})$.
-Moreover, the lower and upper bounds of trial N rates were expanded by 20 kg ha$^{-1}$ to ensure the range of trial N rates can fully cover all cells' plateau points as well as the response curve segments near the plateau points.
+We then subtract 20 kg ha$^{-1}$ from the 0% quantile and add 20 kg ha$^{-1}$ from the 100% quantile to ensure that the range of trial N rates fully encompass the true plateau points.
 The means of these trial N rates across simulations were approximately {80, 130, 154, 184, 219, and 270} kg ha$^{-1}$, while the differences between simulations were small and negligible.
@@
 
-## Economic value of GWR-based VRA
+## Economic value of the GWR-based VRA
 
-The true economic value of the GWR model was measured by the per-ha net revenue ("profit") increase resulting from the utilization of VRA based on the GWR model in comparison to the URA.
+The true economic value of the GWR models was measured by the per-ha net revenue ("profit") increase resulting from the utilization of the VRA based on the GWR models in comparison to the URA.
 The true profit of GWR-based VRA (either GWRR or GWRT) was generated by substituting the GWR-estimated site-specific optimal N rates ($\hat{N}^{*GWR}_j$) into the true yield response functions:
@@
 
-In practice, since the true responses $f_{j, i}(\cdot)$ are unknown, the calculation of the economic value of GWR-based VRA is often based on assumption that the GWR-estimated yield response functions are true.
+In practice, since the true responses $f_{j, i}(\cdot)$ are unknown, the calculation of the economic value of GWR-based VRA is always based on assumption that the GWR-estimated yield response functions are true.
 In this study, the estimated profits of VRA (based on GWR) and URA (based on SCAM) based on the GWR-estimated responses were:
@@
 
-# Results
+# Results and Discussions
 
@@
 For many cells, the SCAM-based estimated EONR is significantly higher than the actual yield-maximizing N rate, resulting in an estimated yield far lower because of the quadratic functional form assumption.
-(Taro: Can you double check the above paragraph?
-I don't remember who wrote it.
-But it does not seem clear to me.) Figure \@ref(fig:why-bias-single) panel (a) illustrates a single cell's true quadratic-plateau yield response and estimated yield response by the mis-specified quadratic GWR.
+Figure \@ref(fig:why-bias-single) panel (a) illustrates the true quadratic-plateau yield response and estimated yield response by the mis-specified quadratic GWR for a single cell.
 The cell's true yield response plateaus at a nitrogen rate of about $`r round(il_data_oe[aunit_id %in% single_aunit, Nk], digits = 0)`$ kg ha$^{-1}$, but the GWR-estimated yield response function suggests that yield should peak at a nitrogen rate of about $`r round(point_data_gwr[type == "GWR", N], digits = 0)`$ kg ha$^{-1}$ and decline thereafter.
@@
 Based on the true profit response, applying the GWR-based recommendation is about \$`r round(true_yield_data[type != "True", diff(profit)], digits = 0)` ha$^{-1}$ less profitable than the SCAM-based recommendation, where this profit differential comes solely from the difference in nitrogen cost since GWR and SCAM yields are equal.
-However, if calculations are based on the cell's GWR-estimated response, profit from the GWR-based recommendation exceeds that from the SCAM-based recommendation by about \$`r round(- point_data_gwr[, diff(profit)], digits = 0)` ha$^{-1}$, which is much larger than the true value of \$`r round(true_yield_data[type != "True", diff(profit)], digits = 0)` ha$^{-1}$.
+However, when calculations are based on the cell's GWR-estimated response, profit from the GWR-based recommendation exceeds that from the SCAM-based recommendation by about \$`r round(- point_data_gwr[, diff(profit)], digits = 0)` ha$^{-1}$, which is much larger than the true value of \$`r round(true_yield_data[type != "True", diff(profit)], digits = 0)` ha$^{-1}$.
 Beyond the difference in nitrogen cost, the falsely estimated yield boost by GWR contributes to the profit differential, thus significantly over-estimating the actual value of GWR-based VRA.
 
-estimated and true yields resulting from GWR-based and SCAM-based EONRs, where the estimated yields are predicted using the estimated yield response function by .
+# Conclusions
 
-(panel a) or profits (panel b) of GWR and SCAM EONR, where the estimated.
-
-# Discussion and Conclusions
-
-Our simulation results show that generating site-specific $R_x$s by applying the basic GWR model (GWRR) with a quadratic functional form to OFPE data tends to have little economic value for site-specific $R_x$s when the true yield response function is quadratic-plateau.
-The GWRR based VRA is on average no more profitable than SCAM-based URA under many price scenarios, particularly when nitrogen price is relatively low compared to the corn price.
-This finding reveals the economic consequences of the widely recognized statistical inaccuracy issue of GWR estimation [@griffith2008spatial; @paez2011simulation; @da2016multiple; @harris2019simulation] and also the problem of assuming quadratic functional form when the true yield response function follows the quadratic-plateau functional form, such as in the corn-nitrogen relationship.
+Our simulation results show that site-specific $R_x$s derived by the quadratic GWR models (GWRR and GWRT) has little economic value over URA derived by a correctly specified uniform response model (SCAM) when the true yield response function is quadratic-plateau.
+However, we showed that the estimated value of the VRA based on the quadratic GWR models were much higher than their actualy values.
+This finding reveals the severe bias in estimating the value of VRA over URA when the VRA was derived from quadratic GWR when the true yield response function follows the quadratic-plateau functional form, such as in the corn-nitrogen relationship.
 Precision agriculture practitioners should be cautious when using GWR for site-specific $R_x$s.
-If the GWR-based approach must be employed to find site-specific input recommendations (e.g., due to lack of field and soil information), our simulation results show that GWRT performs relatively better than GWRR, though its profitability improvement against URA is only moderate.
-
-Previous studies comparing models have predominantly focused on measuring model performance based on statistical accuracy of parameter estimates, such as bias, mean squared error, type I error, and confidence intervals, for both GWR models [@lu2017geographically; @harris2019simulation] and general econometric models [@christopeit2006local; @su2016identifying].
-While these statistical measures are fundamental for evaluating model performance, for practical reasons it is imperative to consider the translation of statistical accuracy into economic value.
-Moreover, the extent of this translation could vary depending on the specific application scenarios.
-The research reported in the present article distinguishes itself from previous literature by explicitly examining the economic value of specific econometric models (GWR) under a model functional form misspecification (quadratic instead of quadratic-plateau), in a specific application (corn site-specific nitrogen management), and under specific context scenarios (normal-sized production field, various market prices, etc.), through a simulation-based methodology.
-We encourage other model comparison studies in empirical economic research to also incorporate similar assessment of economic value.
 
 Our results clearly show that it can be problematic to use GWR under the assumption of a quadratic functional form when the true yield-input relationship is quadratic-plateau.
-@trevisan2021spatial had to choose the quadratic functional form because no readily usable statistical software or package could be used to implement nonlinear GWR.
+@trevisan2021spatial had to choose the quadratic functional form because no readily usable statistical software or package could be used to implement quadratic-plateau GWR at the time.
 The only nonlinear model available at the moment is the linear-plateau GWR by @lambert2022geographically.
@@
 
-Most importantly, whether using GWRT or GWRR, researchers must be cautious about their estimated values of VRA when the model is assumed to be quadratic but the true underlying yield-input response is quadratic-plateau.
+Most importantly, whether using GWRT or GWRR, researchers must be cautious about their estimated values of VRA when the model is assumed to be quadratic but the true underlying yield-input response is quadratic-plateau in reality.
 Our results show that it is likely that they will over-estimate their true values and the bias can be misleadingly high with non-negligible probability.
@@
 Whatever the underlying statistical methods for yield response functions may be, researchers are likely to overestimate the true value of their methods.
-It would be an interesting future research to investigate the bias in other commonly used statistical methods in the literature on site-specific yield response estimation (such as regression with interaction terms of field characteristics, machine learning, and more) by using a similar simulation-based evaluation approach as done in this study.
-
-<!-- # Conclusions
-
-This article examined the economic value of GWR-based VRA and the bias in its estimation in the context of OFPE.
-We showed that VRA based on GWR provides only small economic benefits over URA based on SCAM.
-The relative performances of the model specifications used by @trevisan2021spatial and @rakshit2020 differs based on nitrogen-corn price ratio.
-Finally and most important, we found that both specifications can result in significant over-estimation of the true value of GWR-based site-specific nitrogen rate recommendations.
-It can be concluded that researchers need to be cautious about promoting the GWR-based approach to VRA recommendation.
--->
+In the future, it would be interesting to investigate the bias in other commonly used statistical methods in the literature on site-specific yield response estimation (such as regression with interaction terms of field characteristics, machine learning, and more) by using a similar simulation-based evaluation approach as done in this study.
 

### 2023-11-12 Writing/manuscript_gwr.rmd
modified manuscript

@@
 
-Most importantly, whether using GWRT or GWRR, researchers must be cautious about their estimated values of VRA when the model is assumed to be quadratic but the true underlying yield-input response is quadratic-plateau in reality.
+Our results clearly show that it can be problematic to use GWR under the assumption of a quadratic functional form when the true yield-input relationship is quadratic-plateau.
+@trevisan2021spatial had to choose the quadratic functional form because no readily usable statistical software or package could be used to implement nonlinear GWR.
+The only nonlinear model available at the moment is the linear-plateau GWR by @lambert2022geographically.
+Unfortunately, the estimation of the economically optimal input rate cannot be adjusted according to price using the linear-plateau model as the economically optimal input rate occurs always at the kink (critical input rate where yield plateau is reached).
+Given that many yield-input relationships follow quadratic-plateau functional form for many crops, it would be fruitful to develop a GWR method with quadratic-plateau functional form.
+It should be also possible and interesting to build semi-parametric GWR where the yield response functions are estimated without assuming particular functional forms (like SCAM).
+It is also noted that the recently developed multi-scale GWR model [@fotheringham2017multiscale; @yu2020inference; @comber2022route] allows the bandwidth to be derived separately for each covariate in the model, which would potentially improve the performances of GWR estimates and may need to be incorporated into future research.
+Note, however, that multi-scale GWR models are not necessary in our simulations as we have only one covariate ($N$) in our simulations.
+
+Most importantly, whether using GWRT or GWRR, researchers must be cautious about their estimated values of VRA when the model is assumed to be quadratic but the true underlying yield-input response is quadratic-plateau.
 Our results show that it is likely that they will over-estimate their true values and the bias can be misleadingly high with non-negligible probability.
@@
 Whatever the underlying statistical methods for yield response functions may be, researchers are likely to overestimate the true value of their methods.
-In the future, it would be interesting to investigate the bias in other commonly used statistical methods in the literature on site-specific yield response estimation (such as regression with interaction terms of field characteristics, machine learning, and more) by using a similar simulation-based evaluation approach as done in this study.
+It would be an interesting future research to investigate the bias in other commonly used statistical methods in the literature on site-specific yield response estimation (such as regression with interaction terms of field characteristics, machine learning, and more) by using a similar simulation-based evaluation approach as done in this study.
+
+<!-- # Conclusions
+
+This article examined the economic value of GWR-based VRA and the bias in its estimation in the context of OFPE.
+We showed that VRA based on GWR provides only small economic benefits over URA based on SCAM.
+The relative performances of the model specifications used by @trevisan2021spatial and @rakshit2020 differs based on nitrogen-corn price ratio.
+Finally and most important, we found that both specifications can result in significant over-estimation of the true value of GWR-based site-specific nitrogen rate recommendations.
+It can be concluded that researchers need to be cautious about promoting the GWR-based approach to VRA recommendation.
+-->
 

### 2023-11-12 Writing/manuscript_gwr.rmd
Updates from Overleaf

--- 2023-11-12 Writing/manuscript_gwr.rmd
@@
 For many cells, the SCAM-based estimated EONR is significantly higher than the actual yield-maximizing N rate, resulting in an estimated yield far lower because of the quadratic functional form assumption.
-(Taro: Can you double check the above paragraph?
-I don't remember who wrote it.
-But it does not seem clear to me.) Figure \@ref(fig:why-bias-single) panel (a) illustrates a single cell's true quadratic-plateau yield response and estimated yield response by the mis-specified quadratic GWR.
+Figure \@ref(fig:why-bias-single) panel (a) illustrates a single cell's true quadratic-plateau yield response and estimated yield response by the mis-specified quadratic GWR.
 The cell's true yield response plateaus at a nitrogen rate of about $`r round(il_data_oe[aunit_id %in% single_aunit, Nk], digits = 0)`$ kg ha$^{-1}$, but the GWR-estimated yield response function suggests that yield should peak at a nitrogen rate of about $`r round(point_data_gwr[type == "GWR", N], digits = 0)`$ kg ha$^{-1}$ and decline thereafter.

### 2023-11-15 Writing/manuscript_gwr.rmd
manuscript modified

--- 2023-11-12 Writing/manuscript_gwr.rmd
@@
     readRDS() %>%
-  .[, type := ifelse(transfer == 0, "GWRR", "GWRT")] %>%
-  .[, bias := pi_diff_est - pi_diff] %>%
-  # only display the 25% (5.44), 50% (6.56), 75% (7.67) price ratio
+    # === do not need QD result
+    .[model!="QD", ] %>% 
+    # === modify model names
+    .[model=="GWR-R", model := "GWRR"] %>% 
+    .[model=="GWR-T", model := "GWRT"] %>% 
+    # === only need  25% (5.44), 50% (6.56), 75% (7.67) price ratio
     .[pRatio %in% c(5.44, 6.56, 7.67), ] %>%
     # === label price ratio
-  .[, pLabelName := "Price Ratio (N/corn)"] %>%
-  .[pRatio == 5.44, pLabel := "Low (5.44)"] %>%
-  .[pRatio == 6.56, pLabel := "Middle (6.56)"] %>%
-  .[pRatio == 7.67, pLabel := "High (7.67)"] %>%
-  .[, pLabel := factor(pLabel, levels = c("Low (5.44)", "Middle (6.56)", "High (7.67)"))]
+    .[pRatio == 5.44, pLabel := "5.44 (Low)"] %>%
+    .[pRatio == 6.56, pLabel := "6.56 (Middle)"] %>%
+    .[pRatio == 7.67, pLabel := "7.67 (High)"] %>%
+    # === estimation bias
+    .[, bias := pi_diff_est - pi_diff]
 
@@
 We consider two sets of functional-form specifications used by recently published studies of site-specific input management that apply GWR to data from OFPE.
-We show that both GWR approaches suffer significant positive bias, which can lead to large over-estimation of the economic value of applying GWR methods.
+We show that both GWR approaches suffer significant positive bias, which can lead to large overestimation of the economic value of applying GWR methods.
 We conclude that in many circumstances the information gleaned from using GWR may be far less valuable than has been claimed.
@@
 GWR has been presented as a valuable tool for the estimation of site-specific yield response functions used to derive site-specific input rate recommendations from data generated by OFPE [@rakshit2020; @trevisan2021spatial].
-@trevisan2021spatial, in particular, reported an unusually high potential gain of $58 per hectare from transitioning from the optimal uniform application rate to optimal site-specific application rates.
-Such a figure is notably higher than what has been suggested by previous studies on the value of variable rate application (VRA) over uniform rate application (URA) [@bullock1998does; @koch2004economic; @thrikawala1999economic].
-We suspect that their reported estimate for the benefit of GWR-based VRA over URA may be significantly over-estimated for the very reasons mentioned earlier.
-First, their model for corn yield response to nitrogen is mostly likely mis-specified.
-Numerous past agronomic studies recognize that corn yield follows a quadratic-plateau response to nitrogen, yet a simple quadratic model was employed by @trevisan2021spatial.
-Similarly, @rakshit2020 also used quadratic model.
+@trevisan2021spatial, in particular, reported the economic value of GWR-based variable rate application (VRA) over the optimal uniform rate application (URA) in corn nitrogen management.
+However, the existing GWR estimations of yield response functions are using a simple linear or quadratic functional form specification.
+Numerous past agronomic studies recognize that crop yield responses usually follow nonlinear functional forms.
+For example, corn yield follows a quadratic-plateau response to nitrogen, yet a simple quadratic model was employed by @trevisan2021spatial.
 Ideally, the GWR model should be specified with quadratic-plateau or more flexible functional forms.
-However, no software package is readily usable to estimate GWR with quadratic-plateau fucntional form.
-Second, GWR itself has faced criticism regarding the statistical reliability of its coefficient estimations [@griffith2008spatial; @harris2019simulation; @paez2011simulation; @da2016multiple].
-We hypothesize that the intersection of these two issues—the model mis-specification and the inherent limitations of GWR—may have led to a substantial overestimation of the economic value of switching from URA to VRA.
+However, no software package is readily usable to estimate GWR with quadratic-plateau functional form.
+The currently used quadratic GWR models are mostly likely mis-specified for yield response functions.
+Furthermore, GWR itself has faced criticism regarding the statistical reliability of its coefficient estimations [@griffith2008spatial; @harris2019simulation; @paez2011simulation; @da2016multiple].
+We hypothesize that the intersection of these two issues—the model mis-specification and the inherent limitations of GWR—may have led to a substantial overestimation of the economic value of the GWR-based VRA over URA.
+Given the notably high economic value ($58 per hectare) of GWR-based VRA reported in @trevisan2021spatial compared to previous studies on VRA economic evaluation [@bullock1998does; @koch2004economic; @thrikawala1999economic], our suspicion stands a good chance of being plausible.
 
-(Taro: I feel the primary objective should be two-folded.
-As Nathan summarized in his email, they should be (1) the true economic value of GWR-based VRA and, (2) the bias in the estimation of that value.
-But, you make the final call.) The primary objective of this study is to examine the degree and direction of bias in the estimation of the economic value of GWR-based variable nitrogen rate recommendations, especially when the yield response to nitrogen is incorrectly specified as quadratic in the GWR model instead of the correct quadratic-plateau function.
+The primary objective of this study is to examine the degree and direction of bias in the estimation of the economic value of GWR-based variable nitrogen rate recommendations in corn production, especially when the yield response to nitrogen is incorrectly specified as quadratic in the GWR model instead of the correct quadratic-plateau function.
 (Nathan's emphasis: "a difference between quadratic GWR and a more flexible functional form with no spatial heterogeneity".
@@
 Herein, "economically optimal" pertains strictly to the maximization of private production profitability for farmers and does not imply "socially optimal."] stemming from functional form mis-specifcatin combined with statistical inaccuracies in the coefficient estimation of the model.
-We found that a mis-specified GWR model tends to result in substantial over-estimation of the economic value of GWR-based VRA over URA.
+We found that a mis-specified GWR model tends to result in substantial overestimation of the economic value of GWR-based VRA over URA.
 
@@
 
-In practice, since the true responses $f_{j, i}(\cdot)$ are unknown, the calculation of the economic value of GWR-based VRA is always based on assumption that the GWR-estimated yield response functions are true.
-In this study, the estimated profits of VRA (based on GWR) and URA (based on SCAM) based on the GWR-estimated responses were:
+In practice, since the true responses $f_{j, i}(\cdot)$ are unknown, the calculation of the economic value of the GWR-based VRA is always relying on the assumption that the GWR-estimated yield response functions are true.
+In this study, the estimated profits of the GWR-based VRA and SCAM-based URA by using the GWR-estimated responses were:
 
@@
 
-## Comparing the values of GWR-based VRA and SCAM-based URA
+## The true economic value of the GWR-based VRA
 
-Figure \@ref(fig:pi-dif-dist) shows the distribution of $\Delta^{GWR}$, the true profit difference between the GWR-based VRA and the SCAM-based URA, at three different price scenarios which represent the historically low (5.44), middle (6.56), and high (7.67) nitrogen-corn price ratio (\$/kg : \$/kg).
+The distribution of the true economic value of the quadratic GWR-based VRA over the SCAM-based URA, $\Delta^{GWR}$, from the 1,000 simulations, is shown in Figure \@ref(fig:value-vra).
+Three different price scenarios are examined to represent the historically low (5.44), middle (6.56), and high (7.67) nitrogen-corn price ratio (\$/kg : \$/kg).
 Historical corn ($p$) and nitrogen fertilizer ($w$) prices from 2002 to 2022 were obtained from the USDA National Agricultural Statistics Service [@NASS2022] and DTN Retail Fertilizer Trends [@DTN2022], and were transformed into monthly data.
@@
 
-The comparative advantage of GWRR and GWRT varies significantly depending on the nitrogen-corn price ratio.
-Specifically, GWRR performs better as nitrogen becomes more expensive relative to corn, while the opposite is the case for GWRT.
-At the low price ratio of 5.44, VRA based on GWRR is no better than SCAM-based URA.
-However, when the price ratio increases to $6.56$, the median benefit of GWRR is $`r round(mean_data_value[type == "GWRR" & pLabel == "Middle", pi_diff], digits = 2)` per hectare.
-At the high price ratio of 7.67, the median benefit is $`r round(mean_data_value[type == "GWRR" & pLabel == "High", pi_diff], digits = 2)` per hectare.
-On the other hand, the median benefit of VRA based on GWRT at the low price ratio of 5.44 is $`r round(mean_data_value[type == "GWRT" & pLabel == "Low", pi_diff], digits = 2)` per hectare, but the benefit is reduced to $`r round(mean_data_value[type == "GWRT" & pLabel == "Middle", pi_diff], digits = 2)` per hectare when the price ratio is 6.56, and $`r round(mean_data_value[type == "GWRT" & pLabel == "High", pi_diff], digits = 2)` per hectare when 7.67.
+The true economic values of VRA derived by the mis-specified site-specific response models (quadratic GWRR and GWRT) are only moderate over URA derived by a correctly specified uniform response model (SCAM) when the true yield response function is quadratic-plateau.
+The median of the true economic values ranges from as small as \$0.81 per hectare to a moderate \$7.83 per hectare, depending on price scenarios and models used.
+In addition, in any price and model scenario, nearly half of the true economic values are negative, meaning a considerable probability that the GWR-based VRA are actually less profitable than the SCAM-based URA.
 
+The GWRR and GWRT models are slightly different in their economic performances.
+Specifically, GWRR performs better as nitrogen-corn price ratio increases, while the opposite is the case for GWRT.
 Figure \@ref(fig:bias-est-eonr) provides insights into this phenomenon, showing the distribution of the average ratio of estimated EONR to true EONR.
 A value lower than 1 means that EONR is underestimated on average.
-GWRR tends to over-estimate EONR at lower price ratios, but the magnitude of over-estimation falls as the price ratio rises.
-The opposite trend is true for GWRT.
-At the high price ratio, the degree of EONR over-estimation is quite significant.
-Since a high-price ratio means nitrogen is relatively expensive, the economic cost of over-estimation of EONR increases with the price ratio.
-
-To illustrate the difference in the GWRR and GWRT outcomes, Figure \@ref(fig:true-vs-estimated-optn-gwr-r) presents for a single simulation round the estimated site-specific EONR plotted against the true site-specific EONR.
-The site-specific EONR estimates are both inaccurate, but differently inaccurate.
+GWRR tends to overestimate EONR at lower price ratios, but the magnitude of overestimation falls as the price ratio rises.
+The opposite trend is true for GWRT, where at the high price ratio the degree of EONR overestimation is quite significant.
+Since a high-price ratio means nitrogen is relatively expensive, the economic cost of overestimation of EONR increases with the price ratio.
+Figure \@ref(fig:true-vs-estimated-optn-gwr-r) presents for a single simulation round the estimated site-specific EONR plotted against the true site-specific EONR.
+The site-specific EONR estimates are both inaccurate, but each in its way.
 The range of EONR estimates by GWRR is very wide because the coefficient on $N^2$ is allowed to vary site specifically in GWRR.
@@
 
-## Bias in the estimation of the value of GWR-based VRA
+## Bias in the estimated economic value of the GWR-based VRA
 
-Next, we examine the bias in the estimated value of GWR-based VRA.
-Figure \@ref(fig:bias-est-pi) shows the distribution of the bias in the estimation of the value of GWR-based VRA ($\hat{\Delta}^{GWR} - \Delta^{GWR}$).
-For example, the value of 10 would mean that the estimated value of GWR-based VRA over-estimates its true value by $10 per ha.
-As the figure shows, GWRR-based VRA appears to perform better than it truly does, presenting significant positive bias across the relative price range.
-That is, researchers would tend to significantly over-estimate the value of VRA based on GWRR.
-When the GWR estimates are considered to define true yield response, the inaccuracy of GWRR generates over-estimation of the heterogeneity of yield response within the field, which can lead to significant over-estimation of the value of GWRR itself.
+The estimated economic values of the GWR-based VRA over the SCAM-based URA, $\hat{\Delta}^{GWR}$, however, are much larger than the true values.
+The distribution of the estimated economic values is also shown in Figure \@ref(fig:value-vra), where the median ranges from \$17.15 per hectare to as large as \$45.62 per hectare, surpassing the actual values across all simulation scenarios.
+Moreover, the estimated economic values are positive in almost all rounds of simulation, suggesting that the GWR-based VRA are almost always more profitable than the SCAM-based URA.
+But this is significantly erroneous, as nearly half of the time the GWR-based VRA is actually less profitable than SCAM-based URA.
+These simulation results reveal a substantial overestimation of the GWR-based VRA's economic value when the GWR-estimated site-specific yield response functions are used to substitute the true (but unknown) response functions.
+That is, in applied research, the quadratic GWR models would tend to create a misleading impression of superior performance in VRA recommendations compared to their actual performance.
 
+The bias in the estimated value, i.e., the discrepancy between the estimated and true economic values $\hat{\Delta}^{GWR} - \Delta^{GWR}$, reaches as large as approximately \$40 per hectare for the GWRR model.
+When the GWR estimates are considered to define true yield response, the inaccuracy of GWRR generates overestimation of the heterogeneity of yield response within the field, which can lead to significant overestimation of the value of GWRR itself.
 GWRT exhibits a different pattern of bias.
-At low price ratios, the GWRT approach displays smaller bias compared to GWRR.
+At low price ratios, the GWRT approach displays smaller bias of about \$10 per hectare.
 This is partially because GWRT tends to understate the heterogeneity of the site-specific yield response functions as was seen in Figure \@ref(fig:true-vs-estimated-optn-gwr-r).
-As the price ratio rises, bias increases.
-This is due to the significant over-estimation of EONR by GWRT, as illustrated by Figure \@ref(fig:bias-est-eonr).
+As the price ratio rises, bias increases to approximately \$30 per hectare.
+This is due to the significant overestimation of EONR by GWRT, as illustrated by Figure \@ref(fig:bias-est-eonr).
 Unlike the GWRR approach, the distribution of the bias by the GWRT approach has a fat tail, indicating that there is a greater chance of encountering large positive bias in the estimated value of VRA over URA.
 
-Figure \@ref(fig:why-bias-many) illustrates how over-estimation of the value of VRA can occur.
-It shows yield response functions estimated by GWRT and estimated yields associated with the GWR-based EONR rates and SCAM-based EONR rates for 50 randomly chosen cells in a single simulation.
+Figure \@ref(fig:why-bias-many) illustrates how overestimation of the value of VRA can occur.
+It shows yield response functions estimated by GWRT and the estimated yields associated with the GWR-based EONR rates and SCAM-based EONR rates for 50 randomly chosen cells in a single round of simulation.
 Since GWR-based EONRs were obtained assuming the yield response functions estimated by GWR, by construction they out-perform the SCAM-based estimates in every cell.
@@
 The cell's true yield response plateaus at a nitrogen rate of about $`r round(il_data_oe[aunit_id %in% single_aunit, Nk], digits = 0)`$ kg ha$^{-1}$, but the GWR-estimated yield response function suggests that yield should peak at a nitrogen rate of about $`r round(point_data_gwr[type == "GWR", N], digits = 0)`$ kg ha$^{-1}$ and decline thereafter.
-The true yield differential between recommended N rates by GWR and SCAM is 0, while the estimated yield differential is about `r round(point_data_gwr[type == "GWR", yield] - point_data_gwr[type == "SCAM", yield], digits = 2)` ton ha$^{-1}$, leading to the over-estimation of the GWR yield benefit.
+The true yield differential between recommended N rates by GWR and SCAM is 0, while the estimated yield differential is about `r round(point_data_gwr[type == "GWR", yield] - point_data_gwr[type == "SCAM", yield], digits = 2)` ton ha$^{-1}$, leading to the overestimation of the GWR yield benefit.
 Panel (b) illustrates the corresponding true and estimated profit response curves.
@@
 However, when calculations are based on the cell's GWR-estimated response, profit from the GWR-based recommendation exceeds that from the SCAM-based recommendation by about \$`r round(- point_data_gwr[, diff(profit)], digits = 0)` ha$^{-1}$, which is much larger than the true value of \$`r round(true_yield_data[type != "True", diff(profit)], digits = 0)` ha$^{-1}$.
-Beyond the difference in nitrogen cost, the falsely estimated yield boost by GWR contributes to the profit differential, thus significantly over-estimating the actual value of GWR-based VRA.
+Beyond the difference in nitrogen cost, the falsely estimated yield boost by GWR contributes to the profit differential, thus significantly overestimating the actual value of GWR-based VRA.
 
@@
 
-Our simulation results show that site-specific $R_x$s derived by the quadratic GWR models (GWRR and GWRT) has little economic value over URA derived by a correctly specified uniform response model (SCAM) when the true yield response function is quadratic-plateau.
-However, we showed that the estimated value of the VRA based on the quadratic GWR models were much higher than their actualy values.
-This finding reveals the severe bias in estimating the value of VRA over URA when the VRA was derived from quadratic GWR when the true yield response function follows the quadratic-plateau functional form, such as in the corn-nitrogen relationship.
-Precision agriculture practitioners should be cautious when using GWR for site-specific $R_x$s.
+Our simulation results indicate that variable rate application (VRA) derived from the mis-specified quadratic GWR models (GWRR and GWRT) only has small economic values over uniform rate application (URA) derived from a correctly specified uniform response model (SCAM) when the true yield response function is quadratic-plateau, such as in the corn-nitrogen relationship.
+However, there is a notable risk of researchers misconstruing the economic values of the quadratic GWR-based VRA as substantially higher than its true values when substituting estimated site-specific yield response functions for the true response functions.
+This bias in overestimation could be substantial, reaching approximately $40 per hectare.
+Practitioners in precision agriculture should exercise caution when employing GWR for site-specific input recommendations
 
 Our results clearly show that it can be problematic to use GWR under the assumption of a quadratic functional form when the true yield-input relationship is quadratic-plateau.
-@trevisan2021spatial had to choose the quadratic functional form because no readily usable statistical software or package could be used to implement quadratic-plateau GWR at the time.
-The only nonlinear model available at the moment is the linear-plateau GWR by @lambert2022geographically.
-Unfortunately, the estimation of the economically optimal input rate cannot be adjusted according to price using the linear-plateau model as the economically optimal input rate occurs always at the kink (critical input rate where yield plateau is reached).
-Given that many yield-input relationships follow quadratic-plateau functional form for many crops, it would be fruitful to develop a GWR method with quadratic-plateau functional form.
-It should be also possible and interesting to build semi-parametric GWR where the yield response functions are estimated without assuming particular functional forms (like SCAM).
-It is also noted that the recently developed multi-scale GWR model [@fotheringham2017multiscale; @yu2020inference; @comber2022route] allows the bandwidth to be derived separately for each covariate in the model, which would potentially improve the performances of GWR estimates and may need to be incorporated into future research.
-Note, however, that multi-scale GWR models are not necessary in our simulations as we have only one covariate ($N$) in our simulations.
-
-Our results clearly show that it can be problematic to use GWR under the assumption of a quadratic functional form when the true yield-input relationship is quadratic-plateau.
-@trevisan2021spatial had to choose the quadratic functional form because no readily usable statistical software or package could be used to implement nonlinear GWR.
+Previous studies estimating corn yield responses using GWR had to choose the quadratic functional form because no readily usable statistical software or package could be used to implement quadratic-plateau GWR at the time.
 The only nonlinear model available at the moment is the linear-plateau GWR by @lambert2022geographically.
@@
 Most importantly, whether using GWRT or GWRR, researchers must be cautious about their estimated values of VRA when the model is assumed to be quadratic but the true underlying yield-input response is quadratic-plateau.
-Our results show that it is likely that they will over-estimate their true values and the bias can be misleadingly high with non-negligible probability.
-The extremely high values of VRA reported in @trevisan2021spatial are likely to have reflected this bias.
+Our results show that it is likely that they will overestimate their true values and the bias can be misleadingly high with non-negligible probability.
 Indeed, the bias problem we have raised here is likely to be observed for other statistical methods as well because the bias comes from the assumption that the _estimated_ yield response functions are true.
@@
 It would be an interesting future research to investigate the bias in other commonly used statistical methods in the literature on site-specific yield response estimation (such as regression with interaction terms of field characteristics, machine learning, and more) by using a similar simulation-based evaluation approach as done in this study.
-
-<!-- # Conclusions
-
-This article examined the economic value of GWR-based VRA and the bias in its estimation in the context of OFPE.
-We showed that VRA based on GWR provides only small economic benefits over URA based on SCAM.
-The relative performances of the model specifications used by @trevisan2021spatial and @rakshit2020 differs based on nitrogen-corn price ratio.
-Finally and most important, we found that both specifications can result in significant over-estimation of the true value of GWR-based site-specific nitrogen rate recommendations.
-It can be concluded that researchers need to be cautious about promoting the GWR-based approach to VRA recommendation.
--->
 
@@
 
-```{r fig.id = "field-layout", fig.cap = "Simulated field layout with spatial unit definitions", fig.width = 7}
-# knitr::include_graphics(here::here("GitControlled/Writing/Figures/g_layout.png"))
-g_layout
-```
-
-```{r fig.id = "field-N-design", fig.cap = "Experiment design of nitrogen (N) rates", out.width = "6in", fig.width = 6}
-# knitr::include_graphics(here::here("GitControlled/Writing/Figures/g_exp.png"))
-g_exp
-```
-
-```{r, fig.id = "pi-dif-dist", fig.cap = "The true economic value of GWR-based VRA over SCAM-based URA by two GWR models (GWRR and GWRT) and at three nitrogen-corn price ratios", out.width = "6.5in", fig.width = 6}
-# knitr::include_graphics(here::here("GitControlled/Writing/Figures/g_value.png"))
+```{r, fig.id = "value-vra", fig.cap = "The economic value of the quadratic GWR-based VRA over SCAM-based URA.
+The true values are calculated using the true yield response functions, while the estimated values are calculated using the quadratic GWR-estimated yield response functions.
+Two GWR models (GWRR and GWRT) are used.
+The values are calculated at three nitrogen-corn price ratios ($/kg : $/kg) while the corn price is set at $0.28/kg.", out.width = "7in", fig.width = 6.5}
 g_value
@@
 
-```{r fig.id = "why-bias-many", fig.cap = "The cause of significant over-estimation of the value of GWR-based VRA", fig.width = 6}
+```{r fig.id = "why-bias-many", fig.cap = "The cause of significant overestimation of the value of GWR-based VRA", fig.width = 6}
 # knitr::include_graphics(here::here("GitControlled/Writing/Figures/g_why_bias_many.png"))
@@
 
-```{r fig.id = "why-bias-single", fig.cap = "An illustration of over-estimation of the value of GWR-based VRA over SCAM-based URA",fig.width = 6.5, fig.height = 6}
+```{r fig.id = "why-bias-single", fig.cap = "An illustration of overestimation of the value of GWR-based VRA over SCAM-based URA",fig.width = 6.5, fig.height = 6}
 # knitr::include_graphics(here::here("GitControlled/Writing/Figures/g_why_bias_single.png"))
@@
 Stated roughly, using GWR takes the latter approach, which has the advantage of not needing a costly map of field characteristics values.
+
+```{r fig.id = "field-layout", fig.cap = "Simulated field layout with spatial unit definitions", fig.width = 7}
+# knitr::include_graphics(here::here("GitControlled/Writing/Figures/g_layout.png"))
+g_layout
+```
+
+```{r fig.id = "field-N-design", fig.cap = "Experiment design of nitrogen (N) rates", out.width = "6in", fig.width = 6}
+# knitr::include_graphics(here::here("GitControlled/Writing/Figures/g_exp.png"))
+g_exp
+```

### 2023-11-15 Writing/manuscript_gwr.rmd
old paragraph back

@@
 GWR has been presented as a valuable tool for the estimation of site-specific yield response functions used to derive site-specific input rate recommendations from data generated by OFPE [@rakshit2020; @trevisan2021spatial].
-@trevisan2021spatial, in particular, reported the economic value of GWR-based variable rate application (VRA) over the optimal uniform rate application (URA) in corn nitrogen management.
-However, the existing GWR estimations of yield response functions are using a simple linear or quadratic functional form specification.
-Numerous past agronomic studies recognize that crop yield responses usually follow nonlinear functional forms.
-For example, corn yield follows a quadratic-plateau response to nitrogen, yet a simple quadratic model was employed by @trevisan2021spatial.
+@trevisan2021spatial, in particular, reported an unusually high potential gain of $58 per hectare from transitioning from the optimal uniform application rate to optimal site-specific application rates.
+Such a figure is notably higher than what has been suggested by previous studies on the value of variable rate application (VRA) over uniform rate application (URA) [@bullock1998does; @koch2004economic; @thrikawala1999economic].
+We suspect that their reported estimate for the benefit of GWR-based VRA over URA may be significantly over-estimated for the very reasons mentioned earlier.
+First, their model for corn yield response to nitrogen is mostly likely mis-specified.
+Numerous past agronomic studies recognize that corn yield follows a quadratic-plateau response to nitrogen, yet a simple quadratic model was employed by @trevisan2021spatial.
+Similarly, @rakshit2020 also used quadratic model.
 Ideally, the GWR model should be specified with quadratic-plateau or more flexible functional forms.
-However, no software package is readily usable to estimate GWR with quadratic-plateau functional form.
-The currently used quadratic GWR models are mostly likely mis-specified for yield response functions.
-Furthermore, GWR itself has faced criticism regarding the statistical reliability of its coefficient estimations [@griffith2008spatial; @harris2019simulation; @paez2011simulation; @da2016multiple].
-We hypothesize that the intersection of these two issues—the model mis-specification and the inherent limitations of GWR—may have led to a substantial overestimation of the economic value of the GWR-based VRA over URA.
-Given the notably high economic value ($58 per hectare) of GWR-based VRA reported in @trevisan2021spatial compared to previous studies on VRA economic evaluation [@bullock1998does; @koch2004economic; @thrikawala1999economic], our suspicion stands a good chance of being plausible.
+However, no software package is readily usable to estimate GWR with quadratic-plateau fucntional form.
+Second, GWR itself has faced criticism regarding the statistical reliability of its coefficient estimations [@griffith2008spatial; @harris2019simulation; @paez2011simulation; @da2016multiple].
+We hypothesize that the intersection of these two issues—the model mis-specification and the inherent limitations of GWR—may have led to a substantial overestimation of the economic value of switching from URA to VRA.
 

### 2023-11-16 Codes/3_make_figures_publication.rmd
Updates from Overleaf
xiaofei's edut

@@
   readRDS() %>%
-  .[, type := ifelse(transfer == 0, "GWRR", "GWRT")] %>%
-  .[, bias := pi_diff_est - pi_diff] %>%
-  # only display the 25% (5.44), 50% (6.56), 75% (7.67) price ratio
+    # === do not need QD result
+    .[model!="QD", ] %>% 
+    # === modify model names
+    .[model=="GWR-R", model := "GWRR"] %>% 
+    .[model=="GWR-T", model := "GWRT"] %>% 
+    # === only need  25% (5.44), 50% (6.56), 75% (7.67) price ratio
     .[pRatio %in% c(5.44, 6.56, 7.67), ] %>%
-  # === label price ratio
-  .[, pLabelName := "Price Ratio (N/corn)"] %>%
-  .[pRatio == 5.44, pLabel := "Low (5.44)"] %>%
-  .[pRatio == 6.56, pLabel := "Middle (6.56)"] %>%
-  .[pRatio == 7.67, pLabel := "High (7.67)"] %>%
-  .[, pLabel := factor(pLabel, levels = c("Low (5.44)", "Middle (6.56)", "High (7.67)"))]
+    # === label prices
+    .[pRatio == 5.44, pLabel := "5.44 (Low)"] %>%
+    .[pRatio == 6.56, pLabel := "6.56 (Middle)"] %>%
+    .[pRatio == 7.67, pLabel := "7.67 (High)"] %>%
+    # === estimation bias
+    .[, bias := pi_diff_est - pi_diff]
 ```
 
-# The value of GWR-based VRA over SCAM-based URA for GWR-R and GWR-T
+# The value of GWR-based VRA over SCAM-based URA
 
 ```{r}
-# fig.id = "pi-dif-dist",
-# fig.cap = "The value of GWR-based VRA over SCAM-based URA for GWR-R and GWR-T"
+# fig.id = "value-vra",
+# fig.cap = "The economic value of the quadratic GWR-based VRA over SCAM-based URA"
 mean_data_value <-
     results %>%
-  .[, .(pi_diff = median(pi_diff)),
-    by = c("field_col", "pLabel", "type")
+    .[, .(pi_diff = median(pi_diff),
+          pi_diff_est = median(pi_diff_est),
+          bias = median(bias)),
+      by = c("field_col", "pLabel", "model")
     ]
-
-# saveRDS(mean_data_value, "Shared/Results/mean_data_value.rds")
 
@@
   geom_histogram(
-    aes(x = pi_diff),
-    fill = NA,
-    color = "blue",
-    bins = 50,
-    linewidth = 0.2
+        aes(x = pi_diff, fill = "True", color = "True"),
+        alpha = 0.1, bins = 80, size = 0.2
+    ) +
+    geom_histogram(
+        aes(x = pi_diff_est, fill = "Estimated", color = "Estimated"),
+        alpha = 0.4, bins = 80, size = 0.2
     ) +
@@
         aes(xintercept = pi_diff),
-    color = "red",
-    linewidth = 0.5
+        color = "blue", size = 0.5
+    ) +
+    geom_vline(
+        data = mean_data_value,
+        aes(xintercept = pi_diff_est),
+        color = "red", size = 0.5
+    ) +
+    geom_text(
+        data = mean_data_value, color = "blue",
+        aes(
+            x = ifelse(pi_diff < 65, pi_diff - 5, pi_diff - 20), y = 100,
+            label = paste0("Median=", round(pi_diff, 2))
+        ),
+        angle = 0, hjust = 0.9, vjust = 0, size = 2.5
     ) +
@@
         aes(
-      x = ifelse(pi_diff < 65, pi_diff + 5, pi_diff - 20), y = 150,
-      label = paste0("Median = ", round(pi_diff, 2))
+            x = ifelse(pi_diff_est < 65, pi_diff_est + 4, pi_diff_est - 20), y = 100,
+            label = paste0("Median=", round(pi_diff_est, 2))
         ),
-    angle = 0,
-    hjust = -0.1,
-    vjust = 0,
-    size = 3,
-    family = "Times"
+        angle = 0, hjust = -0.1, vjust = 0, size = 2.5
     ) +
-  facet_grid(pLabel ~ type) +
+    scale_color_manual(name = "", values = c("True" = "blue", "Estimated" = "red"),
+                       breaks = c("True", "Estimated")) +
+    scale_fill_manual(name = "", values = c("True" = "blue", "Estimated" = "red"),
+                      breaks = c("True", "Estimated")) +
+    facet_grid(pLabel ~ model) +
     scale_y_continuous(expand = c(0, 0)) +
-  scale_x_continuous(breaks = 20 * (-2:3), limits = c(-45, 60)) +
-  xlab("The value of VRA over URA ($ per ha)") +
+    scale_x_continuous(breaks = 20 * (-2:4), limits = c(-30, 90)) +
+    scale_y_continuous(sec.axis = sec_axis(~ . , name = "Nitrogen-Corn Price Ratio", breaks = NULL, labels = NULL),
+                       expand = c(0, 0)) +
+    xlab("Economic value of VRA over URA ($ per ha)") +
     ylab("Number of Simulation Cases") +
+    theme(
+        text = element_text(family = "Times New Roman"),
+        panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        panel.background = element_blank(),
+        panel.border = element_rect(fill = NA),
+        legend.position='bottom',
+        legend.key.size = unit(0.3, 'cm')
+    ) +
   theme_fig
@@
   g_value,
-  width = 6,
+  width = 7,
   height = 5,
@@
 
-# EONR estimation tendency
+# EONR estimation bias
 
 ```{r}
-# ggplot(est_data) +
-# geom_histogram(aes(x = opt_N_scam)) +
-# facet_grid(round(pN, digits = 2) ~ .)
-
 est_data <-
@@
   unnest() %>%
-  data.table() %>%
-  .[, type := ifelse(transfer == 0, "GWRR", "GWRT")]
+  data.table()
 
@@
   .[, pRatio := pN / pCorn] %>%
-  # only display the 25% (5.44), 50% (6.56), 75% (7.67) price ratio
+    # === do not need QD result
+    .[model!="QD", ] %>% 
+    # === modify model names
+    .[model=="GWR-R", model := "GWRR"] %>% 
+    .[model=="GWR-T", model := "GWRT"] %>% 
+    # === only need  25% (5.44), 50% (6.56), 75% (7.67) price ratio
     .[pRatio %in% c(5.44, 6.56, 7.67), ] %>%
-  # === label price ratio
-  .[, pLabelName := "Price Ratio (N/corn)"] %>%
-  .[pRatio == 5.44, pLabel := "Low (5.44)"] %>%
-  .[pRatio == 6.56, pLabel := "Middle (6.56)"] %>%
-  .[pRatio == 7.67, pLabel := "High (7.67)"] %>%
-  .[, pLabel := factor(pLabel, levels = c("Low (5.44)", "Middle (6.56)", "High (7.67)"))] %>%
-  .[, .(eonr_ratio = mean(opt_N_gwr / opt_N_scam)), by = .(type, sim, pLabel)]
+    # === label prices
+    .[pRatio == 5.44, pLabel := "5.44 (Low)"] %>%
+    .[pRatio == 6.56, pLabel := "6.56 (Middle)"] %>%
+    .[pRatio == 7.67, pLabel := "7.67 (High)"] %>% 
+    .[, .(eonr_ratio = mean(opt_N_gwr / opt_N_scam)), by = .(model, sim, pLabel)]
 
@@
     aes(x = eonr_ratio),
-    color = "blue",
+    color = "black",
     fill = NA,
@@
   ) +
-  geom_vline(xintercept = 1, color = "red") +
-  facet_grid(pLabel ~ type) +
+  geom_vline(xintercept = 1, color = "black") +
+  facet_grid(pLabel ~ model) +
+  scale_y_continuous(expand = c(0, 0)) +
+  scale_y_continuous(sec.axis = sec_axis(~ . , name = "Nitrogen-Corn Price Ratio", breaks = NULL, labels = NULL),
+                       expand = c(0, 0)) +
   ylab("Number of Simulation Cases") +
@@
   g_comp_eonr,
-  width = 6,
-  height = 5,
-  dpi = 600
-)
-```
-
-# Bias in the estimation of the value of GWR-based VRA over SCAM-based URA
-
-```{r}
-# fig.id = "bias-est-pi",
-# fig.cap = "Bias in the estimation of the value of GWR-based VRA over SCAM-based URA for GWR-R and GWR-T"
-
-# mean_data_bias[type == "GWRT" & pLabel == 10.35, bias] %>% hist
-
-median_bias_data <-
-  results %>%
-  .[, bias := pi_diff_est - pi_diff] %>%
-  .[, .(bias = median(bias)),
-    by = c("field_col", "pLabel", "type")
-  ] %>%
-  print()
-
-g_bias <-
-  results %>%
-  .[, bias := pi_diff_est - pi_diff] %>%
-  .[bias < 150, ] %>%
-  ggplot(data = .) +
-  geom_histogram(
-    aes(x = bias),
-    fill = NA,
-    color = "blue",
-    size = 0.2,
-    bins = 50
-  ) +
-  geom_vline(
-    data = median_bias_data, aes(xintercept = bias),
-    color = "red",
-    size = 0.5
-  ) +
-  geom_text(
-    data = median_bias_data, color = "red",
-    aes(
-      x = ifelse(bias < 65, bias + 2, bias - 85), y = 100,
-      label = paste0("Median = ", round(bias, 2)),
-      family = "Times"
-    ),
-    angle = 0, hjust = -0.1, vjust = 0, size = 3
-  ) +
-  facet_grid(pLabel ~ type) +
-  scale_y_continuous(expand = c(0, 0)) +
-  xlab("Bias in the Estimation of the Value of VRA over URA ($ per ha)") +
-  ylab("Number of Simulation Cases") +
-  theme_fig
-
-ggsave(
-  "GitControlled/Writing/Figures/g_bias.png",
-  g_bias,
   width = 6,

### 2023-11-16 Writing/manuscript_gwr.rmd
xiaofei's edut

@@
 This bias could manifest as either an underestimation or overestimation of VRA's value.
-The bias can be exacerbated by mis-specification of the functional form, as this can lead to immediate mis-representation of the true yield response, further skewing the estimated value of VRA.
+The bias can be exacerbated by mis-specification of the functional form in step (1), as this can lead to immediate mis-representation of the true yield response, further skewing the estimated value of VRA.
 
 Two primary approaches exist for deriving variable rate application (VRA) recommendations from OFPE data.
-The first approach integrates soil sampling and/or field characteristic data (such as topography) with OFPE data (yield, input) to estimate site-specific yield response functions.
+The first approach integrates soil sampling and/or field characteristic data (such as topography) into OFPE data (yield, input) to estimate site-specific yield response functions.
 In this approach, interacations of inputs and soil/field characteristics are explicilty modeled.
@@
 But deploying sophisticated sensors to gather field characteristics data is also costly, and the effects of their generation and use on farming profitability remains in question [@gardner2021economic]].
+For additional details, Appendix I discusses the microeconomics-based conceptual framework for estimating yield-to-input response functions using OFPE data.
 
@@
 The primary objective of this study is to examine the degree and direction of bias in the estimation of the economic value of GWR-based variable nitrogen rate recommendations in corn production, especially when the yield response to nitrogen is incorrectly specified as quadratic in the GWR model instead of the correct quadratic-plateau function.
-(Nathan's emphasis: "a difference between quadratic GWR and a more flexible functional form with no spatial heterogeneity".
-Shall we put it here?)  We will employ Monte Carlo simulations, which allow us to accurately define and know the true yield response function within our data-generating process, providing a means to quantify the degree of bias present.
+We will employ Monte Carlo simulations, which allow us to accurately define and know the true yield response function within our data-generating process, providing a means to quantify the degree of bias present.
 
@@
 
-This study conducts Monte Carlo simulations to evaluate the bias in the estimation of the value of VRA over URA when VRA is derived from quadratic GWR model when the true yield response function follows quadratic-plateau functional form.
+This study conducts Monte Carlo simulations to evaluate the bias in estimating the economic value of variable rate application (VRA) over uniform rate application (URA) when VRA is derived from quadratic geographically weighted regression (GWR) model and the true yield response function follows a quadratic-plateau functional form.
 We consider two sets of GWR specifications: one used in @rakshit2020 and the other in @trevisan2021spatial.
@@
 
-Figure \@ref(fig:field-layout) shows a simulated field's layout and defines the spatial units of the simulated OFPEs.
-The basic spatial unit of the field is a 6m $\times$ 6m "cell", which is the resolution at which the field characteristics data (i.e., parameters of the "true" yield response function) were allowed to vary.
+A simulated on-farm precision experiment (OFPE) field was created, with the basic spatial unit of the field being a 6m $\times$ 6m "cell", which is the resolution at which the field characteristics data (i.e., parameters of the "true" yield response function) were allowed to vary.
 It was assumed, however, that yields could not be monitored at such a high resolution.
@@
 Therefore, the yield data's resolution was 18m $\times$ 12m (3 cells $\times$ 2 cells, called a "subplot").
-The N rate unit was 18m $\times$ 72m (3 cells $\times$ 12 cells, called a "plot") to accommodate the variable-rate applicator's application resolution.
+The N trial rate application unit was 18m $\times$ 72m (3 cells $\times$ 12 cells, called a "plot") to accommodate the variable-rate applicator's application resolution.
 A 12m "transition zone" was placed between two plots (that is, a 6m "transition zone" on each end of a plot), so that when the experimental N rate changed, the harvester had 12m to "clear" and begin to record accurately on a plot with an N rate different from its predecessor's.
@@
 The couplet $(j, i)$ is used to identify individual cells.
+Figure A1 in Appendix II shows the simulated OFPE field's layout with spatial unit definitions.
 
@@
 The spatial distributions of cell-level parameters $\alpha_{j, i}$, $\beta_{j, i}$, $\gamma_{j,i}$, $\tau_{j, i}$, and the error term $\varepsilon_{j, i}$ were simulated by generating spatially correlated random fields using unconditional Gaussian geostatistical simulation based on the specified variograms [@dietrich1996fast; @wood1994simulation].
-The simulation processes were conducted using the R package gstat [@graler16].
+The simulation processes were conducted using the R package gstat [@graler16], and Figure A3 in Appendix II illustrates the cell-level spatial distribution of the true yield response parameters in one simulation.
 Specifically, the model is spherical, the nugget variance is zero, and the range is 600 meters.
@@
 
-Figure ??
-illustrates the spatial distribution map of cell-level $N^*_{j,i}$ for one example simulation.
 Note that the true $N^*_{j,i}$s are not observable by producers or researchers, and are not used in the profit calculation in this study.
@@
 
-Figures \@ref(fig:field-layout) and \@ref(fig:field-N-design) illustrate the Latin square trial design assumed in each simulation.
-The field was partitioned into a 4-block $\times$ 2-block grid, in which each block was partitioned into a 6-plot $\times$ 6-plot grid with each of six N rates assigned to exactly one plot in each row and each column of the block (i.e., a Latin square).
-A special patterned Latin square [@li2023trial] was utilized to ensure that no adjacent N plots were assigned the same N rate, and furthermore, the order of N rates in each row of every block was specified to avoid relatively large changes in N rates (due to the technological limitations of N application equipment commonly witnessed in real-world OFPE).
+A 6 $\times$ 6 Latin square trial design was utilized in each simulated on-farm experiment.
+The field was partitioned into a 4-block $\times$ 2-block grid (see Figure A1 of Appendix II), in which each block was partitioned into a 6-plot $\times$ 6-plot grid with each of six N rates assigned to exactly one plot in each row and each column of the block (i.e., a Latin square).
+The Latin square has a special pattern  [@li2023trial] to ensure that no adjacent N plots were assigned the same N rate, and furthermore, the order of N rates in each row of every block was specified to avoid relatively large changes in N rates (due to the technological limitations of N application equipment commonly witnessed in real-world OFPE).
 
@@
 The means of these trial N rates across simulations were approximately {80, 130, 154, 184, 219, and 270} kg ha$^{-1}$, while the differences between simulations were small and negligible.
+The spatial map of the trial N rates within the field by the Latin square design was illustrated in Figure A2 of Appendix II.
 
@@
 For many cells, the SCAM-based estimated EONR is significantly higher than the actual yield-maximizing N rate, resulting in an estimated yield far lower because of the quadratic functional form assumption.
-Figure \@ref(fig:why-bias-single) panel (a) illustrates the true quadratic-plateau yield response and estimated yield response by the mis-specified quadratic GWR for a single cell.
+Figure \@ref(fig:why-bias-single) panel (a) illustrates the true quadratic-plateau yield response curve and estimated yield response curve by the mis-specified quadratic GWR for a single cell.
 The cell's true yield response plateaus at a nitrogen rate of about $`r round(il_data_oe[aunit_id %in% single_aunit, Nk], digits = 0)`$ kg ha$^{-1}$, but the GWR-estimated yield response function suggests that yield should peak at a nitrogen rate of about $`r round(point_data_gwr[type == "GWR", N], digits = 0)`$ kg ha$^{-1}$ and decline thereafter.
@@
 
-```{r fig.id = "bias-est-pi", fig.cap = "Bias in the estimation of the value of GWR-based VRA over SCAM-based URA by two GWR models (GWRR and GWRT) and at three nitrogen-corn price ratios", fig.width = 6}
-# knitr::include_graphics(here::here("GitControlled/Writing/Figures/g_bias.png"))
-g_bias
-```
-
 ```{r fig.id = "why-bias-many", fig.cap = "The cause of significant overestimation of the value of GWR-based VRA", fig.width = 6}
@@
 `r run_pagebreak()`
-
-# Conceptual Framework: Estimation of Yield-to-input Response Relationships Using OFPE Data
-
-OFPE can provide detailed as-applied input and yield data at dense resolutions over entire fields, which if well analyzed may provide valuable information that can improve site-specific input application recommendations [@bullock2019data; @lacoste2021farm].
-Consider a yield response function $y = f(\textbf{x}, \textbf{c})$, where following @bullock2000agronomic, $\textbf{x}$ is a vector of input management variables and $\textbf{c}$ is a vector of spatial variables describing field and soil characteristics^[For simplicity, we suppress discussion of the need to bring variance in weather data into yield response estimation.
-Obviously, generation and use of weather data is necessary to provide meaningful probabilistic analysis and input management advice.].
-Letting a field site $i$ be defined as a contiguous area characterized uniformly by a value $\textbf{c}_i$ of the vector of field and soil characteristics, its *site-specific yield response function* is the reduced form of the field's yield response function created when the value of the vector of characteristics variables is set at the site's value, $\textbf{c}_i$:  $f_i(\textbf{x}) \equiv f(\textbf{x}, \textbf{c}_i)$.
-This conceptualization suggests two methods of estimating a field's site-specific yield responses.
-The first is to estimate a "map" of the field characteristics, for example thought of as a set of the field's $n \geq 1$ sites' values of the characteristics vector: $\{\textbf{c}_1,\dots, \textbf{c}_n\}$.
-With that map, regressing yield on $\textbf{x}$ and $\textbf{c}$ generates an estimated "field-specific" yield response function $\hat{f}(\textbf{x},\textbf{c})$.
-Estimates of site-specific yield response functions can then be obtained by inserting the value of the site's characteristic variables into the estimate of the field-specific response function: $\hat{f}_i(\textbf{x}) \equiv \hat{f}(\textbf{x},\textbf{c}_i)$.
-Alternatively, a site-specific yield response function might be estimated simply by taking (input rate, yield) data from points around a site of interest $i$, and regressing yield on input application rates to attain the estimate $\hat{f}_i (\textbf{x})$.
-Stated roughly, using GWR takes the latter approach, which has the advantage of not needing a costly map of field characteristics values.
-
-```{r fig.id = "field-layout", fig.cap = "Simulated field layout with spatial unit definitions", fig.width = 7}
-# knitr::include_graphics(here::here("GitControlled/Writing/Figures/g_layout.png"))
-g_layout
-```
-
-```{r fig.id = "field-N-design", fig.cap = "Experiment design of nitrogen (N) rates", out.width = "6in", fig.width = 6}
-# knitr::include_graphics(here::here("GitControlled/Writing/Figures/g_exp.png"))
-g_exp
-```

### 2023-11-16 Writing/supplementary_appendix.rmd
xiaofei's edut

@@
       readRDS() %>%
-      .[, type := ifelse(transfer == 0, "GWRR", "GWRT")] %>%
-      .[, bias := pi_diff_est - pi_diff] %>%
-      # only display the 25% (5.44), 50% (6.56), 75% (7.67) price ratio
+    # === do not need QD result
+    .[model!="QD", ] %>% 
+    # === modify model names
+    .[model=="GWR-R", model := "GWRR"] %>% 
+    .[model=="GWR-T", model := "GWRT"] %>% 
+    # === only need  25% (5.44), 50% (6.56), 75% (7.67) price ratio
     .[pRatio %in% c(5.44, 6.56, 7.67), ] %>%
-      # === label price ratio
-      .[, pLabelName := "Price Ratio (N/corn)"] %>%
-      .[pRatio == 5.44, pLabel := "Low"] %>%
-      .[pRatio == 6.56, pLabel := "Middle"] %>%
-      .[pRatio == 7.67, pLabel := "High"] %>%
-      .[, pLabel := factor(pLabel, levels = c("Low", "Middle", "High"))] %>%
-      .[, p_ratio_text := paste0("Price Ratio (N/Corn) \n = ", pRatio, " (", pLabel, ")")]
+    # === label prices
+    .[pRatio == 5.44, pLabel := "5.44 (Low)"] %>%
+    .[pRatio == 6.56, pLabel := "6.56 (Middle)"] %>%
+    .[pRatio == 7.67, pLabel := "7.67 (High)"] %>%
+    # === estimation bias
+    .[, bias := pi_diff_est - pi_diff]
   )) %>%
@@
     results %>%
-      .[, .(pi_diff = median(pi_diff)),
-        by = .(field_col, p_ratio_text, type)
+      .[, .(pi_diff = median(pi_diff),
+      pi_diff_est = median(pi_diff_est),
+      bias = median(bias)),
+        by = .(field_col, pLabel, model)
       ]
@@
           geom_histogram(
-        aes(x = pi_diff),
-        fill = NA,
-        color = "blue",
-        bins = 50,
-        size = 0.2
+        aes(x = pi_diff, fill = "True", color = "True"),
+        alpha = 0.1, bins = 80, size = 0.2
+    ) +
+    geom_histogram(
+        aes(x = pi_diff_est, fill = "Estimated", color = "Estimated"),
+        alpha = 0.4, bins = 80, size = 0.2
     ) +
     geom_vline(
-        data = median_data_value,
+        data = mean_data_value,
         aes(xintercept = pi_diff),
-        color = "red",
-        size = 0.5
+        color = "blue", size = 0.5
+    ) +
+    geom_vline(
+        data = mean_data_value,
+        aes(xintercept = pi_diff_est),
+        color = "red", size = 0.5
     ) +
     geom_text(
-        data = median_data_value, color = "red",
+        data = mean_data_value, color = "blue",
         aes(
-          x = ifelse(pi_diff < 65, pi_diff + 5, pi_diff - 20),
-          y = 150,
-          label = paste0("Median = ", round(pi_diff, 2))
+            x = ifelse(pi_diff < 65, pi_diff - 5, pi_diff - 20), y = 100,
+            label = paste0("Median=", round(pi_diff, 2))
         ),
-        angle = 0, hjust = -0.1, vjust = 0, size = 3,
-        family = "Times"
-      ) +
-      facet_grid(p_ratio_text ~ type) +
-      scale_y_continuous(expand = c(0, 0), limits = c(NA, 200)) +
-      scale_x_continuous(breaks = 20 * (-2:4), limits = c(-45, 80)) +
-      theme(
-        panel.spacing.y = unit(0.3, "cm")
-      ) +
-      xlab("The value of VRA over URA ($ per ha)") +
-      ylab("Number of Simulation Cases")
-  )) %>%
-  #* ===========================================================
-  #* Plots of the bias in the value of GWR
-  #* ===========================================================
-  mutate(median_bias_data = list(
-    results %>%
-      .[, bias := pi_diff_est - pi_diff] %>%
-      .[, .(bias = median(bias)),
-        by = .(field_col, p_ratio_text, type)
-      ]
-  )) %>%
-  mutate(g_bias = list(
-    results %>%
-      .[, bias := pi_diff_est - pi_diff] %>%
-      .[bias < 150, ] %>%
-      ggplot(data = .) +
-      geom_histogram(
-        aes(x = bias),
-        fill = NA,
-        color = "blue",
-        size = 0.2,
-        bins = 50
-      ) +
-      geom_vline(
-        data = median_bias_data, aes(xintercept = bias),
-        color = "red",
-        size = 0.5
+        angle = 0, hjust = 0.9, vjust = 0, size = 2.5
     ) +
     geom_text(
-        data = median_bias_data, color = "red",
+        data = mean_data_value, color = "red",
         aes(
-          x = ifelse(bias < 65, bias + 2, bias - 85), y = 100,
-          label = paste0("Median = ", round(bias, 2))
+            x = ifelse(pi_diff_est < 65, pi_diff_est + 4, pi_diff_est - 20), y = 100,
+            label = paste0("Median=", round(pi_diff_est, 2))
         ),
-        angle = 0, hjust = -0.1, vjust = 0, size = 3,
-        family = "Times"
+        angle = 0, hjust = -0.1, vjust = 0, size = 2.5
     ) +
-      facet_grid(p_ratio_text ~ type) +
+    scale_color_manual(name = "", values = c("True" = "blue", "Estimated" = "red"),
+                       breaks = c("True", "Estimated")) +
+    scale_fill_manual(name = "", values = c("True" = "blue", "Estimated" = "red"),
+                      breaks = c("True", "Estimated")) +
+    facet_grid(pLabel ~ model) +
     scale_y_continuous(expand = c(0, 0)) +
+    scale_x_continuous(breaks = 20 * (-2:4), limits = c(-30, 90)) +
+    scale_y_continuous(sec.axis = sec_axis(~ . , name = "Nitrogen-Corn Price Ratio", breaks = NULL, labels = NULL),
+                       expand = c(0, 0)) +
+    xlab("Economic value of VRA over URA ($ per ha)") +
+    ylab("Number of Simulation Cases") +
     theme(
-        panel.spacing.y = unit(0.3, "cm")
-      ) +
-      xlab("Bias in the Estimation of the Value of VRA over URA ($ per ha)") +
-      ylab("Number of Simulation Cases")
+        text = element_text(family = "Times New Roman"),
+        panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        panel.background = element_blank(),
+        panel.border = element_rect(fill = NA),
+        legend.position='bottom',
+        legend.key.size = unit(0.3, 'cm')
+    )
   )) %>%
-  select(kernel, g_value, g_bias)
+    select(kernel, g_value)
 ```
 
-# Appendix I: Historical Corn and Nitrogen Prices {-}
+# Appendix I: Conceptual Framework of Estimating Yield-to-input Response Relationships Using OFPE Data {-}
+
+OFPE can provide detailed as-applied input and yield data at dense resolutions over entire fields, which if well analyzed may provide valuable information that can improve site-specific input application recommendations [@bullock2019data; @lacoste2021farm].
+Consider a yield response function $y = f(\textbf{x}, \textbf{c})$, where following @bullock2000agronomic, $\textbf{x}$ is a vector of input management variables and $\textbf{c}$ is a vector of spatial variables describing field and soil characteristics^[For simplicity, we suppress discussion of the need to bring variance in weather data into yield response estimation.
+Obviously, generation and use of weather data is necessary to provide meaningful probabilistic analysis and input management advice.].
+Letting a field site $i$ be defined as a contiguous area characterized uniformly by a value $\textbf{c}_i$ of the vector of field and soil characteristics, its *site-specific yield response function* is the reduced form of the field's yield response function created when the value of the vector of characteristics variables is set at the site's value, $\textbf{c}_i$:  $f_i(\textbf{x}) \equiv f(\textbf{x}, \textbf{c}_i)$.
+This conceptualization suggests two methods of estimating a field's site-specific yield responses.
+The first is to estimate a "map" of the field characteristics, for example thought of as a set of the field's $n \geq 1$ sites' values of the characteristics vector: $\{\textbf{c}_1,\dots, \textbf{c}_n\}$.
+With that map, regressing yield on $\textbf{x}$ and $\textbf{c}$ generates an estimated "field-specific" yield response function $\hat{f}(\textbf{x},\textbf{c})$.
+Estimates of site-specific yield response functions can then be obtained by inserting the value of the site's characteristic variables into the estimate of the field-specific response function: $\hat{f}_i(\textbf{x}) \equiv \hat{f}(\textbf{x},\textbf{c}_i)$.
+Alternatively, a site-specific yield response function might be estimated simply by taking (input rate, yield) data from points around a site of interest $i$, and regressing yield on input application rates to attain the estimate $\hat{f}_i (\textbf{x})$.
+Stated roughly, using GWR takes the latter approach, which has the advantage of not needing a costly map of field characteristics values.
+
+# Appendix II: Maps of the Simulated On-farm Precision Experiment Field {-}
+
+This appendix section provides the detailed spatial maps for the field layout with spatial unit definitions, experiment design of nitrogen (N) rates, and spatial distribution of the true yield response parameters of the simulated on-farm precision experiment (OFPE) field.
+
+```{r fig.id = "field-layout", fig.cap = "Simulated field layout with spatial unit definitions", fig.width = 7}
+knitr::include_graphics(here::here("GitControlled/Writing/Figures/g_layout.png"))
+g_layout
+```
+
+```{r fig.id = "field-N-design", fig.cap = "Experiment design of nitrogen (N) rates", out.width = "6in", fig.width = 7}
+knitr::include_graphics(here::here("GitControlled/Writing/Figures/g_exp.png"))
+g_exp
+```
+
+```{r fig.id = "field-N-design", fig.cap = "Spatial distribution of the true yield response parameters in one simulation", out.width = "6in", fig.width = 7}
+knitr::include_graphics(here::here("GitControlled/Writing/Figures/appendix/g_par.png"))
+g_par
+```
+
+# Appendix III: Historical Corn and Nitrogen Prices {-}
 
@@
 
-# Appendix II: Results with Alternative Kernel Functions {-}
+# Appendix IV: Results with Alternative Kernel Functions {-}
 
@@
 "}
-knitr::include_graphics("kernel_function_list.png")
+knitr::include_graphics(here::here("GitControlled/Writing/Figures/appendix/kernel_function_list.png"))
 ```
@@
 
-## Comparing the values of GWR-based VRA and SCAM-based URA {-}
+Figures A\@ref(fig:value-kernel-exp) through A\@ref(fig:value-kernel-tricube) show the distributions of the true and estimated economic value of GWR-based VRA (\Delta^{GWR} and $\hat{\Delta}^{GWR}$) using four alternative kernels (Exponential, Boxcar, Bi-square, and Tri-cube).
+The true values are calculated using the true yield response functions, while the estimated values are calculated using the quadratic GWR-estimated yield response functions.
+Two GWR models (GWRR and GWRT) are used.
+The values are calculated at three nitrogen-corn price ratios ($/kg : $/kg) while the corn price is set at $0.28/kg.
+A substantial overestimation of the GWR-based VRA's economic value compared to its true value is present for all kernels, which is consistent with the Gaussian kernel result.
+Using the Gaussian kernel, GWRR performs better as the price ratio increases, and GWRT performs better as the price ratio decreases.
+This holds true across all the other kernel function choices as well.
+The presence of a similar fat tail in the GWRT value distribution is also evident.
+The magnitudes of the estimation bias vary across kernel function choices, but the differences are not substantial and do not affect qualitatively our conclusions drawn in the main text.
 
-Figures A\@ref(fig:value-kernel-exp) through A\@ref(fig:value-kernel-tricube) show the distributions of the true economic value of GWR using four different kernels (Exponential, Boxcar, Bi-square, and Tri-cube):
-
-\begin{equation}
-\Delta^{GWR}=\Pi^{GWR}-\Pi^{SCAM}.
-(\#eq:label)
-\end{equation}
-
-Using the Gaussian kernel, we found that GWRR performs better as the price ratio increases, and GWRT performs better as the price ratio decreases (see Figure 3 of the main text).
-This holds true across all the other kernel function choices.
-Although there are some variations in the magnitudes of $\Delta^{GWR}$ among different kernel function choices, these differences do not significantly affect the conclusions drawn in the main text.
-
-```{r, fig.id = "value-kernel-exp", fig.cap = "The true economic value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios using the Exponential kernel function", fig.height = 6}
+ ```{r, fig.id = "value-kernel-exp", fig.cap = "The economic value of the quadratic GWR-based VRA over SCAM-based URA using the Exponential kernel function", fig.height = 7}
 gg_appendix$g_value[[2]]
@@
 
-```{r, fig.id = "value-kernel-boxcar", fig.cap = "The true economic value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios using the Boxcar kernel function", fig.height = 6}
+```{r, fig.id = "value-kernel-boxcar", fig.cap = "The economic value of the quadratic GWR-based VRA over SCAM-based URA using the Boxcar kernel function", fig.height = 7}
 gg_appendix$g_value[[3]]
@@
 
-```{r, fig.id = "value-kernel-bs", fig.cap = "The true economic value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios using the Bi-square kernel function", fig.height = 6}
+```{r, fig.id = "value-kernel-bs", fig.cap = "The economic value of the quadratic GWR-based VRA over SCAM-based URA using the Bi-square kernel function", fig.height = 7}
 gg_appendix$g_value[[4]]
@@
 
-```{r, fig.id = "value-kernel-tricube", fig.cap = "The true economic value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios using the Tri-cube kernel function", fig.height = 6}
-gg_appendix$g_value[[5]]
-```
-
-`r run_pagebreak()`
-
-## Bias in the estimation of the value of GWR-based VRA {-}
-
-Figures A\@ref(fig:bias-kernel-exp) through A\@ref(fig:bias-kernel-tricube) show the distribution of the bias in the estimated economic value of GWR.
-Similar to the findings from using the Gaussian kernel presented in Figure 6 under the Gaussian kernel, the GWRR consistently exhibits significant over-estimation of the value of GWR-based VRA across all other kernel function choices.
-Also, the GWRT demonstrates smaller over-estimation at low price ratios compared to GWRR, while the over-estimation increases as price ratio rises.
-The presence of a similar fat tail in the GWRT bias distribution is also evident.
-The magnitudes of the estimation bias vary across kernel function choices, but the differences are not substantial and do not affect qualitatively our conclusions drawn in the main text.
-
-```{r, fig.id = "bias-kernel-exp", fig.cap = "Bias in the estimation of the value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios using the Exponential kernel function", fig.height = 6}
-gg_appendix$g_bias[[2]]
-```
-
-```{r, fig.id = "bias-kernel-boxcar", fig.cap = "Bias in the estimation of the value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios using the Boxcar kernel function", fig.height = 6}
-gg_appendix$g_value[[3]]
-```
-
-```{r, fig.id = "bias-kernel-bs", fig.cap = "Bias in the estimation of the value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios using the Bi-square kernel function", fig.height = 6}
-gg_appendix$g_value[[4]]
-```
-
-```{r, fig.id = "bias-kernel-tricube", fig.cap = "Bias in the estimation of the value of GWR-based VRA for two GWR models (GWRR and GWRT) and under three nitrogen-corn price ratios using the Tri-cube kernel function", fig.height = 6}
+```{r, fig.id = "value-kernel-tricube", fig.cap = "The economic value of the quadratic GWR-based VRA over SCAM-based URA using the Tri-cube kernel function", fig.height = 7}
 gg_appendix$g_value[[5]]

### 2023-11-16 Writing/JAAEA/2ndRoundRevision/reply_to_reviewer_1.rmd
finalized

--- 2023-11-05 Writing/JAAEA/2ndRoundRevision/reply_to_reviewer_1.rmd
@@
 
-**Response**: This is good to know because the authors do not mention this at all in the paper.
-But, they only provide bare matlab codes without any readme file.
-I would not call this readily available.
-However, we will drop the sentence.
-(We understand that you told us we cannot ignore this comment, but we just wanted to point this out because we are keeping that sentence.)
+**Response**: We appreciate your observation regarding the existing linear plateau GWR package.
+Upon reviewing the @lambert2022geographically paper, we found that their supplemental materials solely offer raw MATLAB code without a corresponding readme file, which might not qualify as readily available.
+Nevertheless, we have removed that sentence in the abstract.
+But we have retained this information in the main text, as the nonlinear GWR model is still not standard routines in many contemporary mainstream statistical packages.
 
 2.
-<span style = "color: blue;">A flat response could have produced the "high values" of VRA reported by Trevisan et al., not the method used to estimate yield response.
+<span style = "color: blue;"> A flat response could have produced the "high values" of VRA reported by Trevisan et al., not the method used to estimate yield response.
 A quadratic functional form (and even a quad-response with a plateau) will likely produce optimal n-rates outside the experimental n-rates if the response is flat.</span>
@@
 
-We realized that we did not state thaa we limited the estimted EONR to the range of the experimental rates. We added the following sentence to the manuscript on page ??, line ??":
+We realized that we did not state that we limited the estimted EONR to the range of the experimental rates. We added the following sentence to the manuscript on page ??, line ??":
 
@@
 
-**Response**:
-
-This comment clearly shows that this reviewer did not pay attention to our replies to his comments (the first round review, comment 1).
-In our reply to his comments, we clearly stated that the site-specific parameters are indeed spatially correlated.
-We also ensured that the coefficients on the linear and quadratic N-rates were constrained to be positive and negative.
-This is not a hard task.
-We share all the codes written in R on a publicly accessible repository.
-Anybody can check how this was done in our paper.
+**Response**: This comment indicates that the reviewer might have missed our responses to their initial comments (first-round review, comment 1).
+In our reply, we explicitly highlighted the site-specific parameters are indeed spatially correlated.
+Additionally, we also ensured that the coefficients on the linear and quadratic N-rates were constrained to be positive and negative.
+This was implemented transparently in our R code, accessible to anyone through our publicly available repository.
+We invite reviewers or interested parties to examine our paper's code for detailed insights into these implementations.
 
@@
 
-**Response**:
+**Response**: Site-specific parameters and errors were generated for each of the 1,000 Monte Carlo iterations, resulting in distinct spatial patterns of Economic Optimum Nitrogen Rate (EONR) for each simulation instance.
+However, the parameters of the variogram (such as nugget and sill) remain consistent across simulations, ensuring that the spatial dependence of the site-specific parameters is the same across all simulations.
 
-Site-specific parameters and errors were generated for each of the 1,000 Monte Carlo iterations, resulting in distinct spatial patterns of Economic Optimum Nitrogen Rate (EONR) for each simulation instance.
-However, the parameters of the variogram (such as nugget and sill) remain consistent across simulations, ensuring that the spatial dependence of the site-specific parameters is the same.
-
-Clarifying sentences were added to page ??, line ??.
+Clarifying sentences were added to page ??, lines ??.
 
@@
 
-**Response**:
-
-We agree that we can provide more information on how the data is generated. The error term follows the normal distribution with spatial correlation (a sentence on this added on page ??, line ??).
+**Response**: We agree that we can provide more information on how the data is generated.
+The error term follows the normal distribution with spatial correlation (a sentence on this added on page ??, line ??).
 
 However, we emphasize that we are dedicated for reproducibility of our work and all the computer programs are made publicly available at the GitHub repository dedicated for this project (The url of this repository is shared in the manuscript in page ??, line??).
-It is simply impossible to describe all the details of the simulations.
-Reproducibility can be achieved only when the full computer programs are shared, which we do.
+It is impractical to describe all the simulations details in writing.
+Reproducibility can be achieved when running the full computer programs we shared.
 
@@
 
+**Response**: Ignored as suggested
+
 <span style = "color: blue;">Other notes:
@@
 
-**Response**: Ignored as suggested
+**Response**: We apologize for the figure number errors.
+Those were generated by the online PDF compiling tool of JAAEA submision website.
+We will communicate with the journal editor and technician to solve the errors.

### 2023-11-16 Writing/JAAEA/2ndRoundRevision/reply_to_reviewer_2.rmd
more replies
finalized

--- 2023-11-05 Writing/JAAEA/2ndRoundRevision/reply_to_reviewer_2.rmd
@@
 
-+ <span style = "color: blue;">I still believe this research is related to studies that examine the economic value of forecasting models by assessing the economic effects stemming from inaccuracy (e.g.,
-reduction in a business’ profits by assuming a mean-squared-error loss function instead of an
-asymmetric loss, for example). Although there have been improvements in references to the
-agronomy and statistical literatures, it would still be useful to add 1-2 sentences in the
-conclusion that reference the broader economics literature on this topic. </span>
++ <span style = "color: blue;">I still believe this research is related to studies that examine the economic value of forecasting models by assessing the economic effects stemming from inaccuracy (e.g., reduction in a business’ profits by assuming a mean-squared-error loss function instead of an asymmetric loss, for example).
+Although there have been improvements in references to the agronomy and statistical literatures, it would still be useful to add 1-2 sentences in the conclusion that reference the broader economics literature on this topic.
+</span>
 
-Response: We do not address this as you suggested.
+**Response**: We do not address this as you suggested.
 
@@
 
-Response:
+**Response**: We have added that clarification in the footnote 1 on page ??
+as: "Note that while the environmental consequences of fertilizer management carry significant societal importance, they fall outside the purview of this study.
+Herein, "economically optimal" pertains strictly to the maximization of private production profitability for farmers and does not imply "socially optimal."
 
@@
 
-Response:
+**Response**: We apologize for the figure number errors.
+Those were generated by the online PDF compiling tool of JAAEA submision website.
+We will communicate with the journal editor and technician to solve the errors.
 
@@
 
-Response: Instead of making the suggested changes, we simply renamed the Methods section to "Methods: Monte Carlo Simulations," so that it is clear that all the subsequent sections are about simulations.
+**Response**: Instead of making the suggested changes, we simply renamed the Methods section to "Methods: Monte Carlo Simulations," so that it is clear that all the subsequent sections are about simulations.
 
@@
 
-Response: We apologize this mistake. This has been fixed in this version of the manuscript.
+**Response**: Thank you for pointing out this issue.
+The figure DPI information was automatically shown by the journal's submission website.
+We will communicate with the journal editor and technician to solve it.
 
@@
 
-Response: You are correct and we have removed the sentence entirely.
+**Response**: You are correct and we have removed the sentence entirely.
 
@@
 
-Response: We have modified the sentence to the following so that it describes what GWR does more accurately:
+**Response**: We have modified the sentence to the following so that it describes what GWR does more accurately:
 
@@
   - New: "Alternatively, a site-specific yield response function might be estimated simply by giving greater weights to the points around a site of interest"
+
+That part of discussion has also been moved to the Appendix I in the revised submission. Please see page ??, lines ?? in Appendix I.
 
@@
 
-Response: We dropped the sentence.
+**Response**: We dropped the sentence.
 
@@
 
-Response: We edited the sentence according to your suggestion.
+**Response**: We edited the sentence according to your suggestion. (See page ??, line ??)
 
@@
 
-Response: It follows a normal distribution in a way it is spatially correlated. This has been made clear in the manuscript (see page ??, line ??).
+**Response**: The sentence was revised as "$\varepsilon_{j, i}$ is a stochastic error term following a normal distribution and is spatially autocorrelated." to eliminate this confusion (see page ??, line ??).
 
@@
 
-Response: We added an explanation that the 600m range was chosen based on empirical data of our existing on-farm trials (see page ??, lines ??).
+**Response**: We added an explanation that the 600m range was chosen based on empirical data of our existing on-farm trials (see page ??, lines ??):
+
+"The choice of 600m range in this study was based on empirical data generated through eight on-farm randomized N field trials conducted by the Data-Intensive Farm Management Project (DIFM) project in 2018 [@bullock2019data]."
 
@@
 
-Response: We followed your suggestions and texts were modified accordingly.
+**Response**: We followed your suggestions and texts were modified accordingly. See page ??, lines ??.
 
@@
 
-Response:
+**Response**: Here at the beginning of this session, we only briefly introduce the procedure of estimating uniform EONR.
+The more detailed explanation of how EONR is calculated by solving for maximization of p\cdot \hat{f}^{SCAM} (N)-w\cdot N was described in the later part (see page ??, line ??).
 
@@
 
-Response: Expalining how the shape constraint is imposed would take more than a page of mathematical explanations.
+**Response**: Expalining how the shape constraint is imposed would take more than a page of mathematical explanations.
 We added a footnote that cites Pya's journal article titled "Shape constrained additive models" published in Statistics and computing.
+(See page ??, line ??).
 
@@
 
-Response: There is no speculation in this sentence.
+**Response**: We would argue that there is no speculation in this sentence.
 We are stating a drawback of linear-plateau model.
@@
 
-Response:
+**Response**: We added the following details to the Figure notes: "The experimental field contains a total of 288 N trial plots, arranged in 24 rows $\times$ 12 columns.
+Each N plot contains 5 effective yield subplots (as illustrated in Figure A1, Panel b), and the total number of subplots is 1,440.
+The total number of effective cells are 8,640 (72 rows $\times$ 120 columns)".
+This figure has been moved to the Appendix II and is now numbered as Figure A2.
 
@@
 
-Response: We followed your suggestion.
+**Response**: We followed your suggestion. The revised writing is on page ??, line ??.
 
@@
 
-Response: We have changed the wording to "In this scenario."
+**Response**: We have changed the wording to "In this scenario." The revised writing is on page ??, line ??.
 
@@
 
-Response: We followed your suggestion.
+**Response**: No longer relevant as the entire paragraph was deleted based on the editor's suggestion.

### 2023-11-16 Codes/3_make_figures_publication.rmd
finalized

@@
   geom_vline(xintercept = 1, color = "black") +
+  geom_text(
+        data = data.table(xintercept=1), color = "black",
+        aes(
+            x = xintercept, y = 80,
+            label = "Ratio = 1"
+        ),
+        angle = 0, hjust = 1.1, vjust = 0, size = 3
+    ) +
   facet_grid(pLabel ~ model) +
@@
   scale_shape_discrete(name = "EONR") +
-  scale_linetype_discrete(name = "Yield Response Fnctions") +
+  scale_linetype_discrete(name = "Yield Response Functions") +
   ggtitle("(a) Estimated and True Yields") +
@@
   scale_shape_discrete(name = "EONR") +
-  scale_linetype_discrete(name = "Profit Response Fnctions") +
+  scale_linetype_discrete(name = "Profit Response Functions") +
   ggtitle("(b) Estimated and True Profits") +

### 2023-11-16 Writing/manuscript_gwr.rmd
finalized

@@
   results %>%
-  .[, .(pi_diff = median(pi_diff)),
-    by = c("field_col", "pLabel", "type")
+    .[, .(pi_diff = median(pi_diff),
+          pi_diff_est = median(pi_diff_est),
+          bias = median(bias)),
+      by = c("field_col", "pLabel", "model")
     ] 
@@
 
-**Abstract**: Geographically weighted regression (GWR) has been presented as a valuable tool for the estimation of site-specific yield response functions used to derive site-specific input rate recommendations from data generated by on-farm precision experimentation (OFPE).
-But most of the applications of GWR in this context have assumed a quadratic yield response function, despite a scientific consensus that the yield-input relationships modeled are better represented by the quadratic-plateau functional form.
-The key objective of this paper is to investigate whether, when the true functional form of yield response is quadratic-plateau, assuming a quadratic form introduces bias into the GWR estimation of the economic value of site-specific recommendation maps.
-We consider two sets of functional-form specifications used by recently published studies of site-specific input management that apply GWR to data from OFPE.
-We show that both GWR approaches suffer significant positive bias, which can lead to large overestimation of the economic value of applying GWR methods.
-We conclude that in many circumstances the information gleaned from using GWR may be far less valuable than has been claimed.
+**Abstract**: Geographically weighted regression (GWR) has been presented as a valuable tool for the estimation of site-specific yield response functions to derive variable rate input recommendations.
+This study uses Monte Carlo simulations to demonstrate that, when GWR's yield response functional form is mis-specified as quadratic while the true yield-input relationship is quadratic-plateau, using GWR can lead to large overestimation of the economic value of variable rate application of input rates compared to its actual value.
 We encourage the statistical community to develop tools in software packages providing GWR that allow more flexibility in functional form assumptions.
@@
 Recently, on-farm precision experimentation (OFPE) has emerged as a popular method among agricultural researchers and practitioners.
-It provides a cost-effective way to gather high-resolution data on yields and input trials, which is crucial for informing site-specific crop input management [@bullock2019data; @lacoste2021farm for reference].
+It provides a cost-effective way to gather high-resolution data on yields and input trials, which is crucial for informing site-specific crop input management [@bullock2019data; @lacoste2021farm].
 One of the enduring research goal in this domain is the estimation of the value of variable rate application (VRA) of inputs like fertilizer and seeds compared to traditional uniform rate application (URA).
@@
 The first approach integrates soil sampling and/or field characteristic data (such as topography) into OFPE data (yield, input) to estimate site-specific yield response functions.
-In this approach, interacations of inputs and soil/field characteristics are explicilty modeled.
+In this approach, interactions of inputs and soil/field characteristics are explicitly modeled.
 One can then plug in site-specific soil/field characteristics to the estimated model to represent site-specific yield response functions.
@@
 Ideally, the GWR model should be specified with quadratic-plateau or more flexible functional forms.
-However, no software package is readily usable to estimate GWR with quadratic-plateau fucntional form.
+However, no software package is readily usable to estimate GWR with quadratic-plateau functional form.
 Second, GWR itself has faced criticism regarding the statistical reliability of its coefficient estimations [@griffith2008spatial; @harris2019simulation; @paez2011simulation; @da2016multiple].
@@
 
-The primary objective of this study is to examine the degree and direction of bias in the estimation of the economic value of GWR-based variable nitrogen rate recommendations in corn production, especially when the yield response to nitrogen is incorrectly specified as quadratic in the GWR model instead of the correct quadratic-plateau function.
+The primary objective of this study is to examine the degree and direction of bias in the evaluation of the economic value of GWR-based variable nitrogen rate recommendations in corn production, especially when the yield response to nitrogen is incorrectly specified as quadratic in the GWR model instead of the correct quadratic-plateau function.
 We will employ Monte Carlo simulations, which allow us to accurately define and know the true yield response function within our data-generating process, providing a means to quantify the degree of bias present.
@@
 Instead, we seek to assess the economic repercussions^[Note that while the environmental consequences of fertilizer management carry significant societal importance, they fall outside the purview of this study.
-Herein, "economically optimal" pertains strictly to the maximization of private production profitability for farmers and does not imply "socially optimal."] stemming from functional form mis-specifcatin combined with statistical inaccuracies in the coefficient estimation of the model.
+Herein, "economically optimal" pertains strictly to the maximization of private production profitability for farmers and does not imply "socially optimal."] stemming from functional form mis-specification combined with statistical inaccuracies in the coefficient estimation of the model.
 We found that a mis-specified GWR model tends to result in substantial overestimation of the economic value of GWR-based VRA over URA.
@@
 The process and components of the simulation analysis are detailed below.
-Our simulations are run using R [@R], and all the R programs are publicly accessible at the following GitHub direcotry: https://github.com/tmieno2/GWR_value.
+Our simulations are run using R [@R], and all the R programs are publicly accessible at the following GitHub directory: https://github.com/tmieno2/GWR_value.
 
@@
 
-A 6 $\times$ 6 Latin square trial design was utilized in each simulated on-farm experiment.
-The field was partitioned into a 4-block $\times$ 2-block grid (see Figure A1 of Appendix II), in which each block was partitioned into a 6-plot $\times$ 6-plot grid with each of six N rates assigned to exactly one plot in each row and each column of the block (i.e., a Latin square).
-The Latin square has a special pattern  [@li2023trial] to ensure that no adjacent N plots were assigned the same N rate, and furthermore, the order of N rates in each row of every block was specified to avoid relatively large changes in N rates (due to the technological limitations of N application equipment commonly witnessed in real-world OFPE).
+In each simulated on-farm experiment, the field was partitioned into a 4-block $\times$ 2-block grid (see Figure A1 of Appendix II), in which each block was partitioned into a 6-plot $\times$ 6-plot grid with each of six N rates assigned to exactly one plot in each row and each column of the block (i.e., a Latin square).
+The Latin square implemented here has a special pattern  [@li2023economic] to ensure that no adjacent N plots were assigned the same N rate, and furthermore, the order of N rates in each row of every block was specified to avoid relatively large changes in N rates (due to the technological limitations of N application equipment commonly witnessed in real-world OFPE).
 
@@
 Figure \@ref(fig:why-bias-many) illustrates how overestimation of the value of VRA can occur.
-It shows yield response functions estimated by GWRT and the estimated yields associated with the GWR-based EONR rates and SCAM-based EONR rates for 50 randomly chosen cells in a single round of simulation.
+It shows quadratic yield response functions estimated by GWRT and the estimated yields associated with the GWR-based EONR rates and SCAM-based EONR rates for 50 randomly chosen cells in a single round of simulation.
 Since GWR-based EONRs were obtained assuming the yield response functions estimated by GWR, by construction they out-perform the SCAM-based estimates in every cell.
@@
 Whatever the underlying statistical methods for yield response functions may be, researchers are likely to overestimate the true value of their methods.
-It would be an interesting future research to investigate the bias in other commonly used statistical methods in the literature on site-specific yield response estimation (such as regression with interaction terms of field characteristics, machine learning, and more) by using a similar simulation-based evaluation approach as done in this study.
+In the future, it would be interesting to investigate the bias in other commonly used statistical methods in the literature on site-specific yield response estimation (such as regression with interaction terms of field characteristics, machine learning, and more) by using a similar simulation-based evaluation approach as done in this study.
 

### 2023-11-16 Writing/supplementary_appendix.rmd
finalized

@@
 Estimates of site-specific yield response functions can then be obtained by inserting the value of the site's characteristic variables into the estimate of the field-specific response function: $\hat{f}_i(\textbf{x}) \equiv \hat{f}(\textbf{x},\textbf{c}_i)$.
-Alternatively, a site-specific yield response function might be estimated simply by taking (input rate, yield) data from points around a site of interest $i$, and regressing yield on input application rates to attain the estimate $\hat{f}_i (\textbf{x})$.
+Alternatively, a site-specific yield response function might be estimated simply by giving greater weights to the points around a site of interest, and regressing yield on input application rates to attain the estimate $\hat{f}_i (\textbf{x})$.
 Stated roughly, using GWR takes the latter approach, which has the advantage of not needing a costly map of field characteristics values.
@@
 
-```{r fig.id = "field-N-design", fig.cap = "Experiment design of nitrogen (N) rates", out.width = "6in", fig.width = 7}
+```{r fig.id = "field-N-design", fig.cap = "Experiment design of nitrogen (N) rates.
+Note: The experimental field contains a total of 288 N trial plots, arranged in 24 rows $\times$ 12 columns.
+Each N plot contains 5 effective yield subplots (as illustrated in Figure A1, Panel b), and the total number of subplots is 1,440.
+The total number of effective cells are 8,640 (72 rows $\times$ 120 columns)", out.width = "6in", fig.width = 7}
 knitr::include_graphics(here::here("GitControlled/Writing/Figures/g_exp.png"))
